### 2016-05-30 finalPaper.tex
added the draft

%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[british,aps,superscriptaddress,nofootinbib,times]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=2cm}
\setcounter{secnumdepth}{3}
\usepackage{verbatim}
\usepackage{refstyle}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{esint}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
\AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
\RS@ifundefined{subref}
  {\def\RSsubtxt{section~}\newref{sub}{name = \RSsubtxt}}
  {}
\RS@ifundefined{thmref}
  {\def\RSthmtxt{theorem~}\newref{thm}{name = \RSthmtxt}}
  {}
\RS@ifundefined{lemref}
  {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
  {}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
  \theoremstyle{definition}
  \newtheorem{defn}[thm]{\protect\definitionname}
  \theoremstyle{remark}
  \newtheorem{rem}[thm]{\protect\remarkname}
  \theoremstyle{plain}
  \newtheorem*{prop*}{\protect\propositionname}
  \theoremstyle{plain}
  \newtheorem{lem}[thm]{\protect\lemmaname}
  \theoremstyle{plain}
  \newtheorem{prop}[thm]{\protect\propositionname}
  \theoremstyle{definition}
  \newtheorem{example}[thm]{\protect\examplename}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{xcolor}
%\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\makeatother

\usepackage{babel}
  \providecommand{\definitionname}{Definition}
  \providecommand{\examplename}{Example}
  \providecommand{\lemmaname}{Lemma}
  \providecommand{\propositionname}{Proposition}
  \providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}

\begin{document}

\title{An alternative to contextuality}

\author{Atul Singh Arora}

\email{ms11003@iisermohali.ac.in}

\selectlanguage{british}%

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}

\author{Arvind}

\email{arvind@iisermohali.ac.in}

\selectlanguage{british}%

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\begin{abstract}
We reconsider the no-go theorems on hidden variables and conclude
that the notion of contextuality is not a necessary feature of quantum
mechanics. We provide an alternative view, motivated by consistency
requirements between Bohmian Mechanics and the said theorems. This
is accomplished by identifying a new classical property, we call `multiplicativity'.
We propose a non-contextual hidden variable model, consistent with
all predictions of QM (for discrete spaces). Advantages of this view
are illuminated by discussion of implications of non-multiplicativity
to non-locality and its relation to contextuality.
\end{abstract}
\maketitle

\section{Introduction}

Background: Since Einstein's \cite{EinsteinEPR} work on completeness
of quantum mechanics and the subsequent seminal work of Bell, assessing
compatibility of hidden variable models has proven to be repeatedly
useful. It has had foundational implications, for instance it gave
a precise meaning to locality, and engendered pragmatic advantages,
such as security, randomness certification etc. While Bell showed
that local hidden variable models can not describe nature, the Kochen
Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
ruled out an even larger class of hidden variable models. The notion
of contextuality was identified which also, in recent times has been
harnessed for computation and cryptography. Not all hidden variable
models were, however, proved to be incompatible. Bohm's work \cite{Bohm1,Bohm2}
is one such (in)famous example. This approach has allowed for a precise
interpretation of quantum mechanics.

Previous work {[}the essentials I have already discussed{]}: In this
paper, we take a closer look at the aforesaid no-go theorems and find
that contextuality is in fact not a necessary feature of quantum mechanics.
This has been shown \cite{NoContextuality} by taking disturbances
due to measurements into consideration. Here, however, we construct
a significantly simpler toy model for illustrating not only the aforesaid
but to also delineate a complete alternative to contextuality. The
toy model is a specific case of what we call a c-ingle variable theory.
Its predictions match with those of quantum mechanics for systems
described by arbitrary (discrete) Hilbert spaces.

Triangle: <TODO: ask arvind sir>

Work and results: <summarise what is done in each section>

\section{Context}

The notation used henceforth has been defined below.

\begin{defn}
Notation: (a) $\psi\in\mathcal{H}$ would typically represent the
quantum mechanical state of the system (assumed pure), residing in
the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined
to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$, (c) $[\mathcal{H}]$
is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which
represents the state of the system including hidden variables, (d)
$[\psi]\in[\mathcal{H}]$ will represent the state of the system,
including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$,
(f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$,
(g) the set of all experimental setups is denoted by $\mathcal{E}$,
(h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$.
\end{defn}
In addition to the notation, we use the following definition of non-contextuality.
\begin{defn}
A theory is non-contextual, if it provides a map $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$
to explain measurement outcomes. A theory which is not non-contextual
is contextual.\end{defn}
\begin{rem}
Prediction maps are non-contextual.
\end{rem}
In the literature broader definitions have been suggested which declare
a larger set of theories as non-contextual. For our purposes however,
this restricted definition will suffice. The term contextual is used
to suggest that the value an operator takes might depend on which
other compatible observable it is measured with. Since quantum mechanics
(QM) yields deterministic results only in specific situations, it
is imperative to analyse the meaning of contextuality by `completing'
QM. Hidden variable theories do precisely this and we have at our
disposal the heretic theory of Bohm. Circumventing the details of
the theory, we note its salient feature; with each particle, one associates
precisely defined $(q,p)$ and a wavefunction $\psi$. Consequently,
the outcomes of all experiment are predictable, granted the initial
conditions of the system and the apparatus are known (the `hidden
variables'). The essence of Bohmian Mechanics relevant here can be
captured by the following theorem.
\begin{thm}
$\exists$ a (Bohmian) map $m_{B}:\hat{\mathcal{H}},[\mathcal{H}],\mathcal{E}\to\mathbb{R}$,
and a sequence map $s$, s.t. if $m_{B}$ \& $s$ are assumed to describe
the outcomes of measurements \& the resultant state respectively,
then they are consistent with all predictions of QM.
\end{thm}
Observe that given a Stern-Gerlach setup and the initial conditions
(position \& wavefunction of the particle), according to the theorem,
Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$)
of the particle. Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$
and that the measurement outcome was spin up. Interestingly, it can
be shown \cite{Detlef} that if the direction of the magnetic field
gradient is flipped while everything else is unchanged, the measurement
outcome will now be spin down. This emphasises the fact that $m_{B}$
is not a prediction map. More importantly it entails that $m_{B}$
is contextual. It must be stressed, however, that the contextuality
in this case is not a statement about the context in terms of compatible
observables. Here no two observables are compatible (excluding identity).

\section{Non-Multiplicativity: An alternative to Contextuality}

One can show \cite{KochenSpecker} that under reasonable assumptions,
no non-contextual theory can explain all predictions of QM. We re-state
these results and show that nowhere does contextuality appear to be
a logical necessity. Instead we note that non-contextual theories
with certain properties, we call \emph{multiplicativity} are incompatible
with QM. Viewed from this perspective, non-\emph{multiplicativity}
is the non-classical alternative to contextuality in QM. Precise definitions
of this and a related property \emph{sequential multiplicativity},
are given below. 
\begin{defn}
A prediction map $m$ is \emph{multiplicative }iff 
\[
m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])=f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
\]
where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
observables, $f:\hat{\mathcal{H}}^{\otimes N}\to\mathcal{\hat{H}}$
and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is
one that is not multiplicative.
\end{defn}
Note that if $m$ is taken to represent the measurement outcome (in
QM), then for states of the system which are simultaneous eigenkets
of $\hat{B}_{i}$s, $m$ must clearly be multiplicative. It is, however,
not obvious that this property must always hold. To motivate this,
consider the state $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$,
we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
independently, according to QM, with probability half. Contrary to
this, from a quick computation, it is clear that if one first measures
$\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
product of the results must be $-1$. This is consistent with measuring
$\hat{C}$. To capture this property we define \emph{sequential multiplicativity}
as follows.
\begin{defn}
A prediction map $m$ is \emph{sequentially multiplicative }for a
given sequence map $s$, iff 
\[
m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
\]
where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)+\text{ permutations, making }N!\text{ terms}\}$,
$\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
observables, $[\psi_{i}]\in[\mathcal{H}]$, $f:\hat{\mathcal{H}}^{\otimes N}\to\mathcal{\hat{H}}$
and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
$\forall\,[\psi_{1}]$.
\end{defn}
We now discuss the `proofs of contextuality' in the purview of the
aforesaid.
\begin{thm}
Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
for any arbitrary function $f$, where $\hat{A}_{i}$ are arbitrary
Hermitian operators. If $m$ is assumed to describe the outcomes of
measurements, then no $m$ exists which is consistent with all predictions
of Quantum Mechanics.\end{thm}
\begin{proof}
Bell construction ($\left|\mathcal{H}\right|\ge4$): Consider an operator
$\hat{B}:=a_{1}\otimes b_{1}+a_{2}\otimes b_{1}+a_{1}\otimes b_{2}-a_{2}\otimes b_{2}$
s.t. $-1\le\hat{a}_{i},\hat{b}_{j}\le1$ $\forall\,i,j\in\{1,2,3,4\}$
(which means that the spectrum of $\hat{a}$ and $\hat{b}$ are bounded
above and below). If we assume that a map $m$ of the aforesaid type
exists, then it can be shown that $\left\langle \hat{B}\right\rangle \le2$.
To see this, consider $\hat{A}_{1}=\hat{a}_{1}\otimes\hat{\mathbb{I}}$
and $\hat{A}_{2}=\hat{\mathbb{I}}\otimes\hat{b}_{1}$, so that if
$\hat{C}:=\hat{A}_{1}\hat{A}_{2}$ then property (2) entails that
$m(\hat{C})=m(\hat{A}_{1})m(\hat{A}_{2})$, viz. $m(\hat{a}_{1}\otimes\hat{b}_{1})=m(\hat{a}_{1}\otimes\hat{\mathbb{I}})m(\hat{\mathbb{I}}\otimes\hat{b}_{1})$.
Note that $m(\hat{*})$, may depend on the state $\left|\psi\right\rangle $
and the hidden variables%
\begin{comment}
, where $\hat{*}$ is taken to represent $\hat{B}_{k}$s which can
be generalised to all $\hat{a}_{i}$s and $\hat{b}_{j}$s
\end{comment}
. Therefore, we average over multiple measurements, which corresponds
to averaging over the hidden variables. This is expressed by $\left\langle m(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
One can repeat this argument for each term in $\left\langle \hat{B}\right\rangle $.
Using the fact that $-1\le m(\hat{*})\le1$, and that the extrema
will occur only at the extreme values of $m$, one can plugin $\pm1$
for each $\left\langle m(\hat{*})\right\rangle $ to obtain $\left\langle \hat{B}\right\rangle \le2$.
Quantum mechanically, one can show that $\left\langle \hat{B}\right\rangle =2\sqrt{2}$
for the state $\left|\psi\right\rangle =\left(\left|+-\right\rangle -\left|-+\right\rangle \right)/\sqrt{2}$,
where $\hat{\sigma}_{x}\left|\pm\right\rangle =\pm\left|\pm\right\rangle $,
and $\hat{\sigma}_{x,y,z}$ are the Pauli matrices, given in the z-basis
as 
\[
\hat{\sigma}_{x}\doteq\left[\begin{array}{cc}
0 & 1\\
1 & 0
\end{array}\right],\,\hat{\sigma}_{y}\doteq\left[\begin{array}{cc}
0 & -i\\
i & 0
\end{array}\right],\,\hat{\sigma}_{z}\doteq\left[\begin{array}{cc}
1 & 0\\
0 & -1
\end{array}\right].
\]
The observables are $\hat{a}_{1}=\hat{\sigma}_{z}$ and $\hat{a}_{2}=\hat{\sigma}_{x}$,
while $\hat{b}_{1}=-\frac{\hat{\sigma}_{z}+\hat{\sigma}_{x}}{\sqrt{2}}$
and $\hat{b}_{2}=\frac{\hat{\sigma}_{z}-\hat{\sigma}_{x}}{\sqrt{2}}$.
Since quantum mechanics violates the inequality, $\left\langle \hat{B}\right\rangle \le2$,
we conclude that the map $m$ can not simultaneously exist and be
consistent with QM.
\end{proof}

\begin{proof}
GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider three
observers with one particle each. Each observer can measure two properties,
call them X and Y, with outcomes $\pm1$. The associated operators
are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$. The state of the
system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $
and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$,
$\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
A measurement of $\hat{A}$ would correspond to measurement of property
$X,\,Y$ and $Y$ by the three observers respectively. For a map $m$
consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
Property (b) of the map $\implies1=m(\hat{A}\hat{B}\hat{C})=m(\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\hat{\sigma}_{x}\hat{\sigma}_{y}\otimes\hat{\sigma}_{x})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{y}^{(2)}\hat{\sigma}_{x}^{(2)}\hat{\sigma}_{y}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{x}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{D}\equiv\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}),$
where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$
and so on. It must be stressed that although $\hat{A}$, $\hat{B}$
and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$
do not. We used property (b) over both these sets of operators in
the previous step. Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $,
$\implies m(\hat{D})=-1$ which yields a contradiction. We therefore
conclude that no $m$ with the said properties exists which is consistent
with all predictions of QM.
\end{proof}
Here $m$ maybe viewed as a specific class of prediction maps, that
implicitly depends on the state $[\psi]$. It follows then that the
maps ruled out by the theorem are non-contextual. The set of maps
ruled out, however, can be enlarged by imposing fewer restrictions
on it. This is achieved by the following theorem.
\begin{thm}
Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
(b) $m(f(\hat{B}_{1},\hat{B}_{2},\dots))=f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$,
for any arbitrary function $f$, where $\hat{B}_{i}$ are mutually
commuting Hermitian operators. If $m$ is assumed to describe the
outcomes of measurements, then no $m$ exists which is consistent
with all predictions of Quantum Mechanics.\label{thm:KS}\end{thm}
\begin{proof}
Bell construction ($\left|\mathcal{H}\right|\ge4$): The same proof
as the one presented earlier goes through here also since $[A_{1},A_{2}]=0$.
\end{proof}

\begin{proof}
Generalized GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider
again, three observers with one quantum particle each. Each observer
can measure the properties corresponding to $\hat{\sigma}_{x}$ and
$\hat{\sigma}_{y}$ of his/her particle. The quantum state of these
particles is also the same as before, $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $.
We define as earlier $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$
$\implies\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
Consider in addition the following operators, represented by $\hat{H}_{ij}$.
\[
\hat{H}_{ij}\doteq\left[\begin{array}{ccc}
\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}^{(a)} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y}\otimes\hat{\mathbb{I}}^{(2)} & \mathbb{\hat{I}}\otimes\mathbb{\hat{I}}\otimes\hat{\sigma}_{y}^{(3)}\\
\hat{\sigma}_{y}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(1)} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}^{(b)} & \mathbb{\hat{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{y}^{(3)}\\
\hat{\sigma}_{y}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(1)} & \mathbb{\hat{I}}\otimes\hat{\sigma}_{y}\otimes\hat{\mathbb{I}}^{(2)} & \mathbb{\hat{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{x}^{(c)}\\
\hat{\sigma}_{x}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(a)} & \mathbb{\hat{I}}\otimes\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}^{(b)} & \hat{\mathbb{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{x}^{(c)}
\end{array}\right],
\]
where from property (b) it follows that $m(\hat{A})=m(\hat{H}_{11})m(\hat{H}_{12})m(\hat{H}_{13})$.
Note that $[\hat{H}_{ij},\hat{H}_{ik}]=0$, viz. the operators along
a row commute. To be consistent with QM, $m(\hat{A})=+1$ (similarly
for row 2 and 3). $m(\hat{D})=-1$ imposes that the product $m(\hat{H}_{41})m(\hat{H}_{42})m(\hat{H}_{43})$,
row 4, must be $-1$. Using the notation $m(\hat{H}_{ij})=H_{ij}$,
we can start with the first case. For the last row to yield $-1$,
we must have either one $-1$ assignments or three $-1$ assignments.
Let us look at the first case. Without loss of generality, we can
assume that $H_{41}=H_{42}=+1$ and $H_{43}=-1$. Further, $H_{11}=H_{41}$,
$H_{22}=H_{42}$ and $H_{33}=H_{43}$ by construction (see below).
\[
H_{ij}\doteq\left[\begin{array}{ccc}
1\\
 & 1\\
 &  & -1\\
1 & 1 & -1
\end{array}\right],H_{ij}\doteq\left[\begin{array}{ccc}
1 & \pm1 & \pm1\\
\pm1 & 1 & \pm1\\
\pm1 & \pm1 & -1\\
1 & 1 & -1
\end{array}\right].
\]
Next, one must ensure that the first row yields $+1$ which requires
us to either set $H_{12}=H_{13}$ to $-1$ or $+1$. Let us write
this as $H_{12}=H_{13}=\pm1$ which would entail that $H_{23}=\pm1$
and $H_{32}=\pm1$. {[} Note that the notation implies that when we
choose $+1$, all these are $+1$ and when we choose $-1$, all are
$-1$. We are not allowed to set, say $H_{12}=-1$ and $H_{13}=+1$.
{]} For the second row to be $+1$, we conclude that $H_{21}=\pm1$.
This entails, in turn, that $H_{31}=\pm1$. We now note that the third
row has become $-1$ whereas according to QM, it must be $+1$. It
is left upto the reader to see that similar reasoning also yields
results in inconsistencies with QM. This completes the proof.
\end{proof}

The following proof is not only more general, but also independent
of the initial state of the system.
\begin{proof}
Peres Mermin ($\left|\mathcal{H}\right|\ge4$):

Consider the following set of operators 
\[
\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\mathbb{I}} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
\end{array}\right]
\]
which have the property that all operators along a row (and along
a column) commute. It is trivial to see that this holds for the first
two rows and the first two columns. To see that this holds also for
the last row and column, note the anti-commutation relation, $\{\hat{\sigma}_{x},\hat{\sigma}_{y}\}=0$
and that $\sigma_{z}=i\sigma_{y}\sigma_{x}$, which one may check
explicitly. Another property is that the product of rows (columns)
yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. This can be verified easily
by using the aforesaid relations and the fact that $\sigma^{2}=1$,
for every Pauli matrix. Using this property of $\hat{R}_{i}$ and
$\hat{C}_{j}$, it is easy to show that no map $m$ with the stated
properties can exist. Let us assume on the contrary that $m$ exists.
From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (used property
(a)), we must have an odd number of $-1$ assignments in the third
column. In the remaining columns, the number of $-1$ assignments
must be even for each column. Thus, in the entire square, the number
of $-1$ assignments must be odd. Let us use the same reasoning, but
along the rows. Since each $m(\hat{R}_{i})=1$, we must have even
number of $-1$ assignments along each row. Thus, in the entire square,
the number of $-1$ assignments must be even. We have arrived at a
contradiction and therefore we conclude that our assumption that a
consistent $m$ exists, must be wrong.
\end{proof}

\begin{proof}
Kochen Specker ($\left|\mathcal{H}\right|\ge3$): The original proof
given by \cite{KochenSpecker} is rather involved. Here we will satisfy
ourselves with assuming its validity and applying our constructions
to the aforesaid proof(s).
\end{proof}

\begin{rem}
One could in principle assume $m$, to be s.t. (a) $m(\hat{\mathbb{I}})=1$,
(b) $m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for $\alpha\in\mathbb{R}$,
(c) $m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d) $m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
to deduce (d') $m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
and that $m(\hat{B}_{i})\in$ spectrum of $\hat{B}_{i}$. Effectively
then, condition (b) listed in the theorem is satisfied as a consequence.
Therefore, assuming (a)-(d) as listed here, rules out a larger class
of $m$.
\end{rem}
According to \thmref{KS}, non-contextual maps which are \emph{multiplicative}
must be incompatible with QM. It is apparent that non-contextual maps
which are non-\emph{multiplicative} might be consistent with QM. To
that end, in the following section we first show that this is indeed
the case by removing contextuality from Bohmian Mechanics and supplement
it thereafter by an explicit construction.

Before proceeding we note, however, that QM enforces \emph{sequential
multiplicativity} at least in certain cases. This result will be used
to assess accuracy of any hidden variable model we might propose.
\begin{prop*}
Let the system be in a state, s.t. measurement of $\hat{C}$ yields
repeatable results (same result each time). Then according to QM,
\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
and $\hat{B}_{i}$ are as defined. \end{prop*}
\begin{proof}
Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
are mutually compatible (commuting) and complete set of operators.
If say for instance the set is not complete, then one can add the
missing operators and label them as aforesaid. It follows that $\exists$
$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
Let the state of the system be given by $\left|\psi\right\rangle $
and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
by assumption. For the statement to follow, one need only show that
$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
which satisfy $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
This is the crucial step. Proving this is so is trivial. We start
with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
and take its inner product with $\left\langle \mathbf{b}\right|$
to get 
\begin{eqnarray*}
\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
\end{eqnarray*}
Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then
we can conclude that indeed $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
the required relation. That completes the proof.
\end{proof}
It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
must always hold.

\subsection{Non-contextual Bohmain Mechanics}

Recall that contextuality in Bohmian Mechanics arises from the mapping
between an operator and the experimental setup. Consider the following
proposition.
\begin{lem}
For discrete $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$.\end{lem}
\begin{proof}
To describe an experimental setup corresponding to a measurement,
we use a measuring particle (mass $m_{L}$, say). It is made to interact
with the system for a short duration appropriately and subsequently
we measure the resultant position of the particle, to learn about
the value of the observable of interest. Say for instance, we wish
to measure the observable $\hat{L}$, then the required interaction
Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
Here the first operator acts on the system and second (after the tensor
product symbol) acts on the measuring particle. $a$ quantifies the
interaction strength. {[}TODO: check this{]} It has dimensions of
frequency, if $L$ has dimensions of length. Let us assume that the
system in the state $\left|\psi\right\rangle $. Then it is known
that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $,
where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with
eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but
its removal doesn't cause any significant difficulty). $\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $,
where 
\[
\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
\]
 and $\left|\varphi\right\rangle $ is the state of the measuring
particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
If $t$ is very small, and $a$ very large, s.t. $at=\lambda$ is
a finite number, then one can neglect the free evolution, $\nabla^{2}t$
terms compared to $\hat{H}_{\text{int}}t$. We then have 
\begin{eqnarray*}
\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
 & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
 & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
\end{eqnarray*}
where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
This interaction, effectively entangles the measuring particle, with
the possible `outcomes', eigenstates of the observable $\hat{L}$
of interest. If $\sigma\ll\lambda l$, then according to QM itself,
a position measurement of the measuring particle, would correspond,
in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to
which the system will collapse. Therefore, given an observable, one
can construct the aforesaid experiment to measure its value. We have,
in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
\end{proof}
The proof of this proposition can also be motivated by a simple construction.
Consider that the system of interest are spin half particles. To measure
spin along any direction, there are two directions along which the
magnetic field gradient can be set (as was discussed in the introduction).
The experimentalist agrees to always use a specific direction, thereby
mapping an operator to an experimental setup uniquely. Given this,
one can immediately derive a consistent non-multiplicative prediction
map $m$.
\begin{prop}
The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$,
we call `Bohmian prediction map'.\end{prop}
\begin{proof}
$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.\end{proof}
\begin{prop}
The Bohmian prediction map, $m$ must be non-multiplicative.\end{prop}
\begin{proof}
Since Bohmian Mechanics is consistent with all predictions of QM,
the Bohmian prediction map $m$ must also be. According to \thmref{KS},
$m$ must be non-multiplicative.
\end{proof}

\subsection{C-ingle model | An Explicit Construction}

For readers skeptic about Bohmian Mechanics, the discussion related
to it can be replaced by the following. Let the state of the system
be $\left|\chi\right\rangle $, defined on a discrete Hilbert space
(spin like) and we wish to assign a value to an arbitrary operator
$\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which
has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
This model has the following postulates: \\
1. Initial Hidden Variable: Pick a $c\in[0,1]$, from a uniform random
distribution.\\
2. Assignment/Prediction: The value assigned to $\hat{A}$ is given
by finding the smallest $a$ s.t. 
\[
c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle a'|\chi\right\rangle \right|^{2},
\]
viz. we have specified a prediction map, $m(\hat{A})=a$.\\
3. Update: After measuring an operator, the state must be updated
(collapsed) in accordance with the rules of QM. This completely specifies
the sequence map $s$.

To see how this works, we restrict ourselves to a single spin case.
Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $,
and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
Now, according to the postulates of this theory, $m(\hat{A})=+1$,
if $c\le\cos^{2}\theta$, else $\hat{A}$ will be assigned $-1$.
It follows then, from $c$ being uniformly random in $[0,1]$, that
the statistics agree with predictions of QM. The reader can convince
him(her)self that the said scheme works in general. A more interesting
application of this to the PM situation follows.

We can clearly see that the assignment, described by the prediction
map $m$, is non-contextual since given an operator and a state (+
the hidden variable), the value is uniquely assigned. The map $m$
is non-multiplicative which will be clarified by the following.
\begin{example}
{[}C-ingle model applied to the Peres Mermin situation{]} We apply
the C-ingle model to the Peres Mermin situation discussed earlier.
\begin{comment}
We construct a simplified hidden variable model for the Peres Mermin
situation (TODO: Add as a test of contextuality?) and explicitly show
that the associated prediction map $m$ is non-multiplicative. We
subsequently show that this model is a special case of the C-ingle
model. 
\end{comment}
{} For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
Say from a uniform random distribution we obtained $c=0.4$. To arrive
at the assignments, note that $\left|00\right\rangle $ is an eigenket
of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
Thus, in the first iteration, all these should be assigned their respective
eigenvalues. The remaining operators must be assigned $-1$ as one
can readily verify by explicitly finding the smallest $a$ as described
in postulate 2 of the model (see \eqref{toyModel}). Two remarks are
in order. First, this model is manifestly \emph{non-multiplicative},
for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
where the subscript has been introduced to index the iteration. More
precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$
where the complete state $\left[\left|\psi_{1}\right\rangle \right]$
implicitly refers to both the quantum state $\left|00\right\rangle $
and the hidden variable $c=0.4$. Second, we must impose \emph{sequential
multiplicativity} as a consistency check of the model, which in particular
entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$,
$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are
obtained from postulate 3. Note that for each iteration, a new hidden
variable is generated. To illustrate \emph{sequential multiplicativity},
we must choose to measure $\hat{A}_{33}$. According to step 4, since
$\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the
final state remains $\left|00\right\rangle $. 
\end{example}
\begin{equation}
\begin{array}{c|ccc}
\text{Iteration} & i=1 & i=2 & i=3\\
\left|\psi_{\text{init}}\right\rangle  & \left|00\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}\\
\text{HV/Toss} & c=0.4 & c=0.1 & c=0.7\\
\\
\text{Predictions} & m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-1 & -1 & -1\\
-1 & -1 & -1\\
-1 & -1 & +1
\end{array}\right] & m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-1 & -1 & -1\\
-1 & -1 & -1\\
-1 & -1 & +1
\end{array}\right] & m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+1 & +1 & +1\\
+1 & +1 & -1\\
+1 & +1 & +1
\end{array}\right]\\
\text{(Assignments)}\\
 & m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) & m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) & m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
 & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
\text{Operator}\\
\text{Measured} & \hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1 & \quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad & \hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
\\
\left|\psi_{\text{final}}\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}} & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}
\end{array}\label{eq:toyModel}
\end{equation}
For the next iteration, $i=2$, viz. after the first measurement has
been performed, say the random number generator yielded $c=0.1$.
Since $\left|\psi\right\rangle $ is also unchanged the assignment
remains invariant (in fact any of $c<0.5$ would yield the same result),
which should be evident from the previous exercise. For the final
step we choose to measure $\hat{p}=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
to proceed with sequentially measuring $\hat{C}_{3}$. To simplify
calculations, we note 
\[
\left|00\right\rangle =\frac{(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle )/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle +\left|\tilde{-}\tilde{-}\right\rangle )/\sqrt{2}}{\sqrt{2}},
\]
where $\left|\tilde{\pm}\right\rangle =\left|0\right\rangle \pm i\left|1\right\rangle $
(eigenkets of $\hat{\sigma}_{y}$). Since $\left|00\right\rangle $
is manifestly not an eigenket of $\hat{p}$, we must find an appropriate
eigenket $\left|p_{-}\right\rangle $ s.t. $\hat{p}\left|p_{-}\right\rangle =-\left|p_{-}\right\rangle $,
since $c=0.1$ and $\left\langle p_{-}|00\right\rangle $ is already
$>0.1$. It is immediate that $\left|p_{-}\right\rangle =\left(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle \right)/\sqrt{2}=\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
which becomes the final state. \\
For the final iteration, $i=3$, say we obtain $c=0.7$. So far, we
have $m_{1}(\hat{A}_{33})=1$ and $m_{2}(\hat{A}_{23})=-1$. We must
obtain $m_{3}(\hat{A}_{13})=1$, independent of the value of $c$,
to be consistent. Let's check that. Indeed, according to postulate
2, since $\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}=1\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
$m_{3}(\hat{A}_{13})=1$ for all allowed values of $c$. As a remark,
it maybe emphasised that the $m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$
and $m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which essentially
expresses compatibility of these observables, viz. measurement of
$\hat{A}_{13}$ doesn't affect the result one would obtain by measuring
operators compatible to it (granted they have been measured once before).

\section{Implications}

\subsection{Locality}

\begin{defn}
A theory/model/map is \emph{local} iff two spatially distinct points
can not be influenced instantaneously.
\end{defn}

\begin{prop}
A prediction map $m$ consistent with QM must be non-local.\end{prop}
\begin{proof}
{[}Bell's{]} Formally it is clear, since a violation of Bell's inequality
implies non-locality. Consequently, any consistent completion of QM,
will be non-local. More insight can be gained, although some care
is needed. The notion of compatible observables is that commuting
observables don't disturb each other and can be simultaneously known.
While the statement is not precisely stated, we only need to note
that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$,
for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$
are defined as before. In words, this means that to measure $\hat{C}$,
one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
A multiplication of the values obtained, can be taken to be the value
a measurement of $\hat{C}$ yields. This can be verified by measuring
$\hat{C}$ subsequently. The Bell scenario offers an interesting freedom,
by restricting the form of $\hat{B}_{i}$. To evaluate $\left\langle \hat{B}\right\rangle $,
one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
From the compatibility argument, we need to find the average value
of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$,
viz. $\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
So far, the statements were general. Now we assume that our theory
is non-multiplicative (and non-contextual). A consistent theory (with
QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
However, if the particles are taken far away, then the only way the
theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$
for example), is if the theory is non-local. Locality will entail
that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since
the information about which observable was measured first, can't be
propagated instantaneously. We see therefore that non-locality arises
quite naturally in consistent non-multiplicative theories.
\end{proof}

\begin{prop}
{[}can perhaps be skipped{]} Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$,
corresponding to two particles. $\mathcal{H}_{A}$ and $\mathcal{H}_{B}$
are discrete (correspond to spins say). Let mutually commuting observables
$\hat{B}_{i}$ be s.t. $\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$
or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where
$A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$
are arbitrary observables. If locality is assumed, then a prediction
map $m$ and it's associated sequence map $s$ must be s.t. over these
observables, sequential multiplicativity and multiplicativity become
identical.
\end{prop}

\subsection{Apparent Contextuality}

We have already constructed an explicit non-contextual model, which
is consistent with QM. This model we knew had to be non-multiplicative.
We will see how non-multiplicativity gives rise to what one might
confuse to mean contextuality. Imagine 
\[
\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|-\left[\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|\right],
\]
\[
\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|-\left[\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|\right],
\]
while we define 
\[
\hat{C}=f(\{\hat{B}_{i}\})=0.\left|00\right\rangle \left\langle 00\right|+1.\left|01\right\rangle \left\langle 01\right|+2.\left|10\right\rangle \left\langle 10\right|+3.\left|11\right\rangle \left\langle 11\right|.
\]
$\hat{C}$ maybe viewed as a function of $\hat{B}_{1}$, $\hat{B}_{2}$
and other operators $\hat{B}_{i}$ which are constructed to obtain
a maximally commuting set. A measurement of $\hat{C}$, will collapse
the state into one of the states which are simultaneous eignkets of
$B_{1}$ and $B_{2}$. Consequently, from the observed value of $\hat{C}$,
one can deduce the values of $\hat{B}_{1}$ and $\hat{B}_{2}$. Now
consider $\sqrt{2}\left|\chi\right\rangle =\left|10\right\rangle +\left|01\right\rangle $,
for which $m_{1}(\hat{B}_{1})=1$, and $m_{1}(\hat{B}_{2})=1$, using
the C-ingle model, with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
which one can deduce that $B_{1}$ was $+1$, while $B_{2}$ was $-1$.
This property itself, one may be tempted call contextuality, viz.
the value of $B_{1}$ depends on whether it is measured alone or with
the remaining $\{B_{i}\}$. However, it must be noted that $B_{1}$
has a well defined value, and so does $\hat{C}$. Thus by our accepted
definition, there's no contextuality. It is just that $m_{1}(\hat{C})\neq f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
viz. the theory is non-multiplicative. Note that after measuring $\hat{C}$
however, $m_{2}(\hat{B}_{1})=+1$ and $m_{2}(\hat{B}_{2})=-1$ (for
any value of $c$) consistent with those deduced by measuring $\hat{C}$.

\subsection{Entanglement and Superposition}

It is known that for simultaneous eigenstates of $\hat{B}_{i}$, multiplicativity
must hold. Consequently, any violation of multiplicativity must arise
from states that are superpositions (of the simultaneous eigenkets).
Note however, that entanglement is not necessary to show a violation,
since, for example, the PM test is a state independent test, where
a separable state can be used to arrive at a contradiction. For demonstrating
non-locality using Bell's proof, however, it can be shown that entanglement
is necessary.

\bibliographystyle{apsrev4-1}
\bibliography{references}

\end{document}

### 2016-07-05 finalPaper.tex
the abstract
updated the implications section + added something in the git ignore file
minor fixes, the biblio had issues and fixed the abstract

@@
 \begin{abstract}
-We reconsider the no-go theorems on hidden variables and conclude
-that the notion of contextuality is not a necessary feature of quantum
-mechanics. We provide an alternative view, motivated by consistency
-requirements between Bohmian Mechanics and the said theorems. This
-is accomplished by identifying a new classical property, we call `multiplicativity'.
-We propose a non-contextual hidden variable model, consistent with
-all predictions of QM (for discrete spaces). Advantages of this view
-are illuminated by discussion of implications of non-multiplicativity
-to non-locality and its relation to contextuality.
+We propose a non-contextual hidden variable model, consistent with all predictions of QM (for discrete spaces).
+We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics.
+Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view.
+This is accomplished by identifying a new classical property, we call `multiplicativity'.
+Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality and its relation to contextuality.
 \end{abstract}
@@
 
+TODO: Complete this part.
 \bibliographystyle{apsrev4-1}

### 2016-07-06 finalPaper.tex
made minor changes

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[british,aps,superscriptaddress,nofootinbib,times]{revtex4-1}
+\documentclass[british,aps,superscriptaddress,nofootinbib,times,twocolumn]{revtex4-1}
 \usepackage[T1]{fontenc}
@@
   \newtheorem{example}[thm]{\protect\examplename}
+  \theoremstyle{definition}
+  \newtheorem{notn}[thm]{\protect\notationname}
 
@@
   \providecommand{\theoremname}{Theorem}
+  \providecommand{\notationname}{Notation}
 
@@
 
-\title{An alternative to contextuality}
+\title{A non-contextual hidden variable model for QM}
 
@@
 This is accomplished by identifying a new classical property, we call `multiplicativity'.
-Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality and its relation to contextuality.
+Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.%and its relation to contextuality.
 \end{abstract}
@@
 
-Background: Since Einstein's \cite{EinsteinEPR} work on completeness
-of quantum mechanics and the subsequent seminal work of Bell, assessing
-compatibility of hidden variable models has proven to be repeatedly
-useful. It has had foundational implications, for instance it gave
-a precise meaning to locality, and engendered pragmatic advantages,
-such as security, randomness certification etc. While Bell showed
-that local hidden variable models can not describe nature, the Kochen
-Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
-ruled out an even larger class of hidden variable models. The notion
-of contextuality was identified which also, in recent times has been
-harnessed for computation and cryptography. Not all hidden variable
-models were, however, proved to be incompatible. Bohm's work \cite{Bohm1,Bohm2}
-is one such (in)famous example. This approach has allowed for a precise
-interpretation of quantum mechanics.
+Background: Einstein's \cite{EinsteinEPR} work on incompleteness of quantum mechanics and the subsequent seminal work of Bell, assessing compatibility of hidden variable models with quantum mechanics has proven to be repeatedly useful.
+In Bell's case, for instance, it gave a precise meaning to the foundational notion of locality.
+Further, it has been of pragmatic utility in the areas of security, randomness certification etc.
+While Bell showed that local hidden variable models can not describe nature, the Kochen Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin}) ruled out an even larger class of hidden variable models.
+The notion of contextuality was identified which also, in recent times has been harnessed for computation and cryptography [TOOD: add references].
+Not all hidden variable models were, however, proved to be incompatible.
+Bohm's work \cite{Bohm1,Bohm2} is one such (in)famous example.
+This approach has allowed for an interpretation of quantum mechanics with precise trajectories.
 
-Previous work {[}the essentials I have already discussed{]}: In this
-paper, we take a closer look at the aforesaid no-go theorems and find
-that contextuality is in fact not a necessary feature of quantum mechanics.
-This has been shown \cite{NoContextuality} by taking disturbances
-due to measurements into consideration. Here, however, we construct
-a significantly simpler toy model for illustrating not only the aforesaid
-but to also delineate a complete alternative to contextuality. The
-toy model is a specific case of what we call a c-ingle variable theory.
-Its predictions match with those of quantum mechanics for systems
-described by arbitrary (discrete) Hilbert spaces.
+Previous work {[}the essentials I have already discussed{]}: We take a closer look at the aforesaid no-go theorems and find that contextuality is in fact not a necessary feature of quantum mechanics.
+This has been shown earlier by taking disturbances due to measurements into consideration \cite{NoContextuality}.
+In this paper, we construct a significantly simpler toy model for illustrating not only the aforesaid but to also delineate a complete alternative to contextuality.
+The toy model is a specific case of what we call a c-ingle variable theory.
+Its predictions match with those of quantum mechanics for systems described by arbitrary (discrete) Hilbert spaces.
 
@@
 
-\begin{defn}
-Notation: (a) $\psi\in\mathcal{H}$ would typically represent the
-quantum mechanical state of the system (assumed pure), residing in
-the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined
-to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$, (c) $[\mathcal{H}]$
-is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which
-represents the state of the system including hidden variables, (d)
-$[\psi]\in[\mathcal{H}]$ will represent the state of the system,
-including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$,
-(f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$,
-(g) the set of all experimental setups is denoted by $\mathcal{E}$,
-(h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$.
-\end{defn}
+\begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e.
+the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers.
+\end{notn}
+
 In addition to the notation, we use the following definition of non-contextuality.
 \begin{defn}
-A theory is non-contextual, if it provides a map $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$
-to explain measurement outcomes. A theory which is not non-contextual
-is contextual.\end{defn}
+A theory is non-contextual, if it provides a map $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$ to explain measurement outcomes. A theory which is not non-contextual is contextual.\end{defn}
 \begin{rem}
-Prediction maps are non-contextual.
+A map is non-contextual if it is of the form $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$; prediction maps are non-contextual.
 \end{rem}
-In the literature broader definitions have been suggested which declare
-a larger set of theories as non-contextual. For our purposes however,
-this restricted definition will suffice. The term contextual is used
-to suggest that the value an operator takes might depend on which
-other compatible observable it is measured with. Since quantum mechanics
-(QM) yields deterministic results only in specific situations, it
-is imperative to analyse the meaning of contextuality by `completing'
-QM. Hidden variable theories do precisely this and we have at our
-disposal the heretic theory of Bohm. Circumventing the details of
-the theory, we note its salient feature; with each particle, one associates
-precisely defined $(q,p)$ and a wavefunction $\psi$. Consequently,
-the outcomes of all experiment are predictable, granted the initial
-conditions of the system and the apparatus are known (the `hidden
-variables'). The essence of Bohmian Mechanics relevant here can be
-captured by the following theorem.
+
+In the literature broader definitions have been suggested which declare a larger set of theories as non-contextual.
+For our purposes however, this restricted definition will suffice.
+The term contextual is used to suggest that the value an operator takes might depend on which other compatible observable it is measured with.
+Since quantum mechanics (QM) yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM.
+Hidden variable theories do precisely this and we have at our disposal the heretic theory of Bohm.
+Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$.
+Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `hidden variables').
+The essence of Bohmian Mechanics relevant here can be captured by the following theorem.
+
 \begin{thm}
@@
 \end{thm}
-Observe that given a Stern-Gerlach setup and the initial conditions
-(position \& wavefunction of the particle), according to the theorem,
-Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$)
-of the particle. Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$
-and that the measurement outcome was spin up. Interestingly, it can
-be shown \cite{Detlef} that if the direction of the magnetic field
-gradient is flipped while everything else is unchanged, the measurement
-outcome will now be spin down. This emphasises the fact that $m_{B}$
-is not a prediction map. More importantly it entails that $m_{B}$
-is contextual. It must be stressed, however, that the contextuality
-in this case is not a statement about the context in terms of compatible
-observables. Here no two observables are compatible (excluding identity).
+Observe that given a Stern-Gerlach setup and the initial conditions (position \& wavefunction of the particle), according to the theorem, Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$) of the particle.
+Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$ and that the measurement outcome was spin up.
+Interestingly, it can be shown \cite{Detlef} that if the direction of the magnetic field gradient is flipped while everything else is unchanged, the measurement outcome will now be spin down.
+This emphasises the fact that $m_{B}$ is not a prediction map.
+More importantly it entails that $m_{B}$ is contextual.
+It must be stressed, however, that the contextuality in this case is not a statement about the context in terms of compatible observables.
+Here no two observables are compatible (excluding identity).
 
@@
 
-One can show \cite{KochenSpecker} that under reasonable assumptions,
-no non-contextual theory can explain all predictions of QM. We re-state
-these results and show that nowhere does contextuality appear to be
-a logical necessity. Instead we note that non-contextual theories
-with certain properties, we call \emph{multiplicativity} are incompatible
-with QM. Viewed from this perspective, non-\emph{multiplicativity}
-is the non-classical alternative to contextuality in QM. Precise definitions
-of this and a related property \emph{sequential multiplicativity},
-are given below. 
+One can show \cite{KochenSpecker} that under reasonable assumptions, no non-contextual theory can explain all predictions of QM.
+We re-state these results and show that nowhere does contextuality appear to be a logical necessity.
+Instead we note that non-contextual theories with certain properties, we call \emph{multiplicativity} are incompatible with QM.
+Viewed from this perspective, non-\emph{multiplicativity} is the non-classical alternative to contextuality in QM.
+Precise definitions of this and a related property \emph{sequential multiplicativity}, are given below.
+
 \begin{defn}
-A prediction map $m$ is \emph{multiplicative }iff 
-\[
-m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])=f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
-\]
-where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
-observables, $f:\hat{\mathcal{H}}^{\otimes N}\to\mathcal{\hat{H}}$
-and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is
-one that is not multiplicative.
+A prediction map $m$ is \emph{multiplicative} iff 
+% \[
+% \begin{split}
+% m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
+% f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
+% \end{split}
+% \]
+
+\begin{align*}
+& m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
+& \tilde f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
+\end{align*}
+where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting observables and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is one that is not multiplicative.
 \end{defn}
@@
 not obvious that this property must always hold. To motivate this,
-consider the state $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
+consider the state of two spin half particles, $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
 written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
@@
 we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
-independently, according to QM, with probability half. Contrary to
-this, from a quick computation, it is clear that if one first measures
+independently, according to QM, with probability half. Antithetically it is clear that if one first measures
 $\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
@@
 \begin{defn}
-A prediction map $m$ is \emph{sequentially multiplicative }for a
+A prediction map $m$ is \emph{sequentially multiplicative} for a
 given sequence map $s$, iff 
-\[
-m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
-\]
-where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)+\text{ permutations, making }N!\text{ terms}\}$,
+\begin{align*}
+&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
+&\tilde f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
+\end{align*}
+where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)$ + permutations, making $N!$ terms$\}$,
 $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
-observables, $[\psi_{i}]\in[\mathcal{H}]$, $f:\hat{\mathcal{H}}^{\otimes N}\to\mathcal{\hat{H}}$
-and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
-$\forall\,[\psi_{1}]$.
+observables, $[\psi_{i}]\in[\mathcal{H}]$ and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
+$\forall\,[\psi_{i}]$.
 \end{defn}
@@
 Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
-for any arbitrary function $f$, where $\hat{A}_{i}$ are arbitrary
-Hermitian operators. If $m$ is assumed to describe the outcomes of
-measurements, then no $m$ exists which is consistent with all predictions
-of Quantum Mechanics.\end{thm}
+(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
+where $\hat{A}_{i}$ are arbitrary Hermitian operators.
+If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of Quantum Mechanics.\label{thm:det} \end{thm}
+Here $m$ maybe viewed as a specific class of prediction maps, that
+implicitly depends on the state $[\psi]$. It follows then that the
+maps ruled out by the theorem are non-contextual. The set of maps
+ruled out, however, can be enlarged by imposing fewer restrictions
+on it. This is achieved by the following theorem.
+
+\begin{thm}
+Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
+(b) $m(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$,
+for any arbitrary function $f$, where $\hat{B}_{i}$ are mutually
+commuting Hermitian operators. If $m$ is assumed to describe the
+outcomes of measurements, then no $m$ exists which is consistent
+with all predictions of Quantum Mechanics.\label{thm:KS}\end{thm}
+
+% The following proof is not only more general, but also independent
+% of the initial state of the system.
+\begin{proof}
+Peres Mermin ($\left|\mathcal{H}\right|\ge4$):
+
+Consider the following set of operators 
+\[
+\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
+\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\mathbb{I}} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
+\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
+\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
+\end{array}\right]
+\]
+which have the property that all operators along a row (and along
+a column) commute. It is trivial to see that this holds for the first
+two rows and the first two columns. To see that this holds also for
+the last row and column, note the anti-commutation relation, $\{\hat{\sigma}_{x},\hat{\sigma}_{y}\}=0$
+and that $\sigma_{z}=i\sigma_{y}\sigma_{x}$, which one may check
+explicitly. Another property is that the product of rows (columns)
+yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
+$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
+$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. This can be verified easily
+by using the aforesaid relations and the fact that $\sigma^{2}=1$,
+for every Pauli matrix. Using this property of $\hat{R}_{i}$ and
+$\hat{C}_{j}$, it is easy to show that no map $m$ with the stated
+properties can exist. Let us assume on the contrary that $m$ exists.
+From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (used property
+(a)), we must have an odd number of $-1$ assignments in the third
+column. In the remaining columns, the number of $-1$ assignments
+must be even for each column. Thus, in the entire square, the number
+of $-1$ assignments must be odd. Let us use the same reasoning, but
+along the rows. Since each $m(\hat{R}_{i})=1$, we must have even
+number of $-1$ assignments along each row. Thus, in the entire square,
+the number of $-1$ assignments must be even. We have arrived at a
+contradiction and therefore we conclude that our assumption that a
+consistent $m$ exists, must be wrong.
+\end{proof}
+
+\begin{proof}
+Kochen Specker ($\left|\mathcal{H}\right|\ge3$): The original proof
+given by \cite{KochenSpecker} is rather involved. Here we will satisfy
+ourselves with assuming its validity and applying our constructions
+to the aforesaid proof(s).
+\end{proof}
+
+\begin{rem}
+One could in principle assume $m$, to be s.t. (a) $m(\hat{\mathbb{I}})=1$,
+(b) $m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for $\alpha\in\mathbb{R}$,
+(c) $m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d) $m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
+to deduce (d') $m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
+and that $m(\hat{B}_{i})\in$ spectrum of $\hat{B}_{i}$. Effectively
+then, condition (b) listed in the theorem is satisfied as a consequence.
+Therefore, assuming (a)-(d) as listed here, rules out a larger class
+of $m$.
+\end{rem}
+According to \thmref{KS}, non-contextual maps which are \emph{multiplicative}
+must be incompatible with QM. It is apparent that non-contextual maps
+which are non-\emph{multiplicative} might be consistent with QM. To
+that end, in the following section we first show that this is indeed
+the case by constructing an explicit model and supplement it by removing contextuality from Bohmian Mechanics.
+
+Before proceeding we note, however, that QM enforces \emph{sequential
+multiplicativity} at least in certain cases. This result will be used
+to assess accuracy of any hidden variable model we might propose.
+\begin{prop*}
+Let the system be in a state, s.t. measurement of $\hat{C}$ yields
+repeatable results (same result each time). Then according to QM,
+\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
+and $\hat{B}_{i}$ are as defined. \end{prop*}
+\begin{proof}
+Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
+are mutually compatible (commuting) and complete set of operators.
+If say for instance the set is not complete, then one can add the
+missing operators and label them as aforesaid. It follows that $\exists$
+$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
+s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
+where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
+and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
+Let the state of the system be given by $\left|\psi\right\rangle $
+and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
+by assumption. For the statement to follow, one need only show that
+$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
+which satisfy $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
+This is the crucial step. Proving this is so is trivial. We start
+with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
+and take its inner product with $\left\langle \mathbf{b}\right|$
+to get 
+\begin{eqnarray*}
+\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
+\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
+\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
+\end{eqnarray*}
+Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
+from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
+for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then
+we can conclude that indeed $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
+However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
+$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
+then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
+is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
+the required relation. That completes the proof.
+\end{proof}
+It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
+are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
+eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
+must always hold.
+
+\subsection{C-ingle model | An Explicit Construction}
+
+Let the state of the system
+be $\left|\chi\right\rangle $, defined on a discrete Hilbert space
+(spin like) and we wish to assign a value to an arbitrary operator
+$\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which
+has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
+This model has the following postulates: \\
+1. Initial Hidden Variable: Pick a $c\in[0,1]$, from a uniform random
+distribution.\\
+2. Assignment/Prediction: The value assigned to $\hat{A}$ is given
+by finding the smallest $a$ s.t. 
+\[
+c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle a'|\chi\right\rangle \right|^{2},
+\]
+viz. we have specified a prediction map, $m(\hat{A})=a$.\\
+3. Update: After measuring an operator, the state must be updated
+(collapsed) in accordance with the rules of QM. This completely specifies
+the sequence map $s$.
+
+To see how this works, we restrict ourselves to a single spin case.
+Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $,
+and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
+Now, according to the postulates of this theory, $m(\hat{A})=+1$,
+if $c\le\cos^{2}\theta$, else $\hat{A}$ will be assigned $-1$.
+It follows then, from $c$ being uniformly random in $[0,1]$, that
+the statistics agree with predictions of QM. The reader can convince
+him(her)self that the said scheme works in general. A more interesting
+application of this to the PM situation follows.
+
+We can clearly see that the assignment, described by the prediction
+map $m$, is non-contextual since given an operator and a state (+
+the hidden variable), the value is uniquely assigned. The map $m$
+is non-multiplicative which will be clarified by the following.
+\begin{example}
+{[}C-ingle model applied to the Peres Mermin situation{]} We apply
+the C-ingle model to the Peres Mermin situation discussed earlier.
+\begin{comment}
+We construct a simplified hidden variable model for the Peres Mermin
+situation (TODO: Add as a test of contextuality?) and explicitly show
+that the associated prediction map $m$ is non-multiplicative. We
+subsequently show that this model is a special case of the C-ingle
+model. 
+\end{comment}
+{} For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
+Say from a uniform random distribution we obtained $c=0.4$. To arrive
+at the assignments, note that $\left|00\right\rangle $ is an eigenket
+of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
+Thus, in the first iteration, all these should be assigned their respective
+eigenvalues. The remaining operators must be assigned $-1$ as one
+can readily verify by explicitly finding the smallest $a$ as described
+in postulate 2 of the model (see \eqref{toyModel}). Two remarks are
+in order. First, this model is manifestly \emph{non-multiplicative},
+for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
+where the subscript has been introduced to index the iteration. More
+precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$
+where the complete state $\left[\left|\psi_{1}\right\rangle \right]$
+implicitly refers to both the quantum state $\left|00\right\rangle $
+and the hidden variable $c=0.4$. Second, we must impose \emph{sequential
+multiplicativity} as a consistency check of the model, which in particular
+entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
+where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$,
+$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
+$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are
+obtained from postulate 3. Note that for each iteration, a new hidden
+variable is generated. To illustrate \emph{sequential multiplicativity},
+we must choose to measure $\hat{A}_{33}$. According to step 4, since
+$\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the
+final state remains $\left|00\right\rangle $. 
+\end{example}
+\begin{widetext}
+\begin{equation}
+\begin{array}{c|ccc}
+\text{Iteration} & i=1 & i=2 & i=3\\
+\left|\psi_{\text{init}}\right\rangle  & \left|00\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}\\
+\text{HV/Toss} & c=0.4 & c=0.1 & c=0.7\\
+\\
+\text{Predictions} & m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+-1 & -1 & -1\\
+-1 & -1 & -1\\
+-1 & -1 & +1
+\end{array}\right] & m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+-1 & -1 & -1\\
+-1 & -1 & -1\\
+-1 & -1 & +1
+\end{array}\right] & m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
++1 & +1 & +1\\
++1 & +1 & -1\\
++1 & +1 & +1
+\end{array}\right]\\
+\text{(Assignments)}\\
+ & m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) & m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) & m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
+ & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
+\text{Operator}\\
+\text{Measured} & \hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1 & \quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad & \hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
+\\
+\left|\psi_{\text{final}}\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}} & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}
+\end{array}\label{eq:toyModel}
+\end{equation}
+\end{widetext}
+For the next iteration, $i=2$, viz. after the first measurement has
+been performed, say the random number generator yielded $c=0.1$.
+Since $\left|\psi\right\rangle $ is also unchanged the assignment
+remains invariant (in fact any of $c<0.5$ would yield the same result),
+which should be evident from the previous exercise. For the final
+step we choose to measure $\hat{p}=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
+to proceed with sequentially measuring $\hat{C}_{3}$. To simplify
+calculations, we note 
+\[
+\left|00\right\rangle =\frac{(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle )/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle +\left|\tilde{-}\tilde{-}\right\rangle )/\sqrt{2}}{\sqrt{2}},
+\]
+where $\left|\tilde{\pm}\right\rangle =\left|0\right\rangle \pm i\left|1\right\rangle $
+(eigenkets of $\hat{\sigma}_{y}$). Since $\left|00\right\rangle $
+is manifestly not an eigenket of $\hat{p}$, we must find an appropriate
+eigenket $\left|p_{-}\right\rangle $ s.t. $\hat{p}\left|p_{-}\right\rangle =-\left|p_{-}\right\rangle $,
+since $c=0.1$ and $\left\langle p_{-}|00\right\rangle $ is already
+$>0.1$.
+It is immediate that $\left|p_{-}\right\rangle =\left(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle \right)/\sqrt{2}=\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
+which becomes the final state. \\
+For the final iteration, $i=3$, say we obtain $c=0.7$. So far, we
+have $m_{1}(\hat{A}_{33})=1$ and $m_{2}(\hat{A}_{23})=-1$. We must
+obtain $m_{3}(\hat{A}_{13})=1$, independent of the value of $c$,
+to be consistent. Let's check that. Indeed, according to postulate
+2, since $\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}=1\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
+$m_{3}(\hat{A}_{13})=1$ for all allowed values of $c$. As a remark,
+it maybe emphasised that the $m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$
+and $m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which essentially
+expresses compatibility of these observables, viz. measurement of
+$\hat{A}_{13}$ doesn't affect the result one would obtain by measuring
+operators compatible to it (granted they have been measured once before).
+
+\subsection{Non-contextual Bohmain Mechanics}
+
+Recall that contextuality in Bohmian Mechanics arises from the mapping
+between an operator and the experimental setup. Consider the following
+proposition.
+\begin{lem}
+For discrete $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$.\end{lem}
+\begin{proof}
+To describe an experimental setup corresponding to a measurement,
+we use a measuring particle (mass $m_{L}$, say). It is made to interact
+with the system for a short duration appropriately and subsequently
+we measure the resultant position of the particle, to learn about
+the value of the observable of interest. Say for instance, we wish
+to measure the observable $\hat{L}$, then the required interaction
+Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
+Here the first operator acts on the system and second (after the tensor
+product symbol) acts on the measuring particle. $a$ quantifies the
+interaction strength. {[}TODO: check this{]} It has dimensions of
+frequency, if $L$ has dimensions of length. Let us assume that the
+system in the state $\left|\psi\right\rangle $. Then it is known
+that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $,
+where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with
+eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but
+its removal doesn't cause any significant difficulty). $\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $,
+where 
+\[
+\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
+\]
+ and $\left|\varphi\right\rangle $ is the state of the measuring
+particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
+If $t$ is very small, and $a$ very large, s.t. $at=\lambda$ is
+a finite number, then one can neglect the free evolution, $\nabla^{2}t$
+terms compared to $\hat{H}_{\text{int}}t$. We then have 
+\begin{eqnarray*}
+\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
+ & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
+ & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
+\end{eqnarray*}
+where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
+This interaction, effectively entangles the measuring particle, with
+the possible `outcomes', eigenstates of the observable $\hat{L}$
+of interest. If $\sigma\ll\lambda l$, then according to QM itself,
+a position measurement of the measuring particle, would correspond,
+in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to
+which the system will collapse. Therefore, given an observable, one
+can construct the aforesaid experiment to measure its value. We have,
+in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
+\end{proof}
+The proof of this proposition can also be motivated by a simple construction.
+Consider that the system of interest are spin half particles. To measure
+spin along any direction, there are two directions along which the
+magnetic field gradient can be set (as was discussed in the introduction).
+The experimentalist agrees to always use a specific direction, thereby
+mapping an operator to an experimental setup uniquely. Given this,
+one can immediately derive a consistent non-multiplicative prediction
+map $m$.
+\begin{prop}
+The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$,
+we call `Bohmian prediction map'.\end{prop}
+\begin{proof}
+$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.\end{proof}
+\begin{prop}
+The Bohmian prediction map, $m$ must be non-multiplicative.\end{prop}
+\begin{proof}
+Since Bohmian Mechanics is consistent with all predictions of QM,
+the Bohmian prediction map $m$ must also be. According to \thmref{KS},
+$m$ must be non-multiplicative.
+\end{proof}
+
+\section{Implications}
+
+\subsection{Locality}
+
+\begin{defn}
+A theory/model/map is \emph{local} iff two spatially distinct points
+can not be influenced instantaneously.
+\end{defn}
+
+\begin{prop}
+A prediction map $m$ consistent with QM must be non-local.\end{prop}
+\begin{proof}
+{[}Bell's{]} Formally it is clear, since a violation of Bell's inequality
+implies non-locality. Consequently, any consistent completion of QM,
+will be non-local. More insight can be gained, although some care
+is needed. The notion of compatible observables is that commuting
+observables don't disturb each other and can be simultaneously known.
+While the statement is not precisely stated, we only need to note
+that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$,
+for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$
+are defined as before. In words, this means that to measure $\hat{C}$,
+one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
+A multiplication of the values obtained, can be taken to be the value
+a measurement of $\hat{C}$ yields. This can be verified by measuring
+$\hat{C}$ subsequently. The Bell scenario offers an interesting freedom,
+by restricting the form of $\hat{B}_{i}$. To evaluate $\left\langle \hat{B}\right\rangle $,
+one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
+From the compatibility argument, we need to find the average value
+of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$,
+viz.
+$\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
+So far, the statements were general. Now we assume that our theory
+is non-multiplicative (and non-contextual). A consistent theory (with
+QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
+However, if the particles are taken far away, then the only way the
+theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$
+for example), is if the theory is non-local. Locality will entail
+that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since
+the information about which observable was measured first, can't be
+propagated instantaneously. We see therefore that non-locality arises
+quite naturally in consistent non-multiplicative theories.
+\end{proof}
+
+\begin{prop}
+{[}can perhaps be skipped{]} Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$,
+corresponding to two particles. $\mathcal{H}_{A}$ and $\mathcal{H}_{B}$
+are discrete (correspond to spins say). Let mutually commuting observables
+$\hat{B}_{i}$ be s.t. $\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$
+or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where
+$A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$
+are arbitrary observables. If locality is assumed, then a prediction
+map $m$ and it's associated sequence map $s$ must be s.t. over these
+observables, sequential multiplicativity and multiplicativity become
+identical.
+\end{prop}
+
+\subsection{Apparent Contextuality}
+
+We have already constructed an explicit non-contextual model, which
+is consistent with QM. This model we knew had to be non-multiplicative.
+We will see how non-multiplicativity gives rise to what one might
+confuse to mean contextuality. Imagine 
+\[
+\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|-\left[\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|\right],
+\]
+\[
+\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|-\left[\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|\right],
+\]
+while we define 
+\begin{align*}
+\hat{C}&=f(\{\hat{B}_{i}\}) \\ 
+       &=0.\left|00\right\rangle \left\langle 00\right|+1.\left|01\right\rangle \left\langle 01\right|+2.\left|10\right\rangle \left\langle 10\right|+3.\left|11\right\rangle \left\langle 11\right|.
+\end{align*}
+$\hat{C}$ maybe viewed as a function of $\hat{B}_{1}$, $\hat{B}_{2}$
+and other operators $\hat{B}_{i}$ which are constructed to obtain
+a maximally commuting set. A measurement of $\hat{C}$, will collapse
+the state into one of the states which are simultaneous eignkets of
+$B_{1}$ and $B_{2}$. Consequently, from the observed value of $\hat{C}$,
+one can deduce the values of $\hat{B}_{1}$ and $\hat{B}_{2}$. Now
+consider $\sqrt{2}\left|\chi\right\rangle =\left|10\right\rangle +\left|01\right\rangle $,
+for which $m_{1}(\hat{B}_{1})=1$, and $m_{1}(\hat{B}_{2})=1$, using
+the C-ingle model, with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
+which one can deduce that $B_{1}$ was $+1$, while $B_{2}$ was $-1$.
+This property itself, one may be tempted call contextuality, viz.
+the value of $B_{1}$ depends on whether it is measured alone or with
+the remaining $\{B_{i}\}$. However, it must be noted that $B_{1}$
+has a well defined value, and so does $\hat{C}$. Thus by our accepted
+definition, there's no contextuality. It is just that $m_{1}(\hat{C})\neq f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
+viz. the theory is non-multiplicative. Note that after measuring $\hat{C}$
+however, $m_{2}(\hat{B}_{1})=+1$ and $m_{2}(\hat{B}_{2})=-1$ (for
+any value of $c$) consistent with those deduced by measuring $\hat{C}$.
+
+\subsection{Entanglement and Superposition}
+
+It is known that for simultaneous eigenstates of $\hat{B}_{i}$, multiplicativity
+must hold. Consequently, any violation of multiplicativity must arise
+from states that are superpositions (of the simultaneous eigenkets).
+Note however, that entanglement is not necessary to show a violation,
+since, for example, the PM test is a state independent test, where
+a separable state can be used to arrive at a contradiction. For demonstrating
+non-locality using Bell's proof, however, it can be shown that entanglement
+is necessary.
+
+TODO: Complete this part.
+\begin{appendix}
+\section{Proofs of the two theorems}
+For \thmref{det} we have the following proofs.
 \begin{proof}
@@
 \end{proof}
-Here $m$ maybe viewed as a specific class of prediction maps, that
-implicitly depends on the state $[\psi]$. It follows then that the
-maps ruled out by the theorem are non-contextual. The set of maps
-ruled out, however, can be enlarged by imposing fewer restrictions
-on it. This is achieved by the following theorem.
-\begin{thm}
-Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(f(\hat{B}_{1},\hat{B}_{2},\dots))=f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$,
-for any arbitrary function $f$, where $\hat{B}_{i}$ are mutually
-commuting Hermitian operators. If $m$ is assumed to describe the
-outcomes of measurements, then no $m$ exists which is consistent
-with all predictions of Quantum Mechanics.\label{thm:KS}\end{thm}
+
+For \thmref{KS} the proofs are as below.
 \begin{proof}
@@
 
-The following proof is not only more general, but also independent
-of the initial state of the system.
-\begin{proof}
-Peres Mermin ($\left|\mathcal{H}\right|\ge4$):
+\end{appendix}
 
-Consider the following set of operators 
-\[
-\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
-\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\mathbb{I}} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
-\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
-\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
-\end{array}\right]
-\]
-which have the property that all operators along a row (and along
-a column) commute. It is trivial to see that this holds for the first
-two rows and the first two columns. To see that this holds also for
-the last row and column, note the anti-commutation relation, $\{\hat{\sigma}_{x},\hat{\sigma}_{y}\}=0$
-and that $\sigma_{z}=i\sigma_{y}\sigma_{x}$, which one may check
-explicitly. Another property is that the product of rows (columns)
-yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
-$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
-$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. This can be verified easily
-by using the aforesaid relations and the fact that $\sigma^{2}=1$,
-for every Pauli matrix. Using this property of $\hat{R}_{i}$ and
-$\hat{C}_{j}$, it is easy to show that no map $m$ with the stated
-properties can exist. Let us assume on the contrary that $m$ exists.
-From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (used property
-(a)), we must have an odd number of $-1$ assignments in the third
-column. In the remaining columns, the number of $-1$ assignments
-must be even for each column. Thus, in the entire square, the number
-of $-1$ assignments must be odd. Let us use the same reasoning, but
-along the rows. Since each $m(\hat{R}_{i})=1$, we must have even
-number of $-1$ assignments along each row. Thus, in the entire square,
-the number of $-1$ assignments must be even. We have arrived at a
-contradiction and therefore we conclude that our assumption that a
-consistent $m$ exists, must be wrong.
-\end{proof}
-
-\begin{proof}
-Kochen Specker ($\left|\mathcal{H}\right|\ge3$): The original proof
-given by \cite{KochenSpecker} is rather involved. Here we will satisfy
-ourselves with assuming its validity and applying our constructions
-to the aforesaid proof(s).
-\end{proof}
-
-\begin{rem}
-One could in principle assume $m$, to be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for $\alpha\in\mathbb{R}$,
-(c) $m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d) $m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
-to deduce (d') $m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
-and that $m(\hat{B}_{i})\in$ spectrum of $\hat{B}_{i}$. Effectively
-then, condition (b) listed in the theorem is satisfied as a consequence.
-Therefore, assuming (a)-(d) as listed here, rules out a larger class
-of $m$.
-\end{rem}
-According to \thmref{KS}, non-contextual maps which are \emph{multiplicative}
-must be incompatible with QM. It is apparent that non-contextual maps
-which are non-\emph{multiplicative} might be consistent with QM. To
-that end, in the following section we first show that this is indeed
-the case by removing contextuality from Bohmian Mechanics and supplement
-it thereafter by an explicit construction.
-
-Before proceeding we note, however, that QM enforces \emph{sequential
-multiplicativity} at least in certain cases. This result will be used
-to assess accuracy of any hidden variable model we might propose.
-\begin{prop*}
-Let the system be in a state, s.t. measurement of $\hat{C}$ yields
-repeatable results (same result each time). Then according to QM,
-\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
-and $\hat{B}_{i}$ are as defined. \end{prop*}
-\begin{proof}
-Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
-are mutually compatible (commuting) and complete set of operators.
-If say for instance the set is not complete, then one can add the
-missing operators and label them as aforesaid. It follows that $\exists$
-$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
-s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
-where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
-and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
-Let the state of the system be given by $\left|\psi\right\rangle $
-and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
-by assumption. For the statement to follow, one need only show that
-$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
-which satisfy $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
-This is the crucial step. Proving this is so is trivial. We start
-with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
-and take its inner product with $\left\langle \mathbf{b}\right|$
-to get 
-\begin{eqnarray*}
-\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
-\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
-f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
-\end{eqnarray*}
-Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
-from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
-for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then
-we can conclude that indeed $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
-However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
-$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
-then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
-is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
-the required relation. That completes the proof.
-\end{proof}
-It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
-are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
-eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
-must always hold.
-
-\subsection{Non-contextual Bohmain Mechanics}
-
-Recall that contextuality in Bohmian Mechanics arises from the mapping
-between an operator and the experimental setup. Consider the following
-proposition.
-\begin{lem}
-For discrete $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$.\end{lem}
-\begin{proof}
-To describe an experimental setup corresponding to a measurement,
-we use a measuring particle (mass $m_{L}$, say). It is made to interact
-with the system for a short duration appropriately and subsequently
-we measure the resultant position of the particle, to learn about
-the value of the observable of interest. Say for instance, we wish
-to measure the observable $\hat{L}$, then the required interaction
-Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
-Here the first operator acts on the system and second (after the tensor
-product symbol) acts on the measuring particle. $a$ quantifies the
-interaction strength. {[}TODO: check this{]} It has dimensions of
-frequency, if $L$ has dimensions of length. Let us assume that the
-system in the state $\left|\psi\right\rangle $. Then it is known
-that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $,
-where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with
-eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but
-its removal doesn't cause any significant difficulty). $\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $,
-where 
-\[
-\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
-\]
- and $\left|\varphi\right\rangle $ is the state of the measuring
-particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
-If $t$ is very small, and $a$ very large, s.t. $at=\lambda$ is
-a finite number, then one can neglect the free evolution, $\nabla^{2}t$
-terms compared to $\hat{H}_{\text{int}}t$. We then have 
-\begin{eqnarray*}
-\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
-\end{eqnarray*}
-where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
-This interaction, effectively entangles the measuring particle, with
-the possible `outcomes', eigenstates of the observable $\hat{L}$
-of interest. If $\sigma\ll\lambda l$, then according to QM itself,
-a position measurement of the measuring particle, would correspond,
-in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to
-which the system will collapse. Therefore, given an observable, one
-can construct the aforesaid experiment to measure its value. We have,
-in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
-\end{proof}
-The proof of this proposition can also be motivated by a simple construction.
-Consider that the system of interest are spin half particles. To measure
-spin along any direction, there are two directions along which the
-magnetic field gradient can be set (as was discussed in the introduction).
-The experimentalist agrees to always use a specific direction, thereby
-mapping an operator to an experimental setup uniquely. Given this,
-one can immediately derive a consistent non-multiplicative prediction
-map $m$.
-\begin{prop}
-The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$,
-we call `Bohmian prediction map'.\end{prop}
-\begin{proof}
-$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.\end{proof}
-\begin{prop}
-The Bohmian prediction map, $m$ must be non-multiplicative.\end{prop}
-\begin{proof}
-Since Bohmian Mechanics is consistent with all predictions of QM,
-the Bohmian prediction map $m$ must also be. According to \thmref{KS},
-$m$ must be non-multiplicative.
-\end{proof}
-
-\subsection{C-ingle model | An Explicit Construction}
-
-For readers skeptic about Bohmian Mechanics, the discussion related
-to it can be replaced by the following. Let the state of the system
-be $\left|\chi\right\rangle $, defined on a discrete Hilbert space
-(spin like) and we wish to assign a value to an arbitrary operator
-$\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which
-has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
-This model has the following postulates: \\
-1. Initial Hidden Variable: Pick a $c\in[0,1]$, from a uniform random
-distribution.\\
-2. Assignment/Prediction: The value assigned to $\hat{A}$ is given
-by finding the smallest $a$ s.t. 
-\[
-c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle a'|\chi\right\rangle \right|^{2},
-\]
-viz. we have specified a prediction map, $m(\hat{A})=a$.\\
-3. Update: After measuring an operator, the state must be updated
-(collapsed) in accordance with the rules of QM. This completely specifies
-the sequence map $s$.
-
-To see how this works, we restrict ourselves to a single spin case.
-Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $,
-and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
-Now, according to the postulates of this theory, $m(\hat{A})=+1$,
-if $c\le\cos^{2}\theta$, else $\hat{A}$ will be assigned $-1$.
-It follows then, from $c$ being uniformly random in $[0,1]$, that
-the statistics agree with predictions of QM. The reader can convince
-him(her)self that the said scheme works in general. A more interesting
-application of this to the PM situation follows.
-
-We can clearly see that the assignment, described by the prediction
-map $m$, is non-contextual since given an operator and a state (+
-the hidden variable), the value is uniquely assigned. The map $m$
-is non-multiplicative which will be clarified by the following.
-\begin{example}
-{[}C-ingle model applied to the Peres Mermin situation{]} We apply
-the C-ingle model to the Peres Mermin situation discussed earlier.
-\begin{comment}
-We construct a simplified hidden variable model for the Peres Mermin
-situation (TODO: Add as a test of contextuality?) and explicitly show
-that the associated prediction map $m$ is non-multiplicative. We
-subsequently show that this model is a special case of the C-ingle
-model. 
-\end{comment}
-{} For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
-Say from a uniform random distribution we obtained $c=0.4$. To arrive
-at the assignments, note that $\left|00\right\rangle $ is an eigenket
-of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
-Thus, in the first iteration, all these should be assigned their respective
-eigenvalues. The remaining operators must be assigned $-1$ as one
-can readily verify by explicitly finding the smallest $a$ as described
-in postulate 2 of the model (see \eqref{toyModel}). Two remarks are
-in order. First, this model is manifestly \emph{non-multiplicative},
-for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
-where the subscript has been introduced to index the iteration. More
-precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$
-where the complete state $\left[\left|\psi_{1}\right\rangle \right]$
-implicitly refers to both the quantum state $\left|00\right\rangle $
-and the hidden variable $c=0.4$. Second, we must impose \emph{sequential
-multiplicativity} as a consistency check of the model, which in particular
-entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
-where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$,
-$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
-$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are
-obtained from postulate 3. Note that for each iteration, a new hidden
-variable is generated. To illustrate \emph{sequential multiplicativity},
-we must choose to measure $\hat{A}_{33}$. According to step 4, since
-$\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the
-final state remains $\left|00\right\rangle $. 
-\end{example}
-\begin{equation}
-\begin{array}{c|ccc}
-\text{Iteration} & i=1 & i=2 & i=3\\
-\left|\psi_{\text{init}}\right\rangle  & \left|00\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}\\
-\text{HV/Toss} & c=0.4 & c=0.1 & c=0.7\\
-\\
-\text{Predictions} & m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
--1 & -1 & -1\\
--1 & -1 & -1\\
--1 & -1 & +1
-\end{array}\right] & m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
--1 & -1 & -1\\
--1 & -1 & -1\\
--1 & -1 & +1
-\end{array}\right] & m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-+1 & +1 & +1\\
-+1 & +1 & -1\\
-+1 & +1 & +1
-\end{array}\right]\\
-\text{(Assignments)}\\
- & m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) & m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) & m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
- & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
-\text{Operator}\\
-\text{Measured} & \hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1 & \quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad & \hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
-\\
-\left|\psi_{\text{final}}\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}} & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}
-\end{array}\label{eq:toyModel}
-\end{equation}
-For the next iteration, $i=2$, viz. after the first measurement has
-been performed, say the random number generator yielded $c=0.1$.
-Since $\left|\psi\right\rangle $ is also unchanged the assignment
-remains invariant (in fact any of $c<0.5$ would yield the same result),
-which should be evident from the previous exercise. For the final
-step we choose to measure $\hat{p}=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
-to proceed with sequentially measuring $\hat{C}_{3}$. To simplify
-calculations, we note 
-\[
-\left|00\right\rangle =\frac{(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle )/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle +\left|\tilde{-}\tilde{-}\right\rangle )/\sqrt{2}}{\sqrt{2}},
-\]
-where $\left|\tilde{\pm}\right\rangle =\left|0\right\rangle \pm i\left|1\right\rangle $
-(eigenkets of $\hat{\sigma}_{y}$). Since $\left|00\right\rangle $
-is manifestly not an eigenket of $\hat{p}$, we must find an appropriate
-eigenket $\left|p_{-}\right\rangle $ s.t. $\hat{p}\left|p_{-}\right\rangle =-\left|p_{-}\right\rangle $,
-since $c=0.1$ and $\left\langle p_{-}|00\right\rangle $ is already
-$>0.1$.
-It is immediate that $\left|p_{-}\right\rangle =\left(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle \right)/\sqrt{2}=\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
-which becomes the final state. \\
-For the final iteration, $i=3$, say we obtain $c=0.7$. So far, we
-have $m_{1}(\hat{A}_{33})=1$ and $m_{2}(\hat{A}_{23})=-1$. We must
-obtain $m_{3}(\hat{A}_{13})=1$, independent of the value of $c$,
-to be consistent. Let's check that. Indeed, according to postulate
-2, since $\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}=1\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
-$m_{3}(\hat{A}_{13})=1$ for all allowed values of $c$. As a remark,
-it maybe emphasised that the $m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$
-and $m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which essentially
-expresses compatibility of these observables, viz. measurement of
-$\hat{A}_{13}$ doesn't affect the result one would obtain by measuring
-operators compatible to it (granted they have been measured once before).
-
-\section{Implications}
-
-\subsection{Locality}
-
-\begin{defn}
-A theory/model/map is \emph{local} iff two spatially distinct points
-can not be influenced instantaneously.
-\end{defn}
-
-\begin{prop}
-A prediction map $m$ consistent with QM must be non-local.\end{prop}
-\begin{proof}
-{[}Bell's{]} Formally it is clear, since a violation of Bell's inequality
-implies non-locality. Consequently, any consistent completion of QM,
-will be non-local. More insight can be gained, although some care
-is needed. The notion of compatible observables is that commuting
-observables don't disturb each other and can be simultaneously known.
-While the statement is not precisely stated, we only need to note
-that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$,
-for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$
-are defined as before. In words, this means that to measure $\hat{C}$,
-one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
-A multiplication of the values obtained, can be taken to be the value
-a measurement of $\hat{C}$ yields. This can be verified by measuring
-$\hat{C}$ subsequently. The Bell scenario offers an interesting freedom,
-by restricting the form of $\hat{B}_{i}$. To evaluate $\left\langle \hat{B}\right\rangle $,
-one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
-From the compatibility argument, we need to find the average value
-of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$,
-viz.
-$\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
-So far, the statements were general. Now we assume that our theory
-is non-multiplicative (and non-contextual). A consistent theory (with
-QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
-However, if the particles are taken far away, then the only way the
-theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$
-for example), is if the theory is non-local. Locality will entail
-that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since
-the information about which observable was measured first, can't be
-propagated instantaneously. We see therefore that non-locality arises
-quite naturally in consistent non-multiplicative theories.
-\end{proof}
-
-\begin{prop}
-{[}can perhaps be skipped{]} Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$,
-corresponding to two particles. $\mathcal{H}_{A}$ and $\mathcal{H}_{B}$
-are discrete (correspond to spins say). Let mutually commuting observables
-$\hat{B}_{i}$ be s.t. $\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$
-or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where
-$A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$
-are arbitrary observables. If locality is assumed, then a prediction
-map $m$ and it's associated sequence map $s$ must be s.t. over these
-observables, sequential multiplicativity and multiplicativity become
-identical.
-\end{prop}
-
-\subsection{Apparent Contextuality}
-
-We have already constructed an explicit non-contextual model, which
-is consistent with QM. This model we knew had to be non-multiplicative.
-We will see how non-multiplicativity gives rise to what one might
-confuse to mean contextuality. Imagine 
-\[
-\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|-\left[\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|\right],
-\]
-\[
-\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|-\left[\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|\right],
-\]
-while we define 
-\[
-\hat{C}=f(\{\hat{B}_{i}\})=0.\left|00\right\rangle \left\langle 00\right|+1.\left|01\right\rangle \left\langle 01\right|+2.\left|10\right\rangle \left\langle 10\right|+3.\left|11\right\rangle \left\langle 11\right|.
-\]
-$\hat{C}$ maybe viewed as a function of $\hat{B}_{1}$, $\hat{B}_{2}$
-and other operators $\hat{B}_{i}$ which are constructed to obtain
-a maximally commuting set. A measurement of $\hat{C}$, will collapse
-the state into one of the states which are simultaneous eignkets of
-$B_{1}$ and $B_{2}$. Consequently, from the observed value of $\hat{C}$,
-one can deduce the values of $\hat{B}_{1}$ and $\hat{B}_{2}$. Now
-consider $\sqrt{2}\left|\chi\right\rangle =\left|10\right\rangle +\left|01\right\rangle $,
-for which $m_{1}(\hat{B}_{1})=1$, and $m_{1}(\hat{B}_{2})=1$, using
-the C-ingle model, with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
-which one can deduce that $B_{1}$ was $+1$, while $B_{2}$ was $-1$.
-This property itself, one may be tempted call contextuality, viz.
-the value of $B_{1}$ depends on whether it is measured alone or with
-the remaining $\{B_{i}\}$. However, it must be noted that $B_{1}$
-has a well defined value, and so does $\hat{C}$. Thus by our accepted
-definition, there's no contextuality. It is just that $m_{1}(\hat{C})\neq f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
-viz. the theory is non-multiplicative. Note that after measuring $\hat{C}$
-however, $m_{2}(\hat{B}_{1})=+1$ and $m_{2}(\hat{B}_{2})=-1$ (for
-any value of $c$) consistent with those deduced by measuring $\hat{C}$.
-
-\subsection{Entanglement and Superposition}
-
-It is known that for simultaneous eigenstates of $\hat{B}_{i}$, multiplicativity
-must hold. Consequently, any violation of multiplicativity must arise
-from states that are superpositions (of the simultaneous eigenkets).
-Note however, that entanglement is not necessary to show a violation,
-since, for example, the PM test is a state independent test, where
-a separable state can be used to arrive at a contradiction. For demonstrating
-non-locality using Bell's proof, however, it can be shown that entanglement
-is necessary.
-
-TODO: Complete this part.
 \bibliographystyle{apsrev4-1}

### 2016-07-06 finalPaper.tex
added another proof for the determinism theorem, fixed a few other things and updated the git ignore

@@
 \begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e.
-the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers.
+the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should strictly be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.}.
 \end{notn}
@@
 from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
-for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then
-we can conclude that indeed $c=f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
+for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
 However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
@@
 \begin{proof}
+Trivial yet most general proof ($\left|\mathcal{H}\right|\ge2$): Consider $\hat A _1 = \sigma_y$, $\hat A_2 =\sigma_x$, $\hat C = f(\hat A_1,\hat A_2) = i\hat A_1 \hat A_2=\sigma_z$.
+Now we know that $m(\hat \sigma_j)=\pm1$ which entails that $m(\hat C)=  im(\hat A_1)m(\hat A_2)=i$ where we have used property (b).
+However, $m(\hat C)=m(\hat \sigma_z)=\pm1$ which is a contradiction.
+Thus no consistent $m$ can exist.
+\end{proof}
+
+\begin{proof}
 Bell construction ($\left|\mathcal{H}\right|\ge4$): Consider an operator

### 2016-07-06 finalPaper.tex
added the block diagram and included the quick description of the work

@@
 \AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
+\AtBeginDocument{\providecommand\figref[1]{\ref{fig:#1}}}
+\AtBeginDocument{\providecommand\secref[1]{\ref{sec:#1}}}
+\AtBeginDocument{\providecommand\ssecref[1]{\ref{ssec:#1}}}
+
 \RS@ifundefined{subref}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{graphicx}
+\graphicspath{ {images/} }
+
 \usepackage{xcolor}
@@
 
-Triangle: <TODO: ask arvind sir>
+Triangle: <TODO: ask arvind sir, see \figref{block}>
 
-Work and results: <summarise what is done in each section>
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{block1}
+\caption{Non-contextuality is not inconsistent with QM}
+\label{fig:block}\end{figure}
 
-\section{Context}
+Work and results: In \secref{context} we establish a notation and definitions to facilitate further discussions.
+In \secref{nonMultiplicativity} we introduce the notion of multiplicativity and that of sequential multiplicativity.
+We review the `contextuality' theorem and prove some results about multiplicativity.
+We construct an explicit non-contextual model in \ssecref{cingle} and apply it to the very proof of `contextuality' to illustrate non-multiplicativity.
+This is supplemented by a discussion about Bohmian Mechanics in \ssecref{nonContBohm} where contextuality is removed by hand.
+The paper is concluded with discussion of implications of multiplicativity on locality, entanglement, superposition and apparent contextuality in \secref{implications}.
+
+\section{Context \label{sec:context}}
 
@@
 
-\section{Non-Multiplicativity: An alternative to Contextuality}
+\section{Non-Multiplicativity: An alternative to Contextuality \label{sec:nonMultiplicativity}}
 
@@
 
-\subsection{C-ingle model | An Explicit Construction}
+\subsection{C-ingle model | An Explicit Construction \label{ssec:cingle}}
 
@@
 
-\subsection{Non-contextual Bohmain Mechanics}
+\subsection{Non-contextual Bohmain Mechanics \label{ssec:nonContBohm}}
 
@@
 
-\section{Implications}
+\section{Implications \label{sec:implications}}
 

### 2016-07-06 finalPaper.tex
Made minor updates after a small discussion with Prof Arvind

@@
 \begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e.
-the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should strictly be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.}.
+the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.
+In fact the values should be restricted to the spectrum of the associated observables.}.
 \end{notn}
@@
 Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$.
+The construction is such that the particles are guided by the wavefunction.
 Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `hidden variables').
@@
 we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
-independently, according to QM, with probability half. Antithetically it is clear that if one first measures
+independently, according to QM, with probability half. Here multiplicativity doesn't seem to hold. Antithetically it is clear that if one first measures
 $\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
@@
 
-Before proceeding we note, however, that QM enforces \emph{sequential
-multiplicativity} at least in certain cases. This result will be used
-to assess accuracy of any hidden variable model we might propose.
+Before proceeding we note, however, that QM can enforce \emph{sequential multiplicativity}. This result will be used to assess accuracy of any hidden variable model we might propose.
 \begin{prop*}
@@
 GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider three
-observers with one particle each. Each observer can measure two properties,
+observers with one spin half particle each. Each observer can measure two properties,
 call them X and Y, with outcomes $\pm1$. The associated operators

### 2016-07-07 preReleases/version2/finalPaper.tex
removed redundancy, shifted more proofs to the appendix, added references, looked at the literature to ensure nothing was missed, fixed the BM section etc.

--- 2016-07-06 finalPaper.tex
@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[british,aps,superscriptaddress,nofootinbib,times,twocolumn]{revtex4-1}
+\documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
 \usepackage[T1]{fontenc}
@@
 
-\title{A non-contextual hidden variable model for QM}
+\title{A non-contextual hidden variable model for Quantum Mechanics}
 
@@
 \begin{abstract}
-We propose a non-contextual hidden variable model, consistent with all predictions of QM (for discrete spaces).
+We propose a non-contextual hidden variable model, consistent with all predictions of Quantum Mechanics (QM).
 We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics.

### 2016-07-07 finalPaper.tex
Fixed some typographical issues; QM quantum mechanics like and fixed some proposition etc. related things

@@
 \AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
+\AtBeginDocument{\providecommand\lemref[1]{\ref{lem:#1}}}
+\AtBeginDocument{\providecommand\propref[1]{\ref{prop:#1}}}
 \AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
@@
   {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
+  {}
+\RS@ifundefined{propref}
+  {\def\RSproptxt{proposition~}\newref{prop}{name = \RSproptxt}}
   {}
@@
 \begin{abstract}
-We propose a non-contextual hidden variable model, consistent with all predictions of QM (for discrete spaces).
-We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics.
-Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view.
+We propose a non-contextual hidden variable model, consistent with all predictions of quantum mechanics (QM).
+We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of QM.
+Motivated by consistency requirements between bohmian mechanics and the said theorems, we provide an alternative view.
 This is accomplished by identifying a new classical property, we call `multiplicativity'.
-Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.%and its relation to contextuality.
+It turns out that if this condition is relaxed one is able to construct hidden variable models which are consistent with QM.
+Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.
+Our model is for finite dimensional quantum systems, however, generalization to the infinite dimensional case should be possible.
+%and its relation to contextuality.
 \end{abstract}
@@
 
-Background: Einstein's \cite{EinsteinEPR} work on incompleteness of quantum mechanics and the subsequent seminal work of Bell, assessing compatibility of hidden variable models with quantum mechanics has proven to be repeatedly useful.
+Einstein's \cite{EinsteinEPR} work on incompleteness of QM and the subsequent seminal work of Bell \cite{Bell1964}, assessing compatibility of hidden variable (HV) models with QM has proven to be repeatedly useful.
 In Bell's case, for instance, it gave a precise meaning to the foundational notion of locality.
 Further, it has been of pragmatic utility in the areas of security, randomness certification etc.
-While Bell showed that local hidden variable models can not describe nature, the Kochen Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin}) ruled out an even larger class of hidden variable models.
-The notion of contextuality was identified which also, in recent times has been harnessed for computation and cryptography [TOOD: add references].
-Not all hidden variable models were, however, proved to be incompatible.
+\cite{Ekert,PironioRndmnssCrtfcn} While Bell showed that local HV models can not describe nature, the Kochen Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin}) ruled out an even larger class of HV models.
+Consequently the notion of contextuality was identified, methods to experimentally test it were proposed and evidence in its favour reported \cite{SimonContExpProp,HuangContExp,YangContExp,HasegawaContExp}.
+Contextuality also, in recent times has been harnessed for computation and cryptography \cite{HowardCntxCmptn,CabelloCntxScrt}.
+[]Contextuality has also stirred further investigation of foundational aspects of QM: relation between contextuality and classicality has been explored \cite{PawelCntxClsscl}, contextuality has been quantified in terms of memory \cite{MatthiasCntxMmry} and bounded memory in conjunction with contextuality has been used to show completeness of QM \cite{CabelloMmryQM}.[] Not all HV models were, however, proved to be incompatible by the aforesaid theorem.
 Bohm's work \cite{Bohm1,Bohm2} is one such (in)famous example.
-This approach has allowed for an interpretation of quantum mechanics with precise trajectories.
+This approach has allowed for an interpretation of QM with precise trajectories.
 
-Previous work {[}the essentials I have already discussed{]}: We take a closer look at the aforesaid no-go theorems and find that contextuality is in fact not a necessary feature of quantum mechanics.
-This has been shown earlier by taking disturbances due to measurements into consideration \cite{NoContextuality}.
+%Previous work {[}the essentials I have already discussed{]}: 
+We take a closer look at the aforesaid no-go theorems and find that contextuality is in fact not a necessary feature of QM (see \figref{block}).
+This has been shown earlier by taking disturbances due to measurements into consideration \cite{NoContextuality,LaCourNoCntx}.
 In this paper, we construct a significantly simpler toy model for illustrating not only the aforesaid but to also delineate a complete alternative to contextuality.
 The toy model is a specific case of what we call a c-ingle variable theory.
-Its predictions match with those of quantum mechanics for systems described by arbitrary (discrete) Hilbert spaces.
+Its predictions match with those of QM for systems described by arbitrary finite dimensional Hilbert spaces.
 
-Triangle: <TODO: ask arvind sir, see \figref{block}>
+%Triangle: <TODO: ask arvind sir, see \figref{block}>
 
@@
 
-Work and results: In \secref{context} we establish a notation and definitions to facilitate further discussions.
+Organization of this paper is as follows.
+In \secref{context} we establish a notation and definitions to facilitate further discussions.
 In \secref{nonMultiplicativity} we introduce the notion of multiplicativity and that of sequential multiplicativity.
@@
 \begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e.
-the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.
+the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including HVs, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including HVs, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) $f$ is an arbitrary map from $\{ \hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}} \} \to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\{ \hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}} \}$.}, (h) $\tilde{f}$ is a map constructed by replacing observables in $f$ with real numbers.
+%\footnote{$\tilde f$ constructed this way should be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.
 In fact the values should be restricted to the spectrum of the associated observables.}.
@@
 \begin{defn}
-A theory is non-contextual, if it provides a map $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$ to explain measurement outcomes. A theory which is not non-contextual is contextual.\end{defn}
+A theory is non-contextual, if it provides a map $m: \{ \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$ to explain measurement outcomes. A theory which is not non-contextual is contextual.\end{defn}
 \begin{rem}
-A map is non-contextual if it is of the form $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$; prediction maps are non-contextual.
+The notion of non-contextuality may be extended to maps. A map is non-contextual if it is of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$; prediction maps are non-contextual.
 \end{rem}
@@
 The term contextual is used to suggest that the value an operator takes might depend on which other compatible observable it is measured with.
-Since quantum mechanics (QM) yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM.
-Hidden variable theories do precisely this and we have at our disposal the heretic theory of Bohm.
-Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$.
-The construction is such that the particles are guided by the wavefunction.
-Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `hidden variables').
-The essence of Bohmian Mechanics relevant here can be captured by the following theorem.
-
-\begin{thm}
-$\exists$ a (Bohmian) map $m_{B}:\hat{\mathcal{H}},[\mathcal{H}],\mathcal{E}\to\mathbb{R}$,
-and a sequence map $s$, s.t. if $m_{B}$ \& $s$ are assumed to describe
-the outcomes of measurements \& the resultant state respectively,
-then they are consistent with all predictions of QM.
-\end{thm}
-Observe that given a Stern-Gerlach setup and the initial conditions (position \& wavefunction of the particle), according to the theorem, Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$) of the particle.
-Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$ and that the measurement outcome was spin up.
-Interestingly, it can be shown \cite{Detlef} that if the direction of the magnetic field gradient is flipped while everything else is unchanged, the measurement outcome will now be spin down.
-This emphasises the fact that $m_{B}$ is not a prediction map.
-More importantly it entails that $m_{B}$ is contextual.
-It must be stressed, however, that the contextuality in this case is not a statement about the context in terms of compatible observables.
-Here no two observables are compatible (excluding identity).
 
@@
 written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
-$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$,
-we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
+$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
+We must have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
 independently, according to QM, with probability half. Here multiplicativity doesn't seem to hold. Antithetically it is clear that if one first measures
@@
 where $\hat{A}_{i}$ are arbitrary Hermitian operators.
-If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of Quantum Mechanics.\label{thm:det} \end{thm}
+If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of QM\label{thm:det} (see \ref{proofs} for proofs).
+\end{thm}
 Here $m$ maybe viewed as a specific class of prediction maps, that
@@
 outcomes of measurements, then no $m$ exists which is consistent
-with all predictions of Quantum Mechanics.\label{thm:KS}\end{thm}
+with all predictions of QM (see \ref{proofs} for more proofs).\label{thm:KS}\end{thm}
 
@@
 \begin{proof}
-Peres Mermin ($\left|\mathcal{H}\right|\ge4$):
+Peres Mermin ($\left|\mathcal{H}\right|\ge4$) \cite{Peres,Mermin}:
 
@@
 \]
-which have the property that all operators along a row (and along
-a column) commute. It is trivial to see that this holds for the first
-two rows and the first two columns. To see that this holds also for
-the last row and column, note the anti-commutation relation, $\{\hat{\sigma}_{x},\hat{\sigma}_{y}\}=0$
-and that $\sigma_{z}=i\sigma_{y}\sigma_{x}$, which one may check
-explicitly. Another property is that the product of rows (columns)
-yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
-$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
-$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. This can be verified easily
-by using the aforesaid relations and the fact that $\sigma^{2}=1$,
-for every Pauli matrix. Using this property of $\hat{R}_{i}$ and
-$\hat{C}_{j}$, it is easy to show that no map $m$ with the stated
-properties can exist. Let us assume on the contrary that $m$ exists.
-From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (used property
-(a)), we must have an odd number of $-1$ assignments in the third
-column. In the remaining columns, the number of $-1$ assignments
-must be even for each column. Thus, in the entire square, the number
-of $-1$ assignments must be odd. Let us use the same reasoning, but
-along the rows. Since each $m(\hat{R}_{i})=1$, we must have even
-number of $-1$ assignments along each row. Thus, in the entire square,
-the number of $-1$ assignments must be even. We have arrived at a
-contradiction and therefore we conclude that our assumption that a
-consistent $m$ exists, must be wrong.
-\end{proof}
-
-\begin{proof}
-Kochen Specker ($\left|\mathcal{H}\right|\ge3$): The original proof
-given by \cite{KochenSpecker} is rather involved. Here we will satisfy
-ourselves with assuming its validity and applying our constructions
-to the aforesaid proof(s).
+which have the property that all operators along a row (or column) commute and that the product of rows (or columns) yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$, $\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$, $\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$.
+Let us assume that $m$ exists.
+From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (as required by property (a)), we must have an odd number of $-1$ assignments in the third column.
+In the remaining columns, the number of $-1$ assignments must be even (for each column).
+Thus, in the entire square, the number of $-1$ assignments must be odd.
+Let us use the same reasoning, but along the rows.
+Since each $m(\hat{R}_{i})=1$, we must have even number of $-1$ assignments along each row.
+Thus, in the entire square, the number of $-1$ assignments must be even.
+We have arrived at a contradiction and therefore we conclude that our assumption that a consistent $m$ exists, must be wrong.
 \end{proof}
@@
 Therefore, assuming (a)-(d) as listed here, rules out a larger class
-of $m$.
+of $m$. \cite{KochenSpecker}
 \end{rem}
@@
 
-Before proceeding we note, however, that QM can enforce \emph{sequential multiplicativity}. This result will be used to assess accuracy of any hidden variable model we might propose.
+Before proceeding we note, however, that QM can enforce \emph{sequential multiplicativity}. This result will be used to assess accuracy of any HV model we might propose.
 \begin{prop*}
@@
 \end{eqnarray*}
-Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
-from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
-for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
+Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $, from completeness.
+If we consider $\left|\mathbf{b}\right\rangle $s for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
 However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
-$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
-then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
-is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
-the required relation. That completes the proof.
+$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $, then nothing can be said.
+We can thus conclude that $\left|\psi\right\rangle $ is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy the required relation.
+That completes the proof.
 \end{proof}
-It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
-are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
-eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
-must always hold.
+It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$ are just $\pm\hat{\mathbb{I}}$, it follows that all states are their eigenstates.
+Consequently, for these operators \emph{sequential multiplicativity} must always hold.
 
@@
 
-Let the state of the system
-be $\left|\chi\right\rangle $, defined on a discrete Hilbert space
-(spin like) and we wish to assign a value to an arbitrary operator
-$\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which
-has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
+Let the state of the system be $\left|\chi\right\rangle $, defined on a finite dimensional Hilbert space and we wish to assign a value to an arbitrary observable $\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
 This model has the following postulates: \\
-1. Initial Hidden Variable: Pick a $c\in[0,1]$, from a uniform random
-distribution.\\
-2. Assignment/Prediction: The value assigned to $\hat{A}$ is given
-by finding the smallest $a$ s.t. 
+1. Initial HV: Pick a $c\in[0,1]$, from a uniform random distribution.\\
+2. Assignment/Prediction: The value assigned to $\hat{A}$ is given by finding the smallest $a$ s.t. 
 \[
@@
 viz. we have specified a prediction map, $m(\hat{A})=a$.\\
-3. Update: After measuring an operator, the state must be updated
-(collapsed) in accordance with the rules of QM. This completely specifies
-the sequence map $s$.
+3. Update: After measuring an operator, the state is updated (collapsed) in accordance with the rules of QM. This completely specifies the sequence map $s$.
 
-To see how this works, we restrict ourselves to a single spin case.
-Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $,
-and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
-Now, according to the postulates of this theory, $m(\hat{A})=+1$,
-if $c\le\cos^{2}\theta$, else $\hat{A}$ will be assigned $-1$.
-It follows then, from $c$ being uniformly random in $[0,1]$, that
-the statistics agree with predictions of QM. The reader can convince
-him(her)self that the said scheme works in general. A more interesting
-application of this to the PM situation follows.
+To see how this works, we restrict ourselves to a single spin half particle.
+Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $, and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
+Now, according to the postulates of this theory, $m(\hat{A})=+1$, if $c\le\cos^{2}\theta$ else $\hat{A}$ is assigned $-1$.
+It follows then, from $c$ being uniformly random in $[0,1]$ that the statistics agree with predictions of QM.
+The reader can convince him(her)self that the said scheme works in general.
 
-We can clearly see that the assignment, described by the prediction
-map $m$, is non-contextual since given an operator and a state (+
-the hidden variable), the value is uniquely assigned. The map $m$
-is non-multiplicative which will be clarified by the following.
+Note that the assignment, described by the prediction map $m$, is non-contextual since given an operator and a state (+ the HV), the value is uniquely assigned.
+The map $m$ is, however, non-multiplicative which is clarified by the following non-trivial example.
 \begin{example}
-{[}C-ingle model applied to the Peres Mermin situation{]} We apply
-the C-ingle model to the Peres Mermin situation discussed earlier.
-\begin{comment}
-We construct a simplified hidden variable model for the Peres Mermin
-situation (TODO: Add as a test of contextuality?) and explicitly show
-that the associated prediction map $m$ is non-multiplicative. We
-subsequently show that this model is a special case of the C-ingle
-model. 
-\end{comment}
-{} For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
-Say from a uniform random distribution we obtained $c=0.4$. To arrive
-at the assignments, note that $\left|00\right\rangle $ is an eigenket
-of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
-Thus, in the first iteration, all these should be assigned their respective
-eigenvalues. The remaining operators must be assigned $-1$ as one
-can readily verify by explicitly finding the smallest $a$ as described
-in postulate 2 of the model (see \eqref{toyModel}). Two remarks are
-in order. First, this model is manifestly \emph{non-multiplicative},
-for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
-where the subscript has been introduced to index the iteration. More
-precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$
-where the complete state $\left[\left|\psi_{1}\right\rangle \right]$
-implicitly refers to both the quantum state $\left|00\right\rangle $
-and the hidden variable $c=0.4$. Second, we must impose \emph{sequential
-multiplicativity} as a consistency check of the model, which in particular
-entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
-where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$,
-$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
-$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are
-obtained from postulate 3. Note that for each iteration, a new hidden
-variable is generated. To illustrate \emph{sequential multiplicativity},
-we must choose to measure $\hat{A}_{33}$. According to step 4, since
-$\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the
-final state remains $\left|00\right\rangle $. 
+C-ingle model applied to the Peres Mermin situation: For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
+Say from a uniform random distribution we obtained $c=0.4$.
+To arrive at the assignments, note that $\left|00\right\rangle $ is an eigenket of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
+Thus, in the first iteration, all these should be assigned their respective eigenvalues.
+The remaining operators must be assigned $-1$ as one can readily verify by explicitly finding the smallest $a$ as described in postulate 2 of the model (see \eqref{toyModel}).
+Two remarks are in order.
+First, this model is manifestly \emph{non-multiplicative}, for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$, where the subscript has been introduced to index the iteration.
+More precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$ where the complete state $\left[\left|\psi_{1}\right\rangle \right]$ implicitly refers to both the quantum state $\left|00\right\rangle $ and the HV $c=0.4$.
+Second, we must impose \emph{sequential multiplicativity} as a consistency check of the model, which in particular entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$, where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$, $m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
+$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are obtained from postulate 3.
+Note that for each iteration, a new HV is generated.
+To illustrate \emph{sequential multiplicativity}, we must choose to measure $\hat{A}_{33}$.
+According to step 3, since $\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the final state remains $\left|00\right\rangle $.
 \end{example}
@@
 which should be evident from the previous exercise. For the final
-step we choose to measure $\hat{p}=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
+step we choose to measure $\hat{p}:=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
 to proceed with sequentially measuring $\hat{C}_{3}$. To simplify
@@
 
-Recall that contextuality in Bohmian Mechanics arises from the mapping
-between an operator and the experimental setup. Consider the following
-proposition.
+Since QM yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM.
+HV theories do precisely this and we have at our disposal the heretic theory of Bohm.
+Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$.
+The construction is such that the particles are guided by the wavefunction.
+Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `HV').
+The essence of Bohmian Mechanics relevant here can be captured by the following theorem.
+
+\begin{defn}
+(a) the set of all experimental setups is denoted by $\mathcal{E}$, (b) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$.
+\end{defn}
+
+\begin{thm}
+$\exists$ a (Bohmian) map $m_{B}:\hat{\mathcal{H}},[\mathcal{H}],\mathcal{E}\to\mathbb{R}$, and a sequence map $s$, s.t.
+if $m_{B}$ \& $s$ are assumed to describe the outcomes of measurements \& the resultant state respectively, then they are consistent with all predictions of QM.
+\end{thm}
+Observe that given a Stern-Gerlach setup and the initial conditions (position \& wavefunction of the particle), according to the theorem, Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$) of the particle.
+Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$ and that the measurement outcome was spin up.
+Interestingly, it has be shown that if the direction of the magnetic field gradient is flipped while everything else is unchanged, the measurement outcome will now be spin down \cite{Detlef}.
+This emphasises the fact that $m_{B}$ is not a prediction map.
+More importantly it entails that $m_{B}$ is contextual.
+It must be stressed, however, that the contextuality in this case is not a statement about the context in terms of compatible observables.
+Here no two observables are compatible (excluding identity).
+Contextuality in Bohmian Mechanics arises from the mapping between an operator and the experimental setup. Consider, however, the following proposition.
 \begin{lem}
-For discrete $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$.\end{lem}
+For finite dimensional $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$. \label{lem:OpeExp} (See \ref{proofs})
+\end{lem}
+The proof of this proposition can be motivated by a simple construction.
+Consider that the system of interest are spin half particles.
+To measure spin along any direction, there are two directions along which the magnetic field gradient can be set (as was discussed in the introduction).
+The experimentalist agrees to always use a specific direction, thereby mapping an operator to an experimental setup uniquely.
+Given this, one can immediately derive a consistent non-multiplicative prediction map $m$.
+\begin{prop}
+The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$, we call `Bohmian prediction map'.
+\end{prop}
 \begin{proof}
-To describe an experimental setup corresponding to a measurement,
-we use a measuring particle (mass $m_{L}$, say). It is made to interact
-with the system for a short duration appropriately and subsequently
-we measure the resultant position of the particle, to learn about
-the value of the observable of interest. Say for instance, we wish
-to measure the observable $\hat{L}$, then the required interaction
-Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
-Here the first operator acts on the system and second (after the tensor
-product symbol) acts on the measuring particle. $a$ quantifies the
-interaction strength. {[}TODO: check this{]} It has dimensions of
-frequency, if $L$ has dimensions of length. Let us assume that the
-system in the state $\left|\psi\right\rangle $. Then it is known
-that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $,
-where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with
-eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but
-its removal doesn't cause any significant difficulty). $\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $,
-where 
-\[
-\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
-\]
- and $\left|\varphi\right\rangle $ is the state of the measuring
-particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
-If $t$ is very small, and $a$ very large, s.t. $at=\lambda$ is
-a finite number, then one can neglect the free evolution, $\nabla^{2}t$
-terms compared to $\hat{H}_{\text{int}}t$. We then have 
-\begin{eqnarray*}
-\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
-\end{eqnarray*}
-where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
-This interaction, effectively entangles the measuring particle, with
-the possible `outcomes', eigenstates of the observable $\hat{L}$
-of interest. If $\sigma\ll\lambda l$, then according to QM itself,
-a position measurement of the measuring particle, would correspond,
-in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to
-which the system will collapse. Therefore, given an observable, one
-can construct the aforesaid experiment to measure its value. We have,
-in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
+$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.
 \end{proof}
-The proof of this proposition can also be motivated by a simple construction.
-Consider that the system of interest are spin half particles. To measure
-spin along any direction, there are two directions along which the
-magnetic field gradient can be set (as was discussed in the introduction).
-The experimentalist agrees to always use a specific direction, thereby
-mapping an operator to an experimental setup uniquely. Given this,
-one can immediately derive a consistent non-multiplicative prediction
-map $m$.
 \begin{prop}
-The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$,
-we call `Bohmian prediction map'.\end{prop}
+The Bohmian prediction map, $m$ must be non-multiplicative.
+\end{prop}
 \begin{proof}
-$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.\end{proof}
-\begin{prop}
-The Bohmian prediction map, $m$ must be non-multiplicative.\end{prop}
-\begin{proof}
-Since Bohmian Mechanics is consistent with all predictions of QM,
-the Bohmian prediction map $m$ must also be. According to \thmref{KS},
-$m$ must be non-multiplicative.
+Since Bohmian Mechanics is consistent with all predictions of QM, the Bohmian prediction map $m$ must also be. According to \thmref{KS}, $m$ must be non-multiplicative.
 \end{proof}
 
-\section{Implications \label{sec:implications}}
+\section{Concluding Remarks \label{sec:implications}}
 
@@
 \begin{defn}
-A theory/model/map is \emph{local} iff two spatially distinct points
-can not be influenced instantaneously.
+A theory/model/map is \emph{local} iff two spatially distinct points can not be influenced instantaneously.
 \end{defn}
@@
 \begin{prop}
-A prediction map $m$ consistent with QM must be non-local.\end{prop}
-\begin{proof}
-{[}Bell's{]} Formally it is clear, since a violation of Bell's inequality
-implies non-locality. Consequently, any consistent completion of QM,
-will be non-local. More insight can be gained, although some care
-is needed. The notion of compatible observables is that commuting
-observables don't disturb each other and can be simultaneously known.
-While the statement is not precisely stated, we only need to note
-that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$,
-for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$
-are defined as before. In words, this means that to measure $\hat{C}$,
-one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
-A multiplication of the values obtained, can be taken to be the value
-a measurement of $\hat{C}$ yields. This can be verified by measuring
-$\hat{C}$ subsequently. The Bell scenario offers an interesting freedom,
-by restricting the form of $\hat{B}_{i}$. To evaluate $\left\langle \hat{B}\right\rangle $,
-one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
-From the compatibility argument, we need to find the average value
-of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$,
-viz.
-$\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
-So far, the statements were general. Now we assume that our theory
-is non-multiplicative (and non-contextual). A consistent theory (with
-QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
-However, if the particles are taken far away, then the only way the
-theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$
-for example), is if the theory is non-local. Locality will entail
-that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since
-the information about which observable was measured first, can't be
-propagated instantaneously. We see therefore that non-locality arises
-quite naturally in consistent non-multiplicative theories.
-\end{proof}
+A prediction map $m$ consistent with QM must be non-local \label{prop:predMapNonLocal} (see \ref{proofs} for details).
+\end{prop}
 
 \begin{prop}
-{[}can perhaps be skipped{]} Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$,
-corresponding to two particles. $\mathcal{H}_{A}$ and $\mathcal{H}_{B}$
-are discrete (correspond to spins say). Let mutually commuting observables
-$\hat{B}_{i}$ be s.t. $\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$
-or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where
-$A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$
-are arbitrary observables. If locality is assumed, then a prediction
-map $m$ and it's associated sequence map $s$ must be s.t. over these
-observables, sequential multiplicativity and multiplicativity become
-identical.
+Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$, corresponding to two particles.
+$\mathcal{H}_{A}$ and $\mathcal{H}_{B}$ are finite dimensional.
+Let mutually commuting observables $\hat{B}_{i}$ be s.t.
+$\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$ or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where $A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$ are arbitrary observables.
+If locality is assumed, then a prediction map $m$ and it's associated sequence map $s$ must be s.t.
+over these observables, sequential multiplicativity and multiplicativity become identical.
 \end{prop}
@@
 
-TODO: Complete this part.
+TODO: Discuss and complete.
 \begin{appendix}
-\section{Proofs of the two theorems}
-For \thmref{det} we have the following proofs.
+\section{Selected Proofs \label{proofs}}
+Proofs of \thmref{det}:
 \begin{proof}
@@
 \begin{proof}
-Bell construction ($\left|\mathcal{H}\right|\ge4$): Consider an operator
-$\hat{B}:=a_{1}\otimes b_{1}+a_{2}\otimes b_{1}+a_{1}\otimes b_{2}-a_{2}\otimes b_{2}$
-s.t. $-1\le\hat{a}_{i},\hat{b}_{j}\le1$ $\forall\,i,j\in\{1,2,3,4\}$
-(which means that the spectrum of $\hat{a}$ and $\hat{b}$ are bounded
-above and below). If we assume that a map $m$ of the aforesaid type
-exists, then it can be shown that $\left\langle \hat{B}\right\rangle \le2$.
-To see this, consider $\hat{A}_{1}=\hat{a}_{1}\otimes\hat{\mathbb{I}}$
-and $\hat{A}_{2}=\hat{\mathbb{I}}\otimes\hat{b}_{1}$, so that if
-$\hat{C}:=\hat{A}_{1}\hat{A}_{2}$ then property (2) entails that
-$m(\hat{C})=m(\hat{A}_{1})m(\hat{A}_{2})$, viz. $m(\hat{a}_{1}\otimes\hat{b}_{1})=m(\hat{a}_{1}\otimes\hat{\mathbb{I}})m(\hat{\mathbb{I}}\otimes\hat{b}_{1})$.
-Note that $m(\hat{*})$, may depend on the state $\left|\psi\right\rangle $
-and the hidden variables%
-\begin{comment}
-, where $\hat{*}$ is taken to represent $\hat{B}_{k}$s which can
-be generalised to all $\hat{a}_{i}$s and $\hat{b}_{j}$s
-\end{comment}
-. Therefore, we average over multiple measurements, which corresponds
-to averaging over the hidden variables.
+Bell construction ($\left|\mathcal{H}\right|\ge4$) \cite{Bell1964}: Consider an operator $\hat{B}:=a_{1}\otimes b_{1}+a_{2}\otimes b_{1}+a_{1}\otimes b_{2}-a_{2}\otimes b_{2}$ s.t.
+$-1\le\hat{a}_{i},\hat{b}_{j}\le1$ $\forall\,i,j\in\{1,2,3,4\}$ (which means that the spectrum of $\hat{a}$ and $\hat{b}$ are bounded above and below).
+If we assume that a map $m$ of the aforesaid type exists, then it can be shown that $\left\langle \hat{B}\right\rangle \le2$.
+To see this, consider $\hat{A}_{1}=\hat{a}_{1}\otimes\hat{\mathbb{I}}$ and $\hat{A}_{2}=\hat{\mathbb{I}}\otimes\hat{b}_{1}$, so that if $\hat{C}:=\hat{A}_{1}\hat{A}_{2}$ then property (2) entails that $m(\hat{C})=m(\hat{A}_{1})m(\hat{A}_{2})$, viz.
+$m(\hat{a}_{1}\otimes\hat{b}_{1})=m(\hat{a}_{1}\otimes\hat{\mathbb{I}})m(\hat{\mathbb{I}}\otimes\hat{b}_{1})$.
+Note that $m(\hat{*})$, may depend on the state $\left|\psi\right\rangle $ and the HVs.
+Therefore, we average over multiple measurements, which corresponds
+to averaging over the HVs.
 This is expressed by $\left\langle m(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
 One can repeat this argument for each term in $\left\langle \hat{B}\right\rangle $.
-Using the fact that $-1\le m(\hat{*})\le1$, and that the extrema
-will occur only at the extreme values of $m$, one can plugin $\pm1$
-for each $\left\langle m(\hat{*})\right\rangle $ to obtain $\left\langle \hat{B}\right\rangle \le2$.
-Quantum mechanically, one can show that $\left\langle \hat{B}\right\rangle =2\sqrt{2}$
-for the state $\left|\psi\right\rangle =\left(\left|+-\right\rangle -\left|-+\right\rangle \right)/\sqrt{2}$,
-where $\hat{\sigma}_{x}\left|\pm\right\rangle =\pm\left|\pm\right\rangle $,
-and $\hat{\sigma}_{x,y,z}$ are the Pauli matrices, given in the z-basis
-as 
-\[
+Using the fact that $-1\le m(\hat{*})\le1$, and that the extrema will occur only at the extreme values of $m$, one can plugin $\pm1$ for each $\left\langle m(\hat{*})\right\rangle $ to obtain $\left\langle \hat{B}\right\rangle \le2$.
+Quantum mechanically, one can show that $\left\langle \hat{B}\right\rangle =2\sqrt{2}$ for the state $\left|\psi\right\rangle =\left(\left|+-\right\rangle -\left|-+\right\rangle \right)/\sqrt{2}$,
+where $\hat{\sigma}_{x}\left|\pm\right\rangle =\pm\left|\pm\right\rangle $, and $\hat{\sigma}_{x,y,z}$ are the Pauli matrices, given in the z-basis as  \[
 \hat{\sigma}_{x}\doteq\left[\begin{array}{cc}
@@
 \end{array}\right].
-\]
-The observables are $\hat{a}_{1}=\hat{\sigma}_{z}$ and $\hat{a}_{2}=\hat{\sigma}_{x}$,
-while $\hat{b}_{1}=-\frac{\hat{\sigma}_{z}+\hat{\sigma}_{x}}{\sqrt{2}}$
-and $\hat{b}_{2}=\frac{\hat{\sigma}_{z}-\hat{\sigma}_{x}}{\sqrt{2}}$.
-Since quantum mechanics violates the inequality, $\left\langle \hat{B}\right\rangle \le2$,
-we conclude that the map $m$ can not simultaneously exist and be
-consistent with QM.
+\] The observables are $\hat{a}_{1}=\hat{\sigma}_{z}$ and $\hat{a}_{2}=\hat{\sigma}_{x}$, while $\hat{b}_{1}=-\frac{\hat{\sigma}_{z}+\hat{\sigma}_{x}}{\sqrt{2}}$ and $\hat{b}_{2}=\frac{\hat{\sigma}_{z}-\hat{\sigma}_{x}}{\sqrt{2}}$.
+Since QM violates the inequality, $\left\langle \hat{B}\right\rangle \le2$, we conclude that the map $m$ can not simultaneously exist and be consistent with QM.
 \end{proof}
@@
 \begin{proof}
-GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider three
-observers with one spin half particle each. Each observer can measure two properties,
-call them X and Y, with outcomes $\pm1$. The associated operators
-are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$. The state of the
-system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $
-and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$,
-$\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
-$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
-and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
-A measurement of $\hat{A}$ would correspond to measurement of property
-$X,\,Y$ and $Y$ by the three observers respectively. For a map $m$
-consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
+GHZ construction ($\left|\mathcal{H}\right|\ge6$) \cite{GHZ}: Consider three observers with one spin half particle each.
+Each observer can measure two properties, call them X and Y, with outcomes $\pm1$.
+The associated operators are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$.
+The state of the system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $ and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$, $\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $, $\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$ and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
+A measurement of $\hat{A}$ would correspond to measurement of property $X,\,Y$ and $Y$ by the three observers respectively.
+For a map $m$ consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
 Property (b) of the map $\implies1=m(\hat{A}\hat{B}\hat{C})=m(\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\hat{\sigma}_{x}\hat{\sigma}_{y}\otimes\hat{\sigma}_{x})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{y}^{(2)}\hat{\sigma}_{x}^{(2)}\hat{\sigma}_{y}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{x}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{D}\equiv\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}),$
-where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$
-and so on. It must be stressed that although $\hat{A}$, $\hat{B}$
-and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$
-do not. We used property (b) over both these sets of operators in
-the previous step. Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $,
-$\implies m(\hat{D})=-1$ which yields a contradiction. We therefore
-conclude that no $m$ with the said properties exists which is consistent
-with all predictions of QM.
+where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$ and so on.
+It must be stressed that although $\hat{A}$, $\hat{B}$ and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$ do not.
+We used property (b) over both these sets of operators in the previous step.
+Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $, $\implies m(\hat{D})=-1$ which yields a contradiction.
+We therefore conclude that no $m$ with the said properties exists which is consistent with all predictions of QM.
 \end{proof}
 
-For \thmref{KS} the proofs are as below.
+Proofs of \thmref{KS}:
 \begin{proof}
-Bell construction ($\left|\mathcal{H}\right|\ge4$): The same proof
-as the one presented earlier goes through here also since $[A_{1},A_{2}]=0$.
+Kochen Specker ($\left|\mathcal{H}\right|\ge3$) \cite{KochenSpecker}: The original proof given by is rather involved.
+Here we will satisfy ourselves with assuming its validity and applying our constructions to the aforesaid proof.
 \end{proof}
@@
 \begin{proof}
-Generalized GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider
-again, three observers with one quantum particle each. Each observer
-can measure the properties corresponding to $\hat{\sigma}_{x}$ and
-$\hat{\sigma}_{y}$ of his/her particle. The quantum state of these
-particles is also the same as before, $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $.
-We define as earlier $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$
-$\implies\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
-$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
-and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
+Bell construction ($\left|\mathcal{H}\right|\ge4$): The same proof as the one presented earlier goes through here also since $[A_{1},A_{2}]=0$.
+\end{proof}
+
+\begin{proof}
+Generalized GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider again, three observers with one quantum particle each.
+Each observer can measure the properties corresponding to $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$ of his/her particle.
+The quantum state of these particles is also the same as before, $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $.
+We define as earlier $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ $\implies\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $, $\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$ and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
 Consider in addition the following operators, represented by $\hat{H}_{ij}$.
@@
 where from property (b) it follows that $m(\hat{A})=m(\hat{H}_{11})m(\hat{H}_{12})m(\hat{H}_{13})$.
-Note that $[\hat{H}_{ij},\hat{H}_{ik}]=0$, viz. the operators along
-a row commute. To be consistent with QM, $m(\hat{A})=+1$ (similarly
-for row 2 and 3). $m(\hat{D})=-1$ imposes that the product $m(\hat{H}_{41})m(\hat{H}_{42})m(\hat{H}_{43})$,
-row 4, must be $-1$. Using the notation $m(\hat{H}_{ij})=H_{ij}$,
-we can start with the first case. For the last row to yield $-1$,
-we must have either one $-1$ assignments or three $-1$ assignments.
-Let us look at the first case. Without loss of generality, we can
-assume that $H_{41}=H_{42}=+1$ and $H_{43}=-1$. Further, $H_{11}=H_{41}$,
-$H_{22}=H_{42}$ and $H_{33}=H_{43}$ by construction (see below).
+Note that $[\hat{H}_{ij},\hat{H}_{ik}]=0$, viz.
+the operators along a row commute.
+To be consistent with QM, $m(\hat{A})=+1$ (similarly for row 2 and 3).
+$m(\hat{D})=-1$ imposes that the product $m(\hat{H}_{41})m(\hat{H}_{42})m(\hat{H}_{43})$, row 4, must be $-1$.
+Using the notation $m(\hat{H}_{ij})=H_{ij}$, we can start with the first case.
+For the last row to yield $-1$, we must have either one $-1$ assignments or three $-1$ assignments.
+Let us look at the first case.
+Without loss of generality, we can assume that $H_{41}=H_{42}=+1$ and $H_{43}=-1$.
+Further, $H_{11}=H_{41}$, $H_{22}=H_{42}$ and $H_{33}=H_{43}$ by construction (see below).
 \[
@@
 \end{array}\right].
-\]
-Next, one must ensure that the first row yields $+1$ which requires
-us to either set $H_{12}=H_{13}$ to $-1$ or $+1$. Let us write
-this as $H_{12}=H_{13}=\pm1$ which would entail that $H_{23}=\pm1$
-and $H_{32}=\pm1$. {[} Note that the notation implies that when we
-choose $+1$, all these are $+1$ and when we choose $-1$, all are
-$-1$. We are not allowed to set, say $H_{12}=-1$ and $H_{13}=+1$.
+\] Next, one must ensure that the first row yields $+1$ which requires us to either set $H_{12}=H_{13}$ to $-1$ or $+1$.
+Let us write this as $H_{12}=H_{13}=\pm1$ which would entail that $H_{23}=\pm1$ and $H_{32}=\pm1$.
+{[} Note that the notation implies that when we choose $+1$, all these are $+1$ and when we choose $-1$, all are $-1$.
+We are not allowed to set, say $H_{12}=-1$ and $H_{13}=+1$.
 {]} For the second row to be $+1$, we conclude that $H_{21}=\pm1$.
-This entails, in turn, that $H_{31}=\pm1$. We now note that the third
-row has become $-1$ whereas according to QM, it must be $+1$. It
-is left upto the reader to see that similar reasoning also yields
-results in inconsistencies with QM. This completes the proof.
+This entails, in turn, that $H_{31}=\pm1$.
+We now note that the third row has become $-1$ whereas according to QM, it must be $+1$.
+It is left upto the reader to see that similar reasoning also yields results in inconsistencies with QM.
+This completes the proof.
+\end{proof}
+
+Proof of \propref{predMapNonLocal}:
+\begin{proof}
+{[}Adapted from Bell's proof \cite{Bell1964}{]} Formally it is clear, since a violation of Bell's inequality implies non-locality.
+Consequently, any consistent completion of QM, will be non-local.
+More insight can be gained, although some care is needed.
+The notion of compatible observables is that commuting observables don't disturb each other and can be simultaneously known.
+While the statement is not precisely stated, we only need to note that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$, for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$ are defined as before.
+In words, this means that to measure $\hat{C}$, one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
+A multiplication of the values obtained, can be taken to be the value a measurement of $\hat{C}$ yields.
+This can be verified by measuring $\hat{C}$ subsequently.
+The Bell scenario offers an interesting freedom, by restricting the form of $\hat{B}_{i}$.
+To evaluate $\left\langle \hat{B}\right\rangle $, one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
+From the compatibility argument, we need to find the average value of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$, viz.
+$\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
+So far, the statements were general.
+Now we assume that our theory is non-multiplicative (and non-contextual).
+A consistent theory (with QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
+However, if the particles are taken far away, then the only way the theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$ for example), is if the theory is non-local.
+Locality will entail
+that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since the information about which observable was measured first, can't be propagated instantaneously.
+We see therefore that non-locality arises quite naturally in consistent non-multiplicative theories.
+\end{proof}
+
+Proof of \lemref{OpeExp}:
+\begin{proof} Adapted from Bohm's work \cite{Bohm2}\\
+To describe an experimental setup corresponding to a measurement, we use a measuring particle (mass $m_{L}$, say).
+It is made to interact with the system for a short duration appropriately and subsequently we measure the resultant position of the particle, to learn about the value of the observable of interest.
+Say for instance, we wish to measure the observable $\hat{L}$, then the required interaction Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
+Here the first operator acts on the system and second (after the tensor product symbol) acts on the measuring particle.
+$a$ quantifies the interaction strength.
+{[}TODO: check this{]} It has dimensions of frequency, if $L$ has dimensions of length.
+Let us assume that the system in the state $\left|\psi\right\rangle $.
+Then it is known that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $, where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but its removal doesn't cause any significant difficulty).
+$\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $, where  \[
+\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
+\]  and $\left|\varphi\right\rangle $ is the state of the measuring particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
+If $t$ is very small, and $a$ very large, s.t.
+$at=\lambda$ is a finite number, then one can neglect the free evolution, $\nabla^{2}t$ terms compared to $\hat{H}_{\text{int}}t$.
+We then have
+\begin{eqnarray*}
+\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
+ & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
+ & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
+\end{eqnarray*}
+where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
+This interaction, effectively entangles the measuring particle, with the possible `outcomes', eigenstates of the observable $\hat{L}$ of interest.
+If $\sigma\ll\lambda l$, then according to QM itself, a position measurement of the measuring particle, would correspond, in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to which the system will collapse.
+Therefore, given an observable, one can construct the aforesaid experiment to measure its value.
+We have, in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
 \end{proof}

### 2016-07-07 finalPaper.tex
Fixed some more typographical issues; section name etc.

@@
 
+\newref{sec}{name=Section~}
+\newref{ssec}{name=Subsection~}
+
 \RS@ifundefined{subref}
@@
 \RS@ifundefined{thmref}
-  {\def\RSthmtxt{theorem~}\newref{thm}{name = \RSthmtxt}}
+  {\def\RSthmtxt{Theorem~}\newref{thm}{name = \RSthmtxt}}
   {}
 \RS@ifundefined{lemref}
-  {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
+  {\def\RSlemtxt{Lemma~}\newref{lem}{name = \RSlemtxt}}
   {}
 \RS@ifundefined{propref}
-  {\def\RSproptxt{proposition~}\newref{prop}{name = \RSproptxt}}
+  {\def\RSproptxt{Proposition~}\newref{prop}{name = \RSproptxt}}
   {}
@@
 \begin{abstract}
-We propose a non-contextual hidden variable model, consistent with all predictions of quantum mechanics (QM).
+We propose a non-contextual hidden variable model, consistent with all predictions of Quantum Mechanics (QM).
 We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of QM.
-Motivated by consistency requirements between bohmian mechanics and the said theorems, we provide an alternative view.
+Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view.
 This is accomplished by identifying a new classical property, we call `multiplicativity'.

### 2016-07-10 preReleases/version4arv/finalPaper.tex
added arvind sirs version (to facilitate printing and for record keeping)

\documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=2cm}
\setcounter{secnumdepth}{3}
\usepackage{verbatim}
\usepackage{refstyle}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{esint}
\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
\AtBeginDocument{\providecommand\lemref[1]{\ref{lem:#1}}}
\AtBeginDocument{\providecommand\propref[1]{\ref{prop:#1}}}
\AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
\AtBeginDocument{\providecommand\figref[1]{\ref{fig:#1}}}
\AtBeginDocument{\providecommand\secref[1]{\ref{sec:#1}}}
\AtBeginDocument{\providecommand\ssecref[1]{\ref{ssec:#1}}}

\newref{sec}{name=Section~}
\newref{ssec}{name=Subsection~}

\RS@ifundefined{subref}
  {\def\RSsubtxt{section~}\newref{sub}{name = \RSsubtxt}}
  {}
\RS@ifundefined{thmref}
  {\def\RSthmtxt{Theorem~}\newref{thm}{name = \RSthmtxt}}
  {}
\RS@ifundefined{lemref}
  {\def\RSlemtxt{Lemma~}\newref{lem}{name = \RSlemtxt}}
  {}
\RS@ifundefined{propref}
  {\def\RSproptxt{Proposition~}\newref{prop}{name = \RSproptxt}}
  {}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
  \theoremstyle{definition}
  \newtheorem{defn}[thm]{\protect\definitionname}
  \theoremstyle{remark}
  \newtheorem{rem}[thm]{\protect\remarkname}
  \theoremstyle{plain}
  \newtheorem*{prop*}{\protect\propositionname}
  \theoremstyle{plain}
  \newtheorem{lem}[thm]{\protect\lemmaname}
  \theoremstyle{plain}
  \newtheorem{prop}[thm]{\protect\propositionname}
  \theoremstyle{definition}
  \newtheorem{example}[thm]{\protect\examplename}
  \theoremstyle{definition}
  \newtheorem{notn}[thm]{\protect\notationname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{xcolor}
%\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\makeatother

\usepackage{babel}
  \providecommand{\definitionname}{Definition}
  \providecommand{\examplename}{Example}
  \providecommand{\lemmaname}{Lemma}
  \providecommand{\propositionname}{Proposition}
  \providecommand{\remarkname}{Remark}
  \providecommand{\theoremname}{Theorem}
  \providecommand{\notationname}{Notation}
\setlength{\itemindent}{0pt}
\begin{document}
\title{A non-contextual hidden variable model for quantum mechanics}
\author{Atul Singh Arora}
\email{ms11003@iisermohali.ac.in}
\selectlanguage{british}%
\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\author{Arvind}
\email{arvind@iisermohali.ac.in}
\selectlanguage{british}%
\affiliation{Indian Institute of Science Education
and Research (IISER), Mohali}
\begin{abstract}
We propose a non-contextual hidden variable model,
consistent with all predictions of quantum
mechanics (QM).  A careful scrutiny of
consistency requirements between any hidden
variable model and  quantum mechanics and the
corresponding no-go theorems, leads us to the
conclusion that the notion of contextuality is not
a necessary feature of QM.  The alternative view
that emerges, hinges on identifying a new classical
property, which we call ``multiplicativity''.  It turns
out that, by relaxing this condition of
``multiplicativity'' on hidden variable models, they
can be made  consistent with QM.  Advantages of
this view are illustrated by considering the
implications of non-multiplicativity to locality,
entanglement, superposition, and  apparent
contextuality. 
\end{abstract}
\pacs{}
\maketitle
\section{Introduction}
\label{introduction}
Quantum mechanics has been one of the most
successful theories in physics so far; however,
there has not yet been a final word on its
completeness and interpretation~\cite{??}.
Einstein's~\cite{EinsteinEPR} work on the
incompleteness of QM and the subsequent seminal
work of Bell~\cite{Bell1964}, assessing the
compatibility of a more complete model involving
hidden variables (HV) and locality with QM, has
provided deep insights into  how the quantum world
differs from its classical counterpart.  In recent
times, these insights have been of pragmatic
utility in the areas of quantum information
processing, where EPR pairs are fundamental motifs
of entanglement~\cite{Ekert,PironioRndmnssCrtfcn}.
The work of  Kochen Specker~\cite{KochenSpecker}
and Gleason et.
al.~\cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
broadened the schism between  HV models and QM.
They showed that it was contextuality and not
non-locality which was at the heart of this schism
and the incompatibility between HV models and QM
can arise even for a single quantum system.
Contextuality has thus been identified as a
fundamental non-classical feature of the quantum
world and experiments have also been propsed and
conducted to this effect~\cite{SimonContExpProp,
HuangContExp,YangContExp,HasegawaContExp}.
Contextuality, on the one hand has led to
investigations on the foundational aspects of
QM~\cite{PawelCntxClsscl,?????}, and on the other
hand has been harnessed for computation and
cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt,??}.
Quantitative measures of contextuality based on
memory~\cite{MatthiasCntxMmry} have also been used
to demonstrate the completeness of
QM~\cite{CabelloMmryQM}.  However, not all HV
models are incompatible with QM, and a very
important case in point is  Bohm's model based on
precise trajectories for quantum
systems~\cite{Bohm1,Bohm2}.

A closer look at the aforesaid no-go theorems
reveals that contextuality is in fact not a
necessary feature of QM (see \figref{block}).
While this has been shown earlier by taking
disturbances due to measurements into
consideration~\cite{NoContextuality,LaCourNoCntx},
we take a different approach and construct a toy
HV model consistent with QM.  The predictions of
the non-contextual toy model that we construct
(which is a special case of a certain class of
models) match with those of QM for systems
described by arbitrary finite-dimensional Hilbert
spaces.  \begin{figure}[h]
\includegraphics[width=\columnwidth]{block1}
\caption{Non-contextuality is not inconsistent
with QM} \label{fig:block}\end{figure} The
algebraic constraints obeyed by quantum
observables may not necessarily be obeyed by the
predictions of an HV model at the level of
individual outcomes.  Those HV models that obey
such algebraic constraints possess a special
property which we call `multiplicativity'.  By
enlarging the scope of HV models to include
non-multiplicative models, we construct an
explicit non-contextual model consistent with QM.
The re-examination of the very proof of
`contextuality'  is used to illustrate
non-multiplicativity, which we propose as an
intrinsic quantum feature as a possible
alternative to contextuality.

{\noindent \bf Notation~:} (a) $\psi\in\mathcal{H}$ 
represents a pure quantum mechanical
state of the system in the Hilbert space
$\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined
to mean the set of Hermitian 
observables for the system, (c)
$[\mathcal{H}]$ is defined to mean
$(\mathcal{H},\,\mathbb{R}^{\otimes})$, which
represents the state of the system including HVs,
(d) $[\psi]\in[\mathcal{H}]$ will represent the
state of the system, including HVs, (e) a
prediction map is
$m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$,
(f) a sequence map is
$s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$,
(g) $f$ is an arbitrary map from $\{
\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
\} \to \hat{\mathcal{H}}$ constructed using
multiplication and addition of the observables,
and multiplication with complex
numbers\footnote{Strictly, the map $f$ would
depend on the operators to ensure preservation of
Hermiticity; thus a given $f$ will be defined only
for a subset of $\{
\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
\}$.}, (h) $\tilde{f}$ is a map constructed by
replacing observables in $f$ with real numbers.

\begin{defn} A theory is non-contextual, if it
provides a map $m: \{
\hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$
to explain measurement outcomes. A theory which is
not non-contextual is contextual.\end{defn}

\begin{rem} The notion of non-contextuality may be
extended to maps. A map is non-contextual if it is
of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}]
\} \to\mathbb{R}$; prediction maps for individual
observables are non-contextual by construction.  
\end{rem}
\begin{rem}
Broader definitions in the literature have been
suggested which declare a larger set of theories
as non-contextual. For our purposes however, this
restricted definition will suffice. The term
contextual is used to suggest that the value an
operator takes might depend on which other
compatible observable it is being  measured with.
\end{rem}

Before we re-examine the result of Kochen and
Specker~\cite{KochenSpecker} that non-contextual
models cannot be compatible with quantum
mechanics, and show that multiplicativity can provide an
alternative to contextuality, we define
multiplicativity more precisely.
\begin{defn}
A prediction map $m$ is \emph{multiplicative} iff
\begin{align*} &
m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])
= \\ & \tilde
f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots
m(\hat{B}_{N},[\psi])), \end{align*}
where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
arbitrary mutually commuting observables and
$[\psi]\in[\mathcal{H}]$. A
\emph{non-multiplicative} map is one that is not
multiplicative.  
\end{defn} 
Note that if $m$ is taken to represent the
measurement outcome (in QM), then for states of
the system which are simultaneous eigenkets of
$\hat{B}_{i}$s, $m$ must clearly be
multiplicative. It is, however, not obvious that
this property must always hold. For example,
consider two spin-half particles in the state 
$\left|1\right\rangle \otimes\left|1\right\rangle
$ written in the computational basis and take
operators 
$\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$
and
$\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$
written in terms of Pauli operators.
We must have $m(\hat{C})=-1$ while
$m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$
independently, according to QM, with probability
half. Here multiplicativity does not seem to hold.
Anti-thetically, it is clear that if one first
measures $\hat{B}_{1}$ and subsequently measures
$\hat{B}_{2}$, then the product of the results
must be $-1$. This is consistent with measuring
$\hat{C}$. To capture this property we define
\emph{sequential multiplicativity} as follows.
\begin{defn} 
A prediction map $m$ is
\emph{sequentially multiplicative} for a given
sequence map $s$, iff \begin{align*}
&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
&\tilde
f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
\end{align*} 
where
$\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{
N! {\rm ~permutations~of~}  k'{\rm s}
\}$, $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
arbitrary mutually commuting observables,
$[\psi_{i}]\in[\mathcal{H}]$ and
$[\psi_{k+1}]\equiv
s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
$\forall\,[\psi_{i}]$.  
\end{defn} 
With these definitions we are now ready to discuss
the `proofs of contextuality'. We first state the
contextuality theorems in our notation:
\begin{thm} 
Let a map
$m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
$m(\hat{\mathbb{I}})=1$, (b)
$m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde
f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$, where
$\hat{A}_{i}$ are arbitrary Hermitian operators.
If $m$ is assumed to describe the outcomes of
measurements, then no $m$ exists which is
consistent with all predictions of
QM\label{thm:det}
\end{thm} 
Here $m$ maybe viewed as a specific
class of prediction maps, that implicitly depends
on the state $[\psi]$. It follows then that the
maps ruled out by the theorem are non-contextual.
The set of maps ruled out, however, can be
enlarged by imposing fewer restrictions on it.
This is achieved by the following theorem.
\begin{thm} Let a map
$m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
$m(\hat{\mathbb{I}})=1$, (b)
$m(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde
f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$, for any
arbitrary function $f$, where $\hat{B}_{i}$ are
mutually commuting Hermitian operators. If $m$ is
assumed to describe the outcomes of measurements,
then no $m$ exists which is consistent with all
predictions of QM. 
\label{thm:KS}
\end{thm}

\begin{proof} Peres Mermin
($\left|\mathcal{H}\right|\ge4$)
\cite{Peres,Mermin}:
For a system composed of two spin-1/2 particles 
consider the following set of operators \[
\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} &
\hat{\sigma}_{x}\otimes\hat{\mathbb{I}} &
\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} &
\hat{\mathbb{I}}\otimes\hat{\sigma}_{y} &
\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} &
\hat{\sigma}_{x}\otimes\hat{\sigma}_{y} &
\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
\end{array}\right] \] which have the property that
all operators along a row (or column) commute and
that the product of rows (or columns) yield
$\hat{R}_{i}=\mathbb{I}$ and
$\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where
$\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. Let us
assume that $m$ exists. From property (b) of the
map, to get $m(\hat{C}_{3})=-1$ (as required by
property (a)), we must have an odd number of $-1$
assignments in the third column. In the remaining
columns, the number of $-1$ assignments must be
even (for each column). Thus, in the entire
square, the number of $-1$ assignments must be
odd. Let us use the same reasoning, but along the
rows. Since each $m(\hat{R}_{i})=1$, we must have
even number of $-1$ assignments along each row.
Thus, in the entire square, the number of $-1$
assignments must be even. We have arrived at a
contradiction and therefore we conclude that our
assumption that a consistent $m$ exists, must be
wrong.  \end{proof}

\begin{rem} One could in principle assume $m$, to
be s.t. (a) $m(\hat{\mathbb{I}})=1$, (b)
$m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for
$\alpha\in\mathbb{R}$, (c)
$m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d)
$m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
to deduce (d')
$m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
and that $m(\hat{B}_{i})\in$ spectrum of
$\hat{B}_{i}$. Effectively then, condition (b)
listed in the theorem is satisfied as a
consequence.  Therefore, assuming (a)-(d) as
listed here, rules out a larger class of $m$.
\cite{KochenSpecker} 
\end{rem} 
It is clear that 
according to
\thmref{KS}, non-contextual maps which are
\emph{multiplicative} must be incompatible with
QM. However, non-contextual maps which are
non-\emph{multiplicative} might be consistent with
QM. We will indeed show this by constructing an
explicit model.

Before proceeding we note, however, that QM can
enforce \emph{sequential multiplicativity}. This
result will be used to assess accuracy of any
proposal of a HV
model.
\begin{prop*} 
Let a QM 
system be in a state, s.t. measurement of
$\hat{C}$ yields repeatable results (same result
each time). Then according to QM, \emph{sequential
multiplicativity} holds, where $\hat{C}\equiv
f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$, and
$\hat{B}_{i}$ are as defined. 
{\color{red} Comment: We need to refer to a specific place
for def}
\end{prop*}
\begin{proof} 
Without loss of generality we can take
$\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$ to be
mutually compatible and a complete set of
operators (Operators can be added to make the set
complete if it not so).
It follows
that $\exists$
$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots
b_{n}^{(l_{n})}\right)\right\rangle $ s.t.
$\hat{B}_{i}\left|\mathbf{b}\right\rangle
=b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
where $l_{i}$ indexes the eigenvalues
corresponding to $\hat{B}_{i}$ and that
$\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle
\left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
{\color{red} Do we need to additional index? $b_j$
can be an index itself}
Let the state of the system
$\left|\psi\right\rangle $ be s.t.
$\hat{C}\left|\psi\right\rangle
=c\left|\psi\right\rangle $. For
the statement to follow, one need only show that
$\left|\psi\right\rangle $ must be made of only
those $\left|\mathbf{b}\right\rangle $s, which
satisfy $c=\tilde
f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots
b_{n}^{(l_{n})})$.  This is the crucial step and
proving this is straightforward. We start with
$\hat{C}\left|\psi\right\rangle
=c\left|\psi\right\rangle $ and take its inner
product with $\left\langle \mathbf{b}\right|$ to
get \begin{eqnarray*} \left\langle
\mathbf{b}\right|\hat{C}\left|\psi\right\rangle  &
= & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\left\langle
\mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})
\left|\psi\right\rangle
& = & c\left\langle \mathbf{b}|\psi\right\rangle
,\\ \tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots
b_{n}^{(l_{n})})\left\langle
\mathbf{b}|\psi\right\rangle  & = & c\left\langle
\mathbf{b}|\psi\right\rangle .  \end{eqnarray*}
Also, we have $\left|\psi\right\rangle
=\sum_{\mathbf{b}}\left\langle
\mathbf{b}|\psi\right\rangle
\left|\mathbf{b}\right\rangle $, from
completeness. If we consider
$\left|\mathbf{b}\right\rangle $s for which
$\left\langle \mathbf{b}|\psi\right\rangle \neq0$,
then we can conclude that indeed $c=\tilde
f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots
b_{n}^{(l_{n})})$. However, when $\left\langle
\mathbf{b}|\psi\right\rangle =0$, viz.
$\left|\mathbf{b}\right\rangle $s that are
orthogonal to $\left|\psi\right\rangle $, then
nothing can be said. We can thus conclude that
$\left|\psi\right\rangle $ is made only of those
$\left|\mathbf{b}\right\rangle $s that satisfy the
required relation. That completes the proof.
\end{proof} 
It is worth noting that in the Peres Mermin
case, where $\hat{R}_{i}$ and $\hat{C}_{j}$ are
just $\pm\hat{\mathbb{I}}$, it follows that all
states are their eigenstates. Consequently, for
these operators \emph{sequential multiplicativity}
must always hold.
%\subsection{C-ingle model | An Explicit
%Construction \label{ssec:cingle}}
We are now ready to describe our explict model.
Let the state of a finite dimensional quantum system
be $\left|\chi\right\rangle $, and we wish to
assign a value to an arbitrary observable 
$\hat{A}=\sum_{a}a\left|a\right\rangle
\left\langle a\right|$, which has 
eigen vectors $\{ \vert
a_j\rangle \}$ and the corresponding ordered eigen
values $\{a_j\}$ such that 
$a_{\rm min}=a_1$
and 
$a_{\rm max}=a_n$

Our model for assigning values have the following
three steps~:
\begin{enumerate}
\item
{\bf Initial HV~:} Pick a number
$c\in[0,1]$, from a uniform random distribution.\
\item
{\bf  
Assignment or Prediction~:}
 The value assigned to
$\hat{A}$ is given by finding the smallest $a$
s.t.  \[
c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle
a'|\chi\right\rangle \right|^{2}, \] viz. we have
specified a prediction map, $m(\hat{A})=a$.
\item
{\bf Update~:} After measuring an operator, the state is
updated (collapsed) in accordance with the rules
of QM. This completely specifies the sequence map
$s$.
\end{enumerate}
To see how this works consider 
single spin half particle in state
$\left|\chi\right\rangle
=\cos\theta\left|0\right\rangle
+\sin\theta\left|1\right\rangle $, and
$\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle
\left\langle 0\right|-\left|1\right\rangle
\left\langle 1\right|$. Now, according to the
postulates of this theory, $m(\hat{A})=+1$, if
the value of randomly generated 
$c\le\cos^{2}\theta$ else $\hat{A}$ is assigned
$-1$. It follows then, from $c$ being uniformly
random in $[0,1]$ that the statistics agree with
predictions of QM. The reader can convince
him(her)self that the said scheme works in
general. {\color{red} Can we give more detail to
convince the read explicitly}

Note that the assignment, described by the
prediction map $m$, is non-contextual since given
an operator and a state (+ the HV $c$), the value is
uniquely assigned. The map $m$ is, however,
non-multiplicative.

To bring out the non-multiplicativity of our model
we apply it to the Peres Mermin situation of two
spin-1/2 particles. Consider the initial state of
the system 
$\left|\psi_{1}\right\rangle
=\left|00\right\rangle $. Assume we 
obtained $c=0.4$ as a random choice. To arrive
at the assignments, note that
$\left|00\right\rangle $ is an eigenket of only
$\hat{R}_{i},\hat{C}_{j}$ and
$\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
Thus, in the first iteration, all these should be
assigned their respective eigenvalues. The
remaining operators must be assigned $-1$ as one
can readily verify by explicitly finding the
smallest $a$ as described in postulate 2 of the
model (see \eqref{toyModel}). Two remarks are in
order. First, this model is manifestly
\emph{non-multiplicative}, for
$m_{1}(\hat{C}_{3})=1\neq
m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
where the subscript has been introduced to index
the iteration. More precisely,
$m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle
=\left|00\right\rangle \right])$ where the
complete state $\left[\left|\psi_{1}\right\rangle
\right]$ implicitly refers to both the quantum
state $\left|00\right\rangle $ and the HV $c=0.4$.
Second, we must impose \emph{sequential
multiplicativity} as a consistency check of the
model, which in particular entails that
$m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
where
$m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle
\right])$,
$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle
\right])$ and $\left|\psi_{2}\right\rangle
,\,\left|\psi_{3}\right\rangle $ are obtained from
postulate 3. Note that for each iteration, a new
HV is generated. To illustrate \emph{sequential
multiplicativity}, we must choose to measure
$\hat{A}_{33}$. According to step 3, since
$\left|00\right\rangle $ is an eigenstate of
$\hat{A}_{33}$, the final state remains
$\left|00\right\rangle $.

For the next iteration, $i=2$, viz.
after the first measurement has been performed,
say the random number generator yielded $c=0.1$.
Since $\left|\psi\right\rangle $ is also unchanged
the assignment remains invariant (in fact any of
$c<0.5$ would yield the same result), which should
be evident from the previous exercise. For the
final step we choose to measure
$\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
to proceed with sequentially measuring
$\hat{C}_{3}$. To simplify calculations, we note
\[ \left|00\right\rangle
=\frac{(\left|\tilde{+}\tilde{-}\right\rangle
+\left|\tilde{-}\tilde{+}\right\rangle
)/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle
+\left|\tilde{-}\tilde{-}\right\rangle
)/\sqrt{2}}{\sqrt{2}}, \] where
$\left|\tilde{\pm}\right\rangle
=\left|0\right\rangle \pm i\left|1\right\rangle $
(eigenkets of $\hat{\sigma}_{y}$). Since
$\left|00\right\rangle $ is manifestly not an
eigenket of $\hat{p}$, we must find an appropriate
eigenket $\left|p_{-}\right\rangle $ s.t.
$\hat{p}\left|p_{-}\right\rangle
=-\left|p_{-}\right\rangle $, since $c=0.1$ and
$\left\langle p_{-}|00\right\rangle $ is already
$>0.1$. It is immediate that
$\left|p_{-}\right\rangle
=\left(\left|\tilde{+}\tilde{-}\right\rangle
+\left|\tilde{-}\tilde{+}\right\rangle
\right)/\sqrt{2}=\left(\left|00\right\rangle
+\left|11\right\rangle \right)/\sqrt{2}$, which
becomes the final state. \\ For the final
iteration, $i=3$, say we obtain $c=0.7$. So far,
we have $m_{1}(\hat{A}_{33})=1$ and
$m_{2}(\hat{A}_{23})=-1$. We must obtain
$m_{3}(\hat{A}_{13})=1$, independent of the value
of $c$, to be consistent. Let's check that.
Indeed, according to postulate 2, since
$\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle
+\left|11\right\rangle
\right)/\sqrt{2}=1\left(\left|00\right\rangle
+\left|11\right\rangle \right)/\sqrt{2}$,
$m_{3}(\hat{A}_{13})=1$ for all allowed values of
$c$. As a remark, it maybe emphasised that the
$m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$ and
$m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which
essentially expresses compatibility of these
observables, viz. measurement of $\hat{A}_{13}$
doesn't affect the result one would obtain by
measuring operators compatible to it (granted they
have been measured once before).

\begin{widetext} \begin{equation}
\begin{array}{c|ccc} \text{Iteration} & i=1 & i=2
& i=3\\ \left|\psi_{\text{init}}\right\rangle  &
\left|00\right\rangle  & \left|00\right\rangle  &
\frac{\left|00\right\rangle +\left|11\right\rangle
}{\sqrt{2}}\\ \text{HV/Toss} & c=0.4 & c=0.1 &
c=0.7\\ \\ \text{Predictions} &
m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
\end{array}\right] &
m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
\end{array}\right] &
m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1
\end{array}\right]\\ \text{(Assignments)}\\ &
m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3)
&
m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3)
&
m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
& m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 &
m_{3}(\hat{C}_{3})=-1\\ \text{Operator}\\
\text{Measured} &
\hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1
&
\quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad
&
\hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
\\ \left|\psi_{\text{final}}\right\rangle  &
\left|00\right\rangle  &
\frac{\left|00\right\rangle +\left|11\right\rangle
}{\sqrt{2}} & \frac{\left|00\right\rangle
+\left|11\right\rangle }{\sqrt{2}}
\end{array}\label{eq:toyModel} \end{equation}
\end{widetext}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red} Will work on CC after everthin else
is done}
\section{Concluding Remarks
\label{sec:implications}} We have already
constructed an explicit non-contextual model,
which is consistent with QM.  This model we knew
had to be non-multiplicative.  We will see how
non-multiplicativity gives rise to what one might
confuse to mean contextuality.  Imagine \[
\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle
\left\langle 00\right|+\left|01\right\rangle
\left\langle 01\right|-\left[\left|10\right\rangle
\left\langle 10\right|+\left|11\right\rangle
\left\langle 11\right|\right], \] \[
\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle
\left\langle 10\right|+\left|11\right\rangle
\left\langle 11\right|-\left[\left|00\right\rangle
\left\langle 00\right|+\left|01\right\rangle
\left\langle 01\right|\right], \] while we define
\begin{align*} \hat{C}&=f(\{\hat{B}_{i}\}) \\
&=0.\left|00\right\rangle \left\langle
00\right|+1.\left|01\right\rangle \left\langle
01\right|+2.\left|10\right\rangle \left\langle
10\right|+3.\left|11\right\rangle \left\langle
11\right|.  \end{align*} $\hat{C}$ maybe viewed as
a function of $\hat{B}_{1}$, $\hat{B}_{2}$ and
other operators $\hat{B}_{i}$ which are
constructed to obtain a maximally commuting set. A
measurement of $\hat{C}$, will collapse the state
into one of the states which are simultaneous
eignkets of $B_{1}$ and $B_{2}$. Consequently,
from the observed value of $\hat{C}$, one can
deduce the values of $\hat{B}_{1}$ and
$\hat{B}_{2}$. Now consider
$\sqrt{2}\left|\chi\right\rangle
=\left|10\right\rangle +\left|01\right\rangle $,
for which $m_{1}(\hat{B}_{1})=1$, and
$m_{1}(\hat{B}_{2})=1$, using the C-ingle model,
with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
which one can deduce that $B_{1}$ was $+1$, while
$B_{2}$ was $-1$.  This property itself, one may
be tempted call contextuality, viz.  the value of
$B_{1}$ depends on whether it is measured alone or
with the remaining $\{B_{i}\}$. However, it must
be noted that $B_{1}$ has a well defined value,
and so does $\hat{C}$. Thus by our accepted
definition, there's no contextuality. It is just
that $m_{1}(\hat{C})\neq
f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
viz. the theory is non-multiplicative. Note that
after measuring $\hat{C}$ however,
$m_{2}(\hat{B}_{1})=+1$ and
$m_{2}(\hat{B}_{2})=-1$ (for any value of $c$)
consistent with those deduced by measuring
$\hat{C}$.

It is known that for simultaneous eigenstates of
$\hat{B}_{i}$, multiplicativity must hold.
Consequently, any violation of multiplicativity
must arise from states that are superpositions (of
the simultaneous eigenkets).  Note however, that
entanglement is not necessary to show a violation,
since, for example, the PM test is a state
independent test, where a separable state can be
used to arrive at a contradiction. For
demonstrating non-locality using Bell's proof,
however, it can be shown that entanglement is
necessary.  \bibliographystyle{apsrev4-1}
\bibliography{references}

\end{document}

### 2016-07-10 preReleases/version5/finalPaper.tex
added this version as a seperate version5 in the folder

--- 2016-07-10 preReleases/version4arv/finalPaper.tex
@@
 \AtBeginDocument{\providecommand\ssecref[1]{\ref{ssec:#1}}}
+\AtBeginDocument{\providecommand\defnref[1]{\ref{defn:#1}}}
+\AtBeginDocument{\providecommand\tblref[1]{\ref{tbl:#1}}}
 
+\newref{tbl}{name=Table~}{}
+\newref{defn}{name=Definition~}{}
 \newref{sec}{name=Section~}
@@
   \theoremstyle{definition}
-  \newtheorem{defn}[thm]{\protect\definitionname}
+  \newtheorem{defn}{\protect\definitionname}
+
   \theoremstyle{remark}
-  \newtheorem{rem}[thm]{\protect\remarkname}
+  \newtheorem{rem}{\protect\remarkname}
+
+  \theoremstyle{remark}
+  \newtheorem{defnrem}{\protect\remarkname}[defn]
+
+  \theoremstyle{remark}
+  \newtheorem{thmrem}{\protect\remarkname}[thm]
+
   \theoremstyle{plain}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+\usepackage{paralist}
 \usepackage{graphicx}
@@
 \setlength{\itemindent}{0pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%This stuff is required for transposing matrices | fine I didn't want to do donkey work
+\usepackage{xparse}
+\usepackage{environ}
+
+\ExplSyntaxOn
+\NewEnviron{bmatrixT}
+ {
+  \marine_transpose:V \BODY
+ }
+
+\int_new:N \l_marine_transpose_row_int
+\int_new:N \l_marine_transpose_col_int
+\seq_new:N \l_marine_transpose_rows_seq
+\seq_new:N \l_marine_transpose_arow_seq
+\prop_new:N \l_marine_transpose_matrix_prop
+\tl_new:N \l_marine_transpose_last_tl
+\tl_new:N \l_marine_transpose_body_tl
+
+\cs_new_protected:Nn \marine_transpose:n
+ {
+  \seq_set_split:Nnn \l_marine_transpose_rows_seq { \\ } { #1 }
+  \int_zero:N \l_marine_transpose_row_int
+  \prop_clear:N \l_marine_transpose_matrix_prop
+  \seq_map_inline:Nn \l_marine_transpose_rows_seq
+   {
+    \int_incr:N \l_marine_transpose_row_int
+    \int_zero:N \l_marine_transpose_col_int
+    \seq_set_split:Nnn \l_marine_transpose_arow_seq { & } { ##1 }
+    \seq_map_inline:Nn \l_marine_transpose_arow_seq
+     {
+      \int_incr:N \l_marine_transpose_col_int
+      \prop_put:Nxn \l_marine_transpose_matrix_prop
+       {
+        \int_to_arabic:n { \l_marine_transpose_row_int }
+        ,
+        \int_to_arabic:n { \l_marine_transpose_col_int }
+       }
+       { ####1 }
+     }
+   }
+   \tl_clear:N \l_marine_transpose_body_tl
+   \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_col_int }
+    {
+     \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_row_int }
+      {
+       \tl_put_right:Nx \l_marine_transpose_body_tl
+        {
+         \prop_item:Nn \l_marine_transpose_matrix_prop { ####1,##1 }
+         \int_compare:nF { ####1 = \l_marine_transpose_row_int } { & }
+        }
+      }
+     \tl_put_right:Nn \l_marine_transpose_body_tl { \\ }
+    }
+   \begin{bmatrix}
+   \l_marine_transpose_body_tl
+   \end{bmatrix}
+ }
+\cs_generate_variant:Nn \marine_transpose:n { V }
+\cs_generate_variant:Nn \prop_put:Nnn { Nx }
+\ExplSyntaxOff
+
 \begin{document}
@@
 \maketitle
-\section{Introduction}
-\label{introduction}
+
 Quantum mechanics has been one of the most
-successful theories in physics so far; however,
+successful theories in physics so far, however,
 there has not yet been a final word on its
@@
 fundamental non-classical feature of the quantum
-world and experiments have also been propsed and
+world and experiments have also been proposed and
 conducted to this effect~\cite{SimonContExpProp,
@@
 consideration~\cite{NoContextuality,LaCourNoCntx},
-we take a different approach and construct a toy
+we take a different approach and construct a
 HV model consistent with QM.  The predictions of
-the non-contextual toy model that we construct
-(which is a special case of a certain class of
-models) match with those of QM for systems
+the aforesaid model match with those of QM for systems
 described by arbitrary finite-dimensional Hilbert
@@
 such algebraic constraints possess a special
-property which we call `multiplicativity'.  By
-enlarging the scope of HV models to include
-non-multiplicative models, we construct an
+property which we call `multiplicativity'.  
+Enlarging the scope of HV models to include
+non-multiplicative models, permits us to construct an
 explicit non-contextual model consistent with QM.
@@
 `contextuality'  is used to illustrate
-non-multiplicativity, which we propose as an
-intrinsic quantum feature as a possible
-alternative to contextuality.
+non-multiplicativity, an intrinsic quantum feature, 
+which we propose as a possible alternative to contextuality.
 
-{\noindent \bf Notation~:} (a) $\psi\in\mathcal{H}$ 
+{\noindent \bf Notation:} (a) $\psi\in\mathcal{H}$ 
 represents a pure quantum mechanical
@@
 
-\begin{rem} The notion of non-contextuality may be
+\begin{defnrem} The notion of non-contextuality may be
 extended to maps. A map is non-contextual if it is
 of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}]
-\} \to\mathbb{R}$; prediction maps for individual
-observables are non-contextual by construction.  
-\end{rem}
-\begin{rem}
+\} \to\mathbb{R}$; prediction maps {\color{red}Comment: Is this really needed ``for individual
+observables''} are non-contextual by construction.  
+\end{defnrem}
+\begin{defnrem}
 Broader definitions in the literature have been
@@
 compatible observable it is being  measured with.
-\end{rem}
+\end{defnrem}
 
@@
 models cannot be compatible with quantum
-mechanics, and show that multiplicativity can provide an
+mechanics and show that multiplicativity can provide an
 alternative to contextuality, we define
@@
 half. Here multiplicativity does not seem to hold.
-Anti-thetically, it is clear that if one first
+Antithetically, it is clear that if one first
 measures $\hat{B}_{1}$ and subsequently measures
@@
 $[\psi_{i}]\in[\mathcal{H}]$ and
-$[\psi_{k+1}]\equiv
+$[\psi_{k+1}] :=
 s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
 $\forall\,[\psi_{i}]$.  
-\end{defn} 
+\label{defn:seqnMltpl}\end{defn} 
 With these definitions we are now ready to discuss
-the `proofs of contextuality'. We first state the
-contextuality theorems in our notation:
-\begin{thm} 
-Let a map
-$m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
-$m(\hat{\mathbb{I}})=1$, (b)
-$m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde
-f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$, where
-$\hat{A}_{i}$ are arbitrary Hermitian operators.
-If $m$ is assumed to describe the outcomes of
-measurements, then no $m$ exists which is
-consistent with all predictions of
-QM\label{thm:det}
-\end{thm} 
-Here $m$ maybe viewed as a specific
-class of prediction maps, that implicitly depends
-on the state $[\psi]$. It follows then that the
-maps ruled out by the theorem are non-contextual.
-The set of maps ruled out, however, can be
-enlarged by imposing fewer restrictions on it.
-This is achieved by the following theorem.
+the `proof of contextuality'. We first state the
+contextuality theorem in our notation:
 \begin{thm} Let a map
@@
 \cite{Peres,Mermin}:
-For a system composed of two spin-1/2 particles 
+For a system composed of two spin-half particles 
 consider the following set of operators \[
@@
 \end{array}\right] \] which have the property that
-all operators along a row (or column) commute and
-that the product of rows (or columns) yield
+all operators along a row (or column) commute. Further,
+the product of rows (or columns) yields
 $\hat{R}_{i}=\mathbb{I}$ and
@@
 $\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where
-$\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$,
-$\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$. Let us
+$\hat{R}_{i}:=\prod_{j}\hat{A}_{ij}$,
+$\hat{C}_{j}:=\prod_{i}\hat{A}_{ij}$. Let us
 assume that $m$ exists. From property (b) of the
@@
 
-\begin{rem} One could in principle assume $m$, to
+\begin{thmrem} One could in principle assume $m$, to
 be s.t. (a) $m(\hat{\mathbb{I}})=1$, (b)
@@
 \cite{KochenSpecker} 
-\end{rem} 
-It is clear that 
-according to
+\end{thmrem} 
+Here $m$ maybe viewed as a specific
+class of prediction maps, that implicitly depends
+on the state $[\psi]$. It is clear that according to
 \thmref{KS}, non-contextual maps which are
@@
 non-\emph{multiplicative} might be consistent with
-QM. We will indeed show this by constructing an
+QM. Indeed it is and we will show this by constructing an
 explicit model.
@@
 \begin{prop*} 
-Let a QM 
+Let a quantum mechanical 
 system be in a state, s.t. measurement of
@@
 each time). Then according to QM, \emph{sequential
-multiplicativity} holds, where $\hat{C}\equiv
+multiplicativity} holds, where $\hat{C}:=
 f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$, and
-$\hat{B}_{i}$ are as defined. 
-{\color{red} Comment: We need to refer to a specific place
-for def}
+$\hat{B}_{i}$ are as defined (in \defnref{seqnMltpl})
 \end{prop*}
@@
 \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
-{\color{red} Do we need to additional index? $b_j$
-can be an index itself}
 Let the state of the system
@@
 orthogonal to $\left|\psi\right\rangle $, then
-nothing can be said. We can thus conclude that
+nothing can be said but that is irrelevant. We can thus conclude that
 $\left|\psi\right\rangle $ is made only of those
 $\left|\mathbf{b}\right\rangle $s that satisfy the
-required relation. That completes the proof.
+required relation.
 \end{proof} 
@@
 Let the state of a finite dimensional quantum system
-be $\left|\chi\right\rangle $, and we wish to
+be $\left|\chi\right\rangle $. We wish to
 assign a value to an arbitrary observable 
@@
 \left\langle a\right|$, which has 
-eigen vectors $\{ \vert
-a_j\rangle \}$ and the corresponding ordered eigen
-values $\{a_j\}$ such that 
+eigenvectors $\{ \vert
+a_j\rangle \}$. The corresponding ordered eigenvalues are $\{a_j\}$ such that 
 $a_{\rm min}=a_1$
 and 
-$a_{\rm max}=a_n$
+$a_{\rm max}=a_n$.
 
-Our model for assigning values have the following
-three steps~:
+Our HV model for QM assigns values in the following
+three steps:
+\setdefaultleftmargin{0pt}{}{}{}{}{}
 \begin{enumerate}
 \item
-{\bf Initial HV~:} Pick a number
+{\bf Initial HV:} Pick a number
 $c\in[0,1]$, from a uniform random distribution.\
@@
 {\bf
-Assignment or Prediction~:}
+Assignment or Prediction:}
  The value assigned to
@@
 \item
-{\bf Update~:} After measuring an operator, the state is
+{\bf Update:} After measuring an operator, the state is
 updated (collapsed) in accordance with the rules
@@
 To see how this works consider 
-single spin half particle in state
+a spin-half particle in the state
 $\left|\chi\right\rangle
 =\cos\theta\left|0\right\rangle
-+\sin\theta\left|1\right\rangle $, and
++\sin\theta\left|1\right\rangle $ and the observable
 $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle
@@
 postulates of this theory, $m(\hat{A})=+1$, if
-the value of randomly generated 
+the randomly generated value for 
 $c\le\cos^{2}\theta$ else $\hat{A}$ is assigned
@@
 random in $[0,1]$ that the statistics agree with
-predictions of QM. The reader can convince
-him(her)self that the said scheme works in
-general. {\color{red} Can we give more detail to
-convince the read explicitly}
+predictions of QM.
 
@@
 To bring out the non-multiplicativity of our model 
+and to convince the reader of its generic validity,
 we apply it to the Peres Mermin situation of two
-spin-1/2 particles. Consider the initial state of
+spin-half particles. Consider the initial state of
 the system 
@@
 smallest $a$ as described in postulate 2 of the
-model (see \eqref{toyModel}). Two remarks are in
+model (see \tblref{HVmodel}). Two remarks are in
 order. First, this model is manifestly
@@
 final step we choose to measure
-$\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
+$\hat p := \hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
 to proceed with sequentially measuring
@@
 
-\begin{widetext} \begin{equation}
-\begin{array}{c|ccc} \text{Iteration} & i=1 & i=2
+%\begin{widetext}
+%\onecolumngrid
+\begin{table*}
+ \begin{equation*}
+\begin{array}{c|ccc} 
+\text{Iteration} & i=1 & i=2
 & i=3\\ \left|\psi_{\text{init}}\right\rangle  &
@@
 \frac{\left|00\right\rangle +\left|11\right\rangle
-}{\sqrt{2}}\\ \text{HV/Toss} & c=0.4 & c=0.1 &
-c=0.7\\ \\ \text{Predictions} &
+}{\sqrt{2}}\\ 
+\text{HV/Toss} & c=0.4 & c=0.1 &
+c=0.7\\ \\ 
+\text{Predictions} &
 m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
@@
 +1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1
-\end{array}\right]\\ \text{(Assignments)}\\ &
+\end{array}\right]\\ 
+\text{(Assignments)}\\ &
 m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3)
@@
 +\left|11\right\rangle }{\sqrt{2}}
-\end{array}\label{eq:toyModel} \end{equation}
-\end{widetext}
+% \begin{bmatrixT} 
+% \text{Iteration} & i=1 & i=2
+% & i=3\\ \left|\psi_{\text{init}}\right\rangle  &
+% \left|00\right\rangle  & \left|00\right\rangle  &
+% \frac{\left|00\right\rangle +\left|11\right\rangle
+% }{\sqrt{2}} \\
+% \text{HV} & c=0.4 & c=0.1 & c=0.7 \\
+
+% \text{Predictions or} &
+% {m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
+% \end{array}\right]} &
+% {m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
+% \end{array}\right]} &
+% {m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% +1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1
+% \end{array}\right]}\\
+
+% \text{(Assignments)} &
+% m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3)
+% &
+% m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3)
+% &
+% m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
+% & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 &
+% m_{3}(\hat{C}_{3})=-1
+% \end{bmatrixT}
+\label{eq:toyModel}
+\end{array}
+% \label{eq:toyModel}
+\end{equation*}
+\caption{HV model applied to the Peres Mermin situation}
+\label{tbl:HVmodel}
+\end{table*}
+%\end{widetext}
 

### 2016-07-11 finalPaper.tex
made various changes

@@
-%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
 \documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
@@
 \usepackage{esint}
-
 \makeatletter
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-
 \AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
@@
   \providecommand{\notationname}{Notation}
+\setlength{\itemindent}{0pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%This stuff is required for transposing matrices | fine I didn't want to do donkey work
+\usepackage{xparse}
+\usepackage{environ}
+
+\ExplSyntaxOn
+\NewEnviron{bmatrixT}
+ {
+  \marine_transpose:V \BODY
+ }
+
+\int_new:N \l_marine_transpose_row_int
+\int_new:N \l_marine_transpose_col_int
+\seq_new:N \l_marine_transpose_rows_seq
+\seq_new:N \l_marine_transpose_arow_seq
+\prop_new:N \l_marine_transpose_matrix_prop
+\tl_new:N \l_marine_transpose_last_tl
+\tl_new:N \l_marine_transpose_body_tl
+
+\cs_new_protected:Nn \marine_transpose:n
+ {
+  \seq_set_split:Nnn \l_marine_transpose_rows_seq { \\ } { #1 }
+  \int_zero:N \l_marine_transpose_row_int
+  \prop_clear:N \l_marine_transpose_matrix_prop
+  \seq_map_inline:Nn \l_marine_transpose_rows_seq
+   {
+    \int_incr:N \l_marine_transpose_row_int
+    \int_zero:N \l_marine_transpose_col_int
+    \seq_set_split:Nnn \l_marine_transpose_arow_seq { & } { ##1 }
+    \seq_map_inline:Nn \l_marine_transpose_arow_seq
+     {
+      \int_incr:N \l_marine_transpose_col_int
+      \prop_put:Nxn \l_marine_transpose_matrix_prop
+       {
+        \int_to_arabic:n { \l_marine_transpose_row_int }
+        ,
+        \int_to_arabic:n { \l_marine_transpose_col_int }
+       }
+       { ####1 }
+     }
+   }
+   \tl_clear:N \l_marine_transpose_body_tl
+   \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_col_int }
+    {
+     \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_row_int }
+      {
+       \tl_put_right:Nx \l_marine_transpose_body_tl
+        {
+         \prop_item:Nn \l_marine_transpose_matrix_prop { ####1,##1 }
+         \int_compare:nF { ####1 = \l_marine_transpose_row_int } { & }
+        }
+      }
+     \tl_put_right:Nn \l_marine_transpose_body_tl { \\ }
+    }
+   \begin{bmatrix}
+   \l_marine_transpose_body_tl
+   \end{bmatrix}
+ }
+\cs_generate_variant:Nn \marine_transpose:n { V }
+\cs_generate_variant:Nn \prop_put:Nnn { Nx }
+\ExplSyntaxOff
 
 \begin{document}
-
-\title{A non-contextual hidden variable model for Quantum Mechanics}
-
+\title{A non-contextual hidden variable model for quantum mechanics}
 \author{Atul Singh Arora}
-
 \email{ms11003@iisermohali.ac.in}
-
 \selectlanguage{british}%
-
 \affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
-
 \author{Arvind}
-
 \email{arvind@iisermohali.ac.in}
-
 \selectlanguage{british}%
-
-\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
+\affiliation{Indian Institute of Science Education
+and Research (IISER), Mohali}
 \begin{abstract}
-We propose a non-contextual hidden variable model, consistent with all predictions of Quantum Mechanics (QM).
-We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of QM.
-Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view.
-This is accomplished by identifying a new classical property, we call `multiplicativity'.
-It turns out that if this condition is relaxed one is able to construct hidden variable models which are consistent with QM.
-Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.
-Our model is for finite dimensional quantum systems, however, generalization to the infinite dimensional case should be possible.
-%and its relation to contextuality.
+We propose a non-contextual hidden variable model,
+consistent with all predictions of quantum
+mechanics (QM).  A careful scrutiny of
+consistency requirements between any hidden
+variable model and  quantum mechanics and the
+corresponding no-go theorems, leads us to the
+conclusion that the notion of contextuality is not
+a necessary feature of QM.  The alternative view
+that emerges, hinges on identifying a new classical
+property, which we call ``multiplicativity''.  It turns
+out that, by relaxing this condition of
+``multiplicativity'' on hidden variable models, they
+can be made  consistent with QM.  Advantages of
+this view are illustrated by considering the
+implications of non-multiplicativity to locality,
+entanglement, superposition, and  apparent
+contextuality. 
 \end{abstract}
+\pacs{}
 \maketitle
 
-\section{Introduction}
+Quantum mechanics has been one of the most
+successful theories in physics so far, however,
+there has not yet been a final word on its
+completeness and interpretation~\cite{??}.
+Einstein's~\cite{EinsteinEPR} work on the
+incompleteness of QM and the subsequent seminal
+work of Bell~\cite{Bell1964}, assessing the
+compatibility of a more complete model involving
+hidden variables (HV) and locality with QM, has
+provided deep insights into  how the quantum world
+differs from its classical counterpart.  In recent
+times, these insights have been of pragmatic
+utility in the areas of quantum information
+processing, where EPR pairs are fundamental motifs
+of entanglement~\cite{Ekert,PironioRndmnssCrtfcn}.
+The work of  Kochen Specker~\cite{KochenSpecker}
+and Gleason et.
+al.~\cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
+broadened the schism between  HV models and QM.
+They showed that it was contextuality and not
+non-locality which was at the heart of this schism
+and the incompatibility between HV models and QM
+can arise even for a single quantum system.
+Contextuality has thus been identified as a
+fundamental non-classical feature of the quantum
+world and experiments have also been proposed and
+conducted to this effect~\cite{SimonContExpProp,
+HuangContExp,YangContExp,HasegawaContExp}.
+Contextuality, on the one hand has led to
+investigations on the foundational aspects of
+QM~\cite{PawelCntxClsscl,?????}, and on the other
+hand has been harnessed for computation and
+cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt,??}.
+Quantitative measures of contextuality based on
+memory~\cite{MatthiasCntxMmry} have also been used
+to demonstrate the completeness of
+QM~\cite{CabelloMmryQM}.  However, not all HV
+models are incompatible with QM, and a very
+important case in point is  Bohm's model based on
+precise trajectories for quantum
+systems~\cite{Bohm1,Bohm2}.
 
-Einstein's \cite{EinsteinEPR} work on incompleteness of QM and the subsequent seminal work of Bell \cite{Bell1964}, assessing compatibility of hidden variable (HV) models with QM has proven to be repeatedly useful.
-In Bell's case, for instance, it gave a precise meaning to the foundational notion of locality.
-Further, it has been of pragmatic utility in the areas of security, randomness certification etc.
-\cite{Ekert,PironioRndmnssCrtfcn} While Bell showed that local HV models can not describe nature, the Kochen Specker theorem \cite{KochenSpecker} (and related work \cite{Gleason,BellOnHiddenVariables,Peres,Mermin}) ruled out an even larger class of HV models.
-Consequently the notion of contextuality was identified, methods to experimentally test it were proposed and evidence in its favour reported \cite{SimonContExpProp,HuangContExp,YangContExp,HasegawaContExp}.
-Contextuality also, in recent times has been harnessed for computation and cryptography \cite{HowardCntxCmptn,CabelloCntxScrt}.
-[]Contextuality has also stirred further investigation of foundational aspects of QM: relation between contextuality and classicality has been explored \cite{PawelCntxClsscl}, contextuality has been quantified in terms of memory \cite{MatthiasCntxMmry} and bounded memory in conjunction with contextuality has been used to show completeness of QM \cite{CabelloMmryQM}.[] Not all HV models were, however, proved to be incompatible by the aforesaid theorem.
-Bohm's work \cite{Bohm1,Bohm2} is one such (in)famous example.
-This approach has allowed for an interpretation of QM with precise trajectories.
+A closer look at the aforesaid no-go theorems
+reveals that contextuality is in fact not a
+necessary feature of QM (see \figref{block}).
+While this has been shown earlier by taking
+disturbances due to measurements into
+consideration~\cite{NoContextuality,LaCourNoCntx},
+we take a different approach and construct a
+HV model consistent with QM.  The predictions of
+the aforesaid model match with those of QM for systems
+described by arbitrary finite-dimensional Hilbert
+spaces.  \begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{block1}
+\caption{Non-contextuality is not inconsistent
+with QM} \label{fig:block}\end{figure} The
+algebraic constraints obeyed by quantum
+observables may not necessarily be obeyed by the
+predictions of an HV model at the level of
+individual outcomes.  Those HV models that obey
+such algebraic constraints possess a special
+property which we call `multiplicativity'.  
+Enlarging the scope of HV models to include
+non-multiplicative models, permits us to construct an
+explicit non-contextual model consistent with QM.
+The re-examination of the very proof of
+`contextuality'  is used to illustrate
+non-multiplicativity, an intrinsic quantum feature, 
+which we propose as a possible alternative to contextuality.
 
-%Previous work {[}the essentials I have already discussed{]}: 
-We take a closer look at the aforesaid no-go theorems and find that contextuality is in fact not a necessary feature of QM (see \figref{block}).
-This has been shown earlier by taking disturbances due to measurements into consideration \cite{NoContextuality,LaCourNoCntx}.
-In this paper, we construct a significantly simpler toy model for illustrating not only the aforesaid but to also delineate a complete alternative to contextuality.
-The toy model is a specific case of what we call a c-ingle variable theory.
-Its predictions match with those of QM for systems described by arbitrary finite dimensional Hilbert spaces.
+{\noindent \bf Notation:} (a) $\psi\in\mathcal{H}$ 
+represents a pure quantum mechanical
+state of the system in the Hilbert space
+$\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined
+to mean the set of Hermitian 
+observables for the system, (c)
+$[\mathcal{H}]$ is defined to mean
+$(\mathcal{H},\,\mathbb{R}^{\otimes})$, which
+represents the state of the system including HVs,
+(d) $[\psi]\in[\mathcal{H}]$ will represent the
+state of the system, including HVs, (e) a
+prediction map is
+$m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$,
+(f) a sequence map is
+$s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$,
+(g) $f$ is an arbitrary map from $\{
+\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
+\} \to \hat{\mathcal{H}}$ constructed using
+multiplication and addition of the observables,
+and multiplication with complex
+numbers\footnote{Strictly, the map $f$ would
+depend on the operators to ensure preservation of
+Hermiticity; thus a given $f$ will be defined only
+for a subset of $\{
+\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
+\}$.}, (h) $\tilde{f}$ is a map constructed by
+replacing observables in $f$ with real numbers.
 
-%Triangle: <TODO: ask arvind sir, see \figref{block}>
+\begin{defn} A theory is non-contextual, if it
+provides a map $m: \{
+\hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$
+to explain measurement outcomes. A theory which is
+not non-contextual is contextual.\end{defn}
 
-\begin{figure}[h]
-\includegraphics[width=\columnwidth]{block1}
-\caption{Non-contextuality is not inconsistent with QM}
-\label{fig:block}\end{figure}
+\begin{defnrem} The notion of non-contextuality may be
+extended to maps. A map is non-contextual if it is
+of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}]
+\} \to\mathbb{R}$; prediction maps {\color{red}Comment: Is this really needed ``for individual
+observables''} are non-contextual by construction.  
+\end{defnrem}
+\begin{defnrem}
+Broader definitions in the literature have been
+suggested which declare a larger set of theories
+as non-contextual. For our purposes however, this
+restricted definition will suffice. The term
+contextual is used to suggest that the value an
+operator takes might depend on which other
+compatible observable it is being  measured with.
+\end{defnrem}
 
-Organization of this paper is as follows.
-In \secref{context} we establish a notation and definitions to facilitate further discussions.
-In \secref{nonMultiplicativity} we introduce the notion of multiplicativity and that of sequential multiplicativity.
-We review the `contextuality' theorem and prove some results about multiplicativity.
-We construct an explicit non-contextual model in \ssecref{cingle} and apply it to the very proof of `contextuality' to illustrate non-multiplicativity.
-This is supplemented by a discussion about Bohmian Mechanics in \ssecref{nonContBohm} where contextuality is removed by hand.
-The paper is concluded with discussion of implications of multiplicativity on locality, entanglement, superposition and apparent contextuality in \secref{implications}.
-
-\section{Context \label{sec:context}}
-
-The notation used henceforth has been defined below.
-
-\begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e.
-the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including HVs, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including HVs, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) $f$ is an arbitrary map from $\{ \hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}} \} \to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\{ \hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}} \}$.}, (h) $\tilde{f}$ is a map constructed by replacing observables in $f$ with real numbers.
-%\footnote{$\tilde f$ constructed this way should be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.
-In fact the values should be restricted to the spectrum of the associated observables.}.
-\end{notn}
-
-In addition to the notation, we use the following definition of non-contextuality.
-\begin{defn}
-A theory is non-contextual, if it provides a map $m: \{ \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$ to explain measurement outcomes. A theory which is not non-contextual is contextual.\end{defn}
-\begin{rem}
-The notion of non-contextuality may be extended to maps. A map is non-contextual if it is of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$; prediction maps are non-contextual.
-\end{rem}
-
-In the literature broader definitions have been suggested which declare a larger set of theories as non-contextual.
-For our purposes however, this restricted definition will suffice.
-The term contextual is used to suggest that the value an operator takes might depend on which other compatible observable it is measured with.
-
-\section{Non-Multiplicativity: An alternative to Contextuality \label{sec:nonMultiplicativity}}
-
-One can show \cite{KochenSpecker} that under reasonable assumptions, no non-contextual theory can explain all predictions of QM.
-We re-state these results and show that nowhere does contextuality appear to be a logical necessity.
-Instead we note that non-contextual theories with certain properties, we call \emph{multiplicativity} are incompatible with QM.
-Viewed from this perspective, non-\emph{multiplicativity} is the non-classical alternative to contextuality in QM.
-Precise definitions of this and a related property \emph{sequential multiplicativity}, are given below.
-
+Before we re-examine the result of Kochen and
+Specker~\cite{KochenSpecker} that non-contextual
+models cannot be compatible with quantum
+mechanics and show that multiplicativity can provide an
+alternative to contextuality, we define
+multiplicativity more precisely.
 \begin{defn}
 A prediction map $m$ is \emph{multiplicative} iff
-% \[
-% \begin{split}
-% m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
-% f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
-% \end{split}
-% \]
+\begin{align*} &
+m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])
+= \\ & \tilde
+f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots
+m(\hat{B}_{N},[\psi])), \end{align*}
+where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
+arbitrary mutually commuting observables and
+$[\psi]\in[\mathcal{H}]$. A
+\emph{non-multiplicative} map is one that is not
+multiplicative.  
+\end{defn} 
+Note that if $m$ is taken to represent the
+measurement outcome (in QM), then for states of
+the system which are simultaneous eigenkets of
+$\hat{B}_{i}$s, $m$ must clearly be
+multiplicative. It is, however, not obvious that
+this property must always hold. For example,
+consider two spin-half particles in the state 
+$\left|1\right\rangle \otimes\left|1\right\rangle
+$ written in the computational basis and take
+operators 
+$\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
+$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$
+and
+$\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$
+written in terms of Pauli operators.
+We must have $m(\hat{C})=-1$ while
+$m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$
+independently, according to QM, with probability
+half. Here multiplicativity does not seem to hold.
+Antithetically, it is clear that if one first
+measures $\hat{B}_{1}$ and subsequently measures
+$\hat{B}_{2}$, then the product of the results
+must be $-1$. This is consistent with measuring
+$\hat{C}$. To capture this property we define
+\emph{sequential multiplicativity} as follows.
+\begin{defn} 
+A prediction map $m$ is
+\emph{sequentially multiplicative} for a given
+sequence map $s$, iff \begin{align*}
+&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
+&\tilde
+f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
+\end{align*} 
+where
+$\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{
+N! {\rm ~permutations~of~}  k'{\rm s}
+\}$, $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
+arbitrary mutually commuting observables,
+$[\psi_{i}]\in[\mathcal{H}]$ and
+$[\psi_{k+1}] :=
+s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
+$\forall\,[\psi_{i}]$.  
+\label{defn:seqnMltpl}\end{defn} 
+With these definitions we are now ready to discuss
+the `proof of contextuality'. We first state the
+contextuality theorem in our notation:
+\begin{thm} Let a map
+$m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
+$m(\hat{\mathbb{I}})=1$, (b)
+$m(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde
+f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$, for any
+arbitrary function $f$, where $\hat{B}_{i}$ are
+mutually commuting Hermitian operators. If $m$ is
+assumed to describe the outcomes of measurements,
+then no $m$ exists which is consistent with all
+predictions of QM. 
+\label{thm:KS}
+\end{thm}
 
-\begin{align*}
-& m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
-& \tilde f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
-\end{align*}
-where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting observables and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is one that is not multiplicative.
-\end{defn}
-Note that if $m$ is taken to represent the measurement outcome (in
-QM), then for states of the system which are simultaneous eigenkets
-of $\hat{B}_{i}$s, $m$ must clearly be multiplicative. It is, however,
-not obvious that this property must always hold. To motivate this,
-consider the state of two spin half particles, $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
-written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
-$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
-We must have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
-independently, according to QM, with probability half. Here multiplicativity doesn't seem to hold. Antithetically it is clear that if one first measures
-$\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
-product of the results must be $-1$. This is consistent with measuring
-$\hat{C}$. To capture this property we define \emph{sequential multiplicativity}
-as follows.
-\begin{defn}
-A prediction map $m$ is \emph{sequentially multiplicative} for a
-given sequence map $s$, iff 
-\begin{align*}
-&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
-&\tilde f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
-\end{align*}
-where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)$ + permutations, making $N!$ terms$\}$,
-$\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
-observables, $[\psi_{i}]\in[\mathcal{H}]$ and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
-$\forall\,[\psi_{i}]$.
-\end{defn}
-We now discuss the `proofs of contextuality' in the purview of the
-aforesaid.
-\begin{thm}
-Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
-where $\hat{A}_{i}$ are arbitrary Hermitian operators.
-If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of QM\label{thm:det} (see \ref{proofs} for proofs).
-\end{thm}
-Here $m$ maybe viewed as a specific class of prediction maps, that
-implicitly depends on the state $[\psi]$. It follows then that the
-maps ruled out by the theorem are non-contextual. The set of maps
-ruled out, however, can be enlarged by imposing fewer restrictions
-on it. This is achieved by the following theorem.
+\begin{proof} Peres Mermin
+($\left|\mathcal{H}\right|\ge4$)
+\cite{Peres,Mermin}:
+For a system composed of two spin-half particles 
+consider the following set of operators \[
+\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
+\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} &
+\hat{\sigma}_{x}\otimes\hat{\mathbb{I}} &
+\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
+\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} &
+\hat{\mathbb{I}}\otimes\hat{\sigma}_{y} &
+\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
+\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} &
+\hat{\sigma}_{x}\otimes\hat{\sigma}_{y} &
+\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
+\end{array}\right] \] which have the property that
+all operators along a row (or column) commute. Further,
+the product of rows (or columns) yields
+$\hat{R}_{i}=\mathbb{I}$ and
+$\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
+$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where
+$\hat{R}_{i}:=\prod_{j}\hat{A}_{ij}$,
+$\hat{C}_{j}:=\prod_{i}\hat{A}_{ij}$. Let us
+assume that $m$ exists. From property (b) of the
+map, to get $m(\hat{C}_{3})=-1$ (as required by
+property (a)), we must have an odd number of $-1$
+assignments in the third column. In the remaining
+columns, the number of $-1$ assignments must be
+even (for each column). Thus, in the entire
+square, the number of $-1$ assignments must be
+odd. Let us use the same reasoning, but along the
+rows. Since each $m(\hat{R}_{i})=1$, we must have
+even number of $-1$ assignments along each row.
+Thus, in the entire square, the number of $-1$
+assignments must be even. We have arrived at a
+contradiction and therefore we conclude that our
+assumption that a consistent $m$ exists, must be
+wrong.  \end{proof}
 
-\begin{thm}
-Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$,
-for any arbitrary function $f$, where $\hat{B}_{i}$ are mutually
-commuting Hermitian operators. If $m$ is assumed to describe the
-outcomes of measurements, then no $m$ exists which is consistent
-with all predictions of QM (see \ref{proofs} for more proofs).\label{thm:KS}\end{thm}
+\begin{thmrem} One could in principle assume $m$, to
+be s.t. (a) $m(\hat{\mathbb{I}})=1$, (b)
+$m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for
+$\alpha\in\mathbb{R}$, (c)
+$m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d)
+$m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
+to deduce (d')
+$m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
+and that $m(\hat{B}_{i})\in$ spectrum of
+$\hat{B}_{i}$. Effectively then, condition (b)
+listed in the theorem is satisfied as a
+consequence.  Therefore, assuming (a)-(d) as
+listed here, rules out a larger class of $m$.
+\cite{KochenSpecker} 
+\end{thmrem} 
+Here $m$ maybe viewed as a specific
+class of prediction maps, that implicitly depends
+on the state $[\psi]$. It is clear that according to
+\thmref{KS}, non-contextual maps which are
+\emph{multiplicative} must be incompatible with
+QM. However, non-contextual maps which are
+non-\emph{multiplicative} might be consistent with
+QM. Indeed it is and we will show this by constructing an
+explicit model.
 
-% The following proof is not only more general, but also independent
-% of the initial state of the system.
+Before proceeding we note, however, that QM can
+enforce \emph{sequential multiplicativity}. This
+result will be used to assess accuracy of any
+proposal of a HV
+model.
+\begin{prop*} 
+Let a quantum mechanical 
+system be in a state, s.t. measurement of
+$\hat{C}$ yields repeatable results (same result
+each time). Then according to QM, \emph{sequential
+multiplicativity} holds, where $\hat{C}:=
+f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$, and
+$\hat{B}_{i}$ are as defined (in \defnref{seqnMltpl})
+\end{prop*}
 \begin{proof} 
-Peres Mermin ($\left|\mathcal{H}\right|\ge4$) \cite{Peres,Mermin}:
+Without loss of generality we can take
+$\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$ to be
+mutually compatible and a complete set of
+operators (Operators can be added to make the set
+complete if it not so).
+It follows
+that $\exists$
+$\left|\mathbf{b}=\left(b_{1},b_{2},\dots
+b_{n}\right)\right\rangle $ s.t.
+$\hat{B}_{i}\left|\mathbf{b}\right\rangle
+=b_{i}\left|\mathbf{b}\right\rangle $,
+and that
+$\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle
+\left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
+Let the state of the system
+$\left|\psi\right\rangle $ be s.t.
+$\hat{C}\left|\psi\right\rangle
+=c\left|\psi\right\rangle $. For
+the statement to follow, one need only show that
+$\left|\psi\right\rangle $ must be made of only
+those $\left|\mathbf{b}\right\rangle $s, which
+satisfy $c=\tilde
+f(b_{1},b_{2},\dots
+b_{n})$.  This is the crucial step and
+proving this is straightforward. We start with
+$\hat{C}\left|\psi\right\rangle
+=c\left|\psi\right\rangle $ and take its inner
+product with $\left\langle \mathbf{b}\right|$ to
+get \begin{eqnarray*} \left\langle
+\mathbf{b}\right|\hat{C}\left|\psi\right\rangle  &
+= & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
+\left\langle
+\mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})
+\left|\psi\right\rangle
+& = & c\left\langle \mathbf{b}|\psi\right\rangle
+,\\ \tilde f(b_{1},b_{2},\dots
+b_{n})\left\langle
+\mathbf{b}|\psi\right\rangle  & = & c\left\langle
+\mathbf{b}|\psi\right\rangle .  \end{eqnarray*}
+Also, we have $\left|\psi\right\rangle
+=\sum_{\mathbf{b}}\left\langle
+\mathbf{b}|\psi\right\rangle
+\left|\mathbf{b}\right\rangle $, from
+completeness. If we consider
+$\left|\mathbf{b}\right\rangle $s for which
+$\left\langle \mathbf{b}|\psi\right\rangle \neq0$,
+then we can conclude that indeed $c=\tilde
+f(b_{1},b_{2},\dots
+b_{n})$. However, when $\left\langle
+\mathbf{b}|\psi\right\rangle =0$, viz.
+$\left|\mathbf{b}\right\rangle $s that are
+orthogonal to $\left|\psi\right\rangle $, then
+nothing can be said but that is irrelevant. We can thus conclude that
+$\left|\psi\right\rangle $ is made only of those
+$\left|\mathbf{b}\right\rangle $s that satisfy the
+required relation.
+\end{proof} 
+It is worth noting that in the Peres Mermin
+case, where $\hat{R}_{i}$ and $\hat{C}_{j}$ are
+just $\pm\hat{\mathbb{I}}$, it follows that all
+states are their eigenstates. Consequently, for
+these operators \emph{sequential multiplicativity}
+must always hold.
+%\subsection{C-ingle model | An Explicit
+%Construction \label{ssec:cingle}}
+We are now ready to describe our explict model.
+Let the state of a finite dimensional quantum system
+be $\left|\chi\right\rangle $. We wish to
+assign a value to an arbitrary observable 
+$\hat{A}=\sum_{a}a\left|a\right\rangle
+\left\langle a\right|$, which has 
+eigenvectors $\{ \vert
+a_j\rangle \}$. The corresponding ordered eigenvalues are $\{a_j\}$ such that 
+$a_{\rm min}=a_1$
+and 
+$a_{\rm max}=a_n$.
 
-Consider the following set of operators 
-\[
-\hat{A}_{ij}\doteq\left[\begin{array}{ccc}
-\hat{\mathbb{I}}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\mathbb{I}} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\\
-\hat{\sigma}_{y}\otimes\hat{\mathbb{I}} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\\
-\hat{\sigma}_{y}\otimes\hat{\sigma}_{x} & \hat{\sigma}_{x}\otimes\hat{\sigma}_{y} & \hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
-\end{array}\right]
-\]
-which have the property that all operators along a row (or column) commute and that the product of rows (or columns) yield $\hat{R}_{i}=\mathbb{I}$ and $\hat{C}_{j}=\mathbb{I}\,(j\neq3)$, $\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where $\hat{R}_{i}\equiv\prod_{j}\hat{A}_{ij}$, $\hat{C}_{j}\equiv\prod_{i}\hat{A}_{ij}$.
-Let us assume that $m$ exists.
-From property (b) of the map, to get $m(\hat{C}_{3})=-1$ (as required by property (a)), we must have an odd number of $-1$ assignments in the third column.
-In the remaining columns, the number of $-1$ assignments must be even (for each column).
-Thus, in the entire square, the number of $-1$ assignments must be odd.
-Let us use the same reasoning, but along the rows.
-Since each $m(\hat{R}_{i})=1$, we must have even number of $-1$ assignments along each row.
-Thus, in the entire square, the number of $-1$ assignments must be even.
-We have arrived at a contradiction and therefore we conclude that our assumption that a consistent $m$ exists, must be wrong.
-\end{proof}
+Our HV model for QM assigns values in the following
+three steps:
+\setdefaultleftmargin{0pt}{}{}{}{}{}
+\begin{enumerate}
+\item
+{\bf Initial HV:} Pick a number
+$c\in[0,1]$, from a uniform random distribution.\
+\item
+{\bf
+Assignment or Prediction:}
+ The value assigned to
+$\hat{A}$ is given by finding the smallest $a$
+s.t.  $c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle
+a'|\chi\right\rangle \right|^{2},$ viz. we have
+specified a prediction map, $m(\hat{A})=a$.
+\item
+{\bf Update:} After measuring an operator, the state is
+updated (collapsed) in accordance with the rules
+of QM. This completely specifies the sequence map
+$s$.
+\end{enumerate}
+To see how this works consider 
+a spin-half particle in the state
+$\left|\chi\right\rangle
+=\cos\theta\left|0\right\rangle
++\sin\theta\left|1\right\rangle $ and the observable
+$\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle
+\left\langle 0\right|-\left|1\right\rangle
+\left\langle 1\right|$. Now, according to the
+postulates of this theory, $m(\hat{A})=+1$, if
+the randomly generated value for 
+$c\le\cos^{2}\theta$ else $\hat{A}$ is assigned
+$-1$. It follows then, from $c$ being uniformly
+random in $[0,1]$ that the statistics agree with
+predictions of QM.
 
-\begin{rem}
-One could in principle assume $m$, to be s.t. (a) $m(\hat{\mathbb{I}})=1$,
-(b) $m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for $\alpha\in\mathbb{R}$,
-(c) $m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d) $m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
-to deduce (d') $m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
-and that $m(\hat{B}_{i})\in$ spectrum of $\hat{B}_{i}$. Effectively
-then, condition (b) listed in the theorem is satisfied as a consequence.
-Therefore, assuming (a)-(d) as listed here, rules out a larger class
-of $m$. \cite{KochenSpecker}
-\end{rem}
-According to \thmref{KS}, non-contextual maps which are \emph{multiplicative}
-must be incompatible with QM. It is apparent that non-contextual maps
-which are non-\emph{multiplicative} might be consistent with QM. To
-that end, in the following section we first show that this is indeed
-the case by constructing an explicit model and supplement it by removing contextuality from Bohmian Mechanics.
+Note that the assignment, described by the
+prediction map $m$, is non-contextual since given
+an operator and a state (+ the HV $c$), the value is
+uniquely assigned. The map $m$ is, however,
+non-multiplicative.
 
-Before proceeding we note, however, that QM can enforce \emph{sequential multiplicativity}. This result will be used to assess accuracy of any HV model we might propose.
-\begin{prop*}
-Let the system be in a state, s.t. measurement of $\hat{C}$ yields
-repeatable results (same result each time). Then according to QM,
-\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
-and $\hat{B}_{i}$ are as defined. \end{prop*}
-\begin{proof}
-Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
-are mutually compatible (commuting) and complete set of operators.
-If say for instance the set is not complete, then one can add the
-missing operators and label them as aforesaid. It follows that $\exists$
-$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
-s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
-where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
-and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
-Let the state of the system be given by $\left|\psi\right\rangle $
-and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
-by assumption. For the statement to follow, one need only show that
-$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
-which satisfy $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
-This is the crucial step. Proving this is so is trivial. We start
-with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
-and take its inner product with $\left\langle \mathbf{b}\right|$
-to get 
-\begin{eqnarray*}
-\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
-\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
-\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
-\end{eqnarray*}
-Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $, from completeness.
-If we consider $\left|\mathbf{b}\right\rangle $s for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
-However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
-$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $, then nothing can be said.
-We can thus conclude that $\left|\psi\right\rangle $ is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy the required relation.
-That completes the proof.
-\end{proof}
-It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$ are just $\pm\hat{\mathbb{I}}$, it follows that all states are their eigenstates.
-Consequently, for these operators \emph{sequential multiplicativity} must always hold.
+To bring out the non-multiplicativity of our model 
+and to convince the reader of its generic validity,
+we apply it to the Peres Mermin situation of two
+spin-half particles. Consider the initial state of
+the system 
+$\left|\psi_{1}\right\rangle
+=\left|00\right\rangle $. Assume we 
+obtained $c=0.4$ as a random choice. To arrive
+at the assignments, note that
+$\left|00\right\rangle $ is an eigenket of only
+$\hat{R}_{i},\hat{C}_{j}$ and
+$\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
+Thus, in the first iteration, all these should be
+assigned their respective eigenvalues. The
+remaining operators must be assigned $-1$ as one
+can readily verify by explicitly finding the
+smallest $a$ as described in postulate 2 of the
+model (see \tblref{HVmodel}). Two remarks are in
+order. First, this model is manifestly
+\emph{non-multiplicative}, for
+$m_{1}(\hat{C}_{3})=1\neq
+m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
+where the subscript has been introduced to index
+the iteration. More precisely,
+$m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle
+=\left|00\right\rangle \right])$ where the
+complete state $\left[\left|\psi_{1}\right\rangle
+\right]$ implicitly refers to both the quantum
+state $\left|00\right\rangle $ and the HV $c=0.4$.
+Second, we must impose \emph{sequential
+multiplicativity} as a consistency check of the
+model, which in particular entails that
+$m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
+where
+$m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle
+\right])$,
+$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle
+\right])$ and $\left|\psi_{2}\right\rangle
+,\,\left|\psi_{3}\right\rangle $ are obtained from
+postulate 3. Note that for each iteration, a new
+HV is generated. To illustrate \emph{sequential
+multiplicativity}, we must choose to measure
+$\hat{A}_{33}$. According to step 3, since
+$\left|00\right\rangle $ is an eigenstate of
+$\hat{A}_{33}$, the final state remains
+$\left|00\right\rangle $.
 
-\subsection{C-ingle model | An Explicit Construction \label{ssec:cingle}}
+For the next iteration, $i=2$, viz.
+after the first measurement has been performed,
+say the random number generator yielded $c=0.1$.
+Since $\left|\psi\right\rangle $ is also unchanged
+the assignment remains invariant (in fact any of
+$c<0.5$ would yield the same result), which should
+be evident from the previous exercise. For the
+final step we choose to measure
+$\hat p := \hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
+to proceed with sequentially measuring
+$\hat{C}_{3}$. To simplify calculations, we note
+\[ \left|00\right\rangle
+=\frac{(\left|\tilde{+}\tilde{-}\right\rangle
++\left|\tilde{-}\tilde{+}\right\rangle
+)/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle
++\left|\tilde{-}\tilde{-}\right\rangle
+)/\sqrt{2}}{\sqrt{2}}, \] where
+$\left|\tilde{\pm}\right\rangle
+=\left|0\right\rangle \pm i\left|1\right\rangle $
+(eigenkets of $\hat{\sigma}_{y}$). Since
+$\left|00\right\rangle $ is manifestly not an
+eigenket of $\hat{p}$, we must find an appropriate
+eigenket $\left|p_{-}\right\rangle $ s.t.
+$\hat{p}\left|p_{-}\right\rangle
+=-\left|p_{-}\right\rangle $, since $c=0.1$ and
+$\left\langle p_{-}|00\right\rangle $ is already
+$>0.1$. It is immediate that
+$\left|p_{-}\right\rangle
+=\left(\left|\tilde{+}\tilde{-}\right\rangle
++\left|\tilde{-}\tilde{+}\right\rangle
+\right)/\sqrt{2}=\left(\left|00\right\rangle
++\left|11\right\rangle \right)/\sqrt{2}$, which
+becomes the final state. \\ For the final
+iteration, $i=3$, say we obtain $c=0.7$. So far,
+we have $m_{1}(\hat{A}_{33})=1$ and
+$m_{2}(\hat{A}_{23})=-1$. We must obtain
+$m_{3}(\hat{A}_{13})=1$, independent of the value
+of $c$, to be consistent. Let's check that.
+Indeed, according to postulate 2, since
+$\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle
++\left|11\right\rangle
+\right)/\sqrt{2}=1\left(\left|00\right\rangle
++\left|11\right\rangle \right)/\sqrt{2}$,
+$m_{3}(\hat{A}_{13})=1$ for all allowed values of
+$c$. As a remark, it maybe emphasised that the
+$m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$ and
+$m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which
+essentially expresses compatibility of these
+observables, viz. measurement of $\hat{A}_{13}$
+doesn't affect the result one would obtain by
+measuring operators compatible to it (granted they
+have been measured once before).
 
-Let the state of the system be $\left|\chi\right\rangle $, defined on a finite dimensional Hilbert space and we wish to assign a value to an arbitrary observable $\hat{A}=\sum_{a}a\left|a\right\rangle \left\langle a\right|$, which has eigenvalues $\{a_{\text{min}}=a_{1}\le a_{2}\dots\le a_{n}=a_{\text{max}}\}$.
-This model has the following postulates: \\
-1. Initial HV: Pick a $c\in[0,1]$, from a uniform random distribution.\\
-2. Assignment/Prediction: The value assigned to $\hat{A}$ is given by finding the smallest $a$ s.t. 
-\[
-c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle a'|\chi\right\rangle \right|^{2},
-\]
-viz. we have specified a prediction map, $m(\hat{A})=a$.\\
-3. Update: After measuring an operator, the state is updated (collapsed) in accordance with the rules of QM. This completely specifies the sequence map $s$.
+%\begin{widetext}
+%\onecolumngrid
+\begin{table*}
+ \begin{equation*}
+\begin{array}{ccc} 
+i=1,c=0.4,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle & i=2,c=0.1,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle & i=3,c=0.7,\left|\psi_{\text{init}}\right\rangle=\frac{\left|00\right\rangle +\left|11\right\rangle}{\sqrt{2}} \\
+%\text{Iteration} & i=1 & i=2 & i=3\\ 
+%\left|\psi_{\text{init}}\right\rangle  & \left|00\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle}{\sqrt{2}}\\ 
+%\text{HV} & c=0.4 & c=0.1 & c=0.7\\ \\
 
-To see how this works, we restrict ourselves to a single spin half particle.
-Say $\left|\chi\right\rangle =\cos\theta\left|0\right\rangle +\sin\theta\left|1\right\rangle $, and $\hat{A}=\hat{\sigma}_{z}=\left|0\right\rangle \left\langle 0\right|-\left|1\right\rangle \left\langle 1\right|$.
-Now, according to the postulates of this theory, $m(\hat{A})=+1$, if $c\le\cos^{2}\theta$ else $\hat{A}$ is assigned $-1$.
-It follows then, from $c$ being uniformly random in $[0,1]$ that the statistics agree with predictions of QM.
-The reader can convince him(her)self that the said scheme works in general.
+m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc} -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
+m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
+m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}+1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1\end{array}\right]\\ \\
 
-Note that the assignment, described by the prediction map $m$, is non-contextual since given an operator and a state (+ the HV), the value is uniquely assigned.
-The map $m$ is, however, non-multiplicative which is clarified by the following non-trivial example.
-\begin{example}
-C-ingle model applied to the Peres Mermin situation: For illustration, let us start with the state $\left|\psi_{1}\right\rangle =\left|00\right\rangle $.
-Say from a uniform random distribution we obtained $c=0.4$.
-To arrive at the assignments, note that $\left|00\right\rangle $ is an eigenket of only $\hat{R}_{i},\hat{C}_{j}$ and $\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$.
-Thus, in the first iteration, all these should be assigned their respective eigenvalues.
-The remaining operators must be assigned $-1$ as one can readily verify by explicitly finding the smallest $a$ as described in postulate 2 of the model (see \eqref{toyModel}).
-Two remarks are in order.
-First, this model is manifestly \emph{non-multiplicative}, for $m_{1}(\hat{C}_{3})=1\neq m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$, where the subscript has been introduced to index the iteration.
-More precisely, $m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle =\left|00\right\rangle \right])$ where the complete state $\left[\left|\psi_{1}\right\rangle \right]$ implicitly refers to both the quantum state $\left|00\right\rangle $ and the HV $c=0.4$.
-Second, we must impose \emph{sequential multiplicativity} as a consistency check of the model, which in particular entails that $m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$, where $m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle \right])$, $m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle \right])$ and
-$\left|\psi_{2}\right\rangle ,\,\left|\psi_{3}\right\rangle $ are obtained from postulate 3.
-Note that for each iteration, a new HV is generated.
-To illustrate \emph{sequential multiplicativity}, we must choose to measure $\hat{A}_{33}$.
-According to step 3, since $\left|00\right\rangle $ is an eigenstate of $\hat{A}_{33}$, the final state remains $\left|00\right\rangle $.
-\end{example}
-\begin{widetext}
-\begin{equation}
-\begin{array}{c|ccc}
-\text{Iteration} & i=1 & i=2 & i=3\\
-\left|\psi_{\text{init}}\right\rangle  & \left|00\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}\\
-\text{HV/Toss} & c=0.4 & c=0.1 & c=0.7\\
-\\
-\text{Predictions} & m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
--1 & -1 & -1\\
--1 & -1 & -1\\
--1 & -1 & +1
-\end{array}\right] & m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
--1 & -1 & -1\\
--1 & -1 & -1\\
--1 & -1 & +1
-\end{array}\right] & m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
-+1 & +1 & +1\\
-+1 & +1 & -1\\
-+1 & +1 & +1
-\end{array}\right]\\
-\text{(Assignments)}\\
- & m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) & m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) & m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
- & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
-\text{Operator}\\
-\text{Measured} & \hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1 & \quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad & \hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
-\\
-\left|\psi_{\text{final}}\right\rangle  & \left|00\right\rangle  & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}} & \frac{\left|00\right\rangle +\left|11\right\rangle }{\sqrt{2}}
-\end{array}\label{eq:toyModel}
-\end{equation}
-\end{widetext}
-For the next iteration, $i=2$, viz. after the first measurement has
-been performed, say the random number generator yielded $c=0.1$.
-Since $\left|\psi\right\rangle $ is also unchanged the assignment
-remains invariant (in fact any of $c<0.5$ would yield the same result),
-which should be evident from the previous exercise. For the final
-step we choose to measure $\hat{p}:=\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
-to proceed with sequentially measuring $\hat{C}_{3}$. To simplify
-calculations, we note 
-\[
-\left|00\right\rangle =\frac{(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle )/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle +\left|\tilde{-}\tilde{-}\right\rangle )/\sqrt{2}}{\sqrt{2}},
-\]
-where $\left|\tilde{\pm}\right\rangle =\left|0\right\rangle \pm i\left|1\right\rangle $
-(eigenkets of $\hat{\sigma}_{y}$). Since $\left|00\right\rangle $
-is manifestly not an eigenket of $\hat{p}$, we must find an appropriate
-eigenket $\left|p_{-}\right\rangle $ s.t. $\hat{p}\left|p_{-}\right\rangle =-\left|p_{-}\right\rangle $,
-since $c=0.1$ and $\left\langle p_{-}|00\right\rangle $ is already
-$>0.1$.
-It is immediate that $\left|p_{-}\right\rangle =\left(\left|\tilde{+}\tilde{-}\right\rangle +\left|\tilde{-}\tilde{+}\right\rangle \right)/\sqrt{2}=\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
-which becomes the final state. \\
-For the final iteration, $i=3$, say we obtain $c=0.7$. So far, we
-have $m_{1}(\hat{A}_{33})=1$ and $m_{2}(\hat{A}_{23})=-1$. We must
-obtain $m_{3}(\hat{A}_{13})=1$, independent of the value of $c$,
-to be consistent. Let's check that. Indeed, according to postulate
-2, since $\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}=1\left(\left|00\right\rangle +\left|11\right\rangle \right)/\sqrt{2}$,
-$m_{3}(\hat{A}_{13})=1$ for all allowed values of $c$. As a remark,
-it maybe emphasised that the $m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$
-and $m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which essentially
-expresses compatibility of these observables, viz. measurement of
-$\hat{A}_{13}$ doesn't affect the result one would obtain by measuring
-operators compatible to it (granted they have been measured once before).
+m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) &
+m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) &
+m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
 
-\subsection{Non-contextual Bohmain Mechanics \label{ssec:nonContBohm}}
+m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
 
-Since QM yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM.
-HV theories do precisely this and we have at our disposal the heretic theory of Bohm.
-Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$.
-The construction is such that the particles are guided by the wavefunction.
-Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `HV').
-The essence of Bohmian Mechanics relevant here can be captured by the following theorem.
+\hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1&
+\quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad&
+\hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
 
-\begin{defn}
-(a) the set of all experimental setups is denoted by $\mathcal{E}$, (b) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$.
-\end{defn}
+\left|\psi_{\text{final}}\right\rangle = \left|00\right\rangle  & \left|\psi_{\text{final}}\right\rangle = \frac{\left|00\right\rangle +\left|11\right\rangle}{\sqrt{2}} & \left|\psi_{\text{final}}\right\rangle = \frac{\left|00\right\rangle+\left|11\right\rangle }{\sqrt{2}}
+% \begin{bmatrixT} 
+% \text{Iteration} & i=1 & i=2
+% & i=3\\ \left|\psi_{\text{init}}\right\rangle  &
+% \left|00\right\rangle  & \left|00\right\rangle  &
+% \frac{\left|00\right\rangle +\left|11\right\rangle
+% }{\sqrt{2}} \\
+% \text{HV} & c=0.4 & c=0.1 & c=0.7 \\
 
-\begin{thm}
-$\exists$ a (Bohmian) map $m_{B}:\hat{\mathcal{H}},[\mathcal{H}],\mathcal{E}\to\mathbb{R}$, and a sequence map $s$, s.t.
-if $m_{B}$ \& $s$ are assumed to describe the outcomes of measurements \& the resultant state respectively, then they are consistent with all predictions of QM.
-\end{thm}
-Observe that given a Stern-Gerlach setup and the initial conditions (position \& wavefunction of the particle), according to the theorem, Bohmian mechanics can predict the value of the spin (say $\hat{\sigma}_{z}$) of the particle.
-Assume that the state of the particle was $(\left|0\right\rangle +\left|1\right\rangle )/\sqrt{2}$ and that the measurement outcome was spin up.
-Interestingly, it has be shown that if the direction of the magnetic field gradient is flipped while everything else is unchanged, the measurement outcome will now be spin down \cite{Detlef}.
-This emphasises the fact that $m_{B}$ is not a prediction map.
-More importantly it entails that $m_{B}$ is contextual.
-It must be stressed, however, that the contextuality in this case is not a statement about the context in terms of compatible observables.
-Here no two observables are compatible (excluding identity).
-Contextuality in Bohmian Mechanics arises from the mapping between an operator and the experimental setup. Consider, however, the following proposition.
-\begin{lem}
-For finite dimensional $\mathcal{H}$, $\exists$ a map $e:\hat{\mathcal{H}}\to\mathcal{E}$. \label{lem:OpeExp} (See \ref{proofs})
-\end{lem}
-The proof of this proposition can be motivated by a simple construction.
-Consider that the system of interest are spin half particles.
-To measure spin along any direction, there are two directions along which the magnetic field gradient can be set (as was discussed in the introduction).
-The experimentalist agrees to always use a specific direction, thereby mapping an operator to an experimental setup uniquely.
-Given this, one can immediately derive a consistent non-multiplicative prediction map $m$.
-\begin{prop}
-The Bohmian map, $m_{B}$ can be restricted to a prediction map $m$, we call `Bohmian prediction map'.
-\end{prop}
-\begin{proof}
-$m(\hat{\mathcal{H}},[\mathcal{H}])=m_{B}(\hat{\mathcal{H}},[\mathcal{H}],e(\hat{\mathcal{H}}))$.
-\end{proof}
-\begin{prop}
-The Bohmian prediction map, $m$ must be non-multiplicative.
-\end{prop}
-\begin{proof}
-Since Bohmian Mechanics is consistent with all predictions of QM, the Bohmian prediction map $m$ must also be. According to \thmref{KS}, $m$ must be non-multiplicative.
-\end{proof}
+% \text{Predictions or} &
+% {m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
+% \end{array}\right]} &
+% {m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1
+% \end{array}\right]} &
+% {m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}
+% +1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1
+% \end{array}\right]}\\
 
-\section{Concluding Remarks \label{sec:implications}}
+% \text{(Assignments)} &
+% m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3)
+% &
+% m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3)
+% &
+% m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
+% & m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 &
+% m_{3}(\hat{C}_{3})=-1
+% \end{bmatrixT}
+\label{eq:toyModel}
+\end{array}
+% \label{eq:toyModel}
+\end{equation*}
+\caption{HV model applied to the Peres Mermin situation}
+\label{tbl:HVmodel}
+\end{table*}
+%\end{widetext}
 
-\subsection{Locality}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\color{red} Will work on CC after everthin else
+is done}
+This has implications to Bohm's HV model as well, Bohmian Mechanics (BM), where the notion of positions (and hence trajectories) is precisely defined and particles are guided by the wavefunction.
+Consequently, given the initial conditions precisely (which is never the case experimentally) one can predict results of all experiments precisely.
+This entails that BM is capable of predicting outcomes of, for instance, a Stern Gerlach experiment.
+However, within BM two experiments which correspond to measurement of the same operator, can yield opposite results.
+Further, this can be demonstrated for a single spin half particle.
+This observation is often used as a demonstration of `contextuality' in BM, although we did not even speak of compatible measurements.
+It turns out, however, that if one restricts oneself to a one-one map between an experiment and an observable (by following some convention for example) then the so called `contextuality' can be removed from BM.
+One finds that the map so obtained from observables to their predictions turns out to be non-multiplicative, suggesting that at least in this case, non-multiplicativity is a more suitable explanation of non-classicality.
 
-\begin{defn}
-A theory/model/map is \emph{local} iff two spatially distinct points can not be influenced instantaneously.
-\end{defn}
+We have already constructed an explicit non-contextual model,
+which is consistent with QM.  This model we knew
+had to be non-multiplicative.  We will see how
+non-multiplicativity gives rise to what one might
+confuse to mean contextuality.  Imagine $\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle
+\left\langle 00\right|+\left|01\right\rangle
+\left\langle 01\right|-\left[\left|10\right\rangle
+\left\langle 10\right|+\left|11\right\rangle
+\left\langle 11\right|\right],$ $
+\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle
+\left\langle 10\right|+\left|11\right\rangle
+\left\langle 11\right|-\left[\left|00\right\rangle
+\left\langle 00\right|+\left|01\right\rangle
+\left\langle 01\right|\right],$ while we define
+$ \hat{C}=f(\{\hat{B}_{i}\})
+=0.\left|00\right\rangle \left\langle
+00\right|+1.\left|01\right\rangle \left\langle
+01\right|+2.\left|10\right\rangle \left\langle
+10\right|+3.\left|11\right\rangle \left\langle
+11\right|. $
 
-\begin{prop}
-A prediction map $m$ consistent with QM must be non-local \label{prop:predMapNonLocal} (see \ref{proofs} for details).
-\end{prop}
+% \begin{align*} \hat{C}&=f(\{\hat{B}_{i}\}) \\
+% &=0.\left|00\right\rangle \left\langle
+% 00\right|+1.\left|01\right\rangle \left\langle
+% 01\right|+2.\left|10\right\rangle \left\langle
+% 10\right|+3.\left|11\right\rangle \left\langle
+% 11\right|.  \end{align*}
+ $\hat{C}$ maybe viewed as
+a function of $\hat{B}_{1}$, $\hat{B}_{2}$ and
+other operators $\hat{B}_{i}$ which are
+constructed to obtain a maximally commuting set. A
+measurement of $\hat{C}$, will collapse the state
+into one of the states which are simultaneous
+eignkets of $B_{1}$ and $B_{2}$. Consequently,
+from the observed value of $\hat{C}$, one can
+deduce the values of $\hat{B}_{1}$ and
+$\hat{B}_{2}$. Now consider
+$\sqrt{2}\left|\chi\right\rangle
+=\left|10\right\rangle +\left|01\right\rangle $,
+for which $m_{1}(\hat{B}_{1})=1$, and
+$m_{1}(\hat{B}_{2})=1$, using the C-ingle model,
+with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
+which one can deduce that $B_{1}$ was $+1$, while
+$B_{2}$ was $-1$.  This property itself, one may
+be tempted call contextuality, viz.  the value of
+$B_{1}$ depends on whether it is measured alone or
+with the remaining $\{B_{i}\}$. However, it must
+be noted that $B_{1}$ has a well defined value,
+and so does $\hat{C}$. Thus by our accepted
+definition, there's no contextuality. It is just
+that $m_{1}(\hat{C})\neq
+\tilde f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
+viz. the theory is non-multiplicative. Note that
+after measuring $\hat{C}$ however,
+$m_{2}(\hat{B}_{1})=+1$ and
+$m_{2}(\hat{B}_{2})=-1$ (for any value of $c$)
+consistent with those deduced by measuring
+$\hat{C}$.
 
-\begin{prop}
-Consider a product Hilbert space $\mathcal{H}_{A}\otimes\mathcal{H}_{B}$, corresponding to two particles.
-$\mathcal{H}_{A}$ and $\mathcal{H}_{B}$ are finite dimensional.
-Let mutually commuting observables $\hat{B}_{i}$ be s.t.
-$\hat{B}_{i}=\hat{\mathbb{I}}\otimes\hat{A}_{\text{B}i}$ or $\hat{B}_{i}=\hat{A}_{\text{A}i}\otimes\hat{\mathbb{I}}$, where $A_{\text{A}i}\in\mathcal{\hat{H}}_{A}$ and $A_{\text{B}i}\in\hat{\mathcal{H}}_{B}$ are arbitrary observables.
-If locality is assumed, then a prediction map $m$ and it's associated sequence map $s$ must be s.t.
-over these observables, sequential multiplicativity and multiplicativity become identical.
-\end{prop}
-
-\subsection{Apparent Contextuality}
-
-We have already constructed an explicit non-contextual model, which
-is consistent with QM. This model we knew had to be non-multiplicative.
-We will see how non-multiplicativity gives rise to what one might
-confuse to mean contextuality. Imagine 
-\[
-\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|-\left[\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|\right],
-\]
-\[
-\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle \left\langle 10\right|+\left|11\right\rangle \left\langle 11\right|-\left[\left|00\right\rangle \left\langle 00\right|+\left|01\right\rangle \left\langle 01\right|\right],
-\]
-while we define 
-\begin{align*}
-\hat{C}&=f(\{\hat{B}_{i}\}) \\ 
-       &=0.\left|00\right\rangle \left\langle 00\right|+1.\left|01\right\rangle \left\langle 01\right|+2.\left|10\right\rangle \left\langle 10\right|+3.\left|11\right\rangle \left\langle 11\right|.
-\end{align*}
-$\hat{C}$ maybe viewed as a function of $\hat{B}_{1}$, $\hat{B}_{2}$
-and other operators $\hat{B}_{i}$ which are constructed to obtain
-a maximally commuting set. A measurement of $\hat{C}$, will collapse
-the state into one of the states which are simultaneous eignkets of
-$B_{1}$ and $B_{2}$. Consequently, from the observed value of $\hat{C}$,
-one can deduce the values of $\hat{B}_{1}$ and $\hat{B}_{2}$. Now
-consider $\sqrt{2}\left|\chi\right\rangle =\left|10\right\rangle +\left|01\right\rangle $,
-for which $m_{1}(\hat{B}_{1})=1$, and $m_{1}(\hat{B}_{2})=1$, using
-the C-ingle model, with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
-which one can deduce that $B_{1}$ was $+1$, while $B_{2}$ was $-1$.
-This property itself, one may be tempted call contextuality, viz.
-the value of $B_{1}$ depends on whether it is measured alone or with
-the remaining $\{B_{i}\}$. However, it must be noted that $B_{1}$
-has a well defined value, and so does $\hat{C}$. Thus by our accepted
-definition, there's no contextuality. It is just that $m_{1}(\hat{C})\neq f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
-viz. the theory is non-multiplicative. Note that after measuring $\hat{C}$
-however, $m_{2}(\hat{B}_{1})=+1$ and $m_{2}(\hat{B}_{2})=-1$ (for
-any value of $c$) consistent with those deduced by measuring $\hat{C}$.
-
-\subsection{Entanglement and Superposition}
-
-It is known that for simultaneous eigenstates of $\hat{B}_{i}$, multiplicativity
-must hold. Consequently, any violation of multiplicativity must arise
-from states that are superpositions (of the simultaneous eigenkets).
-Note however, that entanglement is not necessary to show a violation,
-since, for example, the PM test is a state independent test, where
-a separable state can be used to arrive at a contradiction. For demonstrating
-non-locality using Bell's proof, however, it can be shown that entanglement
-is necessary.
-
-TODO: Discuss and complete.
-\begin{appendix}
-\section{Selected Proofs \label{proofs}}
-Proofs of \thmref{det}:
-\begin{proof}
-Trivial yet most general proof ($\left|\mathcal{H}\right|\ge2$): Consider $\hat A _1 = \sigma_y$, $\hat A_2 =\sigma_x$, $\hat C = f(\hat A_1,\hat A_2) = i\hat A_1 \hat A_2=\sigma_z$.
-Now we know that $m(\hat \sigma_j)=\pm1$ which entails that $m(\hat C)=  im(\hat A_1)m(\hat A_2)=i$ where we have used property (b).
-However, $m(\hat C)=m(\hat \sigma_z)=\pm1$ which is a contradiction.
-Thus no consistent $m$ can exist.
-\end{proof}
-
-\begin{proof}
-Bell construction ($\left|\mathcal{H}\right|\ge4$) \cite{Bell1964}: Consider an operator $\hat{B}:=a_{1}\otimes b_{1}+a_{2}\otimes b_{1}+a_{1}\otimes b_{2}-a_{2}\otimes b_{2}$ s.t.
-$-1\le\hat{a}_{i},\hat{b}_{j}\le1$ $\forall\,i,j\in\{1,2,3,4\}$ (which means that the spectrum of $\hat{a}$ and $\hat{b}$ are bounded above and below).
-If we assume that a map $m$ of the aforesaid type exists, then it can be shown that $\left\langle \hat{B}\right\rangle \le2$.
-To see this, consider $\hat{A}_{1}=\hat{a}_{1}\otimes\hat{\mathbb{I}}$ and $\hat{A}_{2}=\hat{\mathbb{I}}\otimes\hat{b}_{1}$, so that if $\hat{C}:=\hat{A}_{1}\hat{A}_{2}$ then property (2) entails that $m(\hat{C})=m(\hat{A}_{1})m(\hat{A}_{2})$, viz.
-$m(\hat{a}_{1}\otimes\hat{b}_{1})=m(\hat{a}_{1}\otimes\hat{\mathbb{I}})m(\hat{\mathbb{I}}\otimes\hat{b}_{1})$.
-Note that $m(\hat{*})$, may depend on the state $\left|\psi\right\rangle $ and the HVs.
-Therefore, we average over multiple measurements, which corresponds
-to averaging over the HVs.
-This is expressed by $\left\langle m(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
-One can repeat this argument for each term in $\left\langle \hat{B}\right\rangle $.
-Using the fact that $-1\le m(\hat{*})\le1$, and that the extrema will occur only at the extreme values of $m$, one can plugin $\pm1$ for each $\left\langle m(\hat{*})\right\rangle $ to obtain $\left\langle \hat{B}\right\rangle \le2$.
-Quantum mechanically, one can show that $\left\langle \hat{B}\right\rangle =2\sqrt{2}$ for the state $\left|\psi\right\rangle =\left(\left|+-\right\rangle -\left|-+\right\rangle \right)/\sqrt{2}$,
-where $\hat{\sigma}_{x}\left|\pm\right\rangle =\pm\left|\pm\right\rangle $, and $\hat{\sigma}_{x,y,z}$ are the Pauli matrices, given in the z-basis as  \[
-\hat{\sigma}_{x}\doteq\left[\begin{array}{cc}
-0 & 1\\
-1 & 0
-\end{array}\right],\,\hat{\sigma}_{y}\doteq\left[\begin{array}{cc}
-0 & -i\\
-i & 0
-\end{array}\right],\,\hat{\sigma}_{z}\doteq\left[\begin{array}{cc}
-1 & 0\\
-0 & -1
-\end{array}\right].
-\] The observables are $\hat{a}_{1}=\hat{\sigma}_{z}$ and $\hat{a}_{2}=\hat{\sigma}_{x}$, while $\hat{b}_{1}=-\frac{\hat{\sigma}_{z}+\hat{\sigma}_{x}}{\sqrt{2}}$ and $\hat{b}_{2}=\frac{\hat{\sigma}_{z}-\hat{\sigma}_{x}}{\sqrt{2}}$.
-Since QM violates the inequality, $\left\langle \hat{B}\right\rangle \le2$, we conclude that the map $m$ can not simultaneously exist and be consistent with QM.
-\end{proof}
-
-\begin{proof}
-GHZ construction ($\left|\mathcal{H}\right|\ge6$) \cite{GHZ}: Consider three observers with one spin half particle each.
-Each observer can measure two properties, call them X and Y, with outcomes $\pm1$.
-The associated operators are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$.
-The state of the system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $ and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$, $\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $, $\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$ and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
-A measurement of $\hat{A}$ would correspond to measurement of property $X,\,Y$ and $Y$ by the three observers respectively.
-For a map $m$ consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
-Property (b) of the map $\implies1=m(\hat{A}\hat{B}\hat{C})=m(\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\hat{\sigma}_{x}\hat{\sigma}_{y}\otimes\hat{\sigma}_{x})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{y}^{(2)}\hat{\sigma}_{x}^{(2)}\hat{\sigma}_{y}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{x}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{D}\equiv\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}),$
-where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$ and so on.
-It must be stressed that although $\hat{A}$, $\hat{B}$ and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$ do not.
-We used property (b) over both these sets of operators in the previous step.
-Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $, $\implies m(\hat{D})=-1$ which yields a contradiction.
-We therefore conclude that no $m$ with the said properties exists which is consistent with all predictions of QM.
-\end{proof}
-
-Proofs of \thmref{KS}:
-\begin{proof}
-Kochen Specker ($\left|\mathcal{H}\right|\ge3$) \cite{KochenSpecker}: The original proof given by is rather involved.
-Here we will satisfy ourselves with assuming its validity and applying our constructions to the aforesaid proof.
-\end{proof}
-
-\begin{proof}
-Bell construction ($\left|\mathcal{H}\right|\ge4$): The same proof as the one presented earlier goes through here also since $[A_{1},A_{2}]=0$.
-\end{proof}
-
-\begin{proof}
-Generalized GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider again, three observers with one quantum particle each.
-Each observer can measure the properties corresponding to $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$ of his/her particle.
-The quantum state of these particles is also the same as before, $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $.
-We define as earlier $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ $\implies\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $, $\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$ and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
-Consider in addition the following operators, represented by $\hat{H}_{ij}$.
-\[
-\hat{H}_{ij}\doteq\left[\begin{array}{ccc}
-\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}^{(a)} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{y}\otimes\hat{\mathbb{I}}^{(2)} & \mathbb{\hat{I}}\otimes\mathbb{\hat{I}}\otimes\hat{\sigma}_{y}^{(3)}\\
-\hat{\sigma}_{y}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(1)} & \hat{\mathbb{I}}\otimes\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}^{(b)} & \mathbb{\hat{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{y}^{(3)}\\
-\hat{\sigma}_{y}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(1)} & \mathbb{\hat{I}}\otimes\hat{\sigma}_{y}\otimes\hat{\mathbb{I}}^{(2)} & \mathbb{\hat{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{x}^{(c)}\\
-\hat{\sigma}_{x}\otimes\mathbb{\hat{I}}\otimes\hat{\mathbb{I}}^{(a)} & \mathbb{\hat{I}}\otimes\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}^{(b)} & \hat{\mathbb{I}}\otimes\hat{\mathbb{I}}\otimes\hat{\sigma}_{x}^{(c)}
-\end{array}\right],
-\]
-where from property (b) it follows that $m(\hat{A})=m(\hat{H}_{11})m(\hat{H}_{12})m(\hat{H}_{13})$.
-Note that $[\hat{H}_{ij},\hat{H}_{ik}]=0$, viz.
-the operators along a row commute.
-To be consistent with QM, $m(\hat{A})=+1$ (similarly for row 2 and 3).
-$m(\hat{D})=-1$ imposes that the product $m(\hat{H}_{41})m(\hat{H}_{42})m(\hat{H}_{43})$, row 4, must be $-1$.
-Using the notation $m(\hat{H}_{ij})=H_{ij}$, we can start with the first case.
-For the last row to yield $-1$, we must have either one $-1$ assignments or three $-1$ assignments.
-Let us look at the first case.
-Without loss of generality, we can assume that $H_{41}=H_{42}=+1$ and $H_{43}=-1$.
-Further, $H_{11}=H_{41}$, $H_{22}=H_{42}$ and $H_{33}=H_{43}$ by construction (see below).
-\[
-H_{ij}\doteq\left[\begin{array}{ccc}
-1\\
- & 1\\
- &  & -1\\
-1 & 1 & -1
-\end{array}\right],H_{ij}\doteq\left[\begin{array}{ccc}
-1 & \pm1 & \pm1\\
-\pm1 & 1 & \pm1\\
-\pm1 & \pm1 & -1\\
-1 & 1 & -1
-\end{array}\right].
-\] Next, one must ensure that the first row yields $+1$ which requires us to either set $H_{12}=H_{13}$ to $-1$ or $+1$.
-Let us write this as $H_{12}=H_{13}=\pm1$ which would entail that $H_{23}=\pm1$ and $H_{32}=\pm1$.
-{[} Note that the notation implies that when we choose $+1$, all these are $+1$ and when we choose $-1$, all are $-1$.
-We are not allowed to set, say $H_{12}=-1$ and $H_{13}=+1$.
-{]} For the second row to be $+1$, we conclude that $H_{21}=\pm1$.
-This entails, in turn, that $H_{31}=\pm1$.
-We now note that the third row has become $-1$ whereas according to QM, it must be $+1$.
-It is left upto the reader to see that similar reasoning also yields results in inconsistencies with QM.
-This completes the proof.
-\end{proof}
-
-Proof of \propref{predMapNonLocal}:
-\begin{proof}
-{[}Adapted from Bell's proof \cite{Bell1964}{]} Formally it is clear, since a violation of Bell's inequality implies non-locality.
-Consequently, any consistent completion of QM, will be non-local.
-More insight can be gained, although some care is needed.
-The notion of compatible observables is that commuting observables don't disturb each other and can be simultaneously known.
-While the statement is not precisely stated, we only need to note that $m_{k_{1}}(\hat{C})=m_{k_{2}}(\hat{B}_{1})m_{k_{3}}(\hat{B}_{2})$, for $(k_{1},k_{2},k_{3})\in\{(1,2,3),(2,1,3),\dots\}$ where $m_{i}$ are defined as before.
-In words, this means that to measure $\hat{C}$, one can instead first measure $\hat{B}_{1}$ and then measure $\hat{B}_{2}$.
-A multiplication of the values obtained, can be taken to be the value a measurement of $\hat{C}$ yields.
-This can be verified by measuring $\hat{C}$ subsequently.
-The Bell scenario offers an interesting freedom, by restricting the form of $\hat{B}_{i}$.
-To evaluate $\left\langle \hat{B}\right\rangle $, one is required to evaluate $\left\langle \hat{B}_{1}\hat{B}_{2}\right\rangle $.
-From the compatibility argument, we need to find the average value of $m_{3}(\hat{B}_{1}\hat{B}_{2})=m_{1}(\hat{B}_{1})m_{2}(\hat{B}_{2})$, viz.
-$\left\langle m_{3}(\hat{a}_{1}\otimes\hat{b}_{1})\right\rangle =\left\langle m_{1}(\hat{a}_{1}\otimes\hat{\mathbb{I}})\right\rangle \left\langle m_{2}(\hat{\mathbb{I}}\otimes\hat{b}_{1})\right\rangle $.
-So far, the statements were general.
-Now we assume that our theory is non-multiplicative (and non-contextual).
-A consistent theory (with QM), using these assumptions, can and must violate $\left\langle \hat{B}\right\rangle \le2$.
-However, if the particles are taken far away, then the only way the theory can be non-multiplicative ($m_{1}(\hat{B}_{1})\neq m_{2}(\hat{B}_{1})$ for example), is if the theory is non-local.
-Locality will entail
-that $m_{1}(\hat{B}_{1})=m_{2}(\hat{B}_{1})$ for instance, since the information about which observable was measured first, can't be propagated instantaneously.
-We see therefore that non-locality arises quite naturally in consistent non-multiplicative theories.
-\end{proof}
-
-Proof of \lemref{OpeExp}:
-\begin{proof} Adapted from Bohm's work \cite{Bohm2}\\
-To describe an experimental setup corresponding to a measurement, we use a measuring particle (mass $m_{L}$, say).
-It is made to interact with the system for a short duration appropriately and subsequently we measure the resultant position of the particle, to learn about the value of the observable of interest.
-Say for instance, we wish to measure the observable $\hat{L}$, then the required interaction Hamiltonian is given by $\hat{H}_{\text{int}}=a\hat{L}\otimes\hat{p}$.
-Here the first operator acts on the system and second (after the tensor product symbol) acts on the measuring particle.
-$a$ quantifies the interaction strength.
-{[}TODO: check this{]} It has dimensions of frequency, if $L$ has dimensions of length.
-Let us assume that the system in the state $\left|\psi\right\rangle $.
-Then it is known that one can express $\left|\psi\right\rangle =\sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle $, where $\left|l\right\rangle $ are the eigenstates of $\hat{L}$ with eigenvalue $l$ (we have assumed non-degeneracy for simplicity, but its removal doesn't cause any significant difficulty).
-$\left|\Psi_{S}(t)\right\rangle =\hat{U}(t)\left|\psi\right\rangle \otimes\left|\varphi\right\rangle $, where  \[
-\hat{U}(t)=e^{-\frac{i}{\hbar}\left[-\hbar^{2}\frac{\nabla_{1}^{2}}{2m}-\hbar^{2}\frac{\nabla_{2}^{2}}{2m_{L}}+\hat{H}_{\text{int}}\right]t}
-\]  and $\left|\varphi\right\rangle $ is the state of the measuring particle, given by a Guassian centred at the origin, $\varphi(q)=(1/\sqrt{2\pi}\sigma)e^{-q^{2}/2\sigma^{2}}$.
-If $t$ is very small, and $a$ very large, s.t.
-$at=\lambda$ is a finite number, then one can neglect the free evolution, $\nabla^{2}t$ terms compared to $\hat{H}_{\text{int}}t$.
-We then have
-\begin{eqnarray*}
-\left|\Psi_{S}(t)\right\rangle  & = & e^{-\frac{i}{\hbar}a\hat{L}\otimes\hat{p}t}\left|\Psi_{S}\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes e^{-\frac{i}{\hbar}\lambda l\,\hat{p}}\left|\varphi\right\rangle \\
- & = & \sum_{l}\left\langle l|\psi\right\rangle \left|l\right\rangle \otimes\left|\varphi_{\lambda l}\right\rangle ,
-\end{eqnarray*}
-where $\left|\varphi_{q_{0}}\right\rangle =\int dq\varphi(q-q_{0})\left|q\right\rangle $.
-This interaction, effectively entangles the measuring particle, with the possible `outcomes', eigenstates of the observable $\hat{L}$ of interest.
-If $\sigma\ll\lambda l$, then according to QM itself, a position measurement of the measuring particle, would correspond, in a one-to-one way, to the eigenstate/eigenvalue of $\hat{L}$, to which the system will collapse.
-Therefore, given an observable, one can construct the aforesaid experiment to measure its value.
-We have, in effect, explicitly constructed the map $e:\hat{\mathcal{H}}\to\mathcal{E}$.
-\end{proof}
-
-\end{appendix}
-
-\bibliographystyle{apsrev4-1}
+It is known that for simultaneous eigenstates of
+$\hat{B}_{i}$, multiplicativity must hold.
+Consequently, any violation of multiplicativity
+must arise from states that are superpositions (of
+the simultaneous eigenkets).  Note however, that
+entanglement is not necessary to show a violation,
+since, for example, the PM test is a state
+independent test, where a separable state can be
+used to arrive at a contradiction. For
+demonstrating non-locality using Bell's proof,
+however, it can be shown that entanglement is
+necessary.  \bibliographystyle{apsrev4-1}
 \bibliography{references}

### 2016-07-11 finalPaper.tex
fixed the capital and small m (s) issues + fixed some issues I had accidentally ignored

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%This stuff is required for transposing matrices | fine I didn't want to do donkey work
-\usepackage{xparse}
-\usepackage{environ}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%This stuff is required for transposing matrices | fine I didn't want to do donkey work
+% \usepackage{xparse}
+% \usepackage{environ}
 
-\ExplSyntaxOn
-\NewEnviron{bmatrixT}
- {
-  \marine_transpose:V \BODY
- }
+% \ExplSyntaxOn
+% \NewEnviron{bmatrixT}
+%  {
+%   \marine_transpose:V \BODY
+%  }
 
-\int_new:N \l_marine_transpose_row_int
-\int_new:N \l_marine_transpose_col_int
-\seq_new:N \l_marine_transpose_rows_seq
-\seq_new:N \l_marine_transpose_arow_seq
-\prop_new:N \l_marine_transpose_matrix_prop
-\tl_new:N \l_marine_transpose_last_tl
-\tl_new:N \l_marine_transpose_body_tl
+% \int_new:N \l_marine_transpose_row_int
+% \int_new:N \l_marine_transpose_col_int
+% \seq_new:N \l_marine_transpose_rows_seq
+% \seq_new:N \l_marine_transpose_arow_seq
+% \prop_new:N \l_marine_transpose_matrix_prop
+% \tl_new:N \l_marine_transpose_last_tl
+% \tl_new:N \l_marine_transpose_body_tl
 
-\cs_new_protected:Nn \marine_transpose:n
- {
-  \seq_set_split:Nnn \l_marine_transpose_rows_seq { \\ } { #1 }
-  \int_zero:N \l_marine_transpose_row_int
-  \prop_clear:N \l_marine_transpose_matrix_prop
-  \seq_map_inline:Nn \l_marine_transpose_rows_seq
-   {
-    \int_incr:N \l_marine_transpose_row_int
-    \int_zero:N \l_marine_transpose_col_int
-    \seq_set_split:Nnn \l_marine_transpose_arow_seq { & } { ##1 }
-    \seq_map_inline:Nn \l_marine_transpose_arow_seq
-     {
-      \int_incr:N \l_marine_transpose_col_int
-      \prop_put:Nxn \l_marine_transpose_matrix_prop
-       {
-        \int_to_arabic:n { \l_marine_transpose_row_int }
-        ,
-        \int_to_arabic:n { \l_marine_transpose_col_int }
-       }
-       { ####1 }
-     }
-   }
-   \tl_clear:N \l_marine_transpose_body_tl
-   \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_col_int }
-    {
-     \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_row_int }
-      {
-       \tl_put_right:Nx \l_marine_transpose_body_tl
-        {
-         \prop_item:Nn \l_marine_transpose_matrix_prop { ####1,##1 }
-         \int_compare:nF { ####1 = \l_marine_transpose_row_int } { & }
-        }
-      }
-     \tl_put_right:Nn \l_marine_transpose_body_tl { \\ }
-    }
-   \begin{bmatrix}
-   \l_marine_transpose_body_tl
-   \end{bmatrix}
- }
-\cs_generate_variant:Nn \marine_transpose:n { V }
-\cs_generate_variant:Nn \prop_put:Nnn { Nx }
-\ExplSyntaxOff
+% \cs_new_protected:Nn \marine_transpose:n
+%  {
+%   \seq_set_split:Nnn \l_marine_transpose_rows_seq { \\ } { #1 }
+%   \int_zero:N \l_marine_transpose_row_int
+%   \prop_clear:N \l_marine_transpose_matrix_prop
+%   \seq_map_inline:Nn \l_marine_transpose_rows_seq
+%    {
+%     \int_incr:N \l_marine_transpose_row_int
+%     \int_zero:N \l_marine_transpose_col_int
+%     \seq_set_split:Nnn \l_marine_transpose_arow_seq { & } { ##1 }
+%     \seq_map_inline:Nn \l_marine_transpose_arow_seq
+%      {
+%       \int_incr:N \l_marine_transpose_col_int
+%       \prop_put:Nxn \l_marine_transpose_matrix_prop
+%        {
+%         \int_to_arabic:n { \l_marine_transpose_row_int }
+%         ,
+%         \int_to_arabic:n { \l_marine_transpose_col_int }
+%        }
+%        { ####1 }
+%      }
+%    }
+%    \tl_clear:N \l_marine_transpose_body_tl
+%    \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_col_int }
+%     {
+%      \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_row_int }
+%       {
+%        \tl_put_right:Nx \l_marine_transpose_body_tl
+%         {
+%          \prop_item:Nn \l_marine_transpose_matrix_prop { ####1,##1 }
+%          \int_compare:nF { ####1 = \l_marine_transpose_row_int } { & }
+%         }
+%       }
+%      \tl_put_right:Nn \l_marine_transpose_body_tl { \\ }
+%     }
+%    \begin{bmatrix}
+%    \l_marine_transpose_body_tl
+%    \end{bmatrix}
+%  }
+% \cs_generate_variant:Nn \marine_transpose:n { V }
+% \cs_generate_variant:Nn \prop_put:Nnn { Nx }
+% \ExplSyntaxOff
 
@@
 prediction map is
-$m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$,
+$M:\{ \hat{\mathcal{H}},[\mathcal{H}] \}\to\mathbb{R}$,
 (f) a sequence map is
-$s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$,
+$S:\{ \hat{\mathcal{H}},[\mathcal{H}],\mathbb{R} \}\to[\mathcal{H}]$,
 (g) $f$ is an arbitrary map from $\{
@@
 \begin{defn} A theory is non-contextual, if it
-provides a map $m: \{
+provides a map $M: \{
 \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$
@@
 extended to maps. A map is non-contextual if it is
-of the form $m: \{ \hat{\mathcal{H}},[\mathcal{H}]
-\} \to\mathbb{R}$; prediction maps {\color{red}Comment: Is this really needed ``for individual
-observables''} are non-contextual by construction.  
+of the form $M: \{ \hat{\mathcal{H}},[\mathcal{H}]
+\} \to\mathbb{R}$; prediction maps as defined above, for individual observables, are non-contextual by construction.  
 \end{defnrem}
@@
 \begin{defn}
-A prediction map $m$ is \emph{multiplicative} iff
+A prediction map $M$ is \emph{multiplicative} iff
 \begin{align*} &
-m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])
+M(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi])
 = \\ & \tilde
-f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots
-m(\hat{B}_{N},[\psi])), \end{align*}
+f(M(\hat{B}_{1},[\psi]),M(\hat{B}_{2},[\psi]),\dots
+M(\hat{B}_{N},[\psi])), \end{align*}
 where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
@@
 \end{defn} 
-Note that if $m$ is taken to represent the
+Note that if $M$ is taken to represent the
 measurement outcome (in QM), then for states of
 the system which are simultaneous eigenkets of
-$\hat{B}_{i}$s, $m$ must clearly be
+$\hat{B}_{i}$s, $M$ must clearly be
 multiplicative. It is, however, not obvious that
@@
 written in terms of Pauli operators.
-We must have $m(\hat{C})=-1$ while
-$m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$
+We must have $M(\hat{C})=-1$ while
+$M(\hat{B}_{1})=\pm1$ and $M(\hat{B}_{2})=\pm1$
 independently, according to QM, with probability
@@
 sequence map $s$, iff \begin{align*}
-&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
+&M(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
 &\tilde
-f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
+f(M(\hat{B}_{1},[\psi_{k_{1}}]),M(\hat{B}_{2},[\psi_{k_{2}}]),\dots,M(\hat{B}_{N},[\psi_{k_{N}}])),
 \end{align*} 
@@
 $[\psi_{k+1}] :=
-s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
+S(\hat{B}_{k},[\psi_{k}],M(\hat{B}_{k},[\psi_{k}]))$,
 $\forall\,[\psi_{i}]$.  
@@
 \begin{thm} Let a map
-$m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
-$m(\hat{\mathbb{I}})=1$, (b)
-$m(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde
-f(m(\hat{B}_{1}),m(\hat{B}_{2}),\dots)$, for any
+$M:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
+$M(\hat{\mathbb{I}})=1$, (b)
+$M(f(\hat{B}_{1},\hat{B}_{2},\dots))=\tilde
+f(M(\hat{B}_{1}),M(\hat{B}_{2}),\dots)$, for any
 arbitrary function $f$, where $\hat{B}_{i}$ are
@@
 assumed to describe the outcomes of measurements,
-then no $m$ exists which is consistent with all
+then no $M$ exists which is consistent with all
 predictions of QM. 
@@
 $\hat{C}_{j}:=\prod_{i}\hat{A}_{ij}$. Let us
-assume that $m$ exists. From property (b) of the
-map, to get $m(\hat{C}_{3})=-1$ (as required by
+assume that $M$ exists. From property (b) of the
+map, to get $M(\hat{C}_{3})=-1$ (as required by
 property (a)), we must have an odd number of $-1$
@@
 odd. Let us use the same reasoning, but along the
-rows. Since each $m(\hat{R}_{i})=1$, we must have
+rows. Since each $M(\hat{R}_{i})=1$, we must have
 even number of $-1$ assignments along each row.
@@
 contradiction and therefore we conclude that our
-assumption that a consistent $m$ exists, must be
+assumption that a consistent $M$ exists, must be
 wrong.  \end{proof}
 
-\begin{thmrem} One could in principle assume $m$, to
-be s.t. (a) $m(\hat{\mathbb{I}})=1$, (b)
-$m(\alpha\hat{B}_{i})=\alpha m(\hat{B}_{i})$, for
+\begin{thmrem} One could in principle assume $M$, to
+be s.t. (a) $M(\hat{\mathbb{I}})=1$, (b)
+$M(\alpha\hat{B}_{i})=\alpha M(\hat{B}_{i})$, for
 $\alpha\in\mathbb{R}$, (c)
-$m(\hat{B}_{i}^{2})=m(\hat{B}_{i})^{2}$, (d)
-$m(\hat{B}_{i}+\hat{B}_{j})=m(\hat{B}_{i})+m(\hat{B}_{j})$,
+$M(\hat{B}_{i}^{2})=M(\hat{B}_{i})^{2}$, (d)
+$M(\hat{B}_{i}+\hat{B}_{j})=M(\hat{B}_{i})+M(\hat{B}_{j})$,
 to deduce (d')
-$m(\hat{B}_{i}\hat{B}_{j})=m(\hat{B}_{i})m(\hat{B}_{j})$
-and that $m(\hat{B}_{i})\in$ spectrum of
+$M(\hat{B}_{i}\hat{B}_{j})=M(\hat{B}_{i})M(\hat{B}_{j})$
+and that $M(\hat{B}_{i})\in$ spectrum of
 $\hat{B}_{i}$. Effectively then, condition (b)
@@
 consequence.  Therefore, assuming (a)-(d) as
-listed here, rules out a larger class of $m$.
+listed here, rules out a larger class of $M$.
 \cite{KochenSpecker} 
 \end{thmrem} 
-Here $m$ maybe viewed as a specific
+Here $M$ maybe viewed as a specific
 class of prediction maps, that implicitly depends
@@
 mutually compatible and a complete set of
-operators (Operators can be added to make the set
+observables (operators can be added to make the set
 complete if it not so).
@@
 a'|\chi\right\rangle \right|^{2},$ viz. we have
-specified a prediction map, $m(\hat{A})=a$.
+specified a prediction map, $M(\hat{A},[\chi ])=a$.
 \item
@@
 of QM. This completely specifies the sequence map
-$s$.
+$S$.
 \end{enumerate}
@@
 \left\langle 1\right|$. Now, according to the
-postulates of this theory, $m(\hat{A})=+1$, if
+postulates of this theory, $M(\hat{A},[\chi])=+1$, if
 the randomly generated value for 
@@
 Note that the assignment, described by the
-prediction map $m$, is non-contextual since given
+prediction map $M$, is non-contextual since given
 an operator and a state (+ the HV $c$), the value is
-uniquely assigned. The map $m$ is, however,
+uniquely assigned. The map $M$ is, however,
 non-multiplicative.
@@
 \emph{non-multiplicative}, for
-$m_{1}(\hat{C}_{3})=1\neq
-m_{1}(\hat{A}_{13})m_{1}(\hat{A}_{23})m_{1}(\hat{A}_{33})=-1$,
+$M_{1}(\hat{C}_{3})=1\neq
+M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=-1$,
 where the subscript has been introduced to index
 the iteration. More precisely,
-$m_{1}(\hat{O}):=m(\hat{O},\left[\left|\psi_{1}\right\rangle
+$M_{1}(\hat{O}):=M(\hat{O},\left[\left|\psi_{1}\right\rangle
 =\left|00\right\rangle \right])$ where the
@@
 model, which in particular entails that
-$m_{1}(\hat{C}_{3})=m_{1}(\hat{A}_{33})m_{2}(\hat{A}_{23})m_{3}(\hat{A}_{13})$,
+$M_{1}(\hat{C}_{3})=M_{1}(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
 where
-$m_{2}:=m(\hat{O},\left[\left|\psi_{2}\right\rangle
+$M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
 \right])$,
-$m_{3}:=m(\hat{O},\left[\left|\psi_{3}\right\rangle
+$M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
 \right])$ and $\left|\psi_{2}\right\rangle
@@
 iteration, $i=3$, say we obtain $c=0.7$. So far,
-we have $m_{1}(\hat{A}_{33})=1$ and
-$m_{2}(\hat{A}_{23})=-1$. We must obtain
-$m_{3}(\hat{A}_{13})=1$, independent of the value
+we have $M_{1}(\hat{A}_{33})=1$ and
+$M_{2}(\hat{A}_{23})=-1$. We must obtain
+$M_{3}(\hat{A}_{13})=1$, independent of the value
 of $c$, to be consistent. Let's check that.
@@
 +\left|11\right\rangle \right)/\sqrt{2}$,
-$m_{3}(\hat{A}_{13})=1$ for all allowed values of
+$M_{3}(\hat{A}_{13})=1$ for all allowed values of
 $c$. As a remark, it maybe emphasised that the
-$m_{2}(\hat{A}_{33})=m_{3}(\hat{A}_{33})$ and
-$m_{2}(\hat{A}_{23})=m_{3}(\hat{A}_{23})$, which
+$M_{2}(\hat{A}_{33})=M_{3}(\hat{A}_{33})$ and
+$M_{2}(\hat{A}_{23})=M_{3}(\hat{A}_{23})$, which
 essentially expresses compatibility of these
@@
 
-m_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc} -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
-m_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
-m_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}+1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1\end{array}\right]\\ \\
+M_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc} -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
+M_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
+M_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}+1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1\end{array}\right]\\ \\
 
-m_{1}(\hat{R}_{i}),m_{1}(\hat{C}_{j})=+1\,(j\neq3) &
-m_{2}(\hat{R}_{i}),m_{2}(\hat{C}_{j})=+1\,(j\neq3) &
-m_{3}(\hat{R}_{i}),m_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
+M_{1}(\hat{R}_{i}),M_{1}(\hat{C}_{j})=+1\,(j\neq3) &
+M_{2}(\hat{R}_{i}),M_{2}(\hat{C}_{j})=+1\,(j\neq3) &
+M_{3}(\hat{R}_{i}),M_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
 
-m_{1}(\hat{C}_{3})=-1 & m_{2}(\hat{C}_{3})=-1 & m_{3}(\hat{C}_{3})=-1\\
+M_{1}(\hat{C}_{3})=-1 & M_{2}(\hat{C}_{3})=-1 & M_{3}(\hat{C}_{3})=-1\\
 
-\hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};m_{1}(\hat{A}_{13})=+1&
-\quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};m_{2}(\hat{A}_{23})=-1\quad\quad&
-\hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};m_{3}(\hat{A}_{33})=+1\\
+\hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};M_{1}(\hat{A}_{13})=+1&
+\quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};M_{2}(\hat{A}_{23})=-1\quad\quad&
+\hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};M_{3}(\hat{A}_{33})=+1\\
 
@@
 11\right|. $
-
 % \begin{align*} \hat{C}&=f(\{\hat{B}_{i}\}) \\
@@
 =\left|10\right\rangle +\left|01\right\rangle $,
-for which $m_{1}(\hat{B}_{1})=1$, and
-$m_{1}(\hat{B}_{2})=1$, using the C-ingle model,
-with $c<0.5$. However, $m_{1}(\hat{C})=1$, from
+for which $M_{1}(\hat{B}_{1})=1$, and
+$M_{1}(\hat{B}_{2})=1$, using the C-ingle model,
+with $c<0.5$. However, $M_{1}(\hat{C})=1$, from
 which one can deduce that $B_{1}$ was $+1$, while
@@
 definition, there's no contextuality. It is just
-that $m_{1}(\hat{C})\neq
-\tilde f(m_{1}(\hat{B}_{1}),m_{1}(\hat{B}_{2}),\dots)$,
+that $M_{1}(\hat{C})\neq
+\tilde f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
 viz. the theory is non-multiplicative. Note that
 after measuring $\hat{C}$ however,
-$m_{2}(\hat{B}_{1})=+1$ and
-$m_{2}(\hat{B}_{2})=-1$ (for any value of $c$)
+$M_{2}(\hat{B}_{1})=+1$ and
+$M_{2}(\hat{B}_{2})=-1$ (for any value of $c$)
 consistent with those deduced by measuring
@@
 must arise from states that are superpositions (of
-the simultaneous eigenkets).  Note however, that
-entanglement is not necessary to show a violation,
+the simultaneous eigenkets).  Note, however, that
+entanglement is not necessary to show a violation
 since, for example, the PM test is a state
-independent test, where a separable state can be
-used to arrive at a contradiction. For
-demonstrating non-locality using Bell's proof,
-however, it can be shown that entanglement is
-necessary.  \bibliographystyle{apsrev4-1}
+independent test where a separable state can be
+used to arrive at a contradiction. Entanglement 
+can be used to show non-locality of non-multiplicative
+prediction maps using Bell's theorem.
+\bibliographystyle{apsrev4-1}
 \bibliography{references}

### 2016-07-11 preReleases/version6/finalPaper.tex
added the PDFs plus released version 6

--- 2016-07-11 finalPaper.tex
@@
 \newtheorem{thm}{\protect\theoremname}
+
+\theoremstyle{plain}
+\newtheorem*{thm*}{\protect\theoremname}
+
   \theoremstyle{definition}
@@
   \theoremstyle{definition}
-  \newtheorem{notn}[thm]{\protect\notationname}
+  \newtheorem*{notn*}{\protect\notationname}
 
@@
 
-{\noindent \bf Notation:} (a) $\psi\in\mathcal{H}$ 
+%{\noindent \bf Notation:} 
+\begin{notn*}
+(a) $\psi\in\mathcal{H}$ 
 represents a pure quantum mechanical
@@
 replacing observables in $f$ with real numbers.
+\end{notn*}
 
@@
 contextuality theorem in our notation:
-\begin{thm} Let a map
+\begin{thm*} Let a map
 $M:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a)
@@
 \label{thm:KS}
-\end{thm}
+\end{thm*}
 
-\begin{proof} Peres Mermin
+\begin{proof} Peres Mermin [PM]
 ($\left|\mathcal{H}\right|\ge4$)
@@
 on the state $[\psi]$. It is clear that according to
-\thmref{KS}, non-contextual maps which are
+the theorem, non-contextual maps which are
 \emph{multiplicative} must be incompatible with

### 2016-07-12 finalPaper.tex
upadated the conclusions

@@
 consistent with all predictions of quantum
-mechanics (QM).  A careful scrutiny of
-consistency requirements between any hidden
-variable model and  quantum mechanics and the
-corresponding no-go theorems, leads us to the
-conclusion that the notion of contextuality is not
-a necessary feature of QM.  The alternative view
-that emerges, hinges on identifying a new classical
-property, which we call ``multiplicativity''.  It turns
-out that, by relaxing this condition of
-``multiplicativity'' on hidden variable models, they
-can be made  consistent with QM.  Advantages of
-this view are illustrated by considering the
-implications of non-multiplicativity to locality,
-entanglement, superposition, and  apparent
-contextuality. 
+mechanics (QM).  A careful scrutiny of consistency
+requirements between any hidden variable model and
+quantum mechanics and the corresponding no-go
+theorems, leads us to the conclusion that the
+notion of contextuality is not a necessary feature
+of QM.  The alternative view that emerges, hinges
+on identifying a new classical property, which we
+call ``multiplicativity''.  It turns out that, by
+relaxing this condition of ``multiplicativity'' on
+hidden variable models, they can be made
+consistent with QM.  Connection of
+non-multiplicativity to Bohm Model and how it
+apparent contextuality is also discussed.
 \end{abstract}
@@
 \maketitle
-
 Quantum mechanics has been one of the most
@@
 smallest $a$ as described in postulate 2 of the
-model (see \tblref{HVmodel}). Two remarks are in
-order. First, this model is manifestly
+model (see \tblref{HVmodel}). 
+%Two remarks are in
+This model is manifestly
 \emph{non-multiplicative}, for
@@
 M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=-1$,
-where the subscript has been introduced to index
-the iteration. More precisely,
+where the subscript refers to the iteration
+number.
+More precisely,
 $M_{1}(\hat{O}):=M(\hat{O},\left[\left|\psi_{1}\right\rangle
@@
 state $\left|00\right\rangle $ and the HV $c=0.4$.
-Second, we must impose \emph{sequential
-multiplicativity} as a consistency check of the
-model, which in particular entails that
+%Second, we must impose \emph{sequential
+%multiplicativity} as a consistency check of the
+%model, which in particular entails that
+The model however  obeys the \emph{sequential
+multiplicativity} as required for consistency,
+namely,
 $M_{1}(\hat{C}_{3})=M_{1}(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
@@
 
-For the next iteration, $i=2$, viz.
-after the first measurement has been performed,
+For the next iteration, $i=2$, 
+after the first measurement is over
 say the random number generator yielded $c=0.1$.
@@
 the assignment remains invariant (in fact any of
-$c<0.5$ would yield the same result), which should
-be evident from the previous exercise. For the
+$c<0.5$ would yield the same result as
+evident from the previous exercise). For the
 final step we choose to measure
-$\hat p := \hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
+$\hat{A}_{23}(=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y})$,
 to proceed with sequentially measuring
 $\hat{C}_{3}$. To simplify calculations, we note
-\[ \left|00\right\rangle
-=\frac{(\left|\tilde{+}\tilde{-}\right\rangle
+$\left|00\right\rangle
+=\frac{1}{\sqrt 2} \left( (\left|\tilde{+}\tilde{-}\right\rangle
 +\left|\tilde{-}\tilde{+}\right\rangle
@@
 +\left|\tilde{-}\tilde{-}\right\rangle
-)/\sqrt{2}}{\sqrt{2}}, \] where
+)/\sqrt{2}\right) , 
+$
+with
 $\left|\tilde{\pm}\right\rangle
@@
 $\left|00\right\rangle $ is manifestly not an
-eigenket of $\hat{p}$, we must find an appropriate
-eigenket $\left|p_{-}\right\rangle $ s.t.
-$\hat{p}\left|p_{-}\right\rangle
-=-\left|p_{-}\right\rangle $, since $c=0.1$ and
-$\left\langle p_{-}|00\right\rangle $ is already
+eigenket of $A_{23}$, we must find an appropriate
+eigenket $\left|a^-_{23}\right\rangle $ s.t.
+$A_{23}\left|a^{-}_{23}\right\rangle
+=-\left|a^{-}_{23}\right\rangle $, since $c=0.1$ and
+$\left\langle a_{23}^{-}|00\right\rangle $ is already
 $>0.1$. It is immediate that
-$\left|p_{-}\right\rangle
+$\left|a^{-}_{23}\right\rangle
 =\left(\left|\tilde{+}\tilde{-}\right\rangle
@@
 +\left|11\right\rangle \right)/\sqrt{2}$, which
-becomes the final state. \\ For the final
+becomes the final state.
+
+ For the final
 iteration, $i=3$, say we obtain $c=0.7$. So far,
@@
 $M_{3}(\hat{A}_{13})=1$ for all allowed values of
-$c$. As a remark, it maybe emphasised that the
+$c$. It is to be noted that
 $M_{2}(\hat{A}_{33})=M_{3}(\hat{A}_{33})$ and
 $M_{2}(\hat{A}_{23})=M_{3}(\hat{A}_{23})$, which
-essentially expresses compatibility of these
-observables, viz. measurement of $\hat{A}_{13}$
-doesn't affect the result one would obtain by
-measuring operators compatible to it (granted they
-have been measured once before).
+essentially expresses the compatibility of these
+observables; i.e. 
+once measured, the values of observables compatible
+with $\hat{A}_{13}$ are not affected by the 
+measurement of $\hat{A}_{13}$.
 
-%\begin{widetext}
-%\onecolumngrid
 \begin{table*}
@@
 \end{table*}
-%\end{widetext}
+This has implications to Bohm's HV model(BHVM),
+where we have the notion of precise trajectories
+for particle guided by the wavefunction.  In BHVM
+if the initial conditions are precisely known the
+entire trajectory of a particle can be predicted
+including the individual outcome of measurements.
+For the case of a single spin-1/2 particle in a
+Stern Gerlach experiment, BHVM can predict
+opposite results correspond to measurement of the
+same operator.  This observation is often used as
+a demonstration of `contextuality' in BM, although
+we did not even speak of compatible
+measurements\cite{??}.  It turns out, however,
+that if one restricts oneself to a one-one map
+between an experiment and an observable (by
+following a certain convention), the so called
+`contextuality' can be removed from BHVM.  One
+finds that the map so obtained from observables to
+their predictions turns out to be
+non-multiplicative, suggesting that at least in
+this case, non-multiplicativity is a more suitable
+explanation of non-classicality.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\color{red} Will work on CC after everthin else
-is done}
-This has implications to Bohm's HV model as well, Bohmian Mechanics (BM), where the notion of positions (and hence trajectories) is precisely defined and particles are guided by the wavefunction.
-Consequently, given the initial conditions precisely (which is never the case experimentally) one can predict results of all experiments precisely.
-This entails that BM is capable of predicting outcomes of, for instance, a Stern Gerlach experiment.
-However, within BM two experiments which correspond to measurement of the same operator, can yield opposite results.
-Further, this can be demonstrated for a single spin half particle.
-This observation is often used as a demonstration of `contextuality' in BM, although we did not even speak of compatible measurements.
-It turns out, however, that if one restricts oneself to a one-one map between an experiment and an observable (by following some convention for example) then the so called `contextuality' can be removed from BM.
-One finds that the map so obtained from observables to their predictions turns out to be non-multiplicative, suggesting that at least in this case, non-multiplicativity is a more suitable explanation of non-classicality.
+We have  constructed an explicit non-contextual HV
+model consistent with QM which is
+non-multiplicative. We illustrate how
+non-multiplicativity gives rise situations which
+could get confused with presence of contextuality.
 
-We have already constructed an explicit non-contextual model,
-which is consistent with QM.  This model we knew
-had to be non-multiplicative.  We will see how
-non-multiplicativity gives rise to what one might
-confuse to mean contextuality.  Imagine $\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=\left|00\right\rangle
+Imagine
+$
+\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=
+\left|00\right\rangle
 \left\langle 00\right|+\left|01\right\rangle
@@
 \left\langle 10\right|+\left|11\right\rangle
-\left\langle 11\right|\right],$ $
-\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=\left|10\right\rangle
+\left\langle 11\right|\right],
+$ 
+$
+\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=
+\left|10\right\rangle
 \left\langle 10\right|+\left|11\right\rangle
@@
 \left\langle 00\right|+\left|01\right\rangle
-\left\langle 01\right|\right],$ while we define
-$ \hat{C}=f(\{\hat{B}_{i}\})
+\left\langle 01\right|\right],
+$ 
+while we define 
+$
+\hat{C}=f(\{\hat{B}_{i}\})
 =0.\left|00\right\rangle \left\langle
@@
 10\right|+3.\left|11\right\rangle \left\langle
-11\right|. $
-% \begin{align*} \hat{C}&=f(\{\hat{B}_{i}\}) \\
-% &=0.\left|00\right\rangle \left\langle
-% 00\right|+1.\left|01\right\rangle \left\langle
-% 01\right|+2.\left|10\right\rangle \left\langle
-% 10\right|+3.\left|11\right\rangle \left\langle
-% 11\right|.  \end{align*}
- $\hat{C}$ maybe viewed as
-a function of $\hat{B}_{1}$, $\hat{B}_{2}$ and
-other operators $\hat{B}_{i}$ which are
-constructed to obtain a maximally commuting set. A
-measurement of $\hat{C}$, will collapse the state
-into one of the states which are simultaneous
-eignkets of $B_{1}$ and $B_{2}$. Consequently,
-from the observed value of $\hat{C}$, one can
-deduce the values of $\hat{B}_{1}$ and
-$\hat{B}_{2}$. Now consider
+11\right|. 
+$
+$\hat{C}$ maybe viewed as a function of
+$\hat{B}_{1}$, $\hat{B}_{2}$ and other operators
+$\hat{B}_{i}$ which are constructed to obtain a
+maximally commuting set. A measurement of
+$\hat{C}$, will collapse the state into one of the
+states which are simultaneous eignkets of $B_{1}$
+and $B_{2}$. Consequently, from the observed value
+of $\hat{C}$, one can deduce the values of
+$\hat{B}_{1}$ and $\hat{B}_{2}$. Now consider
 $\sqrt{2}\left|\chi\right\rangle
@@
 for which $M_{1}(\hat{B}_{1})=1$, and
-$M_{1}(\hat{B}_{2})=1$, using the C-ingle model,
+$M_{1}(\hat{B}_{2})=1$, using our model,
 with $c<0.5$. However, $M_{1}(\hat{C})=1$, from
@@
 definition, there's no contextuality. It is just
-that $M_{1}(\hat{C})\neq
-\tilde f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
+that $M_{1}(\hat{C})\neq \tilde
+f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
 viz. the theory is non-multiplicative. Note that
@@
 
-It is known that for simultaneous eigenstates of
-$\hat{B}_{i}$, multiplicativity must hold.
-Consequently, any violation of multiplicativity
-must arise from states that are superpositions (of
-the simultaneous eigenkets).  Note, however, that
-entanglement is not necessary to show a violation
-since, for example, the PM test is a state
-independent test where a separable state can be
-used to arrive at a contradiction. Entanglement 
-can be used to show non-locality of non-multiplicative
-prediction maps using Bell's theorem.
-\bibliographystyle{apsrev4-1}
-\bibliography{references}
-
-\end{document}
+Evidently, Multiplicativity must hold for the
+common eigenkets of $\hat{B}_{i}$.  Consequently,
+any violation of multiplicativity must arise from
+states that are superpositions or linear
+combinations of these common eigenkets.  Note,
+however, that entanglement is not necessary to
+show a violation for instance the Peres Mermin
+test is a state independent test where a separable
+state can be used to arrive at a contradiction.
+Entanglement can be used to show non-locality of
+non-multiplicative prediction maps using Bell's
+theorem  however, the notion non-multiplicativity
+is more basic.  \begin{acknowledgments} Arvind
+acknowledges funding from DST India under Grant
+No. EMR/2014/000297.  \end{acknowledgments}
+%\bibliographystyle{apsrev4-1}
+\bibliography{references} \end{document}

### 2016-07-12 finalPaper.tex
upadated further

@@
 hidden variable models, they can be made
-consistent with QM.  Connection of
-non-multiplicativity to Bohm Model and how it
+consistent with QM.  The connection of
+non-multiplicativity to the Bohm Model and to
 apparent contextuality is also discussed.
@@
 \left\langle 1\right|$. Now, according to the
-postulates of this theory, $M(\hat{A},[\chi])=+1$, if
+postulates of this theory, $M(\hat{A},[\chi])=+1$.
+If
 the randomly generated value for 
 $c\le\cos^{2}\theta$ else $\hat{A}$ is assigned
-$-1$. It follows then, from $c$ being uniformly
+$-1$, it then follows,  from $c$ being uniformly
 random in $[0,1]$ that the statistics agree with
-predictions of QM.
+the predictions of QM.
 
-Note that the assignment, described by the
-prediction map $M$, is non-contextual since given
+Note that the assignment described by the
+prediction map $M$ is non-contextual since, given
 an operator and a state (+ the HV $c$), the value is
-uniquely assigned. The map $M$ is, however,
+uniquely assigned. The map $M$ is however,
 non-multiplicative.
@@
 after the first measurement is over
-say the random number generator yielded $c=0.1$.
-Since $\left|\psi\right\rangle $ is also unchanged
+say the random number generator yielded the value $c=0.1$.
+Since $\left|\psi\right\rangle $ is also
+unchanged
 the assignment remains invariant (in fact any of
@@
 (eigenkets of $\hat{\sigma}_{y}$). Since
-$\left|00\right\rangle $ is manifestly not an
+$\left|00\right\rangle$ is manifestly not an
 eigenket of $A_{23}$, we must find an appropriate
@@
 $\left\langle a_{23}^{-}|00\right\rangle $ is already
-$>0.1$. It is immediate that
+$>0.1$. It is evident that
 $\left|a^{-}_{23}\right\rangle
@@
 $M_{3}(\hat{A}_{13})=1$, independent of the value
-of $c$, to be consistent. Let's check that.
+of $c$, to be consistent. Let us check that.
 Indeed, according to postulate 2, since
@@
 \end{table*}
-This has implications to Bohm's HV model(BHVM),
+This has implications to Bohm's HV model (BHVM),
 where we have the notion of precise trajectories
-for particle guided by the wavefunction.  In BHVM
+for particles guided by the wavefunction.  In BHVM
 if the initial conditions are precisely known the
@@
 For the case of a single spin-1/2 particle in a
-Stern Gerlach experiment, BHVM can predict
-opposite results correspond to measurement of the
+Stern-Gerlach experiment, BHVM can predict
+opposite results for two measurements of the
 same operator.  This observation is often used as
@@
 between an experiment and an observable (by
-following a certain convention), the so called
+following a certain convention), the so-called
 `contextuality' can be removed from BHVM.  One
@@
 non-multiplicative. We illustrate how
-non-multiplicativity gives rise situations which
-could get confused with presence of contextuality.
+non-multiplicativity gives rise to situations which
+could get confused with the presence of contextuality.
 
@@
 and so does $\hat{C}$. Thus by our accepted
-definition, there's no contextuality. It is just
+definition, there is no contextuality. It is just
 that $M_{1}(\hat{C})\neq \tilde
@@
 
-Evidently, Multiplicativity must hold for the
+Evidently, multiplicativity must hold for the
 common eigenkets of $\hat{B}_{i}$.  Consequently,
@@
 states that are superpositions or linear
-combinations of these common eigenkets.  Note,
+combinations of these common eigenkets.  Note
 however, that entanglement is not necessary to
-show a violation for instance the Peres Mermin
+show a violation; for instance the Peres Mermin
 test is a state independent test where a separable
@@
 non-multiplicative prediction maps using Bell's
-theorem  however, the notion non-multiplicativity
+theorem  however, the notion of non-multiplicativity
 is more basic.  \begin{acknowledgments} Arvind

### 2016-07-12 finalPaper.tex
made final changes

@@
 \newref{ssec}{name=Subsection~}
+\newref{fig}{name=Figure~}
 
@@
   \theoremstyle{remark}
-  \newtheorem{rem}{\protect\remarkname}
+  \newtheorem*{rem}{\protect\remarkname}
 
@@
 \author{Atul Singh Arora}
-\email{ms11003@iisermohali.ac.in}
+%\email{ms11003@iisermohali.ac.in}
 \selectlanguage{british}%
@@
 \author{Arvind}
-\email{arvind@iisermohali.ac.in}
+%\email{arvind@iisermohali.ac.in}
 \selectlanguage{british}%
@@
 mechanics (QM).  A careful scrutiny of consistency
-requirements between any hidden variable model and
+requirements of any hidden variable model with
 quantum mechanics and the corresponding no-go
@@
 on identifying a new classical property, which we
-call ``multiplicativity''.  It turns out that, by
+call ``multiplicativity''.  It turns out that by
 relaxing this condition of ``multiplicativity'' on
@@
 consistent with QM.  The connection of
-non-multiplicativity to the Bohm Model and to
+non-multiplicativity to Bohm's model and to
 apparent contextuality is also discussed.
@@
 there has not yet been a final word on its
-completeness and interpretation~\cite{??}.
+completeness and interpretation.
 Einstein's~\cite{EinsteinEPR} work on the
@@
 processing, where EPR pairs are fundamental motifs
-of entanglement~\cite{Ekert,PironioRndmnssCrtfcn}.
+of entanglement~\cite{Ekert,PironioRndmnssCrtfcn,NielsenChuang}.
 The work of  Kochen Specker~\cite{KochenSpecker}
@@
 conducted to this effect~\cite{SimonContExpProp,
-HuangContExp,YangContExp,HasegawaContExp}.
+HuangContExp}.
 Contextuality, on the one hand has led to
 investigations on the foundational aspects of
-QM~\cite{PawelCntxClsscl,?????}, and on the other
+QM including attempts to prove completeness of QM~\cite{PawelCntxClsscl,CabelloMmryQM}, and on the other
 hand has been harnessed for computation and
-cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt,??}.
-Quantitative measures of contextuality based on
-memory~\cite{MatthiasCntxMmry} have also been used
-to demonstrate the completeness of
-QM~\cite{CabelloMmryQM}.  However, not all HV
+cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
+However, not all HV
 models are incompatible with QM, and a very
@@
 disturbances due to measurements into
-consideration~\cite{NoContextuality,LaCourNoCntx},
-we take a different approach and construct a
-HV model consistent with QM.  The predictions of
-the aforesaid model match with those of QM for systems
+consideration~\cite{NoContextuality},
+we take a different approach 
+and construct a 
+HV model whose 
+predictions match with those of QM for systems
 described by arbitrary finite-dimensional Hilbert
@@
 the product of rows (or columns) yields
-$\hat{R}_{i}=\mathbb{I}$ and
-$\hat{C}_{j}=\mathbb{I}\,(j\neq3)$,
-$\hat{C}_{3}=-\mathbb{I}$, ($\forall\,i,j$) where
+$\hat{R}_{i}=\hat{\mathbb{I}}$ and
+$\hat{C}_{j}=\hat{\mathbb{I}}\,(j\neq3)$,
+$\hat{C}_{3}=-\hat{\mathbb{I}}$, ($\forall\,i,j$) where
 $\hat{R}_{i}:=\prod_{j}\hat{A}_{ij}$,
@@
 
-\begin{thmrem} One could in principle assume $M$, to
+\begin{rem} One could in principle assume $M$, to
 be s.t. (a) $M(\hat{\mathbb{I}})=1$, (b)
@@
 consequence.  Therefore, assuming (a)-(d) as
-listed here, rules out a larger class of $M$.
-\cite{KochenSpecker} 
-\end{thmrem} 
+listed here, rules out a larger class of $M$~\cite{KochenSpecker}.
+\end{rem} 
 Here $M$ maybe viewed as a specific
@@
 $\left|00\right\rangle$ is manifestly not an
-eigenket of $A_{23}$, we must find an appropriate
+eigenket of $\hat A_{23}$, we must find an appropriate
 eigenket $\left|a^-_{23}\right\rangle $ s.t.
-$A_{23}\left|a^{-}_{23}\right\rangle
+$\hat A_{23}\left|a^{-}_{23}\right\rangle
 =-\left|a^{-}_{23}\right\rangle $, since $c=0.1$ and
@@
 
-\hat{A}_{13}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};M_{1}(\hat{A}_{13})=+1&
+\hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};M_{1}(\hat{A}_{33})=+1&
 \quad\quad\hat{A}_{23}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y};M_{2}(\hat{A}_{23})=-1\quad\quad&
-\hat{A}_{33}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};M_{3}(\hat{A}_{33})=+1\\
+\hat{A}_{13}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};M_{3}(\hat{A}_{13})=+1\\
 
@@
 including the individual outcome of measurements.
-For the case of a single spin-1/2 particle in a
+For the case of a single spin-half particle in a
 Stern-Gerlach experiment, BHVM can predict
@@
 we did not even speak of compatible
-measurements\cite{??}.  It turns out, however,
+measurements~\cite{HardyCntxBM}.  It turns out, however,
 that if one restricts oneself to a one-one map
@@
 states that are superpositions or linear
-combinations of these common eigenkets.  Note
+combinations of these common eigenkets.  Note,
 however, that entanglement is not necessary to
@@
 theorem however, the notion of non-multiplicativity
-is more basic.  \begin{acknowledgments} Arvind
-acknowledges funding from DST India under Grant
-No. EMR/2014/000297.  \end{acknowledgments}
+is more basic.  \begin{acknowledgments} 
+ASA and Arvind acknowledge funding from KVPY and DST Grant No. EMR/2014/000297 respectively.
+%Arvind acknowledges funding from DST India under Grant No. EMR/2014/000297. ASA acknolwedges KVPY, DST for financial support.
+\end{acknowledgments}
 %\bibliographystyle{apsrev4-1}

### 2016-07-13 finalPaper.tex
some small change in finalPaper.tex :P
removed the footnote etc.

@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%This stuff is required for transposing matrices | fine I didn't want to do donkey work
-% \usepackage{xparse}
-% \usepackage{environ}
-
-% \ExplSyntaxOn
-% \NewEnviron{bmatrixT}
-%  {
-%   \marine_transpose:V \BODY
-%  }
-
-% \int_new:N \l_marine_transpose_row_int
-% \int_new:N \l_marine_transpose_col_int
-% \seq_new:N \l_marine_transpose_rows_seq
-% \seq_new:N \l_marine_transpose_arow_seq
-% \prop_new:N \l_marine_transpose_matrix_prop
-% \tl_new:N \l_marine_transpose_last_tl
-% \tl_new:N \l_marine_transpose_body_tl
-
-% \cs_new_protected:Nn \marine_transpose:n
-%  {
-%   \seq_set_split:Nnn \l_marine_transpose_rows_seq { \\ } { #1 }
-%   \int_zero:N \l_marine_transpose_row_int
-%   \prop_clear:N \l_marine_transpose_matrix_prop
-%   \seq_map_inline:Nn \l_marine_transpose_rows_seq
-%    {
-%     \int_incr:N \l_marine_transpose_row_int
-%     \int_zero:N \l_marine_transpose_col_int
-%     \seq_set_split:Nnn \l_marine_transpose_arow_seq { & } { ##1 }
-%     \seq_map_inline:Nn \l_marine_transpose_arow_seq
-%      {
-%       \int_incr:N \l_marine_transpose_col_int
-%       \prop_put:Nxn \l_marine_transpose_matrix_prop
-%        {
-%         \int_to_arabic:n { \l_marine_transpose_row_int }
-%         ,
-%         \int_to_arabic:n { \l_marine_transpose_col_int }
-%        }
-%        { ####1 }
-%      }
-%    }
-%    \tl_clear:N \l_marine_transpose_body_tl
-%    \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_col_int }
-%     {
-%      \int_step_inline:nnnn { 1 } { 1 } { \l_marine_transpose_row_int }
-%       {
-%        \tl_put_right:Nx \l_marine_transpose_body_tl
-%         {
-%          \prop_item:Nn \l_marine_transpose_matrix_prop { ####1,##1 }
-%          \int_compare:nF { ####1 = \l_marine_transpose_row_int } { & }
-%         }
-%       }
-%      \tl_put_right:Nn \l_marine_transpose_body_tl { \\ }
-%     }
-%    \begin{bmatrix}
-%    \l_marine_transpose_body_tl
-%    \end{bmatrix}
-%  }
-% \cs_generate_variant:Nn \marine_transpose:n { V }
-% \cs_generate_variant:Nn \prop_put:Nnn { Nx }
-% \ExplSyntaxOff
-
 \begin{document}
@@
 \author{Atul Singh Arora}
-%\email{ms11003@iisermohali.ac.in}
+\email{ms11003@iisermohali.ac.in}
 \selectlanguage{british}%
@@
 \author{Arvind}
-%\email{arvind@iisermohali.ac.in}
+\email{arvind@iisermohali.ac.in}
 \selectlanguage{british}%
@@
 of QM.  The alternative view that emerges, hinges
-on identifying a new classical property, which we
+on identifying a new classical property which we
 call ``multiplicativity''.  It turns out that by
@@
 there has not yet been a final word on its
-completeness and interpretation.
+completeness and interpretation~\cite{BellSpkblUnspkbl}.
 Einstein's~\cite{EinsteinEPR} work on the
 incompleteness of QM and the subsequent seminal
-work of Bell~\cite{Bell1964}, assessing the
+work of Bell~\cite{BellSpkblUnspkbl}, assessing the
 compatibility of a more complete model involving
@@
 \} \to \hat{\mathcal{H}}$ constructed using
-multiplication and addition of the observables,
+multiplication and addition of compatible observables,
 and multiplication with complex
-numbers\footnote{Strictly, the map $f$ would
-depend on the operators to ensure preservation of
-Hermiticity; thus a given $f$ will be defined only
-for a subset of $\{
-\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
-\}$.}, (h) $\tilde{f}$ is a map constructed by
+numbers
+%\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\{\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}\}$.}
+, (h) $\tilde{f}$ is a map constructed by
 replacing observables in $f$ with real numbers.
@@
 suggested which declare a larger set of theories
-as non-contextual. For our purposes however, this
+as non-contextual. For our purposes, however, this
 restricted definition will suffice. The term
@@
 %Construction \label{ssec:cingle}}
-We are now ready to describe our explict model.
+We are now ready to describe our explicit model.
 Let the state of a finite dimensional quantum system
@@
 an operator and a state (+ the HV $c$), the value is
-uniquely assigned. The map $M$ is however,
+uniquely assigned. The map $M$ is, however,
 non-multiplicative.
@@
 %model, which in particular entails that
-The model however  obeys the \emph{sequential
+The model, however, obeys the \emph{sequential
 multiplicativity} as required for consistency,
@@
 where we have the notion of precise trajectories
-for particles guided by the wavefunction.  In BHVM
+for particles guided by the wave-function.  In BHVM
 if the initial conditions are precisely known the
@@
 $\hat{C}$, will collapse the state into one of the
-states which are simultaneous eignkets of $B_{1}$
-and $B_{2}$. Consequently, from the observed value
+states which are simultaneous eignkets of $\hat{B}_{1}$
+and $\hat{B}_{2}$. Consequently, from the observed value
 of $\hat{C}$, one can deduce the values of
@@
 with $c<0.5$. However, $M_{1}(\hat{C})=1$, from
-which one can deduce that $B_{1}$ was $+1$, while
-$B_{2}$ was $-1$.  This property itself, one may
+which one can deduce that $\hat{B}_{1}$ was $+1$, while
+$\hat{B}_{2}$ was $-1$.  This property itself, one may
 be tempted call contextuality, viz.  the value of
-$B_{1}$ depends on whether it is measured alone or
-with the remaining $\{B_{i}\}$. However, it must
-be noted that $B_{1}$ has a well defined value,
+$\hat{B}_{1}$ depends on whether it is measured alone or
+with the remaining $\{\hat{B}_{i}\}$. However, it must
+be noted that $\hat{B}_{1}$ has a well defined value,
 and so does $\hat{C}$. Thus by our accepted
@@
 viz. the theory is non-multiplicative. Note that
-after measuring $\hat{C}$ however,
+after measuring $\hat{C}$, however,
 $M_{2}(\hat{B}_{1})=+1$ and
@@
 any violation of multiplicativity must arise from
-states that are superpositions or linear
+states that are super-positions or linear
 combinations of these common eigenkets.  Note,
@@
 non-multiplicative prediction maps using Bell's
-theorem however, the notion of non-multiplicativity
+theorem, however, the notion of non-multiplicativity
 is more basic.  \begin{acknowledgments} 

### 2016-07-25 finalPaper.tex
updated after the arXiv comment

@@
 consistent with QM.  The connection of
-non-multiplicativity to Bohm's model and to
+non-``multiplicativity'' to Bohm's model and to
 apparent contextuality is also discussed.
@@
 to explain measurement outcomes. A theory which is
-not non-contextual is contextual.\end{defn}
+not non-contextual is contextual. \cite{peresBook}
+\end{defn}
 
@@
 
-Our HV model for QM assigns values in the following
+Our HV model (similar to Bell's~\cite{BellSpkblUnspkbl}) for QM assigns values in the following
 three steps:

### 2016-07-25 finalPaper.tex
fixed the bell citation issue and added a mini justification letter

@@
 and Gleason et.
-al.~\cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
+al.~\cite{Gleason,BellOnHiddenVariables,Peres,Mermin}
 broadened the schism between  HV models and QM.
@@
 
-Our HV model (similar to Bell's~\cite{BellSpkblUnspkbl}) for QM assigns values in the following
+Our HV model (similar to Bell's~\cite{BellOnHiddenVariables}) for QM assigns values in the following
 three steps:

### 2017-02-08 finalPaper.tex
/ ‘finalPaper.tex’ / ‘references.bib’

--- 2016-07-13 finalPaper.tex
@@
 \documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+%\documentclass[british,aps,superscriptaddress,nofootinbib,twocolumn,prl]{revtex4-1}
+%\usepackage[T1]{fontenc}
+%\usepackage[latin9]{inputenc}
 \usepackage{geometry}
@@
 \usepackage{amssymb}
-\usepackage{esint}
+%\usepackage{esint}
 \makeatletter
@@
 \email{ms11003@iisermohali.ac.in}
-\selectlanguage{british}%
-\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
+%\selectlanguage{british}%
+\affiliation{Department of Physical Sciences, 
+Indian Institute of Science Education and Research
+Mohali, Sector 81 SAS Nagar 140306 Punjab India.}
 \author{Arvind}
 \email{arvind@iisermohali.ac.in}
-\selectlanguage{british}%
-\affiliation{Indian Institute of Science Education
-and Research (IISER), Mohali}
+\affiliation{Department of Physical Sciences, 
+Indian Institute of Science Education and Research
+Mohali, Sector 81 SAS Nagar 140306 Punjab India.}
+%\selectlanguage{british}%
 \begin{abstract}
 We propose a non-contextual hidden variable model,
-consistent with all predictions of quantum
+consistent with all {\color{red} kinematic
+predictions of} quantum
 mechanics (QM).  A careful scrutiny of consistency
@@
 quantum mechanics and the corresponding no-go
-theorems, leads us to the conclusion that the
-notion of contextuality is not a necessary feature
-of QM.  The alternative view that emerges, hinges
-on identifying a new classical property which we
-call ``multiplicativity''.  It turns out that by
+theorems leads us to the conclusion that,
+contrary to common belief,  the notion of
+contextuality is not a necessary feature of QM.
+The alternative view that emerges, hinges on
+identifying a new classical property which we call
+``multiplicativity''.  It turns out that by
 relaxing this condition of ``multiplicativity'' on
 hidden variable models, they can be made
-consistent with QM.  The connection of
-non-multiplicativity to Bohm's model and to
+consistent with QM  while remaining
+non-contextual.  The connection of
+non-``multiplicativity'' to Bohm's model and to
 apparent contextuality is also discussed.
@@
 there has not yet been a final word on its
-completeness and interpretation~\cite{BellSpkblUnspkbl}.
+completeness and
+interpretation~\cite{BellSpkblUnspkbl}.
 Einstein's~\cite{EinsteinEPR} work on the
 incompleteness of QM and the subsequent seminal
-work of Bell~\cite{BellSpkblUnspkbl}, assessing the
-compatibility of a more complete model involving
-hidden variables (HV) and locality with QM, has
-provided deep insights into  how the quantum world
-differs from its classical counterpart.  In recent
-times, these insights have been of pragmatic
-utility in the areas of quantum information
-processing, where EPR pairs are fundamental motifs
-of entanglement~\cite{Ekert,PironioRndmnssCrtfcn,NielsenChuang}.
+work of Bell~\cite{BellSpkblUnspkbl}, assessing
+the compatibility of a more complete model
+involving hidden variables (HV) and locality with
+QM, has provided deep insights into  how the
+quantum world differs from its classical
+counterpart.  In recent times, these insights have
+been of pragmatic utility in the area of quantum
+information processing (QIP), where EPR pairs are
+fundamental motifs of
+entanglement~\cite{Ekert,PironioRndmnssCrtfcn,NielsenChuang}.
 The work of  Kochen Specker~\cite{KochenSpecker}
-and Gleason et.
-al.~\cite{Gleason,BellOnHiddenVariables,Peres,Mermin})
-broadened the schism between  HV models and QM.
-They showed that it was contextuality and not
-non-locality which was at the heart of this schism
-and the incompatibility between HV models and QM
-can arise even for a single quantum system.
-Contextuality has thus been identified as a
-fundamental non-classical feature of the quantum
-world and experiments have also been proposed and
-conducted to this effect~\cite{SimonContExpProp,
+and Gleason {\it
+et.\,al.}~\cite{Gleason,Peres,Mermin} broadened
+the schism between  HV models and QM.  They showed
+that it was contextuality and not non-locality
+which was at the heart of this schism and the
+incompatibility between HV models and QM can arise
+even for a single quantum system.  Contextuality
+has thus been identified as a fundamental
+non-classical feature of the quantum world and
+experiments have also been proposed and conducted
+to this effect~\cite{SimonContExpProp,
 HuangContExp}.
-Contextuality, on the one hand has led to
-investigations on the foundational aspects of
-QM including attempts to prove completeness of QM~\cite{PawelCntxClsscl,CabelloMmryQM}, and on the other
-hand has been harnessed for computation and
+Contextuality, on the one hand has
+led to investigations on the foundational aspects
+of QM including attempts to prove completeness of
+QM~\cite{PawelCntxClsscl,CabelloMmryQM}, and on
+the other hand has been harnessed for computation
+and
 cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
-However, not all HV
-models are incompatible with QM, and a very
-important case in point is  Bohm's model based on
-precise trajectories for quantum
-systems~\cite{Bohm1,Bohm2}.
-
-A closer look at the aforesaid no-go theorems
-reveals that contextuality is in fact not a
-necessary feature of QM (see \figref{block}).
-While this has been shown earlier by taking
-disturbances due to measurements into
-consideration~\cite{NoContextuality},
-we take a different approach 
-and construct a 
-HV model whose 
-predictions match with those of QM for systems
-described by arbitrary finite-dimensional Hilbert
-spaces.  \begin{figure}[h]
+However, not all HV models (e.g.
+Bohm's model based on
+trajectories~\cite{Bohm1,Bohm2}) are incompatible
+with QM~\cite{BellOnHiddenVariables}, and we in
+this letter present a new non-contextual HV model
+consistent with QM.
+\begin{figure}[h]
 \includegraphics[width=0.9\columnwidth]{block1}
 \caption{Non-contextuality is not inconsistent
-with QM} \label{fig:block}\end{figure} The
-algebraic constraints obeyed by quantum
-observables may not necessarily be obeyed by the
-predictions of an HV model at the level of
-individual outcomes.  Those HV models that obey
-such algebraic constraints possess a special
-property which we call `multiplicativity'.  
-Enlarging the scope of HV models to include
-non-multiplicative models, permits us to construct an
-explicit non-contextual model consistent with QM.
+with QM} \label{fig:block}\end{figure}
+A closer scrutiny of the arguments
+leading to the dichotomy between QM and HV models
+reveals that the algebraic constraints obeyed by
+quantum observables may not necessarily be obeyed
+by the predictions of an HV model at the level of
+individual outcomes and  that contextuality is 
+not a necessary feature of QM.  Those HV
+models that obey such algebraic constraints
+possess a special property which we call
+``multiplicativity''.  Enlarging the scope of HV
+models to include non-multiplicative models,
+permits us to construct an explicit non-contextual
+HV model consistent with 
+{\color{red} kinematics predictions of}
+QM (see \figref{block}).
 The re-examination of the very proof of
 `contextuality'  is used to illustrate
-non-multiplicativity, an intrinsic quantum feature, 
-which we propose as a possible alternative to contextuality.
+non-multiplicativity, an intrinsic quantum
+feature, which we propose as a possible
+alternative to contextuality. 
+Non-mulitiplicativity thus might turn out to be
+the key quantum feature distinguishing the quantum
+world from the classical one and may have a role
+to play in QIP protocols.  This provides a new
+way to look at the classical-quantum divide and at
+the foundations of quantum mechanics.
 
-%{\noindent \bf Notation:} 
 \begin{notn*}
-(a) $\psi\in\mathcal{H}$ 
-represents a pure quantum mechanical
-state of the system in the Hilbert space
-$\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined
-to mean the set of Hermitian 
-observables for the system, (c)
-$[\mathcal{H}]$ is defined to mean
-$(\mathcal{H},\,\mathbb{R}^{\otimes})$, which
-represents the state of the system including HVs,
-(d) $[\psi]\in[\mathcal{H}]$ will represent the
-state of the system, including HVs, (e) a
-prediction map is
-$M:\{ \hat{\mathcal{H}},[\mathcal{H}] \}\to\mathbb{R}$,
-(f) a sequence map is
-$S:\{ \hat{\mathcal{H}},[\mathcal{H}],\mathbb{R} \}\to[\mathcal{H}]$,
-(g) $f$ is an arbitrary map from $\{
+(a) $\psi\in\mathcal{H}$ represents a pure quantum
+mechanical state of the system in the Hilbert
+space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is
+defined to mean the set of Hermitian observables
+for the system, (c) $[\mathcal{H}]$ is defined to
+mean $\{\mathcal{H},\,\mathbb{R}^{\otimes}\}$, which
+represents the state  space of the
+system including HVs, (d) $[\psi]\in[\mathcal{H}]$
+will represent the state of the system including
+HVs, (e) a prediction map is $M:\{
+\hat{\mathcal{H}},[\mathcal{H}] \}\to\mathbb{R}$,
+(f) a sequence map is $S:\{
+\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}
+\}\to[\mathcal{H}]$, (g) $f$ is an arbitrary map
+from $\{
 \hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}
 \} \to \hat{\mathcal{H}}$ constructed using
-multiplication and addition of compatible observables,
-and multiplication with complex
-numbers
-%\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\{\hat{\mathcal{H}},\hat{\mathcal{H}},\dots\hat{\mathcal{H}}\}$.}
-, (h) $\tilde{f}$ is a map constructed by
+multiplication and addition of compatible
+observables, and multiplication with complex
+numbers, (h) $\tilde{f}$ is a map constructed by
 replacing observables in $f$ with real numbers.
 \end{notn*}
-
 \begin{defn} A theory is non-contextual, if it
@@
 to explain measurement outcomes. A theory which is
-not non-contextual is contextual.\end{defn}
-
-\begin{defnrem} The notion of non-contextuality may be
-extended to maps. A map is non-contextual if it is
-of the form $M: \{ \hat{\mathcal{H}},[\mathcal{H}]
-\} \to\mathbb{R}$; prediction maps as defined above, for individual observables, are non-contextual by construction.  
+not non-contextual is contextual~\cite{peresBook}.
+\end{defn}
+{\color{red}
+\begin{defnrem}
+A prediction map of the form $M: \{
+\hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$.
+itself can be called  non-contextual.
 \end{defnrem}
+}
 \begin{defnrem}
@@
 suggested which declare a larger set of theories
-as non-contextual. For our purposes, however, this
-restricted definition will suffice. The term
-contextual is used to suggest that the value an
-operator takes might depend on which other
-compatible observable it is being  measured with.
+as non-contextual~\cite{spekkens_pra}. For our
+purposes, however, this restricted definition will
+suffice  and our results will in any case be valid
+for the broader definitions. The term contextual
+is used to suggest that the value an observable
+takes might depend on which other compatible
+observable it is being  measured with.
 \end{defnrem}
-
 Before we re-examine the result of Kochen and
@@
 alternative to contextuality, we define
-multiplicativity more precisely.
+multiplicativity explicitly.
 \begin{defn}
@@
 $\left|1\right\rangle \otimes\left|1\right\rangle
-$ written in the computational basis and take
+$ written in the computational basis and 
 operators 
@@
 independently, according to QM, with probability
-half. Here multiplicativity does not seem to hold.
+half. Here multiplicativity clearly is not
+required to hold.
 Antithetically, it is clear that if one first
@@
 where
-$\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{
-N! {\rm ~permutations~of~}  k'{\rm s}
-\}$, $\hat{B}_{i}\in\hat{\mathcal{H}}$ are
+$\{k_{1},k_{2},\dots,k_{N}\} \in\{
+N! {\rm ~permutations~of~}  k'{\rm s} \}$, 
+$\hat{B}_{i}\in\hat{\mathcal{H}}$ are
 arbitrary mutually commuting observables,
@@
 $\forall\,[\psi_{i}]$.  
-\label{defn:seqnMltpl}\end{defn} 
+\label{defn:seqnMltpl}
+\end{defn} 
 With these definitions we are now ready to discuss
@@
 assignments must be even. We have arrived at a
-contradiction and therefore we conclude that our
-assumption that a consistent $M$ exists, must be
-wrong.  \end{proof}
+contradiction and therefore we conclude 
+that $M$ does not exist
+\end{proof}
 
@@
 $M(\hat{B}_{i}+\hat{B}_{j})=M(\hat{B}_{i})+M(\hat{B}_{j})$,
-to deduce (d')
+to deduce (d)
 $M(\hat{B}_{i}\hat{B}_{j})=M(\hat{B}_{i})M(\hat{B}_{j})$
@@
 consequence.  Therefore, assuming (a)-(d) as
-listed here, rules out a larger class of $M$~\cite{KochenSpecker}.
+listed above, rules out a larger class of
+$M$~\cite{KochenSpecker}.
 \end{rem} 
-Here $M$ maybe viewed as a specific
-class of prediction maps, that implicitly depends
-on the state $[\psi]$. It is clear that according to
-the theorem, non-contextual maps which are
+Here $M$ maybe viewed as a specific class of
+prediction maps, that implicitly depends on the
+state $[\psi]$. It is clear that according to the
+theorem, non-contextual maps which are
 \emph{multiplicative} must be incompatible with
-QM. However, non-contextual maps which are
-non-\emph{multiplicative} might be consistent with
-QM. Indeed it is and we will show this by constructing an
-explicit model.
-
-Before proceeding we note, however, that QM can
-enforce \emph{sequential multiplicativity}. This
-result will be used to assess accuracy of any
-proposal of a HV
-model.
+QM. 
+This leaves open an interesting possibility
+that non-contextual maps which are
+non-\emph{multiplicative} could be consistent with
+QM. We explicitly construct such an HV model and use
+\emph{sequential multiplicativity} as a consistency
+check imposed by QM.
 \begin{prop*} 
@@
 observables (operators can be added to make the set
-complete if it not so).
+complete if needed).
 It follows
@@
 product with $\left\langle \mathbf{b}\right|$ to
-get \begin{eqnarray*} \left\langle
-\mathbf{b}\right|\hat{C}\left|\psi\right\rangle  &
-= & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
-\left\langle
-\mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})
-\left|\psi\right\rangle
-& = & c\left\langle \mathbf{b}|\psi\right\rangle
-,\\ \tilde f(b_{1},b_{2},\dots
-b_{n})\left\langle
-\mathbf{b}|\psi\right\rangle  & = & c\left\langle
-\mathbf{b}|\psi\right\rangle .  \end{eqnarray*}
+get 
+\begin{eqnarray*} 
+c \langle \mathbf{b}|\psi\rangle 
+& = &
+\langle
+\mathbf{b} |\hat{C} |\psi
+\rangle  
+\\
+&=&
+\langle
+\mathbf{b}| f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}) |
+\psi \rangle
+\\ 
+&=&
+\tilde f (b_{1},b_{2},\dots b_{n})
+\langle
+\mathbf{b}|\psi\rangle  
+\end{eqnarray*}
 Also, we have $\left|\psi\right\rangle
@@
 $\left\langle \mathbf{b}|\psi\right\rangle \neq0$,
-then we can conclude that indeed $c=\tilde
+then we find that indeed $c=\tilde
 f(b_{1},b_{2},\dots
-b_{n})$. However, when $\left\langle
-\mathbf{b}|\psi\right\rangle =0$, viz.
-$\left|\mathbf{b}\right\rangle $s that are
-orthogonal to $\left|\psi\right\rangle $, then
-nothing can be said but that is irrelevant. We can thus conclude that
+b_{n})$. The case when $\left\langle
+\mathbf{b}|\psi\right\rangle =0$ is anyway
+irrelevant as the corresponding $\vert b\rangle$
+does not contribute to $\vert \psi\rangle$.
+We can thus conclude that
 $\left|\psi\right\rangle $ is made only of those
@@
 case, where $\hat{R}_{i}$ and $\hat{C}_{j}$ are
-just $\pm\hat{\mathbb{I}}$, it follows that all
+$\pm\hat{\mathbb{I}}$, it follows that all
 states are their eigenstates. Consequently, for
@@
 %Construction \label{ssec:cingle}}
-We are now ready to describe our explicit model.
-Let the state of a finite dimensional quantum system
-be $\left|\chi\right\rangle $. We wish to
+
+We are now ready to describe our 
+model explicitly.
+Let the state of a finite dimensional quantum
+system be $\left|\chi\right\rangle $. We wish to
 assign a value to an arbitrary observable
 $\hat{A}=\sum_{a}a\left|a\right\rangle
-\left\langle a\right|$, which has 
-eigenvectors $\{ \vert
-a_j\rangle \}$. The corresponding ordered eigenvalues are $\{a_j\}$ such that 
-$a_{\rm min}=a_1$
-and 
-$a_{\rm max}=a_n$.
-
-Our HV model for QM assigns values in the following
-three steps:
+\left\langle a\right|$, which has eigenvectors $\{
+\vert a_j\rangle \}$. The corresponding ordered
+eigenvalues are $\{a_j\}$ such that $a_{\rm
+min}=a_1$ and $a_{\rm max}=a_n$.  Our HV model for
+QM assigns values in the following three steps:
 \setdefaultleftmargin{0pt}{}{}{}{}{}
@@
 \end{enumerate}
-To see how this works consider 
-a spin-half particle in the state
+The above HV model works for all quantum systems,
+however, to illustrate its working,
+consider the example of a spin-half particle in the state
 $\left|\chi\right\rangle
@@
 \left\langle 1\right|$. Now, according to the
-postulates of this theory, $M(\hat{A},[\chi])=+1$.
-If
+postulates of this theory, $M(\hat{A},[\chi])=+1$
+if
 the randomly generated value for 
 $c\le\cos^{2}\theta$ else $\hat{A}$ is assigned
-$-1$, it then follows,  from $c$ being uniformly
+$-1$; it then follows,  from $c$ being uniformly
 random in $[0,1]$ that the statistics agree with
-the predictions of QM.
-
-Note that the assignment described by the
+the predictions of QM {\it i.e.}  the
+Born rule. 
+The assignment described by the
 prediction map $M$ is non-contextual since, given
-an operator and a state (+ the HV $c$), the value is
+an operator and a state (alongwith the HV $c$), the value is
 uniquely assigned. The map $M$ is, however,
@@
 To bring out the non-multiplicativity of our model 
-and to convince the reader of its generic validity,
-we apply it to the Peres Mermin situation of two
+explicitly and to show its
+applicability to composite systems,
+we apply the model to the Peres Mermin situation of two
 spin-half particles. Consider the initial state of
@@
 model (see \tblref{HVmodel}).
-%Two remarks are in
-This model is manifestly
-\emph{non-multiplicative}, for
-$M_{1}(\hat{C}_{3})=1\neq
-M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=-1$,
-where the subscript refers to the iteration
-number.
-More precisely,
-$M_{1}(\hat{O}):=M(\hat{O},\left[\left|\psi_{1}\right\rangle
-=\left|00\right\rangle \right])$ where the
-complete state $\left[\left|\psi_{1}\right\rangle
-\right]$ implicitly refers to both the quantum
-state $\left|00\right\rangle $ and the HV $c=0.4$.
-%Second, we must impose \emph{sequential
-%multiplicativity} as a consistency check of the
-%model, which in particular entails that
-The model, however, obeys the \emph{sequential
-multiplicativity} as required for consistency,
-namely,
-$M_{1}(\hat{C}_{3})=M_{1}(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
-where
-$M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
-\right])$,
-$M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
-\right])$ and $\left|\psi_{2}\right\rangle
-,\,\left|\psi_{3}\right\rangle $ are obtained from
-postulate 3. Note that for each iteration, a new
-HV is generated. To illustrate \emph{sequential
-multiplicativity}, we must choose to measure
-$\hat{A}_{33}$. According to step 3, since
-$\left|00\right\rangle $ is an eigenstate of
-$\hat{A}_{33}$, the final state remains
-$\left|00\right\rangle $.
 
@@
 $\left|00\right\rangle
-=\frac{1}{\sqrt 2} \left( (\left|\tilde{+}\tilde{-}\right\rangle
+=\frac{1}{\sqrt 2} \left[ \left(\left|\tilde{+}\tilde{-}\right\rangle
 +\left|\tilde{-}\tilde{+}\right\rangle
-)/\sqrt{2}+(\left|\tilde{+}\tilde{+}\right\rangle
+\right)/\sqrt{2}+\left(\left|\tilde{+}\tilde{+}\right\rangle
 +\left|\tilde{-}\tilde{-}\right\rangle
-)/\sqrt{2}\right) , 
+\right)/\sqrt{2}\right] , 
 $
@@
  \begin{equation*}
+\renewcommand{\arraystretch}{1.5}
 \begin{array}{ccc} 
-i=1,c=0.4,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle & i=2,c=0.1,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle & i=3,c=0.7,\left|\psi_{\text{init}}\right\rangle=\frac{\left|00\right\rangle +\left|11\right\rangle}{\sqrt{2}} \\
+i=1:\,\, c=0.4,\,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle
+&
+i=2:\,\, c=0.1,\,\left|\psi_{\text{init}}\right\rangle=\left|00\right\rangle
+&
+i=3:\,\, c=0.7,\,\left|\psi_{\text{init}}\right\rangle=\frac{1}{\sqrt{2}}
+(\left|00\right\rangle
++\left|11\right\rangle) \\
 %\text{Iteration} & i=1 & i=2 & i=3\\ 
@@
 %\text{HV} & c=0.4 & c=0.1 & c=0.7\\ \\ 
-
+\renewcommand{\arraystretch}{1}
 M_{1}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc} -1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
+\renewcommand{\arraystretch}{1}
 M_{2}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}-1 & -1 & -1\\ -1 & -1 & -1\\ -1 & -1 & +1\end{array}\right] &
-M_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}+1 & +1 & +1\\ +1 & +1 & -1\\ +1 & +1 & +1\end{array}\right]\\ \\
-
-M_{1}(\hat{R}_{i}),M_{1}(\hat{C}_{j})=+1\,(j\neq3) &
-M_{2}(\hat{R}_{i}),M_{2}(\hat{C}_{j})=+1\,(j\neq3) &
-M_{3}(\hat{R}_{i}),M_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
-
+\renewcommand{\arraystretch}{1}
+M_{3}(\hat{A}_{ij})\doteq\left[\begin{array}{ccc}+1
+& +1 & +1\\ +1 & +1 & -1\\ +1 & +1 &
++1\end{array}\right] \\
+M_{1}(\hat{R}_{i}), M_{1}(\hat{C}_{j})=+1\,(j\neq3) &
+M_{2}(\hat{R}_{i}), M_{2}(\hat{C}_{j})=+1\,(j\neq3) &
+M_{3}(\hat{R}_{i}), M_{3}(\hat{C}_{j})=+1\,(j\neq3)\\
 M_{1}(\hat{C}_{3})=-1 & M_{2}(\hat{C}_{3})=-1 & M_{3}(\hat{C}_{3})=-1\\ 
-
 \hat{A}_{33}=\hat{\sigma}_{z}\otimes\hat{\sigma}_{z};M_{1}(\hat{A}_{33})=+1&
@@
 \hat{A}_{13}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x};M_{3}(\hat{A}_{13})=+1\\
-
-\left|\psi_{\text{final}}\right\rangle = \left|00\right\rangle  & \left|\psi_{\text{final}}\right\rangle = \frac{\left|00\right\rangle +\left|11\right\rangle}{\sqrt{2}} & \left|\psi_{\text{final}}\right\rangle = \frac{\left|00\right\rangle+\left|11\right\rangle }{\sqrt{2}}
+\left|\psi_{\text{final}}\right\rangle =
+\left|00\right\rangle  &
+\left|\psi_{\text{final}}\right\rangle =
+\frac{1}{\sqrt{2}}(\left|00\right\rangle
++\left|11\right\rangle) &
+\left|\psi_{\text{final}}\right\rangle =
+\frac{1}{\sqrt{2}}(\left|00\right\rangle+\left|11\right\rangle)
 % \begin{bmatrixT} 
@@
 \end{table*}
-This has implications to Bohm's HV model (BHVM),
-where we have the notion of precise trajectories
-for particles guided by the wave-function.  In BHVM
-if the initial conditions are precisely known the
-entire trajectory of a particle can be predicted
-including the individual outcome of measurements.
-For the case of a single spin-half particle in a
-Stern-Gerlach experiment, BHVM can predict
-opposite results for two measurements of the
-same operator.  This observation is often used as
-a demonstration of `contextuality' in BM, although
-we did not even speak of compatible
-measurements~\cite{HardyCntxBM}.  It turns out, however,
-that if one restricts oneself to a one-one map
-between an experiment and an observable (by
-following a certain convention), the so-called
-`contextuality' can be removed from BHVM.  One
-finds that the map so obtained from observables to
-their predictions turns out to be
-non-multiplicative, suggesting that at least in
-this case, non-multiplicativity is a more suitable
-explanation of non-classicality.
+The \emph{non-multiplicativity} is
+manifest, for $M_{1}(\hat{C}_{3})=1\neq
+M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=-1$,
+where the subscript refers to the iteration
+number.  More precisely,
+$M_{1}(\hat{O}):=M(\hat{O},\left[\left|\psi_{1}\right\rangle
+=\left|00\right\rangle \right])$ where the
+complete state $\left[\left|\psi_{1}\right\rangle
+\right]$ implicitly refers to both the quantum
+state $\left|00\right\rangle $ and the HV $c=0.4$.
+The model, however, obeys the \emph{sequential
+multiplicativity} as required for consistency,
+namely,
+$M_{1}(\hat{C}_{3})=M_{1}
+(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
+where
+$M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
+\right])$,
+$M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
+\right])$ and $\left|\psi_{2}\right\rangle
+,\,\left|\psi_{3}\right\rangle $ are obtained from
+postulate 3. Note that for each iteration, a new
+HV is generated. To illustrate \emph{sequential
+multiplicativity}, we must choose to measure
+$\hat{A}_{33}$. According to step 3, since
+$\left|00\right\rangle $ is an eigenstate of
+$\hat{A}_{33}$, the final state remains
+$\left|00\right\rangle $.
 
-We have  constructed an explicit non-contextual HV
-model consistent with QM which is
-non-multiplicative. We illustrate how
-non-multiplicativity gives rise to situations which
-could get confused with the presence of contextuality.
+Non-multiplicativity has implications to Bohm's HV
+model (BHVM), where if the initial conditions are
+precisely known the entire trajectory of a
+particle (guided by the wavefunction) can be
+predicted including the individual outcome of
+measurements.  BHVM applied to a single spin-half
+particle in a Stern-Gerlach experiment, can
+predict opposite results for two measurements of
+the same operator.  This observation which is
+often used as a demonstration of `contextuality'
+in BM, does not even inolve  overlapping sets of
+compatible measurements to provide two different
+contexts~\cite{HardyCntxBM}.  It turns out that,
+if one constructs  a one-one map between an
+experiment and an observable (by following a
+certain convention), the so-called `contextuality'
+can be removed from BHVM.  However, the prediction
+map so obtained from observables to measurement
+outcomes turns out to be non-multiplicative,
+suggesting that non-multiplicativity is a more
+suitable explanation of non-classicality
+of BHVM.
 
-Imagine
-$
-\hat{B}_{1}=\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}=
+We illustrate how non-multiplicativity gives rise
+to situations which could get confused with the
+presence of contextuality.  Imagine for two sping
+1/2 particles
+\begin{eqnarray*}
+&&\hat{B}_{1}\!=\!\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}\!=\!
 \left|00\right\rangle
@@
 \left\langle 10\right|+\left|11\right\rangle
-\left\langle 11\right|\right],
-$ 
-$
-\hat{B}_{2}=\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}=
+\left\langle 11\right|\right], \\
+&&\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}\!=\!
 \left|10\right\rangle
@@
 \left\langle 00\right|+\left|01\right\rangle
-\left\langle 01\right|\right],
-$ 
-while we define 
-$
-\hat{C}=f(\{\hat{B}_{i}\})
-=0.\left|00\right\rangle \left\langle
-00\right|+1.\left|01\right\rangle \left\langle
-01\right|+2.\left|10\right\rangle \left\langle
-10\right|+3.\left|11\right\rangle \left\langle
+\left\langle 01\right|\right], \\
+&&\hat{C}=f(\{\hat{B}_{i}\}) \\
+&&\quad=1.\left|00\right\rangle \left\langle
+00\right|+2.\left|01\right\rangle \left\langle
+01\right|+3.\left|10\right\rangle \left\langle
+10\right|+4.\left|11\right\rangle \left\langle
 11\right|. 
-$
+\end{eqnarray*}
 $\hat{C}$ maybe viewed as a function of
@@
 $\hat{C}$, will collapse the state into one of the
-states which are simultaneous eignkets of $\hat{B}_{1}$
-and $\hat{B}_{2}$. Consequently, from the observed value
-of $\hat{C}$, one can deduce the values of
-$\hat{B}_{1}$ and $\hat{B}_{2}$. Now consider
+states which are simultaneous eigenkets of
+$\hat{B}_{1}$ and $\hat{B}_{2}$. Consequently,
+from the observed value of $\hat{C}$, one can
+deduce the values of $\hat{B}_{1}$ and
+$\hat{B}_{2}$. Now consider
 $\sqrt{2}\left|\chi\right\rangle
@@
 for which $M_{1}(\hat{B}_{1})=1$, and
-$M_{1}(\hat{B}_{2})=1$, using our model,
-with $c<0.5$. However, $M_{1}(\hat{C})=1$, from
-which one can deduce that $\hat{B}_{1}$ was $+1$, while
-$\hat{B}_{2}$ was $-1$.  This property itself, one may
-be tempted call contextuality, viz.  the value of
-$\hat{B}_{1}$ depends on whether it is measured alone or
-with the remaining $\{\hat{B}_{i}\}$. However, it must
-be noted that $\hat{B}_{1}$ has a well defined value,
-and so does $\hat{C}$. Thus by our accepted
-definition, there is no contextuality. It is just
-that $M_{1}(\hat{C})\neq \tilde
+$M_{1}(\hat{B}_{2})=1$, using our model, with
+$c<0.5$. However, $M_{1}(\hat{C})=1$, from which
+one can deduce that $\hat{B}_{1}$ was $+1$, while
+$\hat{B}_{2}$ was $-1$.  This property itself, one
+may be tempted call contextuality, viz.  the value
+of $\hat{B}_{1}$ depends on whether it is measured
+alone or with the remaining $\{\hat{B}_{i}\}$.
+However, it must be noted that $\hat{B}_{1}$ has a
+well defined value, and so does $\hat{C}$. Thus by
+our accepted definition, there is no
+contextuality. It is just that $M_{1}(\hat{C})\neq
+\tilde
 f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
@@
 consistent with those deduced by measuring
-$\hat{C}$.
+$\hat{C}$.  Evidently, multiplicativity must hold
+for the common eigenkets of $\hat{B}_{i}$'s.
+Consequently, any violation of multiplicativity
+must arise from states that are super-positions or
+linear combinations of these eigenkets.
 
-Evidently, multiplicativity must hold for the
-common eigenkets of $\hat{B}_{i}$.  Consequently,
-any violation of multiplicativity must arise from
-states that are super-positions or linear
-combinations of these common eigenkets.  Note,
-however, that entanglement is not necessary to
-show a violation; for instance the Peres Mermin
-test is a state independent test where a separable
-state can be used to arrive at a contradiction.
-Entanglement can be used to show non-locality of
-non-multiplicative prediction maps using Bell's
-theorem, however, the notion of non-multiplicativity
-is more basic.  \begin{acknowledgments} 
-ASA and Arvind acknowledge funding from KVPY and DST Grant No. EMR/2014/000297 respectively.
-%Arvind acknowledges funding from DST India under Grant No. EMR/2014/000297. ASA acknolwedges KVPY, DST for financial support.
+Clearly, entanglement is not necessary to have a
+non-multiplicative situation; for instance the
+Peres Mermin test is a state independent test
+where a separable state can be used to arrive at a
+contradiction. On the other hand if everyting is
+multiplicative in a situation, can we have
+violation of Bell's inequality or non-locality?
+The answer is no and therefore, one can say that
+Bell's inequalities bring out  non-local
+consequences of  non-multiplicative prediction
+maps and the notion of non-multiplicativity is
+more basic.
+
+In this letter we have presented
+non-multiplicativity as an alternative to
+contextuality and as an essential signature of
+quantumness at the kinematic level.  We expect
+this to provide new insights that will be useful
+in the areas of foundations of QM and QIP.
+{\color{red} Implications of quantum dynamics for
+our model and in general for the notion of
+non-multiplicativity needs to be explored
+further.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgments} ASA and Arvind acknowledge
+funding from KVPY and DST Grant No.
+EMR/2014/000297 respectively.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{acknowledgments}

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’
/ ‘finalPaper.tex’

@@
 We propose a non-contextual hidden variable model,
-consistent with all {\color{red} kinematic
-predictions of} quantum
+consistent with all \color{red} kinematic
+predictions of quantum
 mechanics (QM).  A careful scrutiny of consistency
@@
 contrary to common belief,  the notion of
-contextuality is not a necessary feature of QM.
+contextuality is not a necessary feature of Quantum Statics (QS).
 The alternative view that emerges, hinges on
@@
 hidden variable models, they can be made
-consistent with QM  while remaining
+consistent with QS  while remaining
 non-contextual.  The connection of
@@
 trajectories~\cite{Bohm1,Bohm2}) are incompatible
-with QM~\cite{BellOnHiddenVariables}, and we in
-this letter present a new non-contextual HV model
+with QM~\cite{BellOnHiddenVariables}, and we, in
+this letter, present a new non-contextual HV model
 consistent with QM.

### 2017-02-08 finalPaper.tex
/ ‘finalPaper.tex’
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 \caption{Non-contextuality is not inconsistent
-with QM} \label{fig:block}\end{figure}
+with QS} \label{fig:block}\end{figure}
 A closer scrutiny of the arguments
@@
 HV model consistent with 
-{\color{red} kinematics predictions of}
+kinematics predictions of
 QM (see \figref{block}).
@@
 \end{defn}
-{\color{red}
+
 \begin{defnrem}
-A prediction map of the form $M: \{
-\hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$.
+A prediction map of the form {$M: \{
+\hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$}
 itself can be called  non-contextual.
 \end{defnrem}
-}
+
 \begin{defnrem}

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 We propose a non-contextual hidden variable model,
-consistent with all \color{red} kinematic
+consistent with all kinematic
 predictions of quantum
@@
 in the areas of foundations of QM and QIP.
-{\color{red} Implications of quantum dynamics for
+Implications of quantum dynamics for
 our model and in general for the notion of
-non-multiplicativity needs to be explored
-further.}
+non-multiplicativity need to be explored
+further to assess accuracy of contextuality.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 contextuality and as an essential signature of
-quantumness at the kinematic level.  We expect
-this to provide new insights that will be useful
+quantumness at the kinematic level. {\color{red} Our result
+emphasises the importance of quantum dynamics
+to the discussion of contextuality which may have
+implications on our model and in general on the
+notion of non-multiplicativity.}
+%Implications of quantum dynamics for
+%our model and in general for the notion of
+%non-multiplicativity need to be explored
+%further.
+We expect this to provide new insights that will be useful
 in the areas of foundations of QM and QIP.
-Implications of quantum dynamics for
-our model and in general for the notion of
-non-multiplicativity need to be explored
-further to assess accuracy of contextuality.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’
/ ‘finalPaper.tex’

@@
 violation of Bell's inequality or non-locality?
-The answer is no and therefore, one can say that
+The answer is no and, therefore, one can say that
 Bell's inequalities bring out  non-local
@@
 %further.
-We expect this to provide new insights that will be useful
+%We expect this to provide new insights that will be useful
+We expect {\color{red}our result} to provide new insights that will be useful
 in the areas of foundations of QM and QIP.

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’ + ‘finalPaperNotes.bib’

@@
 experiment and an observable (by following a
-certain convention), the so-called `contextuality'
+certain convention), the so-called ``contextuality''
 can be removed from BHVM.  However, the prediction

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 the same operator.  This observation which is
-often used as a demonstration of `contextuality'
+often used as a demonstration of ``contextuality''
 in BM, does not even inolve  overlapping sets of

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 The re-examination of the very proof of
-`contextuality'  is used to illustrate
+``contextuality''  is used to illustrate
 non-multiplicativity, an intrinsic quantum
@@
 emphasises the importance of quantum dynamics
-to the discussion of contextuality which may have
-implications on our model and in general on the
-notion of non-multiplicativity.}
+to the discussion of contextuality which so far is 
+viewed merely as a kinematic phenomenon.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 emphasises the importance of quantum dynamics
-to the discussion of contextuality which so far is 
-viewed merely as a kinematic phenomenon.}
+to the discussion of contextuality which so far has
+been studied kinematically only.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 to the discussion of contextuality which so far has
-been studied kinematically only.}
+been primarily studied kinematically.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 to the discussion of contextuality which so far has
-been studied kinematically only.}
+primarily been studied kinematically.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 quantumness at the kinematic level. {\color{red} Our result
-emphasises the importance of quantum dynamics
+points out the importance of quantum dynamics
 to the discussion of contextuality which so far has
-been studied kinematically only.}
+primarily been studied kinematically.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 quantumness at the kinematic level. {\color{red} Our result
-points out the importance of quantum dynamics
+points to the importance of quantum dynamics
 to the discussion of contextuality which so far has
-primarily been studied kinematically.}
+effectively been studied kinematically only.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
/ ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 contrary to common belief,  the notion of
-contextuality is not a necessary feature of Quantum Statics (QS).
+contextuality is not a necessary feature of quantum statics (QS).
 The alternative view that emerges, hinges on
@@
 trajectories~\cite{Bohm1,Bohm2}) are incompatible
-with QM~\cite{BellOnHiddenVariables}, and we, in
+with QM~\cite{BellOnHiddenVariables} and we, in
 this letter, present a new non-contextual HV model
@@
 quantumness at the kinematic level. {\color{red} Our result
-points out the importance of quantum dynamics
-to the discussion of contextuality which so far has
-primarily been studied kinematically.}
+points to the importance of quantum dynamics
+on the discussion of contextuality which so far has
+effectively been studied kinematically only.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 quantumness at the kinematic level. {\color{red} Our result
-points to the importance of quantum dynamics
+points to the implications of quantum dynamics
 on the discussion of contextuality which so far has

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 quantumness at the kinematic level. {\color{red} Our result
-points to the importance of quantum dynamics
+points to exploring implications of quantum dynamics
 on the discussion of contextuality which so far has

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 quantumness at the kinematic level. {\color{red} Our result
-points to the importance of quantum dynamics
-on the discussion of contextuality which so far has
-effectively been studied kinematically only.}
+points to a (quantum) dynamical study of contextuality which 
+so far has effectively been analysed kinematically only.}
 %Implications of quantum dynamics for

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 \author{Atul Singh Arora}
-\email{ms11003@iisermohali.ac.in}
+\email{aarora@ulb.ac.be, ms11003@iisermohali.ac.in}
 %\selectlanguage{british}%
@@
 quantumness at the kinematic level. {\color{red} Our result
-points to a (quantum) dynamical study of contextuality which 
-so far has effectively been analysed kinematically only.}
+points to a (quantum) dynamical exploration of contextuality which 
+so far has effectively been studied kinematically only.}
 %Implications of quantum dynamics for

### 2017-02-09 finalPaper.tex
/ ‘finalPaper.tex’
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

--- 2017-02-08 finalPaper.tex
@@
 contrary to common belief,  the notion of
-contextuality is not a necessary feature of quantum statics (QS).
+contextuality is not a necessary feature of quantum kinematics (QK).
 The alternative view that emerges, hinges on
@@
 hidden variable models, they can be made
-consistent with QS  while remaining
+consistent with QK while remaining
 non-contextual.  The connection of
@@
 \caption{Non-contextuality is not inconsistent
-with QS} \label{fig:block}\end{figure}
+with kinematics of QM} \label{fig:block}\end{figure}
 A closer scrutiny of the arguments
@@
 contextuality and as an essential signature of
-quantumness at the kinematic level. {\color{red} Our result
-points to a (quantum) dynamical study of contextuality which 
-so far has effectively been analysed kinematically only.}
+quantumness at the kinematic level. Our result
+points to a (quantum) dynamical exploration of contextuality which 
+so far has effectively been studied kinematically only.
 %Implications of quantum dynamics for

### 2017-02-10 finalPaper.tex
/ ‘finalPaper.tex’
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

@@
 \caption{Non-contextuality is not inconsistent
-with kinematics of QM} \label{fig:block}\end{figure}
+with kinematic predictions of QM} \label{fig:block}\end{figure}
 A closer scrutiny of the arguments
@@
 HV model consistent with 
-kinematics predictions of
+kinematic predictions of
 QM (see \figref{block}).
@@
 %We expect this to provide new insights that will be useful
-We expect {\color{red}our result} to provide new insights that will be useful
+We expect our result to provide new insights that will be useful
 in the areas of foundations of QM and QIP.

### 2017-12-17 version2postPRL/nonContextual.tex
Major update after the PRL feedback and reading the book, papers etc.

--- 2017-02-10 finalPaper.tex
@@
-\documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
-%\documentclass[british,aps,superscriptaddress,nofootinbib,twocolumn,prl]{revtex4-1}
-%\usepackage[T1]{fontenc}
-%\usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=2cm}
-\setcounter{secnumdepth}{3}
+\documentclass[doublecol,british]{epl2} 
+% or \documentclass[page-classic]{epl2} for one column style
+\usepackage[normalem]{ulem}
+
+%\setcounter{secnumdepth}{3}     
+\usepackage{mathtools}
 \usepackage{verbatim}
@@
 \usepackage{amssymb}
-%\usepackage{esint}
+\usepackage{geometry}
+\geometry{verbose,tmargin=3cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=1cm}
 \makeatletter
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
@@
 
+%%%%%%%%%%%%%%%%%%%
+
+\title{Non-contextual Hidden Variable Model for Quantum Mechanics}
+\shorttitle{Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
+
+\author{Atul Singh Arora\inst{1,2} \and Arvind\inst{1} \and Kishor Bharti\inst{3}}
+\shortauthor{A. S. Arora \etal}
+
+\institute{                    
+  \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
+  \inst{2} Université libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
+  \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
+}
+
+\pacs{03.65.Ta}{Foundations of quantum mechanics}
+%\pacs{}{}
+% \pacs{nn.mm.xx}{First pacs description}
+% \pacs{nn.mm.xx}{Second pacs description}
+% \pacs{nn.mm.xx}{Third pacs description}
+
+\abstract{ \color{blue}
+We construct a simple non-contextual hidden variable model consistent with all kinematic predictions of quantum mechanics (QM).
+The famous Bell-KS theorem shows that non-contextual models which satisfy a further reasonable restriction are inconsistent with QM.
+We define a weaker variant of this restriction which captures its essence while still allowing a non-contextual description of QM.
+This is in contrast to contextual toy hidden variable models, such as the one by Bell, and brings out an interesting alternate way of looking at QM.
+This is also related to Bohm's model where it is harder to pin down such features.}
+
 \begin{document}
-\title{A non-contextual hidden variable model for quantum mechanics}
-\author{Atul Singh Arora}
-\email{ms11003@iisermohali.ac.in}
-%\selectlanguage{british}%
-\affiliation{Department of Physical Sciences, 
-Indian Institute of Science Education and Research
-Mohali, Sector 81 SAS Nagar 140306 Punjab India.}
-\author{Arvind}
-\email{arvind@iisermohali.ac.in}
-\affiliation{Department of Physical Sciences, 
-Indian Institute of Science Education and Research
-Mohali, Sector 81 SAS Nagar 140306 Punjab India.}
-%\selectlanguage{british}%
-\begin{abstract}
-We propose a non-contextual hidden variable model,
-consistent with all kinematic
-predictions of quantum
-mechanics (QM).  A careful scrutiny of consistency
-requirements of any hidden variable model with
-quantum mechanics and the corresponding no-go
-theorems leads us to the conclusion that,
-contrary to common belief,  the notion of
-contextuality is not a necessary feature of quantum kinematics (QK).
-The alternative view that emerges, hinges on
-identifying a new classical property which we call
-``multiplicativity''.  It turns out that by
-relaxing this condition of ``multiplicativity'' on
-hidden variable models, they can be made
-consistent with QK while remaining
-non-contextual.  The connection of
-non-``multiplicativity'' to Bohm's model and to
-apparent contextuality is also discussed.
-\end{abstract}
-\pacs{}
+
 \maketitle
+
+\section{Introduction}
 Quantum mechanics has been one of the most
@@
 cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
-However, not all HV models (e.g.
+{\color{blue} While there have been generalisations, in this letter, we restrict ourselves to the standard notion of non-contextuality as used by KS [??].} 
+Not all HV models (e.g.
 Bohm's model based on
-trajectories~\cite{Bohm1,Bohm2}) are incompatible
+trajectories~\cite{Bohm1,Bohm2}), however, are incompatible
 with QM~\cite{BellOnHiddenVariables} and we, in
@@
 consistent with QM.
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{block1}
-\caption{Non-contextuality is not inconsistent
-with kinematic predictions of QM} \label{fig:block}\end{figure}
+% \begin{figure}[h]
+% \includegraphics[width=0.9\columnwidth]{block1}
+% \caption{Non-contextuality is not inconsistent
+% with kinematic predictions of QM} \label{fig:block}\end{figure}
+{\color{blue}
+The KS theorem is applicable to non-contextual HV models which additionally satisfy functional consistency --- algebraic constraints obeyed by commuting quantum observables must be satisfied by the HV model at the level of individual outcomes.
+One of the main justifications given for imposing this was the reasonable requirement that an observable $\hat A^2$ must depend on $\hat A$ even at the HV level because otherwise one can construct HV models where these observables get mapped to random variables with no relation to each other (see [??]).
+As we will show, one can weaken this requirement into what we call weak functional consistency --- functional consistency is demanded only when the observables in question have sharp values.
+This entails that even in the HV model the observables will depend on each other where they should thereby capturing the same idea.
+The consequence of demanding only the weaker variant is that the KS theorem no longer applies and non-contextual HV models can be consistently constructed.
+This is in stark contrast with contextual HV models, such as the one by Bell, which we demonstrate by re-examining a `proof of contextuality' using our model.
+}
+\sout{
 A closer scrutiny of the arguments
@@
 kinematic predictions of
-QM (see \figref{block}).
+QM  %(see \figref{block}).
 The re-examination of the very proof of
@@
 world from the classical one and may have a role
-to play in QIP protocols.  This provides a new
+to play in QIP protocols. }
+This provides a new
 way to look at the classical-quantum divide and at
@@
 
+\section{Non-Contextuality and Functional Consistency}
+We introduce some notation and make the relevant notions precise to facilitate the description and assesment of our model.
 \begin{notn*}
@@
 \begin{defnrem}
+{\color{blue} Broader definitions in the literature have been suggested~\cite{spekkens_pra} which extend the notion to probabilistic HV models.
+The idea is that any feature of a HV model that is not determined solely by the operational aspect of QM is defined to be, in the case of measurements for instance, measurement contextuality.
+To maintain a distinction between different features of HV models, which is of interest here, we stick to the standard definition.}
+\sout{
 Broader definitions in the literature have been
 suggested which declare a larger set of theories
-as non-contextual~\cite{spekkens_pra}. For our
+as non-contextual. For our %~\cite{spekkens_pra}. For our
 purposes, however, this restricted definition will
@@
 takes might depend on which other compatible
-observable it is being  measured with.
+observable it is being  measured with. }
 \end{defnrem}
+
+{\color{blue} 
+In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand the following to establish their no-go theorem.
+}
+
+\sout{
 Before we re-examine the result of Kochen and
-Specker~\cite{KochenSpecker} that non-contextual
+Specker that non-contextual%~\cite{KochenSpecker} that non-contextual
 models cannot be compatible with quantum
@@
 alternative to contextuality, we define
-multiplicativity explicitly.
+multiplicativity explicitly.}
+
 \begin{defn}
-A prediction map $M$ is \emph{multiplicative} iff
+A prediction map $M$ is \emph{functionally consistent} iff
 \begin{align*} &
@@
 $[\psi]\in[\mathcal{H}]$. A
-\emph{non-multiplicative} map is one that is not
-multiplicative.  
+\emph{functionally inconsistent} map is one that is not
+functionally consistent.  
 \end{defn} 
@@
 $\hat{B}_{i}$s, $M$ must clearly be
-multiplicative. It is, however, not obvious that
+functionally consistent. It is, however, not obvious that
 this property must always hold. For example,
@@
 independently, according to QM, with probability
-half. Here multiplicativity clearly is not
-required to hold.
+half. Here functional consistency clearly is not
+required to hold {\color{blue} and indeed this is why it was demanded in addition to being consistent with QM by KS}.
 Antithetically, it is clear that if one first
@@
 must be $-1$. This is consistent with measuring
-$\hat{C}$. To capture this property we define
-\emph{sequential multiplicativity} as follows.
+$\hat{C}$.
+{\color{blue} In our treatment, instead of imposing functional consistency, we demand its aforesaid weaker variant.
+It captures the same idea, however, only when it has a precise meaning according to QM.} To capture this property precisely we define
+\emph{weak functional consistency} as follows.
 \begin{defn} 
-A prediction map $m$ is
-\emph{sequentially multiplicative} for a given
+A prediction map $m$ has
+\emph{weak functional consistency} for a given
 sequence map $s$, iff \begin{align*}
@@
 \end{defn}
+
 With these definitions we are now ready to discuss
@@
 For a system composed of two spin-half particles 
-consider the following set of operators \[
+consider the following set of operators 
+\begin{equation*}
 \hat{A}_{ij}\doteq\left[\begin{array}{ccc}
@@
 \hat{\sigma}_{z}\otimes\hat{\sigma}_{z}
-\end{array}\right] \] which have the property that
+\end{array}\right]
+\end{equation*}
+which have the property that
 all operators along a row (or column) commute. Further,
@@
 theorem, non-contextual maps which are
-\emph{multiplicative} must be incompatible with
+\emph{functionally consistent} must be incompatible with
 QM. 
-This leaves open an interesting possibility
-that non-contextual maps which are
-non-\emph{multiplicative} could be consistent with
-QM. We explicitly construct such an HV model and use
-\emph{sequential multiplicativity} as a consistency
-check imposed by QM.
+This leaves open an interesting possibility that non-contextual maps which have \emph{weak functional consistency} could be consistent with QM.
+{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional consistency} is, in fact, a consequnce of QM.}
 \begin{prop*} 
@@
 $\hat{C}$ yields repeatable results (same result
-each time). Then according to QM, \emph{sequential
-multiplicativity} holds, where $\hat{C}:=
+each time). Then according to QM, \emph{weak functional consistency} holds, where $\hat{C}:=
 f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$, and
@@
 states are their eigenstates. Consequently, for
-these operators \emph{sequential multiplicativity}
+these operators \emph{weak functional consistency}
 must always hold.
-%\subsection{C-ingle model | An Explicit
-%Construction \label{ssec:cingle}}
 
+\section{Construction}
 We are now ready to describe our 
@@
 uniquely assigned. The map $M$ is, however,
-non-multiplicative.
+functionally inconsistent.
 
-To bring out the non-multiplicativity of our model 
-explicitly and to show its
+{\color{blue} To see this functional inconsistency explicitly in} our model and to see its
 applicability to composite systems,
@@
 \end{table*}
-The \emph{non-multiplicativity} is
+The \emph{functional inconsistency} is
 manifest, for $M_{1}(\hat{C}_{3})=1\neq
@@
 state $\left|00\right\rangle $ and the HV $c=0.4$.
-The model, however, obeys the \emph{sequential
-multiplicativity} as required for consistency,
+The model, however, obeys the \emph{weak functional
+consistency} requirement,
 namely,
@@
 postulate 3. Note that for each iteration, a new
-HV is generated. To illustrate \emph{sequential
-multiplicativity}, we must choose to measure
+HV is generated. To illustrate \emph{weak functional consistency}, 
+we must choose to measure
 $\hat{A}_{33}$. According to step 3, since
@@
 
-Non-multiplicativity has implications to Bohm's HV
+\section{Implications and Remarks}
+{ \color{blue} 
+The model demonstrates \emph{function inconsistency} as an alternative signature of quantumness as opposed to contextuality. This view is not just an artifact of the simplicity of the model. 
+It }has implications to Bohm's HV
 model (BHVM), where if the initial conditions are
@@
 often used as a demonstration of ``contextuality''
-in BM, does not even inolve  overlapping sets of
+in BM, does not inolve  overlapping sets of
 compatible measurements to provide two different
-contexts~\cite{HardyCntxBM}.  It turns out that,
+contexts~\cite{HardyCntxBM} {\color{blue}and is therefore not of
+interest here.}  It turns out that,
 if one constructs  a one-one map between an
 experiment and an observable (by following a
-certain convention), the so-called ``contextuality''
+certain convention), this so-called ``contextuality''
 can be removed from BHVM.  However, the prediction
 map so obtained from observables to measurement
-outcomes turns out to be non-multiplicative,
-suggesting that non-multiplicativity is a more
+outcomes turns out to be \emph{functionally inconsistent},
+suggesting that \emph{functional inconsistency} is a more
 suitable explanation of non-classicality
 of BHVM.
+{\color{blue} In fact, our model when appropriately extended to continous variables yields Bohmian trajectories in the single particle  case which suggests that it can be used as a starting point for constructing more interesting families of HV theories that take quantum time dynamics into account as well.
 
-We illustrate how non-multiplicativity gives rise
+Bell himself had constructed a deceptively similar toy model to demonstrate a HV construction that is not ruled out by his contextuality no-go theorem.
+However, his model was contextual (and functionally consistent) which is in stark contrast with our construction which is non-contextual (and functionally inconsistent).
+
+We end with making two short remarks.} First, we illustrate how functional inconsistency gives rise
 to situations which could get confused with the
-presence of contextuality.  Imagine for two sping
+presence of contextuality.  Imagine for two spin
 1/2 particles
@@
 f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
-viz. the theory is non-multiplicative. Note that
+viz. the theory is functionally inconsistent. Note that
 after measuring $\hat{C}$, however,
@@
 consistent with those deduced by measuring
-$\hat{C}$.  Evidently, multiplicativity must hold
+$\hat{C}$.  Evidently, functional consistency must hold
 for the common eigenkets of $\hat{B}_{i}$'s.
-Consequently, any violation of multiplicativity
+Consequently, any violation of functional consistency
 must arise from states that are super-positions or
@@
 
-Clearly, entanglement is not necessary to have a
-non-multiplicative situation; for instance the
+{\color{blue} Second, note that} \sout{Clearly,} entanglement is not necessary to demonstrate
+functional inconsistency; for instance the
 Peres Mermin test is a state independent test
@@
 contradiction. On the other hand if everyting is
-multiplicative in a situation, can we have
+functionally consistent in a situation, can we have
 violation of Bell's inequality or non-locality?
@@
 Bell's inequalities bring out  non-local
-consequences of  non-multiplicative prediction
-maps and the notion of non-multiplicativity is
+consequences of functionally inconsistent prediction
+maps and the notion of functional inconsistency is
 more basic.
 
+\section{Conclusion}
 In this letter we have presented
-non-multiplicativity as an alternative to
+functional inconsistency as an alternative to
 contextuality and as an essential signature of
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{acknowledgments} ASA and Arvind acknowledge
+\acknowledgments
+We are thankful to the anonymous referees for their feedback. ASA and Arvind acknowledge
 funding from KVPY and DST Grant No.
 EMR/2014/000297 respectively.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{acknowledgments}
-%\bibliographystyle{apsrev4-1}
-\bibliography{references} \end{document}
+
+% \begin{thebibliography}{0}
+
+% \bibitem{b.a}
+%   \Name{Author F., Author S. \and Author T.}
+%   \REVIEW{Some Rev. A}{69}{1969}{9691}.
+
+% \bibitem{b.b}
+%   \Name{Author F. \and Author S.}
+%   \Book{Some Book of Interest}
+%   \Editor{A. Editor}
+%   \Vol{9}
+%   \Publ{Publishing house, City}
+%   \Year{1939}
+%   \Page{666}.
+
+% \bibitem{b.c}
+%   \Editor{Editor A.}
+%   \Book{Some Book of Interest}
+%   \Vol{9}
+%   \Publ{Publishing house, City}
+%   \Year{1939}
+%   \Section{A}.
+\bibliographystyle{unsrt}
+\bibliography{references}
+% \end{thebibliography}
+
+\end{document}

### 2017-12-23 version2postPRL/nonContextual.tex
Arvind Sir Update

@@
 
-\author{Atul Singh Arora\inst{1,2} \and Arvind\inst{1} \and Kishor Bharti\inst{3}}
+\author{Atul Singh Arora\inst{1,2} \and Kishor Bharti\inst{3} \and Arvind\inst{1}}
 \shortauthor{A. S. Arora \etal}
@@
 \abstract{ \color{blue}
-We construct a simple non-contextual hidden variable model consistent with all kinematic predictions of quantum mechanics (QM).
-The famous Bell-KS theorem shows that non-contextual models which satisfy a further reasonable restriction are inconsistent with QM.
-We define a weaker variant of this restriction which captures its essence while still allowing a non-contextual description of QM.
-This is in contrast to contextual toy hidden variable models, such as the one by Bell, and brings out an interesting alternate way of looking at QM.
-This is also related to Bohm's model where it is harder to pin down such features.}
-
+We construct a \sout{\color{red} simple} non-contextual
+hidden variable model consistent with all {\color{red} the}
+kinematic predictions of quantum mechanics (QM). The famous
+Bell-KS theorem shows that non-contextual models which
+satisfy a further reasonable restriction are inconsistent
+with QM. {\color{red} In our construction,} we define a
+weaker variant of this restriction which captures its
+essence while still allowing a non-contextual description of
+QM. This is in contrast to {\color{red} the} contextual
+\sout{toy} hidden variable {\color{red} toy} models, such as
+the one by Bell, {\color{red} and}  brings out an interesting
+alternate way of looking at QM. {\color{red} The results}
+also relate to {\color{red} the Bohmian}
+model, where it is harder to pin
+down such features.}
 \begin{document}
@@
 \maketitle
+
+{\color{red} 
+I think that we should use `functional consistency' with a
+hyphen `functional-consistency' and avoid using the word
+`functional inconsistency'. We should instead use 
+`non functional-consistency'
+}
 
@@
 entanglement~\cite{Ekert,PironioRndmnssCrtfcn,NielsenChuang}.
-The work of  Kochen Specker~\cite{KochenSpecker}
+The work of  Kochen Specker (KS)~\cite{KochenSpecker}
 and Gleason {\it
@@
 cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
-{\color{blue} While there have been generalisations, in this letter, we restrict ourselves to the standard notion of non-contextuality as used by KS [??].} 
+{\color{blue} While there have been generalisations, in this
+letter, we restrict ourselves to the standard notion of
+non-contextuality as used by KS~\cite{KochenSpecker}.}
+
 Not all HV models (e.g.
@@
 consistent with QM.
-% \begin{figure}[h]
-% \includegraphics[width=0.9\columnwidth]{block1}
-% \caption{Non-contextuality is not inconsistent
-% with kinematic predictions of QM} \label{fig:block}\end{figure}
+\begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{block2}
+\caption{Non-contextuality is not inconsistent
+with kinematic predictions of QM} \label{fig:block}\end{figure}
 {\color{blue}
-The KS theorem is applicable to non-contextual HV models which additionally satisfy functional consistency --- algebraic constraints obeyed by commuting quantum observables must be satisfied by the HV model at the level of individual outcomes.
-One of the main justifications given for imposing this was the reasonable requirement that an observable $\hat A^2$ must depend on $\hat A$ even at the HV level because otherwise one can construct HV models where these observables get mapped to random variables with no relation to each other (see [??]).
-As we will show, one can weaken this requirement into what we call weak functional consistency --- functional consistency is demanded only when the observables in question have sharp values.
-This entails that even in the HV model the observables will depend on each other where they should thereby capturing the same idea.
-The consequence of demanding only the weaker variant is that the KS theorem no longer applies and non-contextual HV models can be consistently constructed.
-This is in stark contrast with contextual HV models, such as the one by Bell, which we demonstrate by re-examining a `proof of contextuality' using our model.
-}
+The KS theorem is applicable to non-contextual HV models
+which additionally satisfy functional consistency --
+{\it algebraic constraints obeyed by commuting quantum
+observables must be satisfied by the HV model at the level
+of individual outcomes}. 
+One of the main justifications \sout{\color{red} given} for imposing
+this was the \sout{reasonable} requirement that \sout{an}
+{\color{red} the} observable $\hat A^2$ must depend on $\hat
+A$ even at the HV level. This sounds reasonable because
+otherwise one can construct HV models where these
+observables {\color{red} can} get mapped to random variables
+with no relation to each other (see~\cite{KochenSpecker}). 
+As we
+will show, one can weaken this requirement into what we call
+weak functional consistency -- {\it functional consistency is
+demanded only when the observables in question have sharp
+values}. This entails that even in the HV model the
+observables will depend on each other where they should for
+{\color{red} consistency} and not otherwise,
+thereby capturing the same idea {\color{red} without undue
+constraints}. The consequence of
+demanding only the weaker variant is that the KS theorem no
+longer applies and non-contextual HV models can be
+consistently constructed.
+
+{\color{red}  Sentence below needs editing}
+This is in stark contrast with
+contextual HV models, such as the toy
+model\footnote{introduced in connection with Gleason's
+Theorem} by Bell~\cite{BellOnHiddenVariables}, which we
+demonstrate by re-examining a `proof of contextuality' using
+our model.}
 \sout{
@@
 \section{Non-Contextuality and Functional Consistency}
-We introduce some notation and make the relevant notions precise to facilitate the description and assesment of our model.
+We introduce some notation and make the relevant notions
+precise to facilitate the description and assessment of our
+model.
 \begin{notn*}
@@
 \begin{defnrem}
-{\color{blue} Broader definitions in the literature have been suggested~\cite{spekkens_pra} which extend the notion to probabilistic HV models.
-The idea is that any feature of a HV model that is not determined solely by the operational aspect of QM is defined to be, in the case of measurements for instance, measurement contextuality.
-To maintain a distinction between different features of HV models, which is of interest here, we stick to the standard definition.}
+{\color{blue} Broader definitions in the literature have
+been suggested~\cite{spekkens_pra} which extend the notion
+to probabilistic HV models. 
+{\color{red} Sentence below is not clear. Do we
+want to define measurement contextuality? or general
+contextuality in this broader sense?}
+The idea is that any feature of
+a HV model that is not determined solely by the operational
+aspect of QM is defined to be, in the case of measurements
+for instance, measurement contextuality. 
+To maintain a
+distinction between different features of HV models, which
+is of interest here, we stick to the standard definition.}
+
 \sout{
@@
 {\color{blue} 
-In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand the following to establish their no-go theorem.
+In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand \emph{functional consistency} to establish their no-go theorem which is defined below in our notation.
 }
@@
 {\color{blue} In our treatment, instead of imposing functional consistency, we demand its aforesaid weaker variant.
-It captures the same idea, however, only when it has a precise meaning according to QM.} To capture this property precisely we define
+It captures the same idea, however, only when it has a precise meaning according to QM.} \sout{To capture this property precisely we define} {\color{blue} To this end we define}
 \emph{weak functional consistency} as follows.
@@
 This leaves open an interesting possibility that non-contextual maps which have \emph{weak functional consistency} could be consistent with QM.
-{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional consistency} is, in fact, a consequnce of QM.}
+{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional consistency} is, in fact, a consequence of QM.}
 \begin{prop*} 
@@
 often used as a demonstration of ``contextuality''
-in BM, does not inolve  overlapping sets of
+in BM, does not involve  overlapping sets of
 compatible measurements to provide two different
@@
 of BHVM.
-{\color{blue} In fact, our model when appropriately extended to continous variables yields Bohmian trajectories in the single particle  case which suggests that it can be used as a starting point for constructing more interesting families of HV theories that take quantum time dynamics into account as well.
+{\color{blue} In fact, our model when appropriately extended
+to continuous variables yields Bohmian trajectories in the
+single particle  case which suggests that it can be used as
+a starting point for constructing more interesting families
+of HV theories that take quantum time dynamics into account
+as well.
 
-Bell himself had constructed a deceptively similar toy model to demonstrate a HV construction that is not ruled out by his contextuality no-go theorem.
-However, his model was contextual (and functionally consistent) which is in stark contrast with our construction which is non-contextual (and functionally inconsistent).
+Bell himself had constructed a deceptively similar toy
+model\footnote{as referred to earlier} to demonstrate a HV
+construction that is not ruled out by his contextuality
+no-go theorem. However, his model was contextual (and
+functionally consistent) which is in stark contrast with our
+construction which is non-contextual (and functionally
+inconsistent).
 
-We end with making two short remarks.} First, we illustrate how functional inconsistency gives rise
-to situations which could get confused with the
-presence of contextuality.  Imagine for two spin
-1/2 particles
+We end with making two short remarks.} First, we illustrate
+how functional inconsistency gives rise to situations which
+could get confused with the presence of contextuality.
+Imagine for two spin 1/2 particles
 \begin{eqnarray*}
@@
 where a separable state can be used to arrive at a
-contradiction. On the other hand if everyting is
+contradiction. On the other hand if everything is
 functionally consistent in a situation, can we have
@@
 \acknowledgments
-We are thankful to the anonymous referees for their feedback. ASA and Arvind acknowledge
+\sout{We are thankful to the anonymous referees for 
+their feedback.} 
+ASA and Arvind acknowledge
 funding from KVPY and DST Grant No.

### 2017-12-23 version2postPRL/nonContextualv1.tex
Arvind Sir Update

--- 2017-12-17 version2postPRL/nonContextual.tex
@@
 cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
-{\color{blue} While there have been generalisations, in this letter, we restrict ourselves to the standard notion of non-contextuality as used by KS [??].} 
+{\color{blue} While there have been generalisations, in this letter, we restrict ourselves to the standard notion of non-contextuality as used by KS~\cite{KochenSpecker}.} 
 Not all HV models (e.g.
@@
 consistent with QM.
-% \begin{figure}[h]
-% \includegraphics[width=0.9\columnwidth]{block1}
-% \caption{Non-contextuality is not inconsistent
-% with kinematic predictions of QM} \label{fig:block}\end{figure}
+\begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{block2}
+\caption{Non-contextuality is not inconsistent
+with kinematic predictions of QM} \label{fig:block}\end{figure}
 {\color{blue}
 The KS theorem is applicable to non-contextual HV models which additionally satisfy functional consistency --- algebraic constraints obeyed by commuting quantum observables must be satisfied by the HV model at the level of individual outcomes.
-One of the main justifications given for imposing this was the reasonable requirement that an observable $\hat A^2$ must depend on $\hat A$ even at the HV level because otherwise one can construct HV models where these observables get mapped to random variables with no relation to each other (see [??]).
+One of the main justifications given for imposing this was the reasonable requirement that an observable $\hat A^2$ must depend on $\hat A$ even at the HV level because otherwise one can construct HV models where these observables get mapped to random variables with no relation to each other (see~\cite{KochenSpecker}).
 As we will show, one can weaken this requirement into what we call weak functional consistency --- functional consistency is demanded only when the observables in question have sharp values.
@@
 The consequence of demanding only the weaker variant is that the KS theorem no longer applies and non-contextual HV models can be consistently constructed.
-This is in stark contrast with contextual HV models, such as the one by Bell, which we demonstrate by re-examining a `proof of contextuality' using our model.
+This is in stark contrast with contextual HV models, such as the toy model\footnote{introduced in connection with Gleason's Theorem} by Bell~\cite{BellOnHiddenVariables}, which we demonstrate by re-examining a `proof of contextuality' using our model.
 }
@@
 
-Bell himself had constructed a deceptively similar toy model to demonstrate a HV construction that is not ruled out by his contextuality no-go theorem.
+Bell himself had constructed a deceptively similar toy model\footnote{as referred to earlier} to demonstrate a HV construction that is not ruled out by his contextuality no-go theorem.
 However, his model was contextual (and functionally consistent) which is in stark contrast with our construction which is non-contextual (and functionally inconsistent).

### 2017-12-23 version2postPRL/nonContextual.tex
Updated after Arvind sir

@@
 
+% \usepackage{comment}
+% \excludecomment{sout}
+%\let\endsout\relax
+
 %%%%%%%%%%%%%%%%%%%
 
-\title{Non-contextual Hidden Variable Model for Quantum Mechanics}
+\title{A non-contextual Hidden Variable Model for Quantum Mechanics}
 \shorttitle{Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
@@
 \abstract{ \color{blue}
-We construct a \sout{\color{red} simple} non-contextual
+We construct a non-contextual
 hidden variable model consistent with all {\color{red} the}
@@
 QM. This is in contrast to {\color{red} the} contextual
-\sout{toy} hidden variable {\color{red} toy} models, such as
+ hidden variable {\color{red} toy} models, such as
 the one by Bell, {\color{red} and}  brings out an interesting
@@
 
-{\color{red} 
-I think that we should use `functional consistency' with a
-hyphen `functional-consistency' and avoid using the word
-`functional inconsistency'. We should instead use 
-`non functional-consistency'
-}
+% {\color{red} 
+% I think that we should use `functional consistency' with a
+% hyphen `functional-consistency' and avoid using the word
+% `functional inconsistency'. We should instead use 
+% `non functional-consistency'
+% }
 
@@
 The KS theorem is applicable to non-contextual HV models
-which additionally satisfy functional consistency --
-{\it algebraic constraints obeyed by commuting quantum
+which additionally satisfy {\it functional consistency ---
+algebraic constraints obeyed by commuting quantum
 observables must be satisfied by the HV model at the level
 of individual outcomes}. 
-One of the main justifications \sout{\color{red} given} for imposing
-this was the \sout{reasonable} requirement that \sout{an}
+One of the main justifications for imposing
+this was the requirement that
 {\color{red} the} observable $\hat A^2$ must depend on $\hat
@@
 will show, one can weaken this requirement into what we call
-weak functional consistency -- {\it functional consistency is
+{\it weak functional consistency -- functional consistency is
 demanded only when the observables in question have sharp
@@
 
-{\color{red}  Sentence below needs editing}
+{\color{red}  Sentence below has been edited}
 This is in stark contrast with
@@
 model\footnote{introduced in connection with Gleason's
-Theorem} by Bell~\cite{BellOnHiddenVariables}, which we
-demonstrate by re-examining a `proof of contextuality' using
+Theorem} by Bell~\cite{BellOnHiddenVariables} because
+here we consider models where the algebraic constaints of 
+QM are not obeyed in general by the HV model at the level of
+individual outcomes. We demonstrate this contrast
+by re-examining a `proof of contextuality' using
 our model.}
-\sout{
-A closer scrutiny of the arguments
-leading to the dichotomy between QM and HV models
-reveals that the algebraic constraints obeyed by
-quantum observables may not necessarily be obeyed
-by the predictions of an HV model at the level of
-individual outcomes and  that contextuality is 
-not a necessary feature of QM. Those HV
-models that obey such algebraic constraints
-possess a special property which we call
-``multiplicativity''.  Enlarging the scope of HV
-models to include non-multiplicative models,
-permits us to construct an explicit non-contextual
-HV model consistent with 
-kinematic predictions of
-QM  %(see \figref{block}).
-The re-examination of the very proof of
-``contextuality''  is used to illustrate
-non-multiplicativity, an intrinsic quantum
-feature, which we propose as a possible
-alternative to contextuality. 
-Non-mulitiplicativity thus might turn out to be
-the key quantum feature distinguishing the quantum
-world from the classical one and may have a role
-to play in QIP protocols. }
+% {
+% A closer scrutiny of the arguments
+% leading to the dichotomy between QM and HV models
+% reveals that the algebraic constraints obeyed by
+% quantum observables may not necessarily be obeyed
+% by the predictions of an HV model at the level of
+% individual outcomes and  that contextuality is 
+% not a necessary feature of QM. Those HV
+% models that obey such algebraic constraints
+% possess a special property which we call
+% ``multiplicativity''.  Enlarging the scope of HV
+% models to include non-multiplicative models,
+% permits us to construct an explicit non-contextual
+% HV model consistent with 
+% kinematic predictions of
+% QM  %(see \figref{block}).
+% The re-examination of the very proof of
+% ``contextuality''  is used to illustrate
+% non-multiplicativity, an intrinsic quantum
+% feature, which we propose as a possible
+% alternative to contextuality. 
+% Non-mulitiplicativity thus might turn out to be
+% the key quantum feature distinguishing the quantum
+% world from the classical one and may have a role
+% to play in QIP protocols. }
 This provides a new
@@
 to probabilistic HV models. 
-{\color{red} Sentence below is not clear. Do we
-want to define measurement contextuality? or general
-contextuality in this broader sense?}
+% {\color{red} Sentence below is not clear. Do we
+% want to define measurement contextuality? or general
+% contextuality in this broader sense?}
+{\color{red} Next sentence has been re-written.}
 The idea is that any feature of
 a HV model that is not determined solely by the operational
-aspect of QM is defined to be, in the case of measurements
-for instance, measurement contextuality. 
+aspect of QM is defined to be a demonstration of contextuality. 
+If, for instance, this distinction arises in the measurement procedure
+then it is termed as measurement contextuality.
+%In the case of measurements for instance, measurement contextuality. 
 To maintain a
@@
 
-\sout{
-Broader definitions in the literature have been
-suggested which declare a larger set of theories
-as non-contextual. For our %~\cite{spekkens_pra}. For our
-purposes, however, this restricted definition will
-suffice  and our results will in any case be valid
-for the broader definitions. The term contextual
-is used to suggest that the value an observable
-takes might depend on which other compatible
-observable it is being  measured with. }
+% \sout{
+% Broader definitions in the literature have been
+% suggested which declare a larger set of theories
+% as non-contextual. For our %~\cite{spekkens_pra}. For our
+% purposes, however, this restricted definition will
+% suffice  and our results will in any case be valid
+% for the broader definitions. The term contextual
+% is used to suggest that the value an observable
+% takes might depend on which other compatible
+% observable it is being  measured with. }
 \end{defnrem}
@@
 
-\sout{
-Before we re-examine the result of Kochen and
-Specker that non-contextual%~\cite{KochenSpecker} that non-contextual
-models cannot be compatible with quantum
-mechanics and show that multiplicativity can provide an
-alternative to contextuality, we define
-multiplicativity explicitly.}
+% \sout{
+% Before we re-examine the result of Kochen and
+% Specker that non-contextual%~\cite{KochenSpecker} that non-contextual
+% models cannot be compatible with quantum
+% mechanics and show that multiplicativity can provide an
+% alternative to contextuality, we define
+% multiplicativity explicitly.}
 
@@
 $[\psi]\in[\mathcal{H}]$. A
-\emph{functionally inconsistent} map is one that is not
+\emph{non functionally-consistent} map is one that is not
 functionally consistent.  
@@
 {\color{blue} In our treatment, instead of imposing functional consistency, we demand its aforesaid weaker variant.
-It captures the same idea, however, only when it has a precise meaning according to QM.} \sout{To capture this property precisely we define} {\color{blue} To this end we define}
+It captures the same idea, however, only when it has a precise meaning according to QM.} {\color{blue} To this end we define}
 \emph{weak functional consistency} as follows.
@@
 
-{\color{blue} To see this functional inconsistency explicitly in} our model and to see its
+{\color{blue} To see this non functional-consistency explicitly in} our model and to see its
 applicability to composite systems,
@@
 \end{table*}
-The \emph{functional inconsistency} is
+The \emph{non functional-consistency} is
 manifest, for $M_{1}(\hat{C}_{3})=1\neq
@@
 { \color{blue} 
-The model demonstrates \emph{function inconsistency} as an alternative signature of quantumness as opposed to contextuality. This view is not just an artifact of the simplicity of the model. 
+The model demonstrates \emph{non function-consistency} as an alternative signature of quantumness as opposed to contextuality. This view is not just an artifact of the simplicity of the model. 
 It }has implications to Bohm's HV
@@
 map so obtained from observables to measurement
-outcomes turns out to be \emph{functionally inconsistent},
-suggesting that \emph{functional inconsistency} is a more
+outcomes turns out to be \emph{non functionally-consistent},
+suggesting that \emph{non functional-consistency} is a more
 suitable explanation of non-classicality
@@
 functionally consistent) which is in stark contrast with our
-construction which is non-contextual (and functionally
-inconsistent).
+construction which is non-contextual (and non functionally-consistent).
 
 We end with making two short remarks.} First, we illustrate
-how functional inconsistency gives rise to situations which
+how non functional-consistency gives rise to situations which
 could get confused with the presence of contextuality.
@@
 f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
-viz. the theory is functionally inconsistent. Note that
+viz. the theory is non functionally-consistent. Note that
 after measuring $\hat{C}$, however,
@@
 
-{\color{blue} Second, note that} \sout{Clearly,} entanglement is not necessary to demonstrate
-functional inconsistency; for instance the
+{\color{blue} Second, note that} entanglement is not necessary to demonstrate
+non functional-consistency; for instance the
 Peres Mermin test is a state independent test
@@
 Bell's inequalities bring out  non-local
-consequences of functionally inconsistent prediction
-maps and the notion of functional inconsistency is
+consequences of non functionally-consistent prediction
+maps and the notion of non functional-consistency is
 more basic.
@@
 In this letter we have presented
-functional inconsistency as an alternative to
+non functional-consistency as an alternative to
 contextuality and as an essential signature of
@@
 \acknowledgments
-\sout{We are thankful to the anonymous referees for 
-their feedback.} 
 ASA and Arvind acknowledge

### 2017-12-24 version2postPRL/nonContextual.tex
added many updates

@@
 
-\title{A non-contextual Hidden Variable Model for Quantum Mechanics}
+\title{Relexation of functional-consistency allows
+a non-contextual hidden variable model for quantum mechanics
+\\
+\sout{A non-contextual Hidden Variable Model for Quantum
+Mechanics}}
 \shorttitle{Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
@@
 The KS theorem is applicable to non-contextual HV models
-which additionally satisfy {\it functional consistency ---
+which additionally satisfy \emph{functional-consistency ---
 algebraic constraints obeyed by commuting quantum
@@
 will show, one can weaken this requirement into what we call
-{\it weak functional consistency -- functional consistency is
+\emph{weak functional-consistency -- functional-consistency is
 demanded only when the observables in question have sharp
@@
 {\color{blue} 
-In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand \emph{functional consistency} to establish their no-go theorem which is defined below in our notation.
+In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand \emph{functional-consistency} to establish their no-go theorem which is defined below in our notation.
 }
@@
 \begin{defn}
-A prediction map $M$ is \emph{functionally consistent} iff
+A prediction map $M$ is \emph{functionally-consistent} iff
 \begin{align*} &
@@
 \emph{non functionally-consistent} map is one that is not
-functionally consistent.  
+functionally-consistent.  
 \end{defn} 
@@
 $\hat{B}_{i}$s, $M$ must clearly be
-functionally consistent. It is, however, not obvious that
+functionally-consistent. It is, however, not obvious that
 this property must always hold. For example,
@@
 independently, according to QM, with probability
-half. Here functional consistency clearly is not
+half. Here functional-consistency clearly is not
 required to hold {\color{blue} and indeed this is why it was demanded in addition to being consistent with QM by KS}.
@@
 $\hat{C}$.
-{\color{blue} In our treatment, instead of imposing functional consistency, we demand its aforesaid weaker variant.
+{\color{blue} In our treatment, instead of imposing functional-consistency, we demand its aforesaid weaker variant.
 It captures the same idea, however, only when it has a precise meaning according to QM.} {\color{blue} To this end we define}
-\emph{weak functional consistency} as follows.
+\emph{weak functional-consistency} as follows.
 \begin{defn} 
 A prediction map $m$ has
-\emph{weak functional consistency} for a given
+\emph{weak functional-consistency} for a given
 sequence map $s$, iff \begin{align*}
@@
 theorem, non-contextual maps which are
-\emph{functionally consistent} must be incompatible with
+\emph{functionally-consistent} must be incompatible with
 QM. 
-This leaves open an interesting possibility that non-contextual maps which have \emph{weak functional consistency} could be consistent with QM.
-{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional consistency} is, in fact, a consequence of QM.}
+This leaves open an interesting possibility that non-contextual maps which have \emph{weak-functional consistency} could be consistent with QM.
+{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional-consistency} is, in fact, a consequence of QM.}
 \begin{prop*} 
@@
 states are their eigenstates. Consequently, for
-these operators \emph{weak functional consistency}
+these operators \emph{weak functional-consistency}
 must always hold.
@@
 uniquely assigned. The map $M$ is, however,
-functionally inconsistent.
+\emph{functionally-inconsistent}.
 
-{\color{blue} To see this non functional-consistency explicitly in} our model and to see its
+{\color{blue} To see this \emph{non functional-consistency} explicitly in} our model and to see its
 applicability to composite systems,
@@
 state $\left|00\right\rangle $ and the HV $c=0.4$.
-The model, however, obeys the \emph{weak functional
-consistency} requirement,
+The model, however, obeys the \emph{weak functional-consistency} requirement,
 namely,
@@
 postulate 3. Note that for each iteration, a new
-HV is generated. To illustrate \emph{weak functional consistency}, 
+HV is generated. To illustrate \emph{weak functional-consistency}, 
 we must choose to measure
@@
 no-go theorem. However, his model was contextual (and
-functionally consistent) which is in stark contrast with our
-construction which is non-contextual (and non functionally-consistent).
+\emph{functionally-consistent}) which is in stark contrast with our
+construction which is non-contextual (and \emph{non
+functionally-consistent}).
 
 We end with making two short remarks.} First, we illustrate
-how non functional-consistency gives rise to situations which
+how non \emph{functional-consistency} gives rise to situations which
 could get confused with the presence of contextuality.
@@
 f(M_{1}(\hat{B}_{1}),M_{1}(\hat{B}_{2}),\dots)$,
-viz. the theory is non functionally-consistent. Note that
+viz. the theory is \emph{non functionally-consistent}. Note that
 after measuring $\hat{C}$, however,
@@
 consistent with those deduced by measuring
-$\hat{C}$.  Evidently, functional consistency must hold
+$\hat{C}$.  Evidently, \emph{functional-consistency} must hold
 for the common eigenkets of $\hat{B}_{i}$'s.
-Consequently, any violation of functional consistency
+Consequently, any violation of \emph{functional-consistency}
 must arise from states that are super-positions or
@@
 {\color{blue} Second, note that} entanglement is not necessary to demonstrate
-non functional-consistency; for instance the
+\emph{non functional-consistency}; for instance the
 Peres Mermin test is a state independent test
@@
 contradiction. On the other hand if everything is
-functionally consistent in a situation, can we have
+\emph{functionally-consistent} in a situation, can we have
 violation of Bell's inequality or non-locality?
@@
 Bell's inequalities bring out  non-local
-consequences of non functionally-consistent prediction
-maps and the notion of non functional-consistency is
+consequences of \emph{non functionally-consistent} prediction
+maps and the notion of \emph{non functional-consistency} is
 more basic.
@@
 In this letter we have presented
-non functional-consistency as an alternative to
+non \emph{functional-consistency} as an alternative to
 contextuality and as an essential signature of

### 2017-12-24 version2postPRL/nonContextual.tex
again updated with minor changes and title update, removed an irrelevant part in the actual content which got left behind

@@
 
-\title{Relexation of functional-consistency allows
-a non-contextual hidden variable model for quantum mechanics
-\\
-\sout{A non-contextual Hidden Variable Model for Quantum
-Mechanics}}
-\shorttitle{Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
+\title{Revisiting the notion of Contextuality in Quantum Mechanics}
+% \title{Relexation of functional-consistency allows
+% a non-contextual hidden variable model for quantum mechanics
+%\\
+% \sout{A non-contextual Hidden Variable Model for Quantum
+% Mechanics}}
+\shorttitle{ Revisiting Contextuality in QM} 
+%Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
 
@@
 
-\abstract{ \color{blue}
+\abstract{ %
 We construct a non-contextual
-hidden variable model consistent with all {\color{red} the}
+hidden variable model consistent with all { the}
 kinematic predictions of quantum mechanics (QM). The famous
@@
 satisfy a further reasonable restriction are inconsistent
-with QM. {\color{red} In our construction,} we define a
+with QM. { In our construction,} we define a
 weaker variant of this restriction which captures its
 essence while still allowing a non-contextual description of
-QM. This is in contrast to {\color{red} the} contextual
- hidden variable {\color{red} toy} models, such as
-the one by Bell, {\color{red} and}  brings out an interesting
-alternate way of looking at QM. {\color{red} The results}
-also relate to {\color{red} the Bohmian}
+QM. This is in contrast to { the} contextual
+ hidden variable {toy} models, such as
+the one by Bell, { and}  brings out an interesting
+alternate way of looking at QM. { The results}
+also relate to { the Bohmian}
 model, where it is harder to pin
@@
 
-% {\color{red} 
+% { 
 % I think that we should use `functional consistency' with a
@@
 incompatibility between HV models and QM can arise
-even for a single quantum system.  Contextuality
+even for a single indivisible quantum system.  Contextuality
 has thus been identified as a fundamental
@@
 led to investigations on the foundational aspects
-of QM including attempts to prove completeness of
+of QM including attempts to prove the completeness of
 QM~\cite{PawelCntxClsscl,CabelloMmryQM}, and on
@@
 cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
-{\color{blue} While there have been generalisations, in this
+{ While there have been generalisations, in this
 letter, we restrict ourselves to the standard notion of
@@
 with kinematic predictions of QM} \label{fig:block}\end{figure}
-{\color{blue}
+{
 The KS theorem is applicable to non-contextual HV models
@@
 this was the requirement that
-{\color{red} the} observable $\hat A^2$ must depend on $\hat
+{ the} observable $\hat A^2$ must depend on $\hat
 A$ even at the HV level. This sounds reasonable because
 otherwise one can construct HV models where these
-observables {\color{red} can} get mapped to random variables
+observables { can} get mapped to random variables
 with no relation to each other (see~\cite{KochenSpecker}). 
@@
 observables will depend on each other where they should for
-{\color{red} consistency} and not otherwise,
-thereby capturing the same idea {\color{red} without undue
+{ consistency} and not otherwise,
+thereby capturing the same idea { without undue
 constraints}. The consequence of
@@
 
-{\color{red}  Sentence below has been edited}
+% {  Sentence below has been edited}
 This is in stark contrast with
@@
 This provides a new
-way to look at the classical-quantum divide and at
+way of looking at the classical-quantum divide and at
 the foundations of quantum mechanics.
@@
 \begin{defnrem}
-{\color{blue} Broader definitions in the literature have
+{ Broader definitions in the literature have
 been suggested~\cite{spekkens_pra} which extend the notion
 to probabilistic HV models. 
-% {\color{red} Sentence below is not clear. Do we
+% { Sentence below is not clear. Do we
 % want to define measurement contextuality? or general
 % contextuality in this broader sense?}
-{\color{red} Next sentence has been re-written.}
+
 The idea is that any feature of
@@
 
-{\color{blue} 
-In addition to a HV model being non-contextual Kochen and Specker~\cite{KochenSpecker} demand \emph{functional-consistency} to establish their no-go theorem which is defined below in our notation.
+{ 
+In addition to a HV model being non-contextual KS~\cite{KochenSpecker} demand \emph{functional-consistency} to establish their no-go theorem which is defined below in our notation.
 }
@@
 $\hat{B}_{i}$s, $M$ must clearly be
-functionally-consistent. It is, however, not obvious that
+\emph{functionally-consistent}. It is, however, not obvious that
 this property must always hold. For example,
@@
 independently, according to QM, with probability
-half. Here functional-consistency clearly is not
-required to hold {\color{blue} and indeed this is why it was demanded in addition to being consistent with QM by KS}.
+half. Here \emph{functional-consistency} clearly is not
+required to hold { and indeed this is why it was demanded in addition to being consistent with QM by KS}.
 Antithetically, it is clear that if one first
@@
 $\hat{C}$.
-{\color{blue} In our treatment, instead of imposing functional-consistency, we demand its aforesaid weaker variant.
-It captures the same idea, however, only when it has a precise meaning according to QM.} {\color{blue} To this end we define}
+{ In our treatment, instead of imposing \emph{functional-consistency}, we demand its aforesaid weaker variant.
+It captures the same idea, however, only when it has a precise meaning according to QM.} { To this end we define}
 \emph{weak functional-consistency} as follows.
@@
 Here $M$ maybe viewed as a specific class of
-prediction maps, that implicitly depends on the
+prediction maps that implicitly depends on the
 state $[\psi]$. It is clear that according to the
@@
 QM. 
-This leaves open an interesting possibility that non-contextual maps which have \emph{weak-functional consistency} could be consistent with QM.
-{ \color{blue} Before proceeding to do so explicitly we observe that \emph{weak functional-consistency} is, in fact, a consequence of QM.}
+This leaves open an interesting possibility that non-contextual maps which have \emph{weak functional-consistency} could be consistent with QM.
+{  Before proceeding to do so explicitly we observe that \emph{weak functional-consistency} is, in fact, a consequence of QM.}
 \begin{prop*} 
@@
 uniquely assigned. The map $M$ is, however,
-\emph{functionally-inconsistent}.
+\emph{non functionally-consistent}.
 
-{\color{blue} To see this \emph{non functional-consistency} explicitly in} our model and to see its
+{ To see this \emph{non functional-consistency} explicitly in} our model and to see its
 applicability to composite systems,
@@
 $\left|\tilde{\pm}\right\rangle
-=\left|0\right\rangle \pm i\left|1\right\rangle $
+=(\left|0\right\rangle \pm i\left|1\right\rangle)/\sqrt{2} $
 (eigenkets of $\hat{\sigma}_{y}$). Since
@@
 postulate 3. Note that for each iteration, a new
-HV is generated. To illustrate \emph{weak functional-consistency}, 
-we must choose to measure
-$\hat{A}_{33}$. According to step 3, since
-$\left|00\right\rangle $ is an eigenstate of
-$\hat{A}_{33}$, the final state remains
-$\left|00\right\rangle $.
+HV is generated. 
+% To illustrate \emph{weak functional-consistency}, 
+% we must choose to measure
+% $\hat{A}_{33}$. According to step 3, since
+% $\left|00\right\rangle $ is an eigenstate of
+% $\hat{A}_{33}$, the final state remains
+% $\left|00\right\rangle $.
 
 \section{Implications and Remarks}
-{ \color{blue} 
+{  
 The model demonstrates \emph{non function-consistency} as an alternative signature of quantumness as opposed to contextuality. This view is not just an artifact of the simplicity of the model. 
@@
 compatible measurements to provide two different
-contexts~\cite{HardyCntxBM} {\color{blue}and is therefore not of
+contexts~\cite{HardyCntxBM} {and is therefore not of
 interest here.}  It turns out that,
@@
 of BHVM.
-{\color{blue} In fact, our model when appropriately extended
+{ In fact, our model when appropriately extended
 to continuous variables yields Bohmian trajectories in the
@@
 \emph{functionally-consistent}) which is in stark contrast with our
-construction which is non-contextual (and \emph{non
-functionally-consistent}).
+construction which is non-contextual (and has \emph{weak
+functional-consistency}).
 
 We end with making two short remarks.} First, we illustrate
-how non \emph{functional-consistency} gives rise to situations which
+how \emph{non functional-consistency} gives rise to situations which
 could get confused with the presence of contextuality.
@@
 \begin{eqnarray*}
-&&\hat{B}_{1}\!=\!\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}\!=\!
-\left|00\right\rangle
+&&\hat{B}_{1}\!=\!\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}\!=\\
+&&\!\left|00\right\rangle
 \left\langle 00\right|+\left|01\right\rangle
@@
 \left\langle 11\right|\right], \\
-&&\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}\!=\!
-\left|10\right\rangle
+&&\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}\!=\\
+&&\!\left|10\right\rangle
 \left\langle 10\right|+\left|11\right\rangle
@@
 \left\langle 01\right|\right], \\
-&&\hat{C}=f(\{\hat{B}_{i}\}) \\
+&&\hat{C}=\!f(\{\hat{B}_{i}\}) \\
 &&\quad=1.\left|00\right\rangle \left\langle
 00\right|+2.\left|01\right\rangle \left\langle
-01\right|+3.\left|10\right\rangle \left\langle
+01\right|+ \\
+&&\! \quad
+3.\left|10\right\rangle \left\langle
 10\right|+4.\left|11\right\rangle \left\langle
@@
 
-{\color{blue} Second, note that} entanglement is not necessary to demonstrate
+{ Second, note that} entanglement is not necessary to demonstrate
 \emph{non functional-consistency}; for instance the

### 2017-12-25 version2postPRL/nonContextual.tex
updated the spelling of ULB and added the cover letter from onenote
Updated in accordance with Arvind sirs comments

@@
 
-\title{Revisiting the notion of Contextuality in Quantum Mechanics}
+\title{Revisiting the admissibility of non-contextual hidden variable models in quantum mechanics}
 % \title{Relexation of functional-consistency allows
@@
 % Mechanics}}
-\shorttitle{ Revisiting Contextuality in QM} 
+\shorttitle{Admissibility of non-contextual HV models in QM} 
 %Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
@@
   \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
-  \inst{2} Université libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
+  \inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
   \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
@@
 \section{Introduction}
-Quantum mechanics has been one of the most
+Quantum mechanics (QM) has been one of the most
 successful theories in physics so far, however,
@@
 consistent with QM.
+
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{block2}
+\begin{center}
+\includegraphics[width=0.98\columnwidth]{block2}
+\end{center}
 \caption{Non-contextuality is not inconsistent
@@
 { consistency} and not otherwise,
-thereby capturing the same idea { without undue
+thereby capturing the essential idea { without undue
 constraints}. The consequence of
@@
 longer applies and non-contextual HV models can be
-consistently constructed.
-
-% {  Sentence below has been edited}
-This is in stark contrast with
+consistently constructed. This is in stark contrast with
 contextual HV models, such as the toy
@@
 We introduce some notation and make the relevant notions
-precise to facilitate the description and assessment of our
+precise to facilitate the construction of our
 model.
@@
 no-go theorem. However, his model was contextual (and
-\emph{functionally-consistent}) which is in stark contrast with our
+\emph{functionally-consistent}) which is in contrast with our
 construction which is non-contextual (and has \emph{weak
@@
 
-We end with making two short remarks.} First, we illustrate
+We end with two short remarks.} First, we illustrate
 how \emph{non functional-consistency} gives rise to situations which
@@
 In this letter we have presented
-non \emph{functional-consistency} as an alternative to
+\emph{non functional-consistency} as an alternative to
 contextuality and as an essential signature of

### 2018-11-04 version2postPRL/nonContextual.tex
Minor changes
Addressed all the concerns of the referee.

@@
 \usepackage{geometry}
+\usepackage{braket}
 \geometry{verbose,tmargin=3cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=1cm}
@@
   \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
-  \inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
+  \inst{2} Centre for Quantum Information and Communication, Ecole polytechnique de Bruxelles, CP 165,\\Universit\'e libre de Bruxelles (ULB), 1050 Brussels, Belgium \\
+  %\inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
   \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
@@
 The KS theorem is applicable to non-contextual HV models
-which additionally satisfy \emph{functional-consistency ---
-algebraic constraints obeyed by commuting quantum
+which additionally satisfy \emph{functional-consistency---algebraic 
+constraints obeyed by commuting quantum
 observables must be satisfied by the HV model at the level
@@
 will show, one can weaken this requirement into what we call
-\emph{weak functional-consistency -- functional-consistency is
+\emph{weak functional-consistency---functional-consistency is
 demanded only when the observables in question have sharp
@@
 { consistency} and not otherwise,
-thereby capturing the essential idea { without undue
-constraints}. The consequence of
+thereby capturing the essential idea without undue
+constraints. The consequence of
 demanding only the weaker variant is that the KS theorem no
@@
 \begin{defn}
-A prediction map $M$ is \emph{functionally-consistent} iff
+A prediction map $M$ is \emph{functionally-consistent} if
 \begin{align*} &
@@
 \emph{weak functional-consistency} for a given
-sequence map $s$, iff \begin{align*}
+sequence map $s$, if \begin{align*}
 &M(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
@@
 
-\begin{proof} Peres Mermin [PM]
-($\left|\mathcal{H}\right|\ge4$)
+\begin{proof} Due to Peres Mermin for
+$\left|\mathcal{H}\right|\ge4$
 \cite{Peres,Mermin}:
@@
 consider the following set of operators 
-\begin{equation*}
+\begin{equation}\label{eqn:PM}
 \hat{A}_{ij}\doteq\left[\begin{array}{ccc}
@@
 \end{array}\right]
-\end{equation*}
+\end{equation}
 which have the property that
@@
 contradiction and therefore we conclude 
-that $M$ does not exist
+that $M$ does not exist.
 \end{proof}
@@
 f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$, and
-$\hat{B}_{i}$ are as defined (in \defnref{seqnMltpl})
+$\hat{B}_{i}$ are as defined in \defnref{seqnMltpl}.
 \end{prop*}
@@
 system be $\left|\chi\right\rangle $. We wish to
-assign a value to an arbitrary observable
-$\hat{A}=\sum_{a}a\left|a\right\rangle
-\left\langle a\right|$, which has eigenvectors $\{
+assign a value to an arbitrary observable, given in terms of its spectral decomposition as,
+
+$ \hat{A}=\sum_{a\in a_1,a_2,\dots a_n }a\left|a\right\rangle
+\left\langle a\right| $ with $a_1\le a_2 \le \dots a_n$. \sout{which has eigenvectors $\{
 \vert a_j\rangle \}$. The corresponding ordered
 eigenvalues are $\{a_j\}$ such that $a_{\rm
-min}=a_1$ and $a_{\rm max}=a_n$.  Our HV model for
+min}=a_1$ and $a_{\rm max}=a_n$.}  Our HV model for
 QM assigns values in the following three steps:
@@
  The value assigned to
-$\hat{A}$ is given by finding the smallest $a$
-s.t.  $c\le\sum_{a'=a_{\text{min}}}^{a}\left|\left\langle
+$\hat{A}$ is given by finding the smallest $j$ 
+s.t.  $c\le\sum_{a'=a_1}^{a_j}\left|\left\langle
 a'|\chi\right\rangle \right|^{2},$ viz. we have
@@
 random in $[0,1]$ that the statistics agree with
-the predictions of QM {\it i.e.}  the
+the predictions of QM i.e. the
 Born rule. 
@@
 to proceed with sequentially measuring
-$\hat{C}_{3}$. To simplify calculations, we note
+$\hat{C}_{3}$. {\color{blue} Atul: Kishor could you please verify the calculation.} To simplify calculations, we note
+
 $\left|00\right\rangle
-=\frac{1}{\sqrt 2} \left[ \left(\left|\tilde{+}\tilde{-}\right\rangle
-+\left|\tilde{-}\tilde{+}\right\rangle
-\right)/\sqrt{2}+\left(\left|\tilde{+}\tilde{+}\right\rangle
-+\left|\tilde{-}\tilde{-}\right\rangle
+=\frac{1}{\sqrt 2} \left[ \left(\left| \uparrow \downarrow \right\rangle
++\left|\downarrow \uparrow \right\rangle
+\right)/\sqrt{2}+\left(\left|\uparrow \uparrow \right\rangle
++\left|\downarrow \downarrow \right\rangle
 \right)/\sqrt{2}\right] , 
 $
-with
-$\left|\tilde{\pm}\right\rangle
-=(\left|0\right\rangle \pm i\left|1\right\rangle)/\sqrt{2} $
+
+with $\ket{\uparrow} = (\ket{0}+i\ket{1})/\sqrt{2}$ and $\ket{\downarrow}=(\ket{0}-i\ket{1})/\sqrt{2}$
 (eigenkets of $\hat{\sigma}_{y}$). Since
@@
 $\left|a^{-}_{23}\right\rangle
-=\left(\left|\tilde{+}\tilde{-}\right\rangle
-+\left|\tilde{-}\tilde{+}\right\rangle
+=\left(\left|\uparrow \downarrow \right\rangle
++\left|\downarrow \uparrow \right\rangle
 \right)/\sqrt{2}=\left(\left|00\right\rangle
-+\left|11\right\rangle \right)/\sqrt{2}$, which
++\left|11\right\rangle \right)/\sqrt{2}$ which 
 becomes the final state.
@@
 \end{equation*}
-\caption{HV model applied to the Peres Mermin situation}
+\caption{For a given initial state, we apply our HV model to the Peres Mermin square (see Equation \ref{eqn:PM}; $R_j$ ($C_j$) refers to product of the observables along the $j^{\text{th}}$ row (column)) and explicitly write the predictions.
+At each step encoded by $i$, a value of $c\in[0,1]$ is picked from a uniformly random distribution.
+This, together with the state, completely specifies the predicted value of each observable which we denote by the map $M_1$.
+An observable is then selected and measured, which is specified in the second last row  (together with the predicted value assigned to it by the HV model) and the state is then updated to the one specified in the last row using the rules specified by the HV model.
+This state becomes the initial state for the next step.
+Note that we are able to assign values to the Peres Mermin square and they exhibit non functional-consistency.
+To see this, recall that the product of the numbers along any given row should be one if the assignment satisfies functional-consistency but this is not the case even in the very first row of $M_1(\hat A _{ij})$.}
 \label{tbl:HVmodel}
@@
 \emph{functionally-consistent}) which is in contrast with our
-construction which is non-contextual (and has \emph{weak
+construction which is non-contextual (and only has \emph{weak
 functional-consistency}).
@@
 &&\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}\!=\\
-&&\!\left|10\right\rangle
-\left\langle 10\right|+\left|11\right\rangle
-\left\langle 11\right|-\left[\left|00\right\rangle
-\left\langle 00\right|+\left|01\right\rangle
-\left\langle 01\right|\right], \\
+&&\!\left|00\right\rangle \left\langle 00\right|+
+\left|10\right\rangle \left\langle 10\right|-
+\left[\left|01\right\rangle \left\langle 01\right|+
+\left|11\right\rangle \left\langle 11\right|\right], \\
 &&\hat{C}=\!f(\{\hat{B}_{i}\}) \\
@@
 \end{eqnarray*}
-$\hat{C}$ maybe viewed as a function of
+We introduced $\hat{C}$ as an example of a \emph{refinement}, i.e. an observable 
+whose measurement can reveal the values of other compatible observables
+which in this case are $\hat B_1$ and $\hat B_2$. To see this, note that $\hat C$
+maybe viewed as a function of
 $\hat{B}_{1}$, $\hat{B}_{2}$ and other operators
@@
 may be tempted call contextuality, viz.  the value
-of $\hat{B}_{1}$ depends on whether it is measured
+of $\hat{B}_{2}$ depends on whether it is measured
 alone or with the remaining $\{\hat{B}_{i}\}$.
-However, it must be noted that $\hat{B}_{1}$ has a
+However, it must be noted that $\hat{B}_{2}$ has a
 well defined value, and so does $\hat{C}$. Thus by
@@
 maps and the notion of \emph{non functional-consistency} is
-more basic.
+more basic. {\color{blue} Atul: The referee wants a physical meaning of this. I am not sure how to respond.}
 
 \section{Conclusion}
+ {\color{blue} Atul: The refere wants this section to be made more particular; feel free to improve upon/add to the following.}
 In this letter we have presented
 \emph{non functional-consistency} as an alternative to
-contextuality and as an essential signature of
-quantumness at the kinematic level. Our result
+contextuality \sout{and as an essential signature of
+quantumness at the kinematic level} which bolsters the stance that one can not, and must not,
+deduce from the KS theorem that quantum mechanics is contextual without further investigation. We 
+also showed how viewing quantum mechanics this way already clarifies various aspects of Bohmian Mechanics, a completion of quantum mechanics whose proponents included Bell himself. Our result
 points to a (quantum) dynamical exploration of contextuality which 
-so far has effectively been studied kinematically only.
+so far has effectively been studied kinematically only. This should
+help us further rule out specific kinds of contextual/non functionally-consistent models and 
+clarify what quantum mechanics can not be thought of as.
 %Implications of quantum dynamics for
@@
 %We expect this to provide new insights that will be useful
-We expect our result to provide new insights that will be useful
-in the areas of foundations of QM and QIP.
+In addition to its intrinsic value to the fundamental understanding of quantum mechanics, we expect \sout{our result} this investigation to also provide new insights that will be useful
+in the area of quantum computation.
+In particular, it has been shown that an established measure of contextuality can be related directly to a measure of the quantum advantage obtained in the measurement based model of quantum computing [Kishor cite].
+A dynamical study of contextuality/non functional-consistency is expected to open up similar connections and deepen our understanding of the strange computational power of quantum mechanics.
 
 \acknowledgments
-ASA and Arvind acknowledge
-funding from KVPY and DST Grant No.
-EMR/2014/000297 respectively.
+ASA and KB acknowledge funding from KVPY, DST, India. Arvind also acknowledges the DST, India, for support through Grant No.
+EMR/2014/000297.
+ASA acknowledges the Belgian Fonds de la Recherche Scientifique -- FNRS for support through the FRIA grant, numbered F3/5/5MCF/XH/FC16749.
+KB acknowledges the CQT graduate scholarship.
 

### 2018-11-04 version2postPRL/coverLetters2/responseToTheRefereeReport.txt
Updated the cover letter.

EPL

December 5, 2018

Dear Editor(s)

The authors put forward the notion of "non functional-consistency" as an alternative to the notion of quantum mechanical non contextuality and claim that this notion provides an essential signature of quantumness at the kinematic level.

While the first claim is condivisible and to some extent argumented in the ms (see below), the second one ("essential signature") is not really explained and should be better proved or removed.

>> We removed the "essential signature" claim. Indeed, we can not logically conclude this (yet).

The ms is potentially of interest  for the distinguished audience of PLA, but there are too many unclear points to make a definite assessment.  The notation, some of the formulas, and several statements are not very clear and they should be improved before the ms may be considered for publication. Here in the following some mandatory amendments:

- Formula should be numbered and they should be recalled when mentioned in other location of the text;

>> TODO: Still pending! I numbered one formula but can't figure how to fix the rest.

- hat C in the last formula of page 4 should be better defined; what is the exact meaning of 1. |00⟩ ⟨00| + 2. |01⟩ ⟨01| + 3. |10⟩ ⟨10| + 4. |11⟩ ⟨11| ?

>> We have properly motivated the operator C as a refinement operator which is well defined in the contextuality literature (TODO: Kishor, perhaps add a reference.)

- Caption of Table I should be improved and made almost independent of the text

>> We have considerably improved the caption and have indeed made it quite independent of the text.

- The last sentence of the conclusions "We expect our result to provide new insights that will be useful in the areas of foundations of QM and QIP." is too generic. Which insights? Which areas? To which problems?

>> We have restructured the entire conclusion section and addressed the aforesaid by clarifying the insight, making the area of interest more precise and giving an example of where such an insight has been previously used. (TODO: check the conclusion section)

- The last sentence before conclusions is saying "The answer is no and, therefore, one can say that Bell's inequalities bring out non-local consequences of non functionally-consistent prediction maps and the notion of non functional-consistency is more basic" and a question immediately arises: Which is the physical meaning of the  notion of non functional-consistency?

>> TODO: Still pending! I can't figure this one out.

- If possible, avoid notation like |\tilde + \langle

>> Replaced the notation.

We hope that the revised manuscript meets the acceptance criteria.

Sincerely

Arvind

Highlights

* Bell's theorem shows quantum mechanics (QM) can not have a local hidden variable completion.
* Bohm constructs a non-local hidden variable completion of QM; Bell endorses it.
* Kochen Spekker theorem shows QM can not have a non-contextual completion.
* Relaxing an assumption of the KS theorem, allows us to construct a non-contextual completion, but it is forced to be "non functionally-conistent".
* We see Bohm's completion also exhibits "non functional-consistency".

Following are the things we must do.
——————
Response to Reviewers (mandatory)

This should be a separate file labeled "Response to Reviewers" that carefully addresses the issues raised in the comments appended below, point-by-point. You should also include a suitable rebuttal to any specific request for change that you have not made. Mention the page, paragraph, and line number of any revisions that are made.

Highlights (mandatory)

Highlights consist of a short collection of bullet points that convey the core findings of the article and should be submitted in a separate file in the online submission system. Please use 'Highlights' in the file name and include 3 to 5 bullet points (maximum 20 words, including spaces, per bullet point). See the following website for more information

### 2018-11-14 version3PLA/nonContextual.tex
Added Kishor's changes and now working on changing the format to PLA

--- 2018-11-04 version2postPRL/nonContextual.tex
@@
 and
-cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt}.
+cryptography~\cite{HowardCntxCmptn,CabelloCntxScrt,Raussendorf2013,Singh2017}.
 { While there have been generalisations, in this
@@
 \begin{defn} A theory is non-contextual, if it
-provides a map $M: \{
+provides a map, for all observables in $\hat{\mathcal{H}}$, $M: \{
 \hat{\mathcal{H}},[\mathcal{H}] \} \to\mathbb{R}$
@@
 a HV model that is not determined solely by the operational
-aspect of QM is defined to be a demonstration of contextuality. 
+aspect of QM is defined to be a context which in turn can potentially be used to demonstrate contextuality. 
 If, for instance, this distinction arises in the measurement procedure
@@
 \begin{defn} 
-A prediction map $m$ has
+A prediction map $M$ has
 \emph{weak functional-consistency} for a given
@@
 \end{enumerate}
-The above HV model works for all quantum systems,
-however, to illustrate its working,
+The above HV model is expected to work for all quantum systems. 
+We bolster this claim by applying it to a situation where it is 
+most likely to fail, i.e. the aforesaid Peres Mermin situation.
+\sout{The above HV model is expected to work for all quantum systems,
+however, to illustrate its working,} First,
 consider the example of a spin-half particle in the state
@@
 to proceed with sequentially measuring
-$\hat{C}_{3}$. {\color{blue} Atul: Kishor could you please verify the calculation.} To simplify calculations, we note
+$\hat{C}_{3}$. \sout{\color{blue} Atul: Kishor could you please verify the calculation.} To simplify calculations, we note
 
@@
 The \emph{non functional-consistency} is
-manifest, for $M_{1}(\hat{C}_{3})=1\neq
-M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=-1$,
+manifest, for $M_{1}(\hat{C}_{3})=-1\neq
+M_{1}(\hat{A}_{13})M_{1}(\hat{A}_{23})M_{1}(\hat{A}_{33})=1$,
 where the subscript refers to the iteration
@@
 Imagine for two spin 1/2 particles
-\begin{eqnarray*}
-&&\hat{B}_{1}\!=\!\hat{\sigma}_{z}\otimes\hat{\mathbb{I}}\!=\\
-&&\!\left|00\right\rangle
+\begin{eqnarray}
+\label{eqn:B1} \begin{split}
+\hat{B}_{1} = \hat{\sigma}_{z}\otimes\hat{\mathbb{I}} =& \left|00\right\rangle
 \left\langle 00\right|+\left|01\right\rangle
-\left\langle 01\right|-\left[\left|10\right\rangle
+\left\langle 01\right|\\
+& - \left(\left|10\right\rangle
 \left\langle 10\right|+\left|11\right\rangle
-\left\langle 11\right|\right], \\
-&&\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z}\!=\\
-&&\!\left|00\right\rangle \left\langle 00\right|+
-\left|10\right\rangle \left\langle 10\right|-
-\left[\left|01\right\rangle \left\langle 01\right|+
-\left|11\right\rangle \left\langle 11\right|\right], \\
-&&\hat{C}=\!f(\{\hat{B}_{i}\}) \\
-&&\quad=1.\left|00\right\rangle \left\langle
+\left\langle 11\right|\right), \end{split} \\ 
+\label{eqn:B2} \begin{split}
+\hat{B}_{2}\!=\!\hat{\mathbb{I}}\otimes\hat{\sigma}_{z} =& \left|00\right\rangle \left\langle 00\right|+\left|10\right\rangle \left\langle 10\right| \\ 
+&-\left(\left|01\right\rangle \left\langle 01\right|+
+\left|11\right\rangle \left\langle 11\right|\right), \end{split}\\
+\label{eqn:C} \begin{split}
+\hat{C} =& f(\{\hat{B}_{i}\})=\\
+& 1.\left|00\right\rangle \left\langle
 00\right|+2.\left|01\right\rangle \left\langle
 01\right|+ \\
-&&\! \quad
+&\! \quad
 3.\left|10\right\rangle \left\langle
 10\right|+4.\left|11\right\rangle \left\langle
-11\right|. 
-\end{eqnarray*}
-We introduced $\hat{C}$ as an example of a \emph{refinement}, i.e. an observable 
+11\right|. \end{split}
+\end{eqnarray}
+We introduced $\hat{C}$ in Equation \ref{eqn:C} as an example of a \emph{refinement}, i.e. an observable 
 whose measurement can reveal the values of other compatible observables
-which in this case are $\hat B_1$ and $\hat B_2$. To see this, note that $\hat C$
+which in this case are $\hat B_1$ and $\hat B_2$ as defined in Equations \ref{eqn:B1} and \ref{eqn:B2}. To see this, note that $\hat C$
 maybe viewed as a function of
@@
 maps and the notion of \emph{non functional-consistency} is
-more basic. {\color{blue} Atul: The referee wants a physical meaning of this. I am not sure how to respond.}
+more basic.
+The advantages in collaborative tasks such as quantum key distribution \cite{Ekert} and randomness certification \cite{colbeck2009quantum}, to name a few, can be interpreted as physical manifestation of non functional-consistency in quantum mechanics.
+\sout{\color{blue} Atul: The referee wants a physical meaning of this. I am not sure how to respond.}
 
 \section{Conclusion}
- {\color{blue} Atul: The refere wants this section to be made more particular; feel free to improve upon/add to the following.}
+ \sout{\color{blue} Atul: The refere wants this section to be made more particular; feel free to improve upon/add to the following.}
 In this letter we have presented
@@
 in the area of quantum computation.
-In particular, it has been shown that an established measure of contextuality can be related directly to a measure of the quantum advantage obtained in the measurement based model of quantum computing [Kishor cite].
+In particular, it has been shown that an established measure of contextuality can be related directly to a measure of the quantum advantage obtained in the measurement based model of quantum computing \cite{Raussendorf2013} as well as to that in the fault-tolerent model \cite{HowardCntxCmptn}.
 A dynamical study of contextuality/non functional-consistency is expected to open up similar connections and deepen our understanding of the strange computational power of quantum mechanics.
@@
 ASA acknowledges the Belgian Fonds de la Recherche Scientifique -- FNRS for support through the FRIA grant, numbered F3/5/5MCF/XH/FC16749.
-KB acknowledges the CQT graduate scholarship.
+KB acknowledges the CQT Graduate Scholarship.
 

### 2018-11-14 version3supportFiles/PLA/highlights.tex
Added Kishor's changes and now working on changing the format to PLA

\documentclass[12pt]{article}
\addtolength{\topmargin}{-2cm}
\addtolength{\textheight}{3cm}
\addtolength{\oddsidemargin}{-1.5cm}
\addtolength{\textwidth}{2cm}
\usepackage{graphicx}
\pagestyle{empty}
\begin{document}
\thispagestyle{empty}
\centerline{\large \bf Highlights for Review}
\vspace*12pt
In this work we propose a new (to the best of our knowledge)
non-contextual hidden variable model which helps clarify the
limitations of a well-established notion in the foundations
of quantum mechanics, that of contextuality. Contextual
hidden variable models on the other hand are already known
but these are in stark contrast with our model.
Understanding the notion of contextuality and its
implications better is therefore likely to stimulate further
research. Our work contributes towards this older direction
which has witnessed a renewed interest.
\end{document}

### 2018-11-14 version3supportFiles/PLA/non_contextual_pla_revised.tex
Added Kishor's changes and now working on changing the format to PLA

--- 2017-12-25 version2postPRL/nonContextual.tex
@@
-\documentclass[doublecol,british]{epl2} 
-% or \documentclass[page-classic]{epl2} for one column style
-\usepackage[normalem]{ulem}
-
-%\setcounter{secnumdepth}{3}     
-\usepackage{mathtools}
-\usepackage{verbatim}
+\documentclass[5p]{elsarticle}
+%\documentclass[preprint,12pt]{elsarticle}
+\usepackage{color}
+%\tolerance=500
+\raggedbottom
+%\hyphenpenalty=100
+%\usepackage[utf8x]{inputenc}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\journal{Physics Letters A}
+\bibliographystyle{elsarticle-num}
+\makeatletter
+\let\fnref\relax
 \usepackage{refstyle}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{geometry}
-\geometry{verbose,tmargin=3cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=1cm}
-\makeatletter
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
 \theoremstyle{plain}
@@
 \usepackage{paralist}
-\usepackage{graphicx}
-\graphicspath{ {images/} }
-
-\usepackage{xcolor}
-%\usepackage{url}
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\makeatother
-
-\usepackage{babel}
+%\makeatother
+\usepackage[english]{babel}
   \providecommand{\definitionname}{Definition}
@@
   \providecommand{\notationname}{Notation}
-\setlength{\itemindent}{0pt}
+\begin{document}
+\title{Revisiting the admissibility of non-contextual hidden 
+variable models in quantum mechanics}
+%\shorttitle{Admissibility of non-contextual HV models in QM} 
+%\keywords{Non-contextuality, HV Model for QM}
+\author{Atul Singh Arora}
+\ead{atul.singh.arora@ulb.ac.be}
+\address{Department of Physical Sciences,
+Indian Institute of Science Education \&
+Research (IISER) Mohali, Sector 81 SAS Nagar,
+Manauli PO 140306 Punjab India.}
+\address{Centre for Quantum Information and Communication,
+Ecole polytechnique de Bruxelles, CP 165,\\Universit\'e
+libre de Bruxelles (ULB), 1050 Brussels, Belgium}
+\author{Kishor Bharti}
+\ead{kishor.bharti1@gmail.com}
+\address{Centre for Quantum Technologies (CQT), \\National University
+of Singapore (NUS) -  Block S15, 3 Science Drive 2,
+Singapore 117543.  } 
+\author{Arvind}
+\ead{arvind@iisermohali.ac.in}
+\address{Department of Physical Sciences,
+Indian Institute of Science Education \&
+Research (IISER) Mohali, Sector 81 SAS Nagar,
+Manauli PO 140306 Punjab India.}
 
-% \usepackage{comment}
-% \excludecomment{sout}
-%\let\endsout\relax
-
-%%%%%%%%%%%%%%%%%%%
-
-\title{Revisiting the admissibility of non-contextual hidden variable models in quantum mechanics}
-% \title{Relexation of functional-consistency allows
-% a non-contextual hidden variable model for quantum mechanics
-%\\
-% \sout{A non-contextual Hidden Variable Model for Quantum
-% Mechanics}}
-\shorttitle{Admissibility of non-contextual HV models in QM} 
-%Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
-
-\author{Atul Singh Arora\inst{1,2} \and Kishor Bharti\inst{3} \and Arvind\inst{1}}
-\shortauthor{A. S. Arora \etal}
-
-\institute{                    
-  \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
-  \inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
-  \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
-}
-
-\pacs{03.65.Ta}{Foundations of quantum mechanics}
-%\pacs{}{}
-% \pacs{nn.mm.xx}{First pacs description}
-% \pacs{nn.mm.xx}{Second pacs description}
-% \pacs{nn.mm.xx}{Third pacs description}
-
-\abstract{ %
-We construct a non-contextual
-hidden variable model consistent with all { the}
-kinematic predictions of quantum mechanics (QM). The famous
-Bell-KS theorem shows that non-contextual models which
-satisfy a further reasonable restriction are inconsistent
-with QM. { In our construction,} we define a
-weaker variant of this restriction which captures its
-essence while still allowing a non-contextual description of
-QM. This is in contrast to { the} contextual
- hidden variable {toy} models, such as
-the one by Bell, { and}  brings out an interesting
-alternate way of looking at QM. { The results}
-also relate to { the Bohmian}
-model, where it is harder to pin
-down such features.}
-\begin{document}
-
+%\shortauthor{A. S. Arora \etal}
+%\pacs{03.65.Ta}{Foundations of quantum mechanics}
+\begin{abstract}
+We construct a non-contextual hidden variable model
+consistent with all the kinematic predictions of quantum
+mechanics (QM). The famous Bell-KS theorem shows that
+non-contextual models which satisfy a further reasonable
+restriction are inconsistent with QM. In our construction,
+we define a weaker variant of this restriction which
+captures its essence while still allowing a non-contextual
+description of QM. This is in contrast to the contextual
+hidden variable toy models, such as the one by Bell, and
+brings out an interesting alternate way of looking at QM.
+The results also relate to the Bohmian model, where it is
+harder to pin down such features.
+\end{abstract}
 \maketitle
@@
 $\hat{C}_{3}$. To simplify calculations, we note
-$\left|00\right\rangle
+\begin{equation*}
+\left|00\right\rangle
 =\frac{1}{\sqrt 2} \left[ \left(\left|\tilde{+}\tilde{-}\right\rangle
@@
 +\left|\tilde{-}\tilde{-}\right\rangle
-\right)/\sqrt{2}\right] , 
-$
+\right)/\sqrt{2}\right], 
+\end{equation*}
 with
@@
 namely,
-$M_{1}(\hat{C}_{3})=M_{1}
-(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
-where
-$M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
-\right])$,
-$M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
-\right])$ and $\left|\psi_{2}\right\rangle
-,\,\left|\psi_{3}\right\rangle $ are obtained from
+\begin{eqnarray*}
+&&M_{1}(\hat{C}_{3})=M_{1}
+(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13}),
+\nonumber \\
+{\rm where~}
+&&M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
+\right]), \nonumber \\
+&&M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
+\right]) 
+\end{eqnarray*}
+and $\left|\psi_{2}\right\rangle
+,\,\left|\psi_{3}\right\rangle 
+$
+are obtained from
 postulate 3. Note that for each iteration, a new
@@
 
-\acknowledgments
-ASA and Arvind acknowledge
-funding from KVPY and DST Grant No.
+\vspace*{12pt}
+\noindent
+{\bf Acknowledgments:}
+ASA and Arvind acknowledge funding from KVPY and DST Grant No.
   EMR/2014/000297 respectively.
@@
 %   \Section{A}.
-\bibliographystyle{unsrt}
+%\bibliographystyle{unsrt}
 \bibliography{references}

### 2018-11-14 version3supportFiles/PLA/pla_cover.tex
Added Kishor's changes and now working on changing the format to PLA

\documentclass[12pt]{article}
\addtolength{\topmargin}{-2cm}
\addtolength{\textheight}{3cm}
\addtolength{\oddsidemargin}{-1.5cm}
\addtolength{\textwidth}{2cm}
\usepackage{graphicx}
\pagestyle{empty}
\begin{document}
\thispagestyle{empty}
\hspace*{-20pt}
\includegraphics[scale=0.8,angle=0]{iiser_logo.eps}
\begin{minipage}[b]{13.5cm}
\begin{center}
\vspace*{-11pt}
\baselineskip=18pt
{\Large \bf Indian Institute of Science Education\\
\& Research Mohali}\\
{\bf Sector 81, Mohali, Phone \& Fax:+91-172-2790188 
Email:~arvind@iisermohali.co.in}
\vspace*{6pt}
\end{center}
\end{minipage}
\hrule
\vspace*{10pt}
\rightline{Prof. Arvind}
\rightline{May 7, 2018}
\vspace*{10pt}
\begin{flushleft}
Professor Matteo Paris, \\
Editor,\\
Physics Letters A\\
\end{flushleft}
\vspace*{6pt}
\noindent
{\bf Subject:} Manuscript submission\\

\vspace*{6pt}
\noindent
{Dear Professor Paris,}

\vspace*{6pt}

We are herewith submitting a paper titled ``Revisiting the
admissibility of non-contextual hidden variable models in
quantum mechanics'' authored by Atul Singh Arora, Kishor
Bharti and Arvind.

In this work we propose a new (to the best of our knowledge)
non-contextual hidden variable model which helps clarify the
limitations of a well-established notion in the foundations
of quantum mechanics, that of contextuality. Contextual
hidden variable models on the other hand are already known
but these are in stark contrast with our model.
Understanding the notion of contextuality and its
implications better is therefore likely to stimulate further
research. Our work contributes towards this older direction
which has witnessed a renewed interest.

Thanking you,

\vspace*{6pt}
\begin{flushright}
Yours Sincerely, \\
\vspace*{12pt}
Arvind\\
\end{flushright}
\end{document}

### 2018-11-14 version3PLA/nonContextual.tex
Adapted to the PLA format; everything now works

@@
-\documentclass[doublecol,british]{epl2} 
+\documentclass[5p]{elsarticle} 
 % or \documentclass[page-classic]{epl2} for one column style
 \usepackage[normalem]{ulem}
-
+\usepackage{color}
+\raggedbottom
 %\setcounter{secnumdepth}{3}     
-\usepackage{mathtools}
-\usepackage{verbatim}
-\usepackage{refstyle}
+%\usepackage{mathtools}
+%\usepackage{verbatim}
+
 \usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage{amsthm}
 \usepackage{amssymb}
-\usepackage{geometry}
+%\usepackage{geometry}
 \usepackage{braket}
-\geometry{verbose,tmargin=3cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=1cm}
+%\geometry{verbose,tmargin=3cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=1cm}
+%\makeatletter
+
+%%%%%%%%%%%%%%Arvind%%%%%%%%%%%%
+\journal{Physics Letters A}
+\bibliographystyle{elsarticle-num}
 \makeatletter
+\let\fnref\relax
+\usepackage{refstyle}
 
@@
 \usepackage{paralist}
-\usepackage{graphicx}
+\usepackage{hyperref}
+
+\usepackage[english]{babel}
 \graphicspath{ {images/} }
@@
 %\usepackage{url}
-\usepackage{hyperref}
 \hypersetup{
@@
 
-\usepackage{babel}
   \providecommand{\definitionname}{Definition}
@@
 
-\title{Revisiting the admissibility of non-contextual hidden variable models in quantum mechanics}
-% \title{Relexation of functional-consistency allows
-% a non-contextual hidden variable model for quantum mechanics
-%\\
-% \sout{A non-contextual Hidden Variable Model for Quantum
-% Mechanics}}
-\shorttitle{Admissibility of non-contextual HV models in QM} 
-%Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
-
-\author{Atul Singh Arora\inst{1,2} \and Kishor Bharti\inst{3} \and Arvind\inst{1}}
-\shortauthor{A. S. Arora \etal}
-
-\institute{                    
-  \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
-  \inst{2} Centre for Quantum Information and Communication, Ecole polytechnique de Bruxelles, CP 165,\\Universit\'e libre de Bruxelles (ULB), 1050 Brussels, Belgium \\
-  %\inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
-  \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
-}
-
-\pacs{03.65.Ta}{Foundations of quantum mechanics}
-%\pacs{}{}
-% \pacs{nn.mm.xx}{First pacs description}
-% \pacs{nn.mm.xx}{Second pacs description}
-% \pacs{nn.mm.xx}{Third pacs description}
-
-\abstract{ %
+% \title{Revisiting the admissibility of non-contextual hidden variable models in quantum mechanics}
+% % \title{Relexation of functional-consistency allows
+% % a non-contextual hidden variable model for quantum mechanics
+% %\\
+% % \sout{A non-contextual Hidden Variable Model for Quantum
+% % Mechanics}}
+% \shorttitle{Admissibility of non-contextual HV models in QM} 
+% %Non-contextual HV Model for QM} %Insert here a short version of the title if it exceeds 70 characters
+
+% \author{Atul Singh Arora\inst{1,2} \and Kishor Bharti\inst{3} \and Arvind\inst{1}}
+% \shortauthor{A. S. Arora \etal}
+
+% \institute{                    
+%   \inst{1} Indian Institute of Science Education and Research (IISER), Mohali,\\Sector 81 SAS Nagar 140306 Punjab India.\\
+%   \inst{2} Centre for Quantum Information and Communication, Ecole polytechnique de Bruxelles, CP 165,\\Universit\'e libre de Bruxelles (ULB), 1050 Brussels, Belgium \\
+%   %\inst{2} Universit\'e libre de Bruxelles, \\50 av. F. D. Roosevelt - CP 165/59, B-1050 Brussels, Belgium.\\
+%   \inst{3} Centre for Quantum Technologies (CQT), \\National University of Singapore (NUS) -  Block S15, 3 Science Drive 2, Singapore 117543.
+% }
+
+% \pacs{03.65.Ta}{Foundations of quantum mechanics}
+% %\pacs{}{}
+% % \pacs{nn.mm.xx}{First pacs description}
+% % \pacs{nn.mm.xx}{Second pacs description}
+% % \pacs{nn.mm.xx}{Third pacs description}
+
+%%%%%%%%%%%%%%%%%%Injected from Arvind sir's PLA draft variant%%%%%%%%%%%%%%%
+\usepackage{paralist}
+\usepackage{hyperref}
+%\makeatother
+\usepackage[english]{babel}
+  \providecommand{\definitionname}{Definition}
+  \providecommand{\examplename}{Example}
+  \providecommand{\lemmaname}{Lemma}
+  \providecommand{\propositionname}{Proposition}
+  \providecommand{\remarkname}{Remark}
+  \providecommand{\theoremname}{Theorem}
+  \providecommand{\notationname}{Notation}
+\begin{document}
+\title{Revisiting the admissibility of non-contextual hidden 
+variable models in quantum mechanics}
+%\shorttitle{Admissibility of non-contextual HV models in QM} 
+%\keywords{Non-contextuality, HV Model for QM}
+\author{Atul Singh Arora}
+\ead{atul.singh.arora@ulb.ac.be}
+\address{Department of Physical Sciences,
+Indian Institute of Science Education \&
+Research (IISER) Mohali, Sector 81 SAS Nagar,
+Manauli PO 140306 Punjab India.}
+\address{Centre for Quantum Information and Communication,
+Ecole polytechnique de Bruxelles, CP 165,\\Universit\'e
+libre de Bruxelles (ULB), 1050 Brussels, Belgium}
+\author{Kishor Bharti}
+\ead{kishor.bharti1@gmail.com}
+\address{Centre for Quantum Technologies (CQT), \\National University
+of Singapore (NUS) -  Block S15, 3 Science Drive 2,
+Singapore 117543.  } 
+\author{Arvind}
+\ead{arvind@iisermohali.ac.in}
+\address{Department of Physical Sciences,
+Indian Institute of Science Education \&
+Research (IISER) Mohali, Sector 81 SAS Nagar,
+Manauli PO 140306 Punjab India.}
+
+\begin{abstract} %
 We construct a non-contextual
@@
 model, where it is harder to pin
-down such features.}
-\begin{document}
+down such features.\end{abstract}
+%\begin{document}
 
@@
 $\hat{C}_{3}$. \sout{\color{blue} Atul: Kishor could you please verify the calculation.} To simplify calculations, we note
-
-$\left|00\right\rangle
+\[\left|00\right\rangle
 =\frac{1}{\sqrt 2} \left[ \left(\left| \uparrow \downarrow \right\rangle
@@
 \right)/\sqrt{2}\right] , 
-$
-
-with $\ket{\uparrow} = (\ket{0}+i\ket{1})/\sqrt{2}$ and $\ket{\downarrow}=(\ket{0}-i\ket{1})/\sqrt{2}$
+\] with $\ket{\uparrow} = (\ket{0}+i\ket{1})/\sqrt{2}$ and $\ket{\downarrow}=(\ket{0}-i\ket{1})/\sqrt{2}$
 (eigenkets of $\hat{\sigma}_{y}$). Since
@@
 \end{table*}
+{\sloppy
 The \emph{non functional-consistency} is
@@
 namely,
-$M_{1}(\hat{C}_{3})=M_{1}
-(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13})$,
+\[ M_{1}(\hat{C}_{3})=M_{1}
+(\hat{A}_{33})M_{2}(\hat{A}_{23})M_{3}(\hat{A}_{13}), \]
 where
-$M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
-\right])$,
-$M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
-\right])$ and $\left|\psi_{2}\right\rangle
-,\,\left|\psi_{3}\right\rangle $ are obtained from
+\[ M_{2}:=M(\hat{O},\left[\left|\psi_{2}\right\rangle
+\right]), \] 
+\[ M_{3}:=M(\hat{O},\left[\left|\psi_{3}\right\rangle
+\right]) \] and $\left|\psi_{2}\right\rangle
+,\,\left|\psi_{3}\right\rangle$ are obtained from
 postulate 3. Note that for each iteration, a new
-HV is generated. 
+HV is generated. }
 % To illustrate \emph{weak functional-consistency}, 
@@
 
-\acknowledgments
+\section{Acknowledgments}
+{
   ASA and KB acknowledge funding from KVPY, DST, India. Arvind also acknowledges the DST, India, for support through Grant No.
-EMR/2014/000297.
-ASA acknowledges the Belgian Fonds de la Recherche Scientifique -- FNRS for support through the FRIA grant, numbered F3/5/5MCF/XH/FC16749.
-KB acknowledges the CQT Graduate Scholarship.
+  EMR/2014/000297. ASA acknowledges the Belgian Fonds de la Recherche Scientifique (FNRS) for support through 
+  grants no F.4515.16 (QUICTIME), R.50.05.18.F (QuantAlgo) and F3/5/5MCF/XH/ FC16749 (FRIA). KB acknowledges the CQT Graduate Scholarship.
+}
 
